### 2023-07-20 paper/paper.tex
first commit!

\documentclass[remotesensing,article,submit,pdftex,moreauthors]{Definitions/mdpi}

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2022}
\copyrightyear{2022}
%\externaleditor{Academic Editor: Firstname Lastname} % For journal Automation, please change Academic Editor to "Communicated by"
\datereceived{} 
\dateaccepted{} 
\datepublished{} 
%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Robot Team II: Electric Boogaloo}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Robot Team II: Electric Boogaloo}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-5910-0183} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
% \Author{John Waczak $^{1,\dagger,\ddagger}$\orcidA{} and David J. Lary $^{1,\ddagger}$\orcidB{}}
\Author{John Waczak\orcidA{} and David J. Lary\orcidB{}}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{John Waczak and David J. Lary}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Waczak, J.; Lary, D.J.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
  Hanson Center for Space Sciences, University of Texas at Dallas, Richardson,
  TX 75080, USA;}

% $^{1}$ \quad John.Waczak@utdallas.edu\\
% $^{2}$ \quad David.Lary@utdallas.edu}

% Contact information of the corresponding author
\corres{Correspondence: John.Waczak@utdallas.edu}

% Current address and/or shared authorship
%\firstnote{} 
% \secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Fill this out last}

% Keywords
\keyword{Remote Sensing; hyperspectral image; georectification; machine learning}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{Instead of the abstract}
%\entrylink{The Link to this entry published on the encyclopedia platform.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

\subsection{Importance / Human Impact}
oil spill response, contaminated water, environmental surveys, algal blooms,
agriculture, land monitoring, air quality, etc...

paper using spectral indices for water quality assesment \cite{SpectralIndexWaterQuality}

\subsection{Hyperspectral Imaging and Remote Sensing}
paper creating new spectral index for wheat rust \cite{SpectralIndexWheat} \\ 
overview of NDVI \cite{SpectralIndexNDVI} \\ 
paper using spectral indices for desertification \cite{SpectralIndexDesertification}

\subsubsection{HSI sattelite systems}
\subsubsection{HSI drone systems}
\subsubsection{Machine Learning using HSI}
add Xiao He reference here \cite{yu2021pm2}

\subsection{In-situ Measurements / Robot Teams}
\subsubsection{Meteorology}
\subsubsection{Atmospheric Sensing}
add in reference to our AQ sensor network

\subsection{Julia Programming Language}
\subsubsection{scientific computing}
\subsubsection{differentiable programming ($\partial P$)}
\subsubsection{MLJ}
discuss general \textit{learning network} framework and utilization of
Directed Acyclic Graphs for pipeline construction

basic overview of MLJ as a Julia package \cite{MLJ1}\\

detailed description of \textit{learning networks} \cite{MLJ2}

\section{Materials and Methods}
\subsection{Autonomous Collection and Processing of Hyperspectral Images}

website for alta x \cite{freeflyAltaX}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/spectra/radiance.eps}
\caption{Spectral Radiance collected from a single pixel of the HSI.\label{radiancePlot}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/spectra/solar_irradiance.eps}
\caption{Downwelling Irradiance captured via an upward facing spectrometer.\label{irradiancePlot}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/spectra/reflectance_rainbow.eps}
\caption{Single pixel reflectance spectrum created by combining \ref{radiancePlot} with \ref{irradiancePlot}.\label{radiancePlot}}
\end{figure}

\begin{equation}
    R = \pi \frac{L}{E}
\end{equation}

\subsection{Georectification}
paper by Muller \cite{GeorectificationMuller} \\ 
paper by Baumker \cite{GeorectificationBaumker} \\ 
paper by Mostafa \cite{GeorectificationMostafa} \\

NOTE: need to double check \cite{GeorectificationMuller} for convention used ($\Phi$ vs $\phi$)

Heading correction due to longitude deviation in UTM system: 
\begin{equation}
    \kappa_{\text{geodetic}} = \kappa_{\text{geographic}}-\tan^{-1}\left( \sin\Phi \tan(\lambda-\lambda_{cm}) \right)
\end{equation}

scale factor: 
\begin{equation}
    s = \frac{z_{\text{sensor}}-z_{\text{ground}}}{f}
\end{equation}

\begin{equation}
    \begin{pmatrix}
    x \\ y \\ z
    \end{pmatrix}_{\text{Object}}^{\text{UTM}} = 
    f_{\text{geo}}^{\text{UTM}}\begin{pmatrix}
    \lambda \\ 
    \Phi \\ 
    z
    \end{pmatrix}_{\text{GPS}}^{\text{geo}} + sT_{\text{IMU}}^{\text{UTM}}R_{\text{sensor}}^{\text{IMU}}(\kappa, \phi, \omega)\begin{pmatrix}
    0 \\ 
    y_i \\ 
    f
    \end{pmatrix}_{\text{object}}^{\text{sensor}}
\end{equation}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/georectification/georectification.eps}
\caption{Diagram of .\label{georectification1}}
\end{figure}

\subsection{In-situ Data Collection via Robotic Sentinels}

autonomous boat website \cite{Otter}

\subsubsection{data collection process}
\subsubsection{Data Collocation}

\subsubsection{CO}
\subsubsection{CDOM}
\subsubsection{HDO}
\subsubsection{$Na^{+}$}
\subsubsection{$Ca^{2+}$}
\subsubsection{Other Targets}

\subsubsection{Feature Engineering with Remote Sensing Indices}
include discussion of PCA as well as Standardization

\subsection{Exploratory Data Analysis}
\subsubsection{Variable Correlations}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/correlation/target_cor.png}
\caption{Correlation Matrix for Target variables measured by the boat.\label{target_cor}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/correlation/radiance_cor.png}
\caption{Correlation Matrix for Radiance measurements versus Target Variables.\label{rad_cor}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/correlation/reflectance_cor.png}
\caption{Correlation Matrix for Reflectance measurements versus Target Variables.\label{ref_cor}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/correlation/derived_cor.png}
\caption{Correlation Matrix for derived measurements versus Target Variables.\label{derived_cor}}
\end{figure}

\subsubsection{Unsupervised Classification}
\begin{figure}[H]
\includegraphics[width=11 cm]{images/unsupervised/clustering.png}
\caption{Unsupervised clustering of hyper-spectral image data using the K-means algorithm.\label{clustering}}
\end{figure}

\subsection{Machine Learning}

\subsubsection{Machine Learning Models}
include Linear Models, Neural Networks, Decision Trees, Bagging, Boosting, and Stacking\\

The field of Machine Learning has seen the invention of a plethora of models able to perform inference for regression tasks. Naturally, this leads to the challenge of evaluating which model is best for a given problem. In 1992 David Wolpert developed the notion of Stacked Generalization to divorce arbitrary human choice from the model selection process. [1] The key idea is as follows: fit an instance of each model compatible with your dataset. Each model learns different features of the data so that an adjudicating model (called the super-learner) can then be trained to map the predictions from each individual learner to a final output prediction. This is incredibly easy to accomplish in the Julia programming language via the MLJ machine learning framework [2]. We train a variety of learners including artificial neural networks, bagged decision trees, boosted decision trees, polynomial regressors, quantile regressors, LASSO regressors, and K-nearest-neighbors regressors. To ensure proper data hygiene, individual learners are first trained on separate cross validation folds so as not to bias the super-learner. After training the super-learner, each individual model is then trained on the full dataset to produce the best possible model.

paper on stacking \cite{ModelStacking}

\subsection{Model Analysis}
aleatoric and epistemic uncertainty

The black-box nature most machine learning methods makes it difficult to consider how errors propagate through a trained model during the inference process. For many problems such as image classification this is not an issue, however, in physical sensing error considerations are vital to establish detection limits and prediction confidence. Typically, there are three considerations we must make: measurement uncertainty– how much we can trust our model’s inputs, measurement representativeness– how well each data point represents data within a local neighborhood, and model error– how far the prediction is from the true value. Machine learning models are typically trained to minimize the model error. The Julia programming language makes it possible to handle all three.

To address measurement uncertainty, we take advantage of Julia’s advanced automatic differentiation capabilities to enable differentiable programming (∂P). This means that we can take derivatives of our trained ML model with respect to each input feature to perform a sensitivity analysis. The final output uncertainty is then given via linear error propagation theory. [5]

Measurement representativeness can be trickier to handle. For example, in fluids it is common for two species to form a mixing layer that presents as a sharp discontinuity in measurement values. To quantify the degree to which neighboring points diverge we compute the average deviation across input measurements in a neighborhood around each data sample. This information can then be presented with model outputs to identify the regions where our model is valid. Similarly for ensemble ML models we compute the prediction deviation across all base learners to identify the representativeness of a data sample. Inputs that cause a large spread in base learner predictions indicate low representativeness in the training set. This analysis can then be used to plan further data collection missions that minimize time spent collecting data we have already present in our models.

\subsubsection{Uncertainty Propagation via ($\partial P$)}

\subsubsection{Feature Ranking via SHAP values}

shape value paper used in ShapML.jl \cite{SHAPvalues1}

\subsubsection{Data Representativeness}
i.e. the average deviation across pixels used average during collocation process.
Also, we can look at relative disagreement between model predictions in bagged ensemble.

\section{Results}
\subsection{CO}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/CO/CO_dataMap.png}
\caption{Target distribution of CO at Scotty's Ranch.\label{CO_targetMap}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/CO/CO_train-test_hist.png}
\caption{Stratified train-test split for CO.\label{CO_trainTestHist}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/CO/rfr_CO_qq.png}
\caption{Quantile-Quantile plot for CO random forest fit. \label{CO_trainTestHist}}
\end{figure}

\begin{figure}[H]
    \begin{adjustwidth}{-\extralength}{0cm}
    \centering
    \subfigure{\includegraphics[width=0.5\textwidth]{images/CO/rfr_CO_scatter.png}}\qquad
    \subfigure{\includegraphics[width=0.5\textwidth]{images/CO/rfr_CO_qq.png}}
    \end{adjustwidth}
    \caption{(\textbf{a}) Scatterplot for the trained random forest Crudo Oil model. (\textbf{b}) Quantile-Quantile plot for the same fit.}
    \label{CO_fitresult}
\end{figure}

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{images/CO/rfr_CO_featureImportance.png}
    \caption{Ranked feature importance for Crude Oil. Importance is determined via mean absolute SHAP value. \label{CO_shapely}}
\end{figure}

\section{Discussion}
\subsection{For-deployment Models}
\subsubsection{Random Forests}

\subsection{Limitations}
discuss viewing geometry and time of day

\subsection{Extensions and Future Work}
\subsubsection{Physics-informed machine learning}
\subsubsection{Data Augmentation}

\section{Conclusions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work~reported.}

\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''. Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

\institutionalreview{In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals. Please note that the Editorial Office might ask you for further information. Please add ``The study was conducted according to the guidelines of the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).'' OR ``Ethical review and approval were waived for this study, due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans or animals. You might also choose to exclude this statement if the study did not involve humans or animals.}

\informedconsent{Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans.

Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves). Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}

\dataavailability{In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study. Please refer to suggested Data Availability Statements in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}. You might choose to exclude this statement if the study did not report any data.}

\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}

\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section. If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the~results''.}

%% Optional
\sampleavailability{Samples of the compounds ... are available from the authors.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Only for journal Encyclopedia
%\entrylink{The Link to this entry published on the encyclopedia platform.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\abbreviations{Abbreviations}{
The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute\\
DOAJ & Directory of open access journals\\
TLA & Three letter acronym\\
LD & Linear dichroism
\end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixstart
\appendix
\section[\appendixname~\thesection]{}
\subsection[\appendixname~\thesubsection]{}
The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data. Mathematical proofs of results not central to the paper can be added as an appendix.

\begin{table}[H] 
\caption{This is a table caption.\label{tab5}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabularx}
\end{table}

\section[\appendixname~\thesection]{}
All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\printendnotes[custom] % Un-comment to print a list of endnotes
\begin{adjustwidth}{-\extralength}{0cm}
\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
% =====================================
\bibliography{references}

% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{adjustwidth}
\end{document}

### 2023-07-20 paper/template.tex
first commit!

--- 2023-07-20 paper/paper.tex
@@
-\documentclass[remotesensing,article,submit,pdftex,moreauthors]{Definitions/mdpi}
+%  LaTeX support: latex@mdpi.com 
+%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.
+
+%=================================================================
+\documentclass[journal,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
+% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept".
+The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}.
+This is especially recommended for submission to arXiv, where line numbers should be removed before posting.
+For preprints.org, the editorial staff will make this change immediately prior to posting.
+
+%--------------------
+% Class Options:
+%--------------------
+%----------
+% journal
+%----------
+% Choose between the following MDPI journals:
+% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis
+
+%---------
+% article
+%---------
+% The default type of manuscript is "article", but can be replaced by: 
+% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
+% supfile = supplementary materials
+
+%----------
+% submit
+%----------
+% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
+This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information.
+Also, line numbering will be removed.
+Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
+
+%------------------
+% moreauthors
+%------------------
+% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
+
+%---------
+% pdftex
+%---------
+% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
 
@@
 % Full title of the paper (Capitalized)
-\Title{Robot Team II: Electric Boogaloo}
+\Title{Title}
 
 % MDPI internal command: Title for citation in the left column
-\TitleCitation{Robot Team II: Electric Boogaloo}
+\TitleCitation{Title}
 
 % Author Orchid ID: enter ID or remove command
-\newcommand{\orcidauthorA}{0000-0002-5910-0183} % Add \orcidA{} behind the author's name
-\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
+\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
+%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
 
 % Authors, for the paper (add full first names)
-% \Author{John Waczak $^{1,\dagger,\ddagger}$\orcidA{} and David J. Lary $^{1,\ddagger}$\orcidB{}}
-\Author{John Waczak\orcidA{} and David J. Lary\orcidB{}}
+\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}
 
@@
 % MDPI internal command: Authors, for metadata in PDF
-\AuthorNames{John Waczak and David J. Lary}
+\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}
 
 % MDPI internal command: Authors, for citation in the left column
-\AuthorCitation{Waczak, J.; Lary, D.J.}
+\AuthorCitation{Lastname, F.; Lastname, F.; Lastname, F.}
 % If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
@@
 \address{%
-  Hanson Center for Space Sciences, University of Texas at Dallas, Richardson,
-  TX 75080, USA;}
-
-% $^{1}$ \quad John.Waczak@utdallas.edu\\
-% $^{2}$ \quad David.Lary@utdallas.edu}
+$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
+$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}
 
 % Contact information of the corresponding author
-\corres{Correspondence: John.Waczak@utdallas.edu}
+\corres{Correspondence: e-mail@e-mail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}
 
 % Current address and/or shared authorship
-%\firstnote{} 
-% \secondnote{These authors contributed equally to this work.}
+\firstnote{Current address: Affiliation 3} 
+\secondnote{These authors contributed equally to this work.}
 % The commands \thirdnote{} till \eighthnote{} are available for further notes
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{Fill this out last}
+\abstract{A single paragraph of about 200 words maximum.
+For research articles, abstracts should give a pertinent overview of the work.
+We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusion: indicate the main conclusions or interpretations.
+The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}
 
 % Keywords
-\keyword{Remote Sensing; hyperspectral image; georectification; machine learning}
+\keyword{keyword 1; keyword 2; keyword 3 (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\setcounter{section}{-1} %% Remove this when starting to work on the template.
+\section{How to Use this Template}
+
+The template details the sections that can be used in a manuscript.
+Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section).
+Please check the instructions on the authors' page of the journal to verify the correct order and names.
+For any questions, please contact the editorial office of the journal or support@mdpi.com.
+For LaTeX-related questions please contact latex@mdpi.com.%\endnote{This is an endnote.} % To use endnotes, please un-comment \printendnotes below (before References).
+Only journal Laws uses \footnote.
+
+% The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision
+
 \section{Introduction}
 
-\subsection{Importance / Human Impact}
-oil spill response, contaminated water, environmental surveys, algal blooms,
-agriculture, land monitoring, air quality, etc...
+The introduction should briefly place the study in a broad context and highlight why it is important.
+It should define the purpose of the work and its significance.
+The current state of the research field should be reviewed carefully and key publications cited.
+Please highlight controversial and diverging hypotheses when necessary.
+Finally, briefly mention the main aim of the work and highlight the principal conclusions.
+As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
+Citing a journal paper \cite{ref-journal}.
+Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}.
+Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Materials and Methods}
 
-paper using spectral indices for water quality assesment \cite{SpectralIndexWaterQuality}
+Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
+Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
+Please disclose at the submission stage any restrictions on the availability of materials or information.
+New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
 
-\subsection{Hyperspectral Imaging and Remote Sensing}
-paper creating new spectral index for wheat rust \cite{SpectralIndexWheat} \\ 
-overview of NDVI \cite{SpectralIndexNDVI} \\ 
-paper using spectral indices for desertification \cite{SpectralIndexDesertification}
+Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers.
+If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
+They must be provided prior to publication.
 
-\subsubsection{HSI sattelite systems}
-\subsubsection{HSI drone systems}
-\subsubsection{Machine Learning using HSI}
-add Xiao He reference here \cite{yu2021pm2}
+Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
+\begin{quote}
+This is an example of a quote.
+\end{quote}
 
-\subsection{In-situ Measurements / Robot Teams}
-\subsubsection{Meteorology}
-\subsubsection{Atmospheric Sensing}
-add in reference to our AQ sensor network
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
 
-\subsection{Julia Programming Language}
-\subsubsection{scientific computing}
-\subsubsection{differentiable programming ($\partial P$)}
-\subsubsection{MLJ}
-discuss general \textit{learning network} framework and utilization of
-Directed Acyclic Graphs for pipeline construction
+This section may be divided by subheadings.
+It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
+\subsection{Subsection}
+\subsubsection{Subsubsection}
 
-basic overview of MLJ as a Julia package \cite{MLJ1}\\
+Bulleted lists look like this:
+\begin{itemize}
+\item	First bullet;
+\item	Second bullet;
+\item	Third bullet.
+\end{itemize}
 
-detailed description of \textit{learning networks} \cite{MLJ2}
+Numbered lists can be added as follows:
+\begin{enumerate}
+\item	First item; 
+\item	Second item;
+\item	Third item.
+\end{enumerate}
 
-\section{Materials and Methods}
-\subsection{Autonomous Collection and Processing of Hyperspectral Images}
+The text continues here.
 
-website for alta x \cite{freeflyAltaX}
+\subsection{Figures, Tables and Schemes}
+
+All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, Table~\ref{tab2}, etc.
 
 \begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/spectra/radiance.eps}
-\caption{Spectral Radiance collected from a single pixel of the HSI.\label{radiancePlot}}
+\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
+\caption{This is a figure.
+Schemes follow the same formatting.
+If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
+(\textbf{b}) Description of what is contained in the second panel.
+Figures should be placed in the main text near to the first time they are cited.
+A caption on a single line should be centered.\label{fig1}}
 \end{figure}   
+\unskip
 
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/spectra/solar_irradiance.eps}
-\caption{Downwelling Irradiance captured via an upward facing spectrometer.\label{irradiancePlot}}
-\end{figure}
+\begin{table}[H] 
+\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
+\begin{tabularx}{\textwidth}{CCC}
+\toprule
+\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
+\midrule
+Entry 1		& Data			& Data\\
+Entry 2		& Data			& Data\\
+\bottomrule
+\end{tabularx}
+\end{table}
+\unskip
 
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/spectra/reflectance_rainbow.eps}
-\caption{Single pixel reflectance spectrum created by combining \ref{radiancePlot} with \ref{irradiancePlot}.\label{radiancePlot}}
-\end{figure}
+\begin{table}[H]
+\caption{This is a wide table.\label{tab2}}
+	\begin{adjustwidth}{-\extralength}{0cm}
+		\newcolumntype{C}{>{\centering\arraybackslash}X}
+		\begin{tabularx}{\fulllength}{CCCC}
+			\toprule
+			\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}     & \textbf{Title 4}\\
+			\midrule
+			Entry 1		& Data			& Data			& Data\\
+			Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
+			\bottomrule
+		\end{tabularx}
+	\end{adjustwidth}
+	\noindent{\footnotesize{\textsuperscript{1} This is a table footnote.}}
+\end{table}
 
+%\begin{listing}[H]
+%\caption{Title of the listing}
+%\rule{\columnwidth}{1pt}
+%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
+%\rule{\columnwidth}{1pt}
+%\end{listing}
+
+Text.
+
+Text.
+
+\subsection{Formatting of Mathematical Components}
+
+This is the example 1 of equation:
+\begin{linenomath}
 \begin{equation}
-    R = \pi \frac{L}{E}
+a = 1,
 \end{equation}
+\end{linenomath}
+the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
+%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
+This ensures correct linenumbering.
+The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
 
-\subsection{Georectification}
-paper by Muller \cite{GeorectificationMuller} \\ 
-paper by Baumker \cite{GeorectificationBaumker} \\ 
-paper by Mostafa \cite{GeorectificationMostafa} \\
+This is the example 2 of equation:
+\begin{adjustwidth}{-\extralength}{0cm}
+\begin{equation}
+a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
+\end{equation}
+\end{adjustwidth}
 
-NOTE: need to double check \cite{GeorectificationMuller} for convention used ($\Phi$ vs $\phi$)
+% Example of a page in landscape format (with table and table footnote).
+%\startlandscape
+%\begin{table}[H] %% Table in wide page
+%\caption{This is a very wide table.\label{tab3}}
+%	\begin{tabularx}{\textwidth}{CCCC}
+%		\toprule
+%		\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}	& \textbf{Title 4}\\
+%		\midrule
+%		Entry 1		& Data			& Data			& This cell has some longer content that runs over two lines.\\
+%		Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
+%		\bottomrule
+%	\end{tabularx}
+%	\begin{adjustwidth}{+\extralength}{0cm}
+%		\noindent\footnotesize{\textsuperscript{1} This is a table footnote.}
+%	\end{adjustwidth}
+%\end{table}
+%\finishlandscape
 
-Heading correction due to longitude deviation in UTM system: 
-\begin{equation}
-    \kappa_{\text{geodetic}} = \kappa_{\text{geographic}}-\tan^{-1}\left( \sin\Phi \tan(\lambda-\lambda_{cm}) \right)
-\end{equation}
-
-scale factor: 
-\begin{equation}
-    s = \frac{z_{\text{sensor}}-z_{\text{ground}}}{f}
-\end{equation}
-
-\begin{equation}
-    \begin{pmatrix}
-    x \\ y \\ z
-    \end{pmatrix}_{\text{Object}}^{\text{UTM}} = 
-    f_{\text{geo}}^{\text{UTM}}\begin{pmatrix}
-    \lambda \\ 
-    \Phi \\ 
-    z
-    \end{pmatrix}_{\text{GPS}}^{\text{geo}} + sT_{\text{IMU}}^{\text{UTM}}R_{\text{sensor}}^{\text{IMU}}(\kappa, \phi, \omega)\begin{pmatrix}
-    0 \\ 
-    y_i \\ 
-    f
-    \end{pmatrix}_{\text{object}}^{\text{sensor}}
-\end{equation}
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/georectification/georectification.eps}
-\caption{Diagram of .\label{georectification1}}
-\end{figure}
-
-\subsection{In-situ Data Collection via Robotic Sentinels}
-
-autonomous boat website \cite{Otter}
-
-\subsubsection{data collection process}
-\subsubsection{Data Collocation}
-
-\subsubsection{CO}
-\subsubsection{CDOM}
-\subsubsection{HDO}
-\subsubsection{$Na^{+}$}
-\subsubsection{$Ca^{2+}$}
-\subsubsection{Other Targets}
-
-\subsubsection{Feature Engineering with Remote Sensing Indices}
-include discussion of PCA as well as Standardization
-
-\subsection{Exploratory Data Analysis}
-\subsubsection{Variable Correlations}
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/correlation/target_cor.png}
-\caption{Correlation Matrix for Target variables measured by the boat.\label{target_cor}}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/correlation/radiance_cor.png}
-\caption{Correlation Matrix for Radiance measurements versus Target Variables.\label{rad_cor}}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/correlation/reflectance_cor.png}
-\caption{Correlation Matrix for Reflectance measurements versus Target Variables.\label{ref_cor}}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/correlation/derived_cor.png}
-\caption{Correlation Matrix for derived measurements versus Target Variables.\label{derived_cor}}
-\end{figure}
-
-\subsubsection{Unsupervised Classification}
-\begin{figure}[H]
-\includegraphics[width=11 cm]{images/unsupervised/clustering.png}
-\caption{Unsupervised clustering of hyper-spectral image data using the K-means algorithm.\label{clustering}}
-\end{figure}
-
-\subsection{Machine Learning}
-
-\subsubsection{Machine Learning Models}
-include Linear Models, Neural Networks, Decision Trees, Bagging, Boosting, and Stacking\\
-
-The field of Machine Learning has seen the invention of a plethora of models able to perform inference for regression tasks.
-Naturally, this leads to the challenge of evaluating which model is best for a given problem.
-In 1992 David Wolpert developed the notion of Stacked Generalization to divorce arbitrary human choice from the model selection process.
-[1] The key idea is as follows: fit an instance of each model compatible with your dataset.
-Each model learns different features of the data so that an adjudicating model (called the super-learner) can then be trained to map the predictions from each individual learner to a final output prediction.
-This is incredibly easy to accomplish in the Julia programming language via the MLJ machine learning framework [2].
-We train a variety of learners including artificial neural networks, bagged decision trees, boosted decision trees, polynomial regressors, quantile regressors, LASSO regressors, and K-nearest-neighbors regressors.
-To ensure proper data hygiene, individual learners are first trained on separate cross validation folds so as not to bias the super-learner.
-After training the super-learner, each individual model is then trained on the full dataset to produce the best possible model.
-
-paper on stacking \cite{ModelStacking}
-
-\subsection{Model Analysis}
-aleatoric and epistemic uncertainty
-
-The black-box nature most machine learning methods makes it difficult to consider how errors propagate through a trained model during the inference process.
-For many problems such as image classification this is not an issue, however, in physical sensing error considerations are vital to establish detection limits and prediction confidence.
-Typically, there are three considerations we must make: measurement uncertainty– how much we can trust our model’s inputs, measurement representativeness– how well each data point represents data within a local neighborhood, and model error– how far the prediction is from the true value.
-Machine learning models are typically trained to minimize the model error.
-The Julia programming language makes it possible to handle all three.
-
-To address measurement uncertainty, we take advantage of Julia’s advanced automatic differentiation capabilities to enable differentiable programming (∂P).
-This means that we can take derivatives of our trained ML model with respect to each input feature to perform a sensitivity analysis.
-The final output uncertainty is then given via linear error propagation theory.
-[5]
-
-Measurement representativeness can be trickier to handle.
-For example, in fluids it is common for two species to form a mixing layer that presents as a sharp discontinuity in measurement values.
-To quantify the degree to which neighboring points diverge we compute the average deviation across input measurements in a neighborhood around each data sample.
-This information can then be presented with model outputs to identify the regions where our model is valid.
-Similarly for ensemble ML models we compute the prediction deviation across all base learners to identify the representativeness of a data sample.
-Inputs that cause a large spread in base learner predictions indicate low representativeness in the training set.
-This analysis can then be used to plan further data collection missions that minimize time spent collecting data we have already present in our models.
-
-\subsubsection{Uncertainty Propagation via ($\partial P$)}
-
-\subsubsection{Feature Ranking via SHAP values}
-
-shape value paper used in ShapML.jl \cite{SHAPvalues1}
-
-\subsubsection{Data Representativeness}
-i.e. the average deviation across pixels used average during collocation process.
-Also, we can look at relative disagreement between model predictions in bagged ensemble.
-
-\section{Results}
-\subsection{CO}
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/CO/CO_dataMap.png}
-\caption{Target distribution of CO at Scotty's Ranch.\label{CO_targetMap}}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/CO/CO_train-test_hist.png}
-\caption{Stratified train-test split for CO.\label{CO_trainTestHist}}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/CO/rfr_CO_qq.png}
-\caption{Quantile-Quantile plot for CO random forest fit. \label{CO_trainTestHist}}
-\end{figure}
-
+% Example of a figure that spans the whole page width. The same concept works for tables, too.
 \begin{figure}[H]
@@
 \centering
-    \subfigure{\includegraphics[width=0.5\textwidth]{images/CO/rfr_CO_scatter.png}}\qquad
-    \subfigure{\includegraphics[width=0.5\textwidth]{images/CO/rfr_CO_qq.png}}
+\includegraphics[width=15cm]{Definitions/logo-mdpi}
 \end{adjustwidth}
-    \caption{(\textbf{a}) Scatterplot for the trained random forest Crudo Oil model. (\textbf{b}) Quantile-Quantile plot for the same fit.}
-    \label{CO_fitresult}
+\caption{This is a wide figure.\label{fig2}}
 \end{figure}
 
-\begin{figure}[H]
-    \includegraphics[width=10.5 cm]{images/CO/rfr_CO_featureImportance.png}
-    \caption{Ranked feature importance for Crude Oil. Importance is determined via mean absolute SHAP value. \label{CO_shapely}}
-\end{figure}
+Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
+%% Example of a theorem:
+\begin{Theorem}
+Example text of a theorem.
+\end{Theorem}
 
+The text continues here. Proofs must be formatted as follows:
+
+%% Example of a proof:
+\begin{proof}[Proof of Theorem 1]
+Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
+\end{proof}
+The text continues here.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion}
-\subsection{For-deployment Models}
-\subsubsection{Random Forests}
 
-\subsection{Limitations}
-discuss viewing geometry and time of day
+Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
+The findings and their implications should be discussed in the broadest context possible.
+Future research directions may also be highlighted.
 
-\subsection{Extensions and Future Work}
-\subsubsection{Physics-informed machine learning}
-\subsubsection{Data Augmentation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusions}
 
-\section{Conclusions}
+This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Patents}
+
+This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{adjustwidth}{-\extralength}{0cm}
 %\printendnotes[custom] % Un-comment to print a list of endnotes
-\begin{adjustwidth}{-\extralength}{0cm}
+
 \reftitle{References}
@@
 % References, variant A: external bibliography
-% =====================================
-\bibliography{references}
+%=====================================
+%\bibliography{your_external_BibTeX_file}
+
+%=====================================
+% References, variant B: internal bibliography
+%=====================================
+\begin{thebibliography}{999}
+% Reference 1
+\bibitem[Author1(year)]{ref-journal}
+Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
+% Reference 2
+\bibitem[Author2(year)]{ref-book1}
+Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
+% Reference 3
+\bibitem[Author3(year)]{ref-book2}
+Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
+% Reference 4
+\bibitem[Author4(year)]{ref-unpublish}
+Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
+% Reference 5
+\bibitem[Author5(year)]{ref-communication}
+Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
+% Reference 6
+\bibitem[Author6(year)]{ref-proceeding}
+Author 1, A.B.; Author 2, C.D.; Author 3, E.F.
+Title of presentation.
+In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
+% Reference 7
+\bibitem[Author7(year)]{ref-thesis}
+Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
+% Reference 8
+\bibitem[Author8(year)]{ref-url}
+Title of Site. Available online: URL (accessed on Day Month Year).
+\end{thebibliography}
 

### 2023-11-26 5g__hpo-CatBoostRegressor.jl
trying new version

@@ -47,10 +47,10 @@ function parse_commandline()
     s = ArgParseSettings()
 
     @add_arg_table! s begin
-        "--target","-T"
-            help = "Target variable for training. See targetsDict in config.jl for full list."
-            arg_type = Symbol
-            default = :CDOM
+        "--target_index","-i"
+            help = "Index of target variable for training. See targets_dict in config.jl for full list."
+            arg_type = Int
+            default = 1
         "--datapath", "-d"
             help = "Path to directory with data to be used in training"
             arg_type = String

### 2023-11-26 training-functions.jl

@@ -7,7 +7,6 @@ using JSON
 # https://www.kaggle.com/code/prashant111/a-guide-on-xgboost-hyperparameters-tuning/notebook
 
 hpo_ranges = Dict("DecisionTree" => Dict("DecisionTreeRegressor" => [(hpname=:min_samples_leaf, lower=2, upper=100),
-                                                                   #   (hpname=:n_subfeatures, values=[-1,0]),
                                                                       (hpname=:max_depth, values=[-1, 2, 3, 5, 10, 20]),
                                                                       (hpname=:post_prune, values=[false, true])
                                                                       ],
@@ -15,26 +14,20 @@ hpo_ranges = Dict("DecisionTree" => Dict("DecisionTreeRegressor" => [(hpname=:mi
                                                                       (hpname=:min_samples_leaf, lower=2, upper=100),
                                                                       (hpname=:max_depth, values=[-1, 2, 3, 5, 10, 20]),
                                                                       (hpname=:n_subfeatures, values=[-1,0]),
-                                                                   #  (hpname=:n_trees, lower=10, upper=100),
                                                                       (hpname=:n_trees, values=[10, 25, 50, 75, 100, 125, 150]),
                                                                       (hpname=:sampling_fraction, lower=0.65, upper=0.9)
                                                                       ],
                                           ),
-                  "XGBoost" => Dict("XGBoostRegressor" => [(hpname=:eta, lower=0.01, upper=0.2),
-                                                           (hpname=:gamma, lower=0, upper=100),  # not sure about this one
-                                                           (hpname=:max_depth, lower=3, upper=10),
-                                                           (hpname=:min_child_weight, lower=0.0, upper=5.0),
-                                                           (hpname=:max_delta_step, lower=1.0, upper=10.0),
-                                                           (hpname=:subsample, lower=0.5, upper=1.0),
+                  "XGBoost" => Dict("XGBoostRegressor" => [(hpname=:num_round, values=[50,75,100,125,150]),
+                                                           (hpname=:eta, lower=0.01, upper=0.5),
+                                                           (hpname=:max_depth, values=[3,4,5,6,7,8,9]),
                                                            (hpname=:lambda, lower=0.1, upper=5.0),  # L2 regularization. Higher makes model more conservative
                                                            (hpname=:alpha, lower=0.0, upper=1.0), # L1 regularization. Higher makes model more sparse
                                                            ],
[…]

### 2023-11-27 3_feature-exploration.jl
updated for superlearner training

@@ -64,20 +64,31 @@ ETR = @load EvoTreeRegressor pkg=EvoTrees
 # 1. Construct dictionary of models
 MODELS = Dict()
 
-ref_cols = Symbol.(["R_" * lpad(i, 3, "0") for i ∈ 1:length(wavelengths)])
+
+cols_to_use = ["R_" * lpad(i, 3, "0") for i in 1:462]
+cols_to_standardize = ["roll", "pitch", "heading", "view_angle", "solar_azimuth", "solar_elevation", "solar_zenith"]
+cols_to_use = vcat(cols_to_use, cols_to_standardize)
 
 
 
-rbf(x) = exp.(-(x.^2))
 
-# the neural network needs features to be standardized
-nnr = NNR(builder=MLJFlux.MLP(hidden=(1000,), σ=rbf),
-          batch_size = 200,
-          optimiser=Flux.Optimise.ADAM(0.001),
-          lambda = 0.0001,  # default regularization strength (I'm a bit confused by this as sk-learn only has alpha but that seems different here)
+#nnr_mod = NNR(builder=MLJFlux.MLP(hidden=(50,50,50,50,50), σ=Flux.relu),
+nnr_mod = NNR(builder=MLJFlux.MLP(hidden=(50,50,50,50), σ=Flux.relu),
+          batch_size=256,
+          optimiser=Flux.Optimise.ADAM(),
+          lambda = 0.0001,
           rng=42,
-          epochs=200,
+          epochs=500,
           )
+
+
+nnr  = Pipeline(
+    selector=FeatureSelector(features=Symbol.(cols_to_use)),
+    stand=Standardizer(features=Symbol.(cols_to_standardize)),
+    mdl=nnr_mod
+)
+
+
 
 MODELS[:nnr] = (;
                 :longname=>"Neural Network Regressor",
@@ -87,58 +98,44 @@ MODELS[:nnr] = (;
                 )
 
 
+
 # 3. Add XGBoostRegressor. Defaults seem fine...
-MODELS[:xgbr] = (;
-                 :longname=>"XGBoost Regressor",
-                 :savename=>"XGBoostRegressor",
-                 :mdl => XGBR()
-                 )
+# MODELS[:xgbr] = (;
+#                  :longname=>"XGBoost Regressor",
+#                  :savename=>"XGBoostRegressor",
+#                  :mdl => XGBR()
+#                  )
 
 
-MODELS[:etr] = (;
-                :longname=>"Evo Tree Regressor",
[…]

### 2023-11-27 6__train-superlearner.jl

@@ -1,0 +1,132 @@
+# https://discourse.julialang.org/t/generation-of-documentation-fails-qt-qpa-xcb-could-not-connect-to-display/60988
+ENV["GKSwstype"] = "100"
+
+
+using Pkg
+Pkg.activate(".")
+Pkg.instantiate()
+
+
+
+using CSV, DataFrames
+using ProgressMeter
+using Statistics
+using Random
+
+using CairoMakie
+using MintsMakieRecipes
+
+set_theme!(mints_theme)
+update_theme!(
+    figure_padding=30,
+    Axis=(
+        xticklabelsize=20,
+        yticklabelsize=20,
+        xlabelsize=22,
+        ylabelsize=22,
+        titlesize=25,
+    ),
+    Colorbar=(
+        ticklabelsize=20,
+        labelsize=22
+    )
+)
+
+
+using MLJ, Flux, ConformalPrediction
+using ArgParse
+
+
+# pull in targets info
+include("./config.jl")
+include("./viz.jl")
+include("./training-functions.jl")
+
+
+function parse_commandline()
+    s = ArgParseSettings()
+
+    @add_arg_table! s begin
+        "--target_index","-i"
+        help = "Index of target variable for training. See targets_dict in config.jl for full list."
+        arg_type = Int
+        default = 28
+        "--datapath", "-d"
+        help = "Path to directory with data to be used in training"
+        arg_type = String
+        default = "/media/teamlary/LabData/RobotTeam/supervised"
+    end
+
+
+    parsed_args = parse_args(ARGS, s; as_symbols=true)
+
+    idx_target = parsed_args[:target_index]
+    @assert idx_target  > 0 && idx_target <= length(keys(targets_dict))
+    @assert ispath(parsed_args[:datapath]) "datapath does not exist"
+
+    return parsed_args
+end
+
+
+
+
+function main()
+    # seed reproducible pseudo-random number generator
+    @info "Setting random number seed"
+    rng = Xoshiro(42)
+
+    # parse args making sure that supplied target does exist
+    parsed_args = parse_commandline()
+
+    idx_target = parsed_args[:target_index]
+    target_keys = [k for k in keys(targets_dict)]
+    target = target_keys[idx_target]
+
+    datapath = parsed_args[:datapath]
+
+    target_name = String(target)
[…]

### 2023-11-27 training-functions.jl

@@ -380,3 +380,255 @@ function train_hpo(
 
 end
 
+
+
+
+
+cols_to_use = ["R_" * lpad(i, 3, "0") for i in 1:462]
+cols_to_standardize = ["roll", "pitch", "heading", "view_angle", "solar_azimuth", "solar_elevation", "solar_zenith"]
+cols_to_use = vcat(cols_to_use, cols_to_standardize)
+
+
+function train_stack(
+    X, y,
+    Xtest, ytest,
+    target_name, units, target_long,
+    outpath;
+    accelerate=false,
+    unc_method=:simple_inductive,
+    train_ratio=0.91,
+    unc_coverage=0.9,
+    rng=Xoshiro(42),
+    )
+
+    longname = "Model Stack"
+    savename = "superlearner"
+    suffix = "stack"
+
+    @info "\tSetting up save paths"
+
+    outpathdefault = joinpath(outpath, savename, "default")
+    outpath_featuresreduced = joinpath(outpath, savename, "important_only")
+    outpath_hpo = joinpath(outpath, savename, "hyperparameter_optimized")
+    outpath_stack = joinpath(outpath, savename, "superlearner_stack")
+
+    for path ∈ [outpathdefault, outpath_featuresreduced, outpath_hpo, outpath_stack]
+        if !isdir(path)
+            mkpath(path)
+        end
+    end
+
+    path_to_use = outpath_stack
+
+
+    # 1. Train model
+    @info "\tSetting model random seed"
+
+    # go through each model and load the hpo optimized version where possible
+
+
+    # ------------ NNR ----------------------
+    nnr_mod = NNR(builder=MLJFlux.MLP(hidden=(50,50,50,50), σ=Flux.relu),
+                  batch_size=256,
+                  optimiser=Flux.Optimise.ADAM(),
+                  lambda = 0.0001,
+                  rng=42,
+                  epochs=300,
+                  )
+
+
+    nnr  = Pipeline(
+        selector=FeatureSelector(features=Symbol.(cols_to_use)),
+        stand=Standardizer(features=Symbol.(cols_to_standardize)),
+        mdl=nnr_mod
+    )
+
+
+    # -----------Bag of Trees --------------
+
+    dtr = DTR()
+    try
+        hp_path = joinpath(outpath, "DecisionTreeRegressor", "hyperparameter_optimized", "hp_defaults.json")
+        hp_defaults = JSON.parsefile(hp_path)
+        for (key, val) in hp_defaults
[…]

### 2023-11-27 paper/paper.tex
updated paper with abstract notes

@@
 % Abstract (Do not insert blank lines, i.e. \\)
-\abstract{Fill this out last}
+\abstract{A robust characterization of model uncertainties is critical for any time-sensitive or dangerous application...To that end we employ a combination of model stacking together with Conformal Prediction by which we are able to blend together a variety of ML models while simultaneously estimating confidence intervals for the resulting predictions.
+}
 

### 2023-11-28 make-slurm-scripts.jl
setting up super learner job

@@ -34,69 +34,69 @@ end
 
 
 
-make_slurm_jobs(;
-                script_to_run="5a__hpo-DecisionTreeRegressor.jl",
-                basename="5a-",
-                n_tasks=4,
-                datapath="/scratch/jwaczak/data/robot-team/supervised",
-                )
-
-
-make_slurm_jobs(;
-                script_to_run="5b__hpo-RandomForestRegressor.jl",
-                basename="5b-",
-                n_tasks=4,
-                datapath="/scratch/jwaczak/data/robot-team/supervised",
-                )
-
-
-make_slurm_jobs(;
-                script_to_run="5c__hpo-XGBoostRegressor.jl",
-                basename="5c-",
-                n_tasks=4,
-                datapath="/scratch/jwaczak/data/robot-team/supervised",
-                )
-
-
-make_slurm_jobs(;
-                script_to_run="5d__hpo-KNNRegressor.jl",
-                basename="5d-",
-                n_tasks=4,
-                datapath="/scratch/jwaczak/data/robot-team/supervised",
-                )
-
-
-make_slurm_jobs(;
-                script_to_run="5e__hpo-EvoTreeRegressor.jl",
-                basename="5e-",
-                n_tasks=2,
-                datapath="/scratch/jwaczak/data/robot-team/supervised",
-                )
-
-
-make_slurm_jobs(;
-                script_to_run="5f__hpo-LGBMRegressor.jl",
-                basename="5f-",
-                n_tasks=4,
-                datapath="/scratch/jwaczak/data/robot-team/supervised",
-                )
-
-
-make_slurm_jobs(;
-                script_to_run="5g__hpo-CatBoostRegressor.jl",
-                basename="5g-",
-                n_tasks=4,
-                datapath="/scratch/jwaczak/data/robot-team/supervised",
-                )
+# make_slurm_jobs(;
+#                 script_to_run="5a__hpo-DecisionTreeRegressor.jl",
+#                 basename="5a-",
+#                 n_tasks=4,
+#                 datapath="/scratch/jwaczak/data/robot-team/supervised",
+#                 )
 
 
 # make_slurm_jobs(;
-#                 script_to_run="7__superlearner.jl",
-#                 basename="7_sl_",
+#                 script_to_run="5b__hpo-RandomForestRegressor.jl",
+#                 basename="5b-",
 #                 n_tasks=4,
[…]

### 2023-12-23 paper/template.tex
updated training procedures

@@
 \documentclass[journal,article,submit,pdftex,moreauthors]{Definitions/mdpi}
-% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept".
-The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}.
-This is especially recommended for submission to arXiv, where line numbers should be removed before posting.
-For preprints.org, the editorial staff will make this change immediately prior to posting.
 
@@
 % Choose between the following MDPI journals:
-% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis
+% acoustics, actuators, addictions, admsci, adolescents, aerobiology, aerospace, agriculture, agriengineering, agrochemicals, agronomy, ai, air, algorithms, allergies, alloys, analytica, analytics, anatomia, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arm, arthropoda, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, cyber, dairy, data, ddc, dentistry, dermato, dermatopathology, designs, devices, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, future, futureinternet, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, grasses, gucdd, hazardousmatters, healthcare, hearts, hemato, hematolrep, heritage, higheredu, highthroughput, histories, horticulturae, hospitals, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijpb, ijtm, ijtpp, ime, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jcto, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jvd, jzbg, kidneydial, kinasesphosphatases, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing,\gdef\@continuouspages{yes}} nanomaterials, ncrna, ndt, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, %%nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, %oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology,\gdef\@ISSN{2813-0618}\gdef\@continuous pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, platforms, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, receptors, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, sclerosis, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, spectroscj, sports, standards, stats, std, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, targets, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, virtualworlds, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis
+% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal. Changing "submit" to "accept" before posting will remove line numbers.
 
@@
 %---------
-% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
+% The option pdftex is for use with pdfLaTeX. Remove "pdftex" for (1) compiling with LaTeX & dvi2pdf (if eps figures are used) or for (2) compiling with XeLaTeX.
 
 %=================================================================
-% MDPI internal commands
+% MDPI internal commands - do not modify
 \firstpage{1} 
@@
 \articlenumber{0}
-\pubyear{2022}
-\copyrightyear{2022}
-%\externaleditor{Academic Editor: Firstname Lastname} % For journal Automation, please change Academic Editor to "Communicated by"
-\datereceived{} 
-\dateaccepted{} 
-\datepublished{} 
-%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
-%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
+\pubyear{2024}
+\copyrightyear{2023}
+%\externaleditor{Academic Editor: Firstname Lastname}
+\datereceived{ } 
+\daterevised{ } % Comment out if no revised date
+\dateaccepted{ } 
+\datepublished{ } 
+%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
+%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
 \hreflink{https://doi.org/} % If needed use \linebreak
 %\doinum{}
-%------------------------------------------------------------------
-% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
-%\pdfoutput=1
+%\pdfoutput=1 % Uncommented for upload to arXiv.org
+%\CorrStatement{yes}  % For updates
 
@@
 % Add packages and commands here.
-The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
+The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
+% cleveref: load \crefname definitions after \begin{document}
+
 %=================================================================
-%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
+% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
 %% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
@@
 % Authors, for the paper (add full first names)
-\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}
+\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{2,\ddagger}$ and Firstname Lastname $^{2,}$*}
 
@@
 % Current address and/or shared authorship
-\firstnote{Current address: Affiliation 3} 
+\firstnote{Current address: Affiliation 3.} 
 \secondnote{These authors contributed equally to this work.}
@@
 For research articles, abstracts should give a pertinent overview of the work.
-We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusion: indicate the main conclusions or interpretations.
+We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusions: indicate the main conclusions or interpretations.
 The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Applied Sciences:
+% Only for the journal Applied Sciences
 %\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Data:
-%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately.
-If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal.
-In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}
-
-%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
+% Only for the journal Data
+%\dataset{DOI number or link to the deposited data set if the data set is published separately.
+If the data set shall be published as a supplement to this paper, this field will be filled by the journal editors.
+In this case, please submit the data set as a supplement.}
+%\datasetlicense{License under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
 
@@
 % Only for the journal Encyclopedia
-%\encyclopediadef{Instead of the abstract}
-%\entrylink{The Link to this entry published on the encyclopedia platform.}
+%\encyclopediadef{For entry manuscripts only: please provide a brief overview of the entry title instead of an abstract.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Advances in Respiratory Medicine
+%\addhighlights{yes}
+%\renewcommand{\addhighlights}{%
+
+%\noindent This is an obligatory section in “Advances in Respiratory Medicine”, whose goal is to increase the discoverability and readability of the article via search engines and other scholars.
+Highlights should not be a copy of the abstract, but a simple text allowing the reader to quickly and simplified find out what the article is about and what can be cited from it.
+Each of these parts should be devoted up to 2~bullet points.\vspace{3pt}\\
+%\textbf{What are the main findings?}
+% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
+% \item First bullet.
+% \item Second bullet.
+% \end{itemize}\vspace{3pt}
+%\textbf{What is the implication of the main finding?}
+% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
+% \item First bullet.
+% \item Second bullet.
+% \end{itemize}
+%}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-% The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision
+% The order of the section titles is different for some journals. Please refer to the "Instructions for Authors” on the journal homepage.
 
@@
 
-All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, Table~\ref{tab2}, etc.
+All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.
 
@@
 Entry 1		& Data			& Data\\
-Entry 2		& Data			& Data\\
+Entry 2		& Data			& Data \textsuperscript{1}\\
 \bottomrule
 \end{tabularx}
+\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
 \end{table}
-\unskip
+
+The text continues here (Figure~\ref{fig2} and Table~\ref{tab2}).
+
+% Example of a figure that spans the whole page width. The same concept works for tables, too.
+\begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=15.5cm]{Definitions/logo-mdpi}
+\end{adjustwidth}
+\caption{This is a wide figure.\label{fig2}}
+\end{figure}
 
@@
 			\midrule
-			Entry 1		& Data			& Data			& Data\\
-			Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
+\multirow[m]{3}{*}{Entry 1 *}	& Data			& Data			& Data\\
+			  	                   & Data			& Data			& Data\\
+			             	      & Data			& Data			& Data\\
+                   \midrule
+\multirow[m]{3}{*}{Entry 2}    & Data			& Data			& Data\\
+			  	                  & Data			& Data			& Data\\
+			             	     & Data			& Data			& Data\\
+                   \midrule
+\multirow[m]{3}{*}{Entry 3}    & Data			& Data			& Data\\
+			  	                 & Data			& Data			& Data\\
+			             	    & Data			& Data			& Data\\
+                  \midrule
+\multirow[m]{3}{*}{Entry 4}   & Data			& Data			& Data\\
+			  	                 & Data			& Data			& Data\\
+			             	    & Data			& Data			& Data\\
 			\bottomrule
@@
 	\end{adjustwidth}
-	\noindent{\footnotesize{\textsuperscript{1} This is a table footnote.}}
+	\noindent{\footnotesize{* Tables may have a footer.}}
 \end{table}
@@
 
-% Example of a figure that spans the whole page width. The same concept works for tables, too.
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
-\centering
-\includegraphics[width=15cm]{Definitions/logo-mdpi}
-\end{adjustwidth}
-\caption{This is a wide figure.\label{fig2}}
-\end{figure}
-
 Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
@@
 %% optional
-%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}
+%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}
 
-% Only for the journal Methods and Protocols:
+% Only for journal Methods and Protocols:
 % If you wish to submit a video article, please do so with any other supplementary material.
-% \supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}
+% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.
+A supporting video article is available at doi: link.}
+
+% Only for journal Hardware:
+% If you wish to submit a video article, please do so with any other supplementary material.
+% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.\vspace{6pt}\\
+%\begin{tabularx}{\textwidth}{lll}
+%\toprule
+%\textbf{Name} & \textbf{Type} & \textbf{Description} \\
+%\midrule
+%S1 & Python script (.py) & Script of python source code used in XX \\
+%S2 & Text (.txt) & Script of modelling code used to make Figure X \\
+%S3 & Text (.txt) & Raw data from experiment X \\
+%S4 & Video (.mp4) & Video demonstrating the hardware in use \\
+%... & ... & ... \\
+%\bottomrule
+%\end{tabularx}
+%}
 
@@
 
-\institutionalreview{In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals.
+\institutionalreview{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study.
+You might choose to exclude this statement if the study did not require ethical approval.
 Please note that the Editorial Office might ask you for further information.
-Please add ``The study was conducted according to the guidelines of the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).'' OR ``Ethical review and approval were waived for this study, due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans or animals.
-You might also choose to exclude this statement if the study did not involve humans or animals.}
+Please add “The study was conducted in accordance with the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving humans.
+OR “The animal study protocol was approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving animals.
+OR “Ethical review and approval were waived for this study due to REASON (please provide a detailed justification).” OR “Not applicable” for studies not involving humans or animals.}
 
@@
 
-\dataavailability{In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study.
-Please refer to suggested Data Availability Statements in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}.
-You might choose to exclude this statement if the study did not report any data.}
+\dataavailability{We encourage all authors of articles published in MDPI journals to share their research data.
+In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study.
+Where no new data were created, or where data is unavailable due to privacy or ethical restrictions, a statement is still required.
+Suggested Data Availability Statements are available in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}.}
+
+% Only for journal Nursing Reports
+%\publicinvolvement{Please describe how the public (patients, consumers, carers) were involved in the research.
+Consider reporting against the GRIPP2 (Guidance for Reporting Involvement of Patients and the Public) checklist.
+If the public were not involved in any aspect of the research add: ``No public involvement in any aspect of this research''.}
+
+% Only for journal Nursing Reports
+%\guidelinesstandards{Please add a statement indicating which reporting guideline was used when drafting the report.
+For example, ``This manuscript was drafted against the XXX (the full name of reporting guidelines and citation) for XXX (type of research) research''.
+A complete list of reporting guidelines can be accessed via the equator network: \url{https://www.equator-network.org/}.}
 
@@
 
-\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
-Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section.
-If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the~results''.}
-
-%% Optional
-\sampleavailability{Samples of the compounds ... are available from the authors.}
+\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflicts of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
+Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript; or in the decision to publish the results must be declared in this section.
+If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript; or in the decision to publish the results''.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Optional
+
 %% Only for journal Encyclopedia
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Optional
 \abbreviations{Abbreviations}{
@@
 LD & Linear dichroism
-\end{tabular}}
+\end{tabular}
+}
 
@@
 \bibitem[Author2(year)]{ref-book1}
-Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
+Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
 % Reference 3
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\PublishersNote{}
 \end{adjustwidth}

### 2023-12-23 1_make-datasets.jl

@@ -114,8 +114,16 @@ function get_data(fpath; threshold=0.25)
     feature_names = []
     target_names = []
     let
-        df_features = CSV.read(joinpath(fpath, "Features.csv"), DataFrame)
-        df_targets = CSV.read(joinpath(fpath, "Targets.csv"), DataFrame)
+        # df_features = vcat(CSV.read(joinpath(fpath, "Features_1.csv"), DataFrame), CSV.read(joinpath(fpath, "Features_2.csv"), DataFrame))
+        # df_targets = vcat(CSV.read(joinpath(fpath, "Targets_1.csv"), DataFrame), CSV.read(joinpath(fpath, "Targets_2.csv"), DataFrame))
+
+        df_features = CSV.read(joinpath(fpath, "Features_2.csv"), DataFrame)
+        df_targets = CSV.read(joinpath(fpath, "Targets_2.csv"), DataFrame)
+
+        # df_features = CSV.read(joinpath(fpath, "Features_1.csv"), DataFrame)
+        # df_targets = CSV.read(joinpath(fpath, "Targets_1.csv"), DataFrame)
+
+
 
         feature_names = names(df_features)
         target_names = names(df_targets)
@@ -245,7 +253,7 @@ for (collection, fpath) in inpaths
         save(joinpath(mapspath_final, "data-map.png"), fig)
         save(joinpath(mapspath_final, "data-map.pdf"), fig)
 
-        (y,X) = make_datasets(data, target_name, feature_names, target_names, ignorecols; rng=rng)
+        (y,X) = make_datasets(data, target_name, feature_names, target_names, ignorecols)
         idx_train, idx_test = partition(eachindex(y), 0.9, shuffle=true, rng=rng)
 
 
@@ -257,5 +265,3 @@ for (collection, fpath) in inpaths
         CSV.write(joinpath(outpath_final, "lat_lon.csv"), df_latlon)
     end
 end
-
-

### 2023-12-23 2_exploratory-data-analysis.jl

@@ -47,7 +47,8 @@ for collection in collections
         @info "\t$(target)"
 
         # collection = "11-23"
-        # target = "NH4"
+        # target = "CDOM"
+
         # load in data
 
         pretty_name = targets_dict[Symbol(target)][2]
@@ -65,6 +66,7 @@ for collection in collections
 
         y = CSV.read(joinpath(data_path, "y.csv"), DataFrame)[:,1]
         # ytest = CSV.read(joinpath(data_path, "ytest.csv"), DataFrame)
+
 
 
         # compute correlation matrix between reflectances
@@ -102,28 +104,26 @@ for collection in collections
         save(joinpath(fig_path, "correlation-width-$(target).pdf"), fig)
 
         # generate target histogram/distribution visualization
-        # ytrain_vals = @view y[:,1]
-        # ytest_vals = @view ytest[:,1]
-
-        # compute number of bins for histogram
-
-
-
         @info "\t\tgenerating histogram..."
+
         fig = Figure();
 
         nbins = 1
         bin_width = maximum(y) - minimum(y)
+
         try
             nbins, bin_width = get_n_bins(y)
         catch e
-            nothing
+            println("Failed to find n_bins")
+            nbins = 30
+            bin_width = (maximum(y) - minimum(y))/nbins
         end
+
 
         ax = Axis(fig[1,1], xlabel="$(pretty_name) ($(units))", ylabel="Counts", title="N bins = $(nbins), bin width=$(round(bin_width, digits=3))")
         ax2 = Axis(fig[1,1], yaxisposition=:right)
         linkxaxes!(ax, ax2)
-        y_hist = fit(Histogram, y; nbins=nbins)
+
         h = hist!(ax, y; bins=nbins, color=(mints_colors[1], 0.75), normalization=:none)
         d = density!(ax2, y[:,1], color=(mints_colors[2], 0.25), strokecolor=(mints_colors[2],0.75), strokewidth=3)
 

### 2023-12-23 3_feature-exploration.jl

@@ -73,7 +73,7 @@ MODELS = Dict()
 
 
 cols_to_use = ["R_" * lpad(i, 3, "0") for i in 1:462]
-cols_to_standardize = ["roll", "pitch", "heading", "view_angle", "solar_azimuth", "solar_elevation", "solar_zenith"]
+cols_to_standardize = ["roll", "pitch", "heading", "view_angle", "solar_azimuth", "solar_elevation", "solar_zenith", "Σrad", "Σdownwelling"]
 cols_to_use = vcat(cols_to_use, cols_to_standardize)
 
 use_metrics = false
@@ -121,13 +121,12 @@ nnr  = Pipeline(
 
 # # # 3. Add XGBoostRegressor. Defaults seem fine...
 
-MODELS[:xgbr] = (;
-                 :longname=>"XGBoost Regressor",
-                 :savename=>"XGBoostRegressor",
-                 :packagename=>"XGBoost",
-                 :mdl=>XGBR(),
-                 )
-
+# MODELS[:xgbr] = (;
+#                  :longname=>"XGBoost Regressor",
+#                  :savename=>"XGBoostRegressor",
+#                  :packagename=>"XGBoost",
+#                  :mdl=>XGBR(),
+#                  )
 
 MODELS[:etr] = (;
                 :longname=>"Evo Tree Regressor",
@@ -137,18 +136,18 @@ MODELS[:etr] = (;
                 )
 
 
-MODELS[:dtr] = (;
-                :longname => "Decision Tree Regressor",
-                :savename => "DecisionTreeRegressor",
-                :mdl => DTR()
-                )
+# MODELS[:dtr] = (;
+#                 :longname => "Decision Tree Regressor",
+#                 :savename => "DecisionTreeRegressor",
+#                 :mdl => DTR()
+#                 )
 
 
-MODELS[:rfr] = (;
-                :longname => "Random Forest Regressor",
-                :savename => "RandomForestRegressor",
-                :mdl => RFR()
-                )
+# MODELS[:rfr] = (;
+#                 :longname => "Random Forest Regressor",
+#                 :savename => "RandomForestRegressor",
+#                 :mdl => RFR()
+#                 )
 
 
 
@@ -156,11 +155,11 @@ MODELS[:rfr] = (;
 # targets_to_try = [:CDOM, :CO, :Na, :Cl]
 
 
[…]

### 2023-12-23 3b_make-maps.jl

@@ -6,8 +6,8 @@ using ProgressMeter
 import CairoMakie as cmk
 using MintsMakieRecipes
 
-set_theme!(mints_theme)
-update_theme!(
+cmk.set_theme!(mints_theme)
+cmk.update_theme!(
     figure_padding=30,
     Axis=(
         xticklabelsize=20,
@@ -52,7 +52,8 @@ satmap = get_background_satmap(w,e,s,n)
 # set up relevant paths
 collection = "11-23"
 hsi_11_23 = joinpath(hsipath, collection)
-scotty_2 = joinpath(hsi_11_23, "Scotty_2")
+flight = "Scotty_1"
+scotty_2 = joinpath(hsi_11_23, flight)
 
 h5_files = [joinpath(scotty_2, f) for f in readdir(scotty_2) if endswith(f, ".h5")]
 
@@ -68,7 +69,7 @@ sort_files_numerical!(h5_files)
 
 # let's open one and extract the data
 # create function to tell if the pixel is on land or not
-function in_water(Datacube, varnames; threshold=0.1)
+function in_water(Datacube, varnames; threshold=0.25)
     idx_mndwi = findfirst(varnames .== "mNDWI")
     return findall(Datacube[idx_mndwi,:,:] .> threshold)
 end
@@ -99,9 +100,9 @@ function get_data_for_pred(h5path, col_names)
 end
 
 
-
 # load model
-model_collection = "11-23"
+# model_collection = "11-23"
+model_collection = "Full"
 ETR = @load EvoTreeRegressor pkg=EvoTrees
 model = "EvoTreeRegressor"
 
@@ -157,95 +158,80 @@ outpath = joinpath(mapspath, model_collection, target_name, "11-23")
 if !ispath(outpath)
     mkpath(outpath)
 end
+savepath = joinpath(outpath, flight)
+if !ispath(savepath)
+    mkpath(savepath)
+end
 
 
-fig = cmk.Figure();
-ax = cmk.Axis(fig[1,1], xlabel="longitude", ylabel="latitude");
-bg = cmk.heatmap!(ax, satmap.w..satmap.e, satmap.s..satmap.n, satmap.img);
-clims = (20.0, 21.5)
 
-@showprogress for h5path in h5_files
-#    h5path = h5_files[1]
+
+
+
+fig_tot = cmk.Figure();
[…]

### 2023-12-23 config.jl

@@ -83,6 +83,8 @@ name_replacements["ARI2"] = "Anthocyanin Reflectance Index 2"
 name_replacements["WBI"] = "Water Band Index"
 name_replacements["MCRI"] = "Modified Chlorophyll Absorption Reflectance Index"
 name_replacements["TCARI"] = "Transformed Chlorophyll Absorption Reflectance Index"
+name_replacements["Σrad"] = "Total Pixel Intensity"
+name_replacements["Σdownwelling"] = "Total Downwelling Intensity"
 
 
 

### 2023-12-23 training-functions.jl

@@ -99,7 +99,7 @@ function train_folds(
 
 
     # fit the machine
-    @info "\tEvaluating model for $(nfolds) folds"
+    # @info "\tEvaluating model for $(nfolds) folds"
     mach = machine(mdl, Xtrain, ytrain)
 
     cv = CV(nfolds=nfolds, rng=rng)
@@ -126,6 +126,12 @@ function train_folds(
 
     yhat_train = MLJ.predict(mach, Xtrain)
     yhat_test = MLJ.predict(mach, Xtest)
+
+    # res_dict["rsq"] = rsq(yhat_test, ytest)
+    # res_dict["rmse"] = rmse(yhat_test, ytest)
+    # res_dict["mae"] = mae(yhat_test, ytest)
+    # res_dict["r"] = cor_coef(yhat_test, ytest)
+
 
 
     # generate plots:
@@ -184,6 +190,7 @@ function train_folds(
         rpt = report(mach);
 
         fi_pairs = feature_importances(mach) #.model, mach.fitresult, rpt);
+
 
         fi_df = DataFrame()
         fi_df.feature_name = [x[1] for x ∈ fi_pairs]

### 2023-12-23 1_make-datasets.jl
updated to use RandomForestRegressor as it produces more beleivable maps

@@ -40,25 +40,23 @@ include("./viz.jl")
 include("./sat-viz.jl")
 
 
-outpath = "/media/teamlary/LabData/RobotTeam/supervised"
+outpath = "/Users/johnwaczak/data/robot-team/supervised"
 if !ispath(outpath)
     mkpath(outpath)
 end
 
-mapspath = "/media/teamlary/LabData/RobotTeam/maps"
+mapspath = "/Users/johnwaczak/data/robot-team/maps"
 if !ispath(mapspath)
     mkpath(mapspath)
 end
 
 
 inpaths = Dict(
-    "11-23" => "/media/teamlary/LabData/RobotTeam/finalized/11-23",
-    # "12-09" => "/media/teamlary/LabData/RobotTeam/finalized/12-09",
-    # "12-10" => "/media/teamlary/LabData/RobotTeam/finalized/12-10",
-    "Full" => "/media/teamlary/LabData/RobotTeam/finalized/Full"
+    "11-23" => "/Users/johnwaczak/data/robot-team/finalized/11-23",
+    "Full" => "/Users/johnwaczak/data/robot-team/finalized/Full"
 )
 
-# inpath = "/media/teamlary/LabData/RobotTeam/finalized/Full"
+# inpath = "/Volumes/LabData/RobotTeam/finalized/Full"
 for (collection, path) in inpaths
     @assert ispath(path)
 end
@@ -72,7 +70,7 @@ e= -97.712413
 satmap = get_background_satmap(w,e,s,n)
 
 
-df = CSV.read("/media/teamlary/LabData/RobotTeam/prepared/12-10/Targets.csv", DataFrame)
+# df = CSV.read("/Users/johnwaczak/data/robot-team/prepared/12-10/Targets.csv", DataFrame)
 
 # gdf = groupby(df, :category)
 

### 2023-12-23 2_exploratory-data-analysis.jl

@@ -31,7 +31,7 @@ include("./config.jl")
 include("./viz.jl")
 
 
-outpath = "/media/teamlary/LabData/RobotTeam/supervised"
+outpath = "/Volumes/LabData/RobotTeam/supervised"
 
 # collections = ["11-23", "12-09", "12-10", "Full"]
 collections = ["11-23", "Full"]
@@ -62,10 +62,18 @@ for collection in collections
 
         @info "\t\tloading data..."
         X = CSV.read(joinpath(data_path, "X.csv"), DataFrame)
-        # Xtest = CSV.read(joinpath(data_path, "Xtest.csv"), DataFrame)
-
         y = CSV.read(joinpath(data_path, "y.csv"), DataFrame)[:,1]
-        # ytest = CSV.read(joinpath(data_path, "ytest.csv"), DataFrame)
+
+        nbins = 1
+        bin_width = maximum(y) - minimum(y)
+        try
+            nbins, bin_width = get_n_bins(y)
+        catch e
+            println("Failed to find n_bins")
+            nbins = 30
+            bin_width = (maximum(y) - minimum(y))/nbins
+        end
+
 
 
 
@@ -107,18 +115,6 @@ for collection in collections
         @info "\t\tgenerating histogram..."
 
         fig = Figure();
-
-        nbins = 1
-        bin_width = maximum(y) - minimum(y)
-
-        try
-            nbins, bin_width = get_n_bins(y)
-        catch e
-            println("Failed to find n_bins")
-            nbins = 30
-            bin_width = (maximum(y) - minimum(y))/nbins
-        end
-
 
         ax = Axis(fig[1,1], xlabel="$(pretty_name) ($(units))", ylabel="Counts", title="N bins = $(nbins), bin width=$(round(bin_width, digits=3))")
         ax2 = Axis(fig[1,1], yaxisposition=:right)

### 2023-12-23 3_feature-exploration.jl

@@ -55,7 +55,7 @@ include("./training-functions.jl")
 
 
 
-datapath = "/media/teamlary/LabData/RobotTeam/supervised"
+datapath = "/Users/johnwaczak/data/robot-team/supervised"
 
 # DecisionTreeRegressor and RandomForestRegressor don't seem to work.
 
@@ -105,11 +105,11 @@ nnr_mod = NNR(
 # # )
 
 
-nnr  = Pipeline(
-    selector=FeatureSelector(features=Symbol.(cols_to_use)),
-    stand=Standardizer(features=Symbol.(cols_to_standardize)),
-    mdl=nnr_mod
-)
+# nnr  = Pipeline(
+#     selector=FeatureSelector(features=Symbol.(cols_to_use)),
+#     stand=Standardizer(features=Symbol.(cols_to_standardize)),
+#     mdl=nnr_mod
+# )
 
 
 # MODELS[:nnr] = (;
@@ -128,12 +128,12 @@ nnr  = Pipeline(
 #                  :mdl=>XGBR(),
 #                  )
 
-MODELS[:etr] = (;
-                :longname=>"Evo Tree Regressor",
-                :savename=>"EvoTreeRegressor",
-                :packagename => "EvoTrees",
-                :mdl => ETR(nrounds=100, nbins=255, eta=0.3, max_depth=6, lambda=1.0, alpha=0.0),
-                )
+# MODELS[:etr] = (;
+#                 :longname=>"Evo Tree Regressor",
+#                 :savename=>"EvoTreeRegressor",
+#                 :packagename => "EvoTrees",
+#                 :mdl => ETR(nrounds=100, nbins=255, eta=0.3, max_depth=6, lambda=1.0, alpha=0.0),
+#                 )
 
 
 # MODELS[:dtr] = (;
@@ -143,12 +143,11 @@ MODELS[:etr] = (;
 #                 )
 
 
-# MODELS[:rfr] = (;
-#                 :longname => "Random Forest Regressor",
-#                 :savename => "RandomForestRegressor",
-#                 :mdl => RFR()
-#                 )
-
+MODELS[:rfr] = (;
+                :longname => "Random Forest Regressor",
+                :savename => "RandomForestRegressor",
+                :mdl => RFR(n_subfeatures=-1, sampling_fraction=0.9, n_trees=150),
+                )
 
 
 # 5. Fit each of the models to different subsets of features.
[…]

### 2023-12-23 3b_make-maps.jl

@@ -23,17 +23,17 @@ cmk.update_theme!(
 )
 
 
-
+Δx = 0.5
 
 include("./config.jl")
 include("./viz.jl")
 include("./sat-viz.jl")
 
 
-datapath = "/media/teamlary/LabData/RobotTeam/supervised"
-hsipath = "/media/teamlary/LabData/RobotTeam/processed/hsi"
+datapath = "/Users/johnwaczak/data/robot-team/supervised"
+hsipath = "/Users/johnwaczak/data/robot-team/processed/hsi"
 
-mapspath = "/media/teamlary/LabData/RobotTeam/maps"
+mapspath = "/Users/johnwaczak/data/robot-team/maps"
 if !ispath(mapspath)
     mkpath(mapspath)
 end
@@ -52,7 +52,7 @@ satmap = get_background_satmap(w,e,s,n)
 # set up relevant paths
 collection = "11-23"
 hsi_11_23 = joinpath(hsipath, collection)
-flight = "Scotty_1"
+flight = "Scotty_2"
 scotty_2 = joinpath(hsi_11_23, flight)
 
 h5_files = [joinpath(scotty_2, f) for f in readdir(scotty_2) if endswith(f, ".h5")]
@@ -78,13 +78,13 @@ end
 
 function get_data_for_pred(h5path, col_names)
     h5 = h5open(h5path, "r")
-    varnames = read(h5["data-Δx_0.1/varnames"])
+    varnames = read(h5["data-Δx_$(Δx)/varnames"])
     # get indices of relevant varnames
     idx_varnames = findall([v in col_names for v in varnames])
-    Data = read(h5["data-Δx_0.1/Data"])[idx_varnames, :, :]
-    IsInbounds = read(h5["data-Δx_0.1/IsInbounds"])
-    Longitudes = read(h5["data-Δx_0.1/Longitudes"])
-    Latitudes = read(h5["data-Δx_0.1/Latitudes"])
+    Data = read(h5["data-Δx_$(Δx)/Data"])[idx_varnames, :, :]
+    IsInbounds = read(h5["data-Δx_$(Δx)/IsInbounds"])
+    Longitudes = read(h5["data-Δx_$(Δx)/Longitudes"])
+    Latitudes = read(h5["data-Δx_$(Δx)/Latitudes"])
     close(h5)
 
     # allocate target prediction array
@@ -104,7 +104,8 @@ end
[…]

### 2023-12-23 config.jl

@@ -85,7 +85,7 @@ name_replacements["MCRI"] = "Modified Chlorophyll Absorption Reflectance Index"
 name_replacements["TCARI"] = "Transformed Chlorophyll Absorption Reflectance Index"
 name_replacements["Σrad"] = "Total Pixel Intensity"
 name_replacements["Σdownwelling"] = "Total Downwelling Intensity"
-
+name_replacements["yaw_minus_azimuth"] = "Heading - Solar Azimuth"
 
 
 

### 2023-12-23 training-functions.jl

@@ -170,6 +170,7 @@ function train_folds(
         yhat_conf = ConformalPrediction.predict(mach_conf, Xtest);
         cov = emp_coverage(yhat_conf, ytest);
         @info "\tEmpirical coverage: $(cov)"
+        res_dict["emp_cov"] = cov
 
         Δy = (yhat_conf[1][2] - yhat_conf[1][1])/2
         res_dict["uncertainty"] = Δy

### 2023-12-23 viz.jl

@@ -276,7 +276,7 @@ end
 
 
 
-function get_n_bins(x::T) where T<:AbstractVector
+function get_n_bins(x)
     # bin_width = 2*iqr(x)/(length(x)^(1/3))  # Freedman-Diaconis rule
     bin_width = 3.49*std(x)/(length(y)^(1/3)) # Scott's rule
     xmin, xmax = extrema(x)

### 2023-12-25 2_exploratory-data-analysis.jl
updated maps

@@ -31,7 +31,7 @@ include("./config.jl")
 include("./viz.jl")
 
 
-outpath = "/Volumes/LabData/RobotTeam/supervised"
+outpath = "/Users/johnwaczak/data/robot-team/supervised"
 
 # collections = ["11-23", "12-09", "12-10", "Full"]
 collections = ["11-23", "Full"]

### 2023-12-25 3b_make-maps.jl

@@ -23,7 +23,8 @@ cmk.update_theme!(
 )
 
 
-Δx = 0.5
+Δx = 0.1
+suffix = "hpo1"
 
 include("./config.jl")
 include("./viz.jl")
@@ -100,147 +101,127 @@ function get_data_for_pred(h5path, col_names)
 end
 
 
-# load model
-# model_collection = "11-23"
-model_collection = "Full"
-ETR = @load EvoTreeRegressor pkg=EvoTrees
-# model = "EvoTreeRegressor"
+RFR = @load RandomForestRegressor pkg=DecisionTree
 model = "RandomForestRegressor"
+model_collections = ["11-23", "Full"]
+suffixes = ["vanilla", "hpo1", "hpo2"]
 
-targets_to_map = [t for t in Symbol.(keys(targets_dict)) if !(t in [:TDS, :Salinity3490])]
-targets_to_map = [:CDOM]
-
-target = :CDOM
-target_name = String(target)
-target_long = targets_dict[target][2]
-units = targets_dict[target][1]
-
-# create model path
-modelpath = joinpath(datapath, model_collection, target_name, "models", model, "default", model*"__vanilla.jls")
-@assert ispath(modelpath)
-mach = machine(modelpath)
-
-data_path = joinpath(datapath, collection, target_name, "data")
-X = CSV.read(joinpath(data_path, "X.csv"), DataFrame)
-y = CSV.read(joinpath(data_path, "y.csv"), DataFrame)[:,1]
-df_lat_long= CSV.read(joinpath(data_path, "lat_lon.csv"), DataFrame)
-latitudes = df_lat_long.latitudes
-longitudes = df_lat_long.longitudes
-
-# make predictions for collocated data
-yhat_boat = predict(mach, X)
+targets_to_map = [t for t in Symbol.(keys(targets_dict)) if !(t in [:TDS, :Salinity3490, :bg, :Br, :NH4, :Turb3488, :Turb3490])]
 
 
-# plot predictions on dataset
-fig = cmk.Figure(;resolution=(1200,500));
-ax1 = cmk.Axis(fig[1,1], xlabel="longitude", ylabel="latitude", title="Data");
-ax2 = cmk.Axis(fig[1,2], xlabel="longitude", ylabel="latitude", title="Predictions");
-bg1 = cmk.heatmap!(ax1, satmap.w..satmap.e, satmap.s..satmap.n, satmap.img);
[…]

### 2023-12-25 training-functions.jl

@@ -10,11 +10,11 @@ hpo_ranges = Dict("DecisionTree" => Dict("DecisionTreeRegressor" => [(hpname=:mi
                                                                       (hpname=:post_prune, values=[false, true])
                                                                       ],
                                          "RandomForestRegressor" => [
-                                                                      (hpname=:min_samples_leaf, lower=2, upper=100),
-                                                                      (hpname=:max_depth, values=[-1, 2, 3, 5, 10, 20]),
-                                                                      (hpname=:n_subfeatures, values=[-1,0]),
-                                                                      (hpname=:n_trees, values=[10, 25, 50, 75, 100, 125, 150]),
-                                                                      (hpname=:sampling_fraction, lower=0.65, upper=0.9)
+                                                                      #(hpname=:min_samples_leaf, lower=2, upper=100),
+                                                                      #(hpname=:max_depth, values=[-1, 2, 3, 5, 10, 20]),
+                                                                      (hpname=:n_subfeatures, lower=50, upper=450,),
+                                                                      (hpname=:n_trees, lower=50, upper=250),
+                                                                      (hpname=:sampling_fraction, lower=0.75, upper=0.95)
                                                                       ],
                                           ),
                  "XGBoost" => Dict("XGBoostRegressor" => [(hpname=:num_round, lower=50, upper=100),
@@ -70,6 +70,7 @@ function train_folds(
     suffix="",
     rng=Xoshiro(42),
     nfolds=10,
+    run_occam=true,
     )
 
     @info "\tSetting up save paths"
@@ -271,78 +272,92 @@ function train_folds(
 
         # now retrain the model with a limited number of features
         # N_features_to_use = [1,2, 3, 4, 5,10,15,20,(25:25:(ncol(X)÷25)*25)...]
[…]

### 2023-12-26 3_feature-exploration.jl
updating generation of comparison tables

@@ -255,8 +255,7 @@ GC.gc()
 
 
 
-
-function make_summary_table(modelname, ending)
+function make_summary_table(collection, savename, suffix)
     res_dicts = Dict[]
 
     for target in targets_to_try
@@ -264,10 +263,11 @@ function make_summary_table(modelname, ending)
         target_long = targets_dict[target][2]
         units = targets_dict[target][1]
 
-        res_path = joinpath(datapath, target_name, "models", modelname, "default", modelname*"__vanilla"*ending*".json")
+        res_path = joinpath(datapath, collection, target_name, "models", savename, "default", savename*"__$(suffix).json")
+
+        @assert ispath(res_path)
 
         res_string = read(res_path, String)
-
         res_dict = JSON.parse(res_string)
 
         try
@@ -276,71 +276,45 @@ function make_summary_table(modelname, ending)
             end
             res_dict["target"] = target_name
             res_dict["target_long"] = targets_dict[Symbol(target_name)][2]
-            push!(res_dicts, res_dict
+            push!(res_dicts, res_dict)
         catch e
             println(target_name)
         end
+
     end
 
     df_res = DataFrame(res_dicts)
 
-    sort!(df_res, :rsq_test; rev=true)
-    select!(df_res, [:target_long, :target, :rsq_test, :rsq_train, :rmse_test, :rmse_train, :mae_test, :mae_train, :cov])
+    sort!(df_res, :rsq_mean; rev=true)
+
+    select!(df_res, [:target_long, :target, :rsq_mean, :rsq_std, :rmse_mean, :rmse_std, :mae_mean, :mae_std, :r_mean, :r_std, :uncertainty, :emp_cov])
     rename!(df_res,
             "target_long" => "Target",
             "target" => "Var Name",
-            "rsq_test" => "R² test",
-            "rsq_train" => "R² train",
-            "rmse_test" => "RMSE test",
-            "rmse_train" => "RMSE train",
-            "mae_test" => "MAE test",
-            "mae_train" => "MAE train",
-            "r_test" => "R test",
-            "r_train" => "R train",
-            "cov" => "Empirical Coverage"
[…]

### 2023-12-26 paper/paper.tex
updated paper and added some figures

--- 2023-07-20 paper/paper.tex
@@
-\documentclass[remotesensing,article,submit,pdftex,moreauthors]{Definitions/mdpi}
+%  LaTeX support: latex@mdpi.com 
+%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.
 
 %=================================================================
-% MDPI internal commands
+\documentclass[journal,article,submit,pdftex,moreauthors]{Definitions/mdpi}
+
+%--------------------
+% Class Options:
+%--------------------
+%----------
+% journal
+%----------
+% Choose between the following MDPI journals:
+% acoustics, actuators, addictions, admsci, adolescents, aerobiology, aerospace, agriculture, agriengineering, agrochemicals, agronomy, ai, air, algorithms, allergies, alloys, analytica, analytics, anatomia, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arm, arthropoda, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, cyber, dairy, data, ddc, dentistry, dermato, dermatopathology, designs, devices, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, future, futureinternet, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, grasses, gucdd, hazardousmatters, healthcare, hearts, hemato, hematolrep, heritage, higheredu, highthroughput, histories, horticulturae, hospitals, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijpb, ijtm, ijtpp, ime, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jcto, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jvd, jzbg, kidneydial, kinasesphosphatases, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing,\gdef\@continuouspages{yes}} nanomaterials, ncrna, ndt, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, %%nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, %oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology,\gdef\@ISSN{2813-0618}\gdef\@continuous pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, platforms, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, receptors, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, sclerosis, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, spectroscj, sports, standards, stats, std, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, targets, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, virtualworlds, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis
+% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal. Changing "submit" to "accept" before posting will remove line numbers.
+
+%---------
+% article
+%---------
+% The default type of manuscript is "article", but can be replaced by: 
+% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
+% supfile = supplementary materials
+
+%----------
+% submit
+%----------
+% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
+This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information.
+Also, line numbering will be removed.
+Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
+
+%------------------
+% moreauthors
+%------------------
+% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
+
+%---------
+% pdftex
+%---------
+% The option pdftex is for use with pdfLaTeX. Remove "pdftex" for (1) compiling with LaTeX & dvi2pdf (if eps figures are used) or for (2) compiling with XeLaTeX.
+
+%=================================================================
+% MDPI internal commands - do not modify
 \firstpage{1} 
@@
 % Full title of the paper (Capitalized)
-\Title{Robot Team II: Electric Boogaloo}
+\Title{\textcolor{red}{Robot Team II: Electric Boogaloo}}
 
@@
 \newcommand{\orcidauthorA}{0000-0002-5910-0183} % Add \orcidA{} behind the author's name
-\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
+\newcommand{\orcidauthorB}{0000-0003-4265-9543} % Add \orcidA{} behind the author's name
+%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
 
 % Authors, for the paper (add full first names)
-% \Author{John Waczak $^{1,\dagger,\ddagger}$\orcidA{} and David J. Lary $^{1,\ddagger}$\orcidB{}}
-\Author{John Waczak\orcidA{} and David J. Lary\orcidB{}}
+\Author{John Waczak$^{\dagger}$\orcidA{}, Adam Aker, Lakitha O. H. Wijeratne, Shawhin Talebi, Bharana Fernando, David Schaefer, David J. Lary, $^{\dagger}$\orcidB{}*}
 
@@
 % MDPI internal command: Authors, for metadata in PDF
-\AuthorNames{John Waczak and David J. Lary}
+\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}
 
 % MDPI internal command: Authors, for citation in the left column
-\AuthorCitation{Waczak, J.; Lary, D.J.}
+\AuthorCitation{Waczak, J.; Lary, D.; Lastname, F.}
 % If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
@@
 \address{%
-  Hanson Center for Space Sciences, University of Texas at Dallas, Richardson,
-  TX 75080, USA;}
-
-% $^{1}$ \quad John.Waczak@utdallas.edu\\
-% $^{2}$ \quad David.Lary@utdallas.edu}
+Hanson Center for Space Sciences, University of Texas at Dallas, Richardson, TX 75080, USA\
+}
 
 % Contact information of the corresponding author
-\corres{Correspondence: John.Waczak@utdallas.edu}
+\corres{Correspondence: David.Lary@utdallas.edu} %; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}
 
 % Current address and/or shared authorship
-%\firstnote{} 
-% \secondnote{These authors contributed equally to this work.}
+
 % The commands \thirdnote{} till \eighthnote{} are available for further notes
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{Fill this out last}
+\abstract{\textcolor{red}{A single paragraph of about 200 words maximum.
+For research articles, abstracts should give a pertinent overview of the work.
+We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusions: indicate the main conclusions or interpretations.
+The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}}
 
 % Keywords
-\keyword{Remote Sensing; hyperspectral image; georectification; machine learning}
+\keyword{\textcolor{red}{keyword 1; keyword 2; keyword 3 (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}}
 
@@
 
-\subsection{Importance / Human Impact}
-oil spill response, contaminated water, environmental surveys, algal blooms,
-agriculture, land monitoring, air quality, etc...
+Remote sensing data products
 
-paper using spectral indices for water quality assesment \cite{SpectralIndexWaterQuality}
+Hyper-spectral imagery
 
-\subsection{Hyperspectral Imaging and Remote Sensing}
-paper creating new spectral index for wheat rust \cite{SpectralIndexWheat} \\ 
-overview of NDVI \cite{SpectralIndexNDVI} \\ 
-paper using spectral indices for desertification \cite{SpectralIndexDesertification}
+Launched and soon-to-be-launched HSI satellites
 
-\subsubsection{HSI sattelite systems}
-\subsubsection{HSI drone systems}
-\subsubsection{Machine Learning using HSI}
-add Xiao He reference here \cite{yu2021pm2}
+Generation of in-situe reference measurements for the calibration of remote sensing data products
 
-\subsection{In-situ Measurements / Robot Teams}
-\subsubsection{Meteorology}
-\subsubsection{Atmospheric Sensing}
-add in reference to our AQ sensor network
+Drone based applications of hyper-spectral imagers
 
-\subsection{Julia Programming Language}
-\subsubsection{scientific computing}
-\subsubsection{differentiable programming ($\partial P$)}
-\subsubsection{MLJ}
-discuss general \textit{learning network} framework and utilization of
-Directed Acyclic Graphs for pipeline construction
+Autonomous robotic teams (cite our previous paper)
 
-basic overview of MLJ as a Julia package \cite{MLJ1}\\
+Overview of what we demonstrate here...
 
-detailed description of \textit{learning networks} \cite{MLJ2}
+%The introduction should briefly place the study in a broad context and highlight why it is important.
+It should define the purpose of the work and its significance.
+The current state of the research field should be reviewed carefully and key publications cited.
+Please highlight controversial and diverging hypotheses when necessary.
+Finally, briefly mention the main aim of the work and highlight the principal conclusions.
+As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
+Citing a journal paper \cite{ref-journal}.
+Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}.
+Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Materials and Methods}
-\subsection{Autonomous Collection and Processing of Hyperspectral Images}
 
-website for alta x \cite{freeflyAltaX}
+\subsection{Autonomous Robotic Team}
+\subsubsection{Autonomous Boat: In-situ Sensing}
+\subsubsection{Autonomous Drone: Rapid Hyperspectral Imaging}
 
 \begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/spectra/radiance.eps}
-\caption{Spectral Radiance collected from a single pixel of the HSI.\label{radiancePlot}}
+\includegraphics[width=\columnwidth]{paper/figures/materials-and-methods/annotated-drone.pdf}
+\caption{These are the components of the drone. \label{fig:drone-components}}
 \end{figure}
 
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/spectra/solar_irradiance.eps}
-\caption{Downwelling Irradiance captured via an upward facing spectrometer.\label{irradiancePlot}}
-\end{figure}
+\subsection{Data Collection}
+\subsection{Georectification of Hyperspectral Imagery}
 
 \begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/spectra/reflectance_rainbow.eps}
-\caption{Single pixel reflectance spectrum created by combining \ref{radiancePlot} with \ref{irradiancePlot}.\label{radiancePlot}}
-\end{figure}
-
-\begin{equation}
-    R = \pi \frac{L}{E}
-\end{equation}
-
-\subsection{Georectification}
-paper by Muller \cite{GeorectificationMuller} \\ 
-paper by Baumker \cite{GeorectificationBaumker} \\ 
-paper by Mostafa \cite{GeorectificationMostafa} \\
-
-NOTE: need to double check \cite{GeorectificationMuller} for convention used ($\Phi$ vs $\phi$)
-
-Heading correction due to longitude deviation in UTM system: 
-\begin{equation}
-    \kappa_{\text{geodetic}} = \kappa_{\text{geographic}}-\tan^{-1}\left( \sin\Phi \tan(\lambda-\lambda_{cm}) \right)
-\end{equation}
-
-scale factor: 
-\begin{equation}
-    s = \frac{z_{\text{sensor}}-z_{\text{ground}}}{f}
-\end{equation}
-
-\begin{equation}
-    \begin{pmatrix}
-    x \\ y \\ z
-    \end{pmatrix}_{\text{Object}}^{\text{UTM}} = 
-    f_{\text{geo}}^{\text{UTM}}\begin{pmatrix}
-    \lambda \\ 
-    \Phi \\ 
-    z
-    \end{pmatrix}_{\text{GPS}}^{\text{geo}} + sT_{\text{IMU}}^{\text{UTM}}R_{\text{sensor}}^{\text{IMU}}(\kappa, \phi, \omega)\begin{pmatrix}
-    0 \\ 
-    y_i \\ 
-    f
-    \end{pmatrix}_{\text{object}}^{\text{sensor}}
-\end{equation}
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/georectification/georectification.eps}
-\caption{Diagram of .\label{georectification1}}
-\end{figure}
-
-\subsection{In-situ Data Collection via Robotic Sentinels}
-
-autonomous boat website \cite{Otter}
-
-\subsubsection{data collection process}
-\subsubsection{Data Collocation}
-
-\subsubsection{CO}
-\subsubsection{CDOM}
-\subsubsection{HDO}
-\subsubsection{$Na^{+}$}
-\subsubsection{$Ca^{2+}$}
-\subsubsection{Other Targets}
-
-\subsubsection{Feature Engineering with Remote Sensing Indices}
-include discussion of PCA as well as Standardization
-
-\subsection{Exploratory Data Analysis}
-\subsubsection{Variable Correlations}
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/correlation/target_cor.png}
-\caption{Correlation Matrix for Target variables measured by the boat.\label{target_cor}}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/correlation/radiance_cor.png}
-\caption{Correlation Matrix for Radiance measurements versus Target Variables.\label{rad_cor}}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/correlation/reflectance_cor.png}
-\caption{Correlation Matrix for Reflectance measurements versus Target Variables.\label{ref_cor}}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/correlation/derived_cor.png}
-\caption{Correlation Matrix for derived measurements versus Target Variables.\label{derived_cor}}
-\end{figure}
-
-\subsubsection{Unsupervised Classification}
-\begin{figure}[H]
-\includegraphics[width=11 cm]{images/unsupervised/clustering.png}
-\caption{Unsupervised clustering of hyper-spectral image data using the K-means algorithm.\label{clustering}}
-\end{figure}
-
-\subsection{Machine Learning}
-
-\subsubsection{Machine Learning Models}
-include Linear Models, Neural Networks, Decision Trees, Bagging, Boosting, and Stacking\\
-
-The field of Machine Learning has seen the invention of a plethora of models able to perform inference for regression tasks.
-Naturally, this leads to the challenge of evaluating which model is best for a given problem.
-In 1992 David Wolpert developed the notion of Stacked Generalization to divorce arbitrary human choice from the model selection process.
-[1] The key idea is as follows: fit an instance of each model compatible with your dataset.
-Each model learns different features of the data so that an adjudicating model (called the super-learner) can then be trained to map the predictions from each individual learner to a final output prediction.
-This is incredibly easy to accomplish in the Julia programming language via the MLJ machine learning framework [2].
-We train a variety of learners including artificial neural networks, bagged decision trees, boosted decision trees, polynomial regressors, quantile regressors, LASSO regressors, and K-nearest-neighbors regressors.
-To ensure proper data hygiene, individual learners are first trained on separate cross validation folds so as not to bias the super-learner.
-After training the super-learner, each individual model is then trained on the full dataset to produce the best possible model.
-
-paper on stacking \cite{ModelStacking}
-
-\subsection{Model Analysis}
-aleatoric and epistemic uncertainty
-
-The black-box nature most machine learning methods makes it difficult to consider how errors propagate through a trained model during the inference process.
-For many problems such as image classification this is not an issue, however, in physical sensing error considerations are vital to establish detection limits and prediction confidence.
-Typically, there are three considerations we must make: measurement uncertainty– how much we can trust our model’s inputs, measurement representativeness– how well each data point represents data within a local neighborhood, and model error– how far the prediction is from the true value.
-Machine learning models are typically trained to minimize the model error.
-The Julia programming language makes it possible to handle all three.
-
-To address measurement uncertainty, we take advantage of Julia’s advanced automatic differentiation capabilities to enable differentiable programming (∂P).
-This means that we can take derivatives of our trained ML model with respect to each input feature to perform a sensitivity analysis.
-The final output uncertainty is then given via linear error propagation theory.
-[5]
-
-Measurement representativeness can be trickier to handle.
-For example, in fluids it is common for two species to form a mixing layer that presents as a sharp discontinuity in measurement values.
-To quantify the degree to which neighboring points diverge we compute the average deviation across input measurements in a neighborhood around each data sample.
-This information can then be presented with model outputs to identify the regions where our model is valid.
-Similarly for ensemble ML models we compute the prediction deviation across all base learners to identify the representativeness of a data sample.
-Inputs that cause a large spread in base learner predictions indicate low representativeness in the training set.
-This analysis can then be used to plan further data collection missions that minimize time spent collecting data we have already present in our models.
-
-\subsubsection{Uncertainty Propagation via ($\partial P$)}
-
-\subsubsection{Feature Ranking via SHAP values}
-
-shape value paper used in ShapML.jl \cite{SHAPvalues1}
-
-\subsubsection{Data Representativeness}
-i.e. the average deviation across pixels used average during collocation process.
-Also, we can look at relative disagreement between model predictions in bagged ensemble.
-
-\section{Results}
-\subsection{CO}
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/CO/CO_dataMap.png}
-\caption{Target distribution of CO at Scotty's Ranch.\label{CO_targetMap}}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/CO/CO_train-test_hist.png}
-\caption{Stratified train-test split for CO.\label{CO_trainTestHist}}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{images/CO/rfr_CO_qq.png}
-\caption{Quantile-Quantile plot for CO random forest fit. \label{CO_trainTestHist}}
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=15.5cm]{paper/figures/materials-and-methods/pipeline-figure-2.pdf}
+\end{adjustwidth}
+\caption{This is a wide figure.\label{fig:hsi-pipeline}}
 \end{figure}
@@
 \centering
-    \subfigure{\includegraphics[width=0.5\textwidth]{images/CO/rfr_CO_scatter.png}}\qquad
-    \subfigure{\includegraphics[width=0.5\textwidth]{images/CO/rfr_CO_qq.png}}
+\includegraphics[width=15.5cm]{paper/figures/materials-and-methods/HyperSpectralInfoGraphic.pdf}
 \end{adjustwidth}
-    \caption{(\textbf{a}) Scatterplot for the trained random forest Crudo Oil model. (\textbf{b}) Quantile-Quantile plot for the same fit.}
-    \label{CO_fitresult}
+\caption{This is a wide figure.\label{fig:hsi-infographic}}
 \end{figure}
 
+\subsection{Machine Learning}
+\subsubsection{Data Pre-processing and Feature Generation}
+Add a table of the Features we used here...
+\subsubsection{Models Employed}
+Discuss random forests
+\subsubsection{Hyperparameter Optimization}
+Discuss the parameters we optimize and the evaluation strategy using 10-fold cross validation.
+
+\subsection{Uncertainty Quantification via Conformal Prediction}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
+
+\subsection{Modeling Results}
+
+\begin{table}[H] 
+\caption{This is a table caption.\label{tab:fit-results}}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
+\begin{tabularx}{\textwidth}{CCCCCC}
+\toprule
+\textbf{Target (units)}	& \textbf{$\text{R}^2$}	& \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty (90\% CI)} & \textbf{Empirical Coverage (\%)}\\
+\midrule
+$\mathrm{Na}^+$     & 0.964 $\pm$ 0.006 & 8.10 $\pm$ 0.68 & 5.10 $\pm$ 0.26 & 11.7 & 88.5 \\
+Dissolved Oxygen    & 0.958 $\pm$ 0.005 & 0.119 $\pm$  & 5.10 $\pm$ 0.26 & 11.7 & 88.5 \\
+\bottomrule
+\end{tabularx}
+\end{table}
+
+\subsection{Mapping}
+
+This section may be divided by subheadings.
+It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
+\subsection{Subsection}
+\subsubsection{Subsubsection}
+
+Bulleted lists look like this:
+\begin{itemize}
+\item	First bullet;
+\item	Second bullet;
+\item	Third bullet.
+\end{itemize}
+
+Numbered lists can be added as follows:
+\begin{enumerate}
+\item	First item; 
+\item	Second item;
+\item	Third item.
+\end{enumerate}
+
+The text continues here.
+
+\subsection{Figures, Tables and Schemes}
+
+All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.
+
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{images/CO/rfr_CO_featureImportance.png}
-    \caption{Ranked feature importance for Crude Oil. Importance is determined via mean absolute SHAP value. \label{CO_shapely}}
+\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
+\caption{This is a figure.
+Schemes follow the same formatting.
+If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
+(\textbf{b}) Description of what is contained in the second panel.
+Figures should be placed in the main text near to the first time they are cited.
+A caption on a single line should be centered.\label{fig1}}
+\end{figure}   
+\unskip
+
+\begin{table}[H] 
+\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
+\begin{tabularx}{\textwidth}{CCC}
+\toprule
+\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
+\midrule
+Entry 1		& Data			& Data\\
+Entry 2		& Data			& Data \textsuperscript{1}\\
+\bottomrule
+\end{tabularx}
+\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
+\end{table}
+
+The text continues here (Figure~\ref{fig2} and Table~\ref{tab2}).
+
+% Example of a figure that spans the whole page width. The same concept works for tables, too.
+\begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=15.5cm]{Definitions/logo-mdpi}
+\end{adjustwidth}
+\caption{This is a wide figure.\label{fig2}}
 \end{figure}
 
+\begin{table}[H]
+\caption{This is a wide table.\label{tab2}}
+	\begin{adjustwidth}{-\extralength}{0cm}
+		\newcolumntype{C}{>{\centering\arraybackslash}X}
+		\begin{tabularx}{\fulllength}{CCCC}
+			\toprule
+			\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}     & \textbf{Title 4}\\
+			\midrule
+\multirow[m]{3}{*}{Entry 1 *}	& Data			& Data			& Data\\
+			  	                   & Data			& Data			& Data\\
+			             	      & Data			& Data			& Data\\
+                   \midrule
+\multirow[m]{3}{*}{Entry 2}    & Data			& Data			& Data\\
+			  	                  & Data			& Data			& Data\\
+			             	     & Data			& Data			& Data\\
+                   \midrule
+\multirow[m]{3}{*}{Entry 3}    & Data			& Data			& Data\\
+			  	                 & Data			& Data			& Data\\
+			             	    & Data			& Data			& Data\\
+                  \midrule
+\multirow[m]{3}{*}{Entry 4}   & Data			& Data			& Data\\
+			  	                 & Data			& Data			& Data\\
+			             	    & Data			& Data			& Data\\
+			\bottomrule
+		\end{tabularx}
+	\end{adjustwidth}
+	\noindent{\footnotesize{* Tables may have a footer.}}
+\end{table}
+
+%\begin{listing}[H]
+%\caption{Title of the listing}
+%\rule{\columnwidth}{1pt}
+%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
+%\rule{\columnwidth}{1pt}
+%\end{listing}
+
+Text.
+
+Text.
+
+\subsection{Formatting of Mathematical Components}
+
+This is the example 1 of equation:
+\begin{linenomath}
+\begin{equation}
+a = 1,
+\end{equation}
+\end{linenomath}
+the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
+%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
+This ensures correct linenumbering.
+The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
+
+This is the example 2 of equation:
+\begin{adjustwidth}{-\extralength}{0cm}
+\begin{equation}
+a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
+\end{equation}
+\end{adjustwidth}
+
+% Example of a page in landscape format (with table and table footnote).
+%\startlandscape
+%\begin{table}[H] %% Table in wide page
+%\caption{This is a very wide table.\label{tab3}}
+%	\begin{tabularx}{\textwidth}{CCCC}
+%		\toprule
+%		\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}	& \textbf{Title 4}\\
+%		\midrule
+%		Entry 1		& Data			& Data			& This cell has some longer content that runs over two lines.\\
+%		Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
+%		\bottomrule
+%	\end{tabularx}
+%	\begin{adjustwidth}{+\extralength}{0cm}
+%		\noindent\footnotesize{\textsuperscript{1} This is a table footnote.}
+%	\end{adjustwidth}
+%\end{table}
+%\finishlandscape
+
+Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
+%% Example of a theorem:
+\begin{Theorem}
+Example text of a theorem.
+\end{Theorem}
+
+The text continues here. Proofs must be formatted as follows:
+
+%% Example of a proof:
+\begin{proof}[Proof of Theorem 1]
+Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
+\end{proof}
+The text continues here.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion}
-\subsection{For-deployment Models}
-\subsubsection{Random Forests}
 
-\subsection{Limitations}
-discuss viewing geometry and time of day
+Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
+The findings and their implications should be discussed in the broadest context possible.
+Future research directions may also be highlighted.
 
-\subsection{Extensions and Future Work}
-\subsubsection{Physics-informed machine learning}
-\subsubsection{Data Augmentation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusions}
 
-\section{Conclusions}
+This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Patents}
+
+This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
 
@@
 % References, variant A: external bibliography
-% =====================================
-\bibliography{references}
+%=====================================
+%\bibliography{your_external_BibTeX_file}
+
+%=====================================
+% References, variant B: internal bibliography
+%=====================================
+\begin{thebibliography}{999}
+% Reference 1
+\bibitem[Author1(year)]{ref-journal}
+Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
+% Reference 2
+\bibitem[Author2(year)]{ref-book1}
+Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
+% Reference 3
+\bibitem[Author3(year)]{ref-book2}
+Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
+% Reference 4
+\bibitem[Author4(year)]{ref-unpublish}
+Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
+% Reference 5
+\bibitem[Author5(year)]{ref-communication}
+Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
+% Reference 6
+\bibitem[Author6(year)]{ref-proceeding}
+Author 1, A.B.; Author 2, C.D.; Author 3, E.F.
+Title of presentation.
+In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
+% Reference 7
+\bibitem[Author7(year)]{ref-thesis}
+Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
+% Reference 8
+\bibitem[Author8(year)]{ref-url}
+Title of Site. Available online: URL (accessed on Day Month Year).
+\end{thebibliography}
 

### 2023-12-27 1_make-datasets.jl
added latex output and turned maps back to jet to please Dr Lary

@@ -53,7 +53,9 @@ end
 
 inpaths = Dict(
     "11-23" => "/Users/johnwaczak/data/robot-team/finalized/11-23",
-    "Full" => "/Users/johnwaczak/data/robot-team/finalized/Full"
+    "Full" => "/Users/johnwaczak/data/robot-team/finalized/Full",
+    "12-09" => "/Users/johnwaczak/data/robot-team/finalized/12-09",
+    "12-10" => "/Users/johnwaczak/data/robot-team/finalized/12-10",
 )
 
 # inpath = "/Volumes/LabData/RobotTeam/finalized/Full"
@@ -203,8 +205,8 @@ function make_datasets(data, target, feature_names, target_names, ignorecols)
 end
 
 
-data, feature_names, target_names, ignorecols = get_data(inpaths["11-23"])
-(y,X) = make_datasets(data, "CDOM", feature_names, target_names, ignorecols)
+# data, feature_names, target_names, ignorecols = get_data(inpaths["11-23"])
+# (y,X) = make_datasets(data, "CDOM", feature_names, target_names, ignorecols)
 
 
 for (collection, fpath) in inpaths

### 2023-12-27 3_feature-exploration.jl

@@ -83,17 +83,17 @@ use_metrics = false
 #nnr_mod = NNR(builder=MLJFlux.MLP(hidden=(50,50,50,50,50), σ=Flux.relu)
 # nnr_mod = NNR(builder=MLJFlux.MLP(hidden=(50,50,50,50), σ=Flux.relu)
 
-opt = Flux.Optimise.ADAM()
-# match sklearn.MLPRegressor default parameters
-nnr_mod = NNR(
-    builder=MLJFlux.MLP(hidden=(100,), σ=Flux.relu),
-    batch_size=200,
-    optimiser=Flux.Optimise.ADAM(0.001),
-    lambda = 0.0,
-    alpha = 0.0001,
-    rng=rng,
-    epochs=500,
-)
+# opt = Flux.Optimise.ADAM()
+# # match sklearn.MLPRegressor default parameters
+# nnr_mod = NNR(
+#     builder=MLJFlux.MLP(hidden=(100,), σ=Flux.relu),
+#     batch_size=200,
+#     optimiser=Flux.Optimise.ADAM(0.001),
+#     lambda = 0.0,
+#     alpha = 0.0001,
+#     rng=rng,
+#     epochs=500,
+# )
 
 # nnr_mod = NNR(
 # #     builder=MLJFlux.Short(n_hidden=250, dropout=0.1, σ=Flux.relu),
@@ -129,12 +129,13 @@ nnr_mod = NNR(
 #                  :mdl=>XGBR(),
 #                  )
 
-# MODELS[:etr] = (;
-#                 :longname=>"Evo Tree Regressor",
-#                 :savename=>"EvoTreeRegressor",
-#                 :packagename => "EvoTrees",
-#                 :mdl => ETR(nrounds=100, nbins=255, eta=0.3, max_depth=6, lambda=1.0, alpha=0.0),
-#                 )
+MODELS[:etr] = (;
+                :longname=>"Evo Tree Regressor",
+                :savename=>"EvoTreeRegressor",
+                :packagename => "EvoTrees",
+                :suffix => "vanilla",
+                :mdl => ETR(nrounds=100, nbins=255, eta=0.3, max_depth=6, lambda=1.0, alpha=0.0),
+                )
 
 
 # MODELS[:dtr] = (;
@@ -307,14 +308,89 @@ function make_summary_table(collection, savename, suffix)
 end
 
 
+
+function generate_tex_table(df)
[…]

### 2023-12-27 3b_make-maps.jl

@@ -24,7 +24,6 @@ cmk.update_theme!(
 
 
 Δx = 0.1
-suffix = "hpo1"
 
 include("./config.jl")
 include("./viz.jl")
@@ -50,22 +49,11 @@ e= -97.712413
 satmap = get_background_satmap(w,e,s,n)
 
 
-# set up relevant paths
-collection = "11-23"
-hsi_11_23 = joinpath(hsipath, collection)
-flight = "Scotty_2"
-scotty_2 = joinpath(hsi_11_23, flight)
-
-h5_files = [joinpath(scotty_2, f) for f in readdir(scotty_2) if endswith(f, ".h5")]
-
 # let's add a function to sort them into numerical order
 function sort_files_numerical!(flist)
     idx_sort = sortperm([lpad(split(s[1], "-")[end], 2, "0") for s in split.(flist, ".")])
     flist .= flist[idx_sort]
 end
-
-sort_files_numerical!(h5_files)
-
 
 
 # let's open one and extract the data
@@ -74,7 +62,6 @@ function in_water(Datacube, varnames; threshold=0.25)
     idx_mndwi = findfirst(varnames .== "mNDWI")
     return findall(Datacube[idx_mndwi,:,:] .> threshold)
 end
-
 
 
 function get_data_for_pred(h5path, col_names)
@@ -95,50 +82,67 @@ function get_data_for_pred(h5path, col_names)
     ij_water = in_water(Data, varnames)
 
     Data_pred = Data[:, ij_water]
-    X_hsi = Tables.table(Data_pred', header=names(X))
+    X_hsi = Tables.table(Data_pred', header=col_names)
 
     return X_hsi, Y, ij_water, Latitudes, Longitudes
 end
 
 
 RFR = @load RandomForestRegressor pkg=DecisionTree
-model = "RandomForestRegressor"
-model_collections = ["11-23", "Full"]
-suffixes = ["vanilla", "hpo1", "hpo2"]
+ETR = @load EvoTreeRegressor pkg=EvoTrees
 
-targets_to_map = [t for t in Symbol.(keys(targets_dict)) if !(t in [:TDS, :Salinity3490, :bg, :Br, :NH4, :Turb3488, :Turb3490])]
+model_collections = ["Full"]
+# suffixes = ["vanilla", "hpo1", "hpo2", "vanilla"]
[…]

### 2023-12-27 3c_extra-plots.jl

@@ -1,0 +1,30 @@
+using HDF5, CSV, DataFrames, JSON, Tables
+using MLJ, ConformalPrediction
+using Random, Statistics
+using ProgressMeter
+
+import CairoMakie as cmk
+using MintsMakieRecipes
+
+cmk.set_theme!(mints_theme)
+cmk.update_theme!(
+    figure_padding=30,
+    Axis=(
+        xticklabelsize=20,
+        yticklabelsize=20,
+        xlabelsize=22,
+        ylabelsize=22,
+        titlesize=25,
+    ),
+    Colorbar=(
+        ticklabelsize=20,
+        labelsize=22
+    )
+)
+
+
+include("./config.jl")
+include("./viz.jl")
+include("./sat-viz.jl")
+
+

### 2023-12-27 config.jl

@@ -38,6 +38,45 @@ targets_dict = Dict(
 )
 
 
+
+using LaTeXStrings
+
+targets_latex= Dict(
+    :Br => L"$\mathrm{Br}^-$ (mg/l)",
+    :CDOM => "CDOM (ppb)",
+    :CO => "Crude Oil (ppb)",
+    :Ca => L"$\mathrm{Ca}^{2+}$ (mg/l)",
+    :Chl => L"Chlorophyll A ($\mu$g/l)",
+    :ChlRed => L"Chlorophyll A with Red Excitation ($\mu$g/l)",
+    :Cl => L"$\mathrm{Cl^-}$ (mg/l)",
+    :HDO => "Dissolved Oxygen (mg/l)",
+    :HDO_percent => "Dissolved Oxygen (\\% Sat)",
+    :NH4 => L"\mathrm{NH_4^+} (mg/l-N)",
+    :NO3 => L"\mathrm{NO_3^-} (mg/l-N)",
+    :Na => L"\mathrm{Na^+} (mg/l)",
+    :OB => "Optical Brighteners (ppb)",
+    :RefFuel => "Refined Fuels (ppb)",
+    :Salinity3488 => "Salinity (PSS)",
+    :Salinity3490 => "Salinity (PSS)",
+    :SpCond => L"Conductivity ($\mu$S/cm)",
+    :TDS => "Total Dissolved Solids (mg/l)",
+    :TRYP => "Tryptophan (ppb)",
+    :Temp3488 => "Temperature (°C)",
+    :Temp3489 => "Temperature (°C)",
+    :Temp3490 => "Temperature (°C)",
+    :Turb3489 => "Turbidity (FNU)",
+    :Turb3488 => "Turbidity (FNU)",
+    :Turb3490 => "Turbidity (FNU)",
+    :bg => "Blue-Green Algae [Phycocyanin] (ppb)",
+    :bgm => "Blue-Green Algae [Phycoerythrin] (ppb)",
+    :pH => "pH",
+    :pH_mV => "pH (mV)",
+)
+
+
+
+
+
 # wavelength bins used by sensor
[…]

### 2023-12-27 paper/paper.tex
Updates from Overleaf

@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{\textcolor{red}{A single paragraph of about 200 words maximum.
+\abstract{\textcolor{red}{Advances in hyperspectral imaging technology are enabling significant improvements in the spectral resolution of remote sensing data products with a plethora of new satellites either in development or soon to be launched.
+Utilizing hyperspectral data for environmental assessment requires high quality in-situ data that is both difficult to collect and difficult to align with remote sensing data products due to orbital-dependent revisit times and occlusion by weather and cloud cover.
+In this study, present the results of a series of surveys.}}
+
+% A robust characterization of model uncertainties is critical for any time-sensitive or dangerous application...To that end we employ a combination of model stacking together with Conformal Prediction by which we are able to blend together a variety of ML models while simultaneously estimating confidence intervals for the resulting predictions.
+
+% A single paragraph of about 200 words maximum.
 For research articles, abstracts should give a pertinent overview of the work.
 We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusions: indicate the main conclusions or interpretations.
-The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}}
+The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions
 
 % Keywords
-\keyword{\textcolor{red}{keyword 1; keyword 2; keyword 3 (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}}
+\keyword{\textcolor{red}{Hyperspectral Imaging; Machine Learning; Robotic Teams; UAV;}}
 
@@
 \section{Introduction}
+
+- First sentence about amount of remote sensing data generated per year w/ citation and a forecast for how much it will increase. 
+- Second sentence about the lack of in-situ reference data (this is the limitation we can fill) 
+- Further limitations of current remote sensing data products (spectral resolution, spatial resolution, observation frequency)
+- Discuss newly launched and and soon-to-be-launched satellites with HSI capabilities
+- Discuss use of multi-sepctral imagery for environmental studies
+    - Generation of spectral indices like the NDVI and others which have shown to be helpful for environmental characterization
+    - Cite David's previous CDOM paper that used the Atlantic shipping data.
+- Discuss use of ML in remote sensing/environmental assessment applications.
+Here, the possibilities are limited by the availability of high-quality reference data which is why many remote sensing ML models employ unsupervised methods to enable pixel classification (i.e.
+surface type, cloudiness fraction, etc...)
+- Outline need for in-situ reference data to calibrate HSI data products
+- Autonomous teams are perfect for this application due to their transportability, rapid deployment, and elastic configuration
+- Give examples of drone use for smart agriculture, etc... 
+- Give examples of autonomous boat use for water studies, cleanup, etc... 
+- Describe our work to create a robotic team which can do all of this...
+
+% https://gisgeography.com/hyperspectral-imaging/
+% https://hyperspectral.azavea.com/
+% https://sentinels.copernicus.eu/web/sentinel/user-guides/sentinel-1-sar/document-library/-/asset_publisher/1dO7RF5fJMbd/content/sentinel-high-level-operations-plan  <-- for amount of data produced by sentinel
+The main areas of usage for hyperspectral imagery can be categorized into 8 groups. This includes vegetation, agriculture, geology, soil, water resources, disaster, and land use.
+
+The underlying principle is that it improves any type of classification.
+For example, you can get more detail for geologic surface composition.
+The same is true for vegetation types, soil classes, and land cover too.
+
+Hyperspectral imaging helps identify pests for crop management.
+Water resources are about understanding bathymetry, water quality, and chemistry.
+And it’s been used for disaster management such as prevention and post-monitoring
+
+Step 1: Introduce your topic
+Step 2: Describe the background
+Step 3: Establish your research problem
+Step 4: Specify your objective(s)
+Step 5: Map out your paper
+
+The introduction should answer three important questions:
+1. What am I writing about?
+2. Why is it important?
+3. What do I want the reader to know about it?
+
+Step 1: Establish a Territory
+"In recent years..." or "researchers have become interested..."
+
+Step 2: Establish a Niche
+- Identify a gap that your research fills
+
+In (cite last robot team paper) we outlined a paradigmatic approach to the generation of remote sensing data sets for water-based environmental studies by employing a coordinated team of autonomous sensing sentinels.
+In this paper, we demonstrate the use of this platform across multiple observation periods...
 
@@
 Add a table of the Features we used here...
+
+\begin{table}[H]
+  \caption{Dervied spectral indices used as additional model filters. \label{tab:spectral-features}}
+  \begin{adjustwidth}{-\extralength}{0cm}
+  \newcolumntype{C}{>{\centering\arraybackslash}X}
+  \begin{tabularx}{\fulllength}{CCCCCC}
+    \toprule
+    \textbf{Target (units)} & \textbf{$\text{R}^2$} & \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty} & \textbf{Empirical Coverage (\%)}\\
+    \midrule
+    Temperature (°C) & 0.999 ± 5.1e-5 & 0.0546 ± 0.0022 & 0.0316 ± 0.0015 & ± 0.084 & 89.7\\
+    \midrule
+    Conductivity ($\mu$S/cm) & 0.999 ± 0.00011 & 0.888 ± 0.067 & 0.497 ± 0.025 & ± 1.3 & 91.5\\
+    \midrule
+    $\mathrm{Ca}^{2+}$ (mg/l) & 0.999 ± 0.00031 & 0.544 ± 0.058 & 0.267 ± 0.013 & ± 0.72 & 89.9\\
+    \midrule
+    Dissolved Oxygen (mg/l) & 0.998 ± 0.00015 & 0.0931 ± 0.004 & 0.055 ± 0.0022 & ± 0.14 & 88.5\\
+    \midrule
+    Salinity (PSS) & 0.995 ± 0.00061 & 0.00124 ± 6.2e-5 & 0.000432 ± 2.6e-5 & ± 0.0009 & 90.1\\
+    \midrule
+    Tryptophan (ppb) & 0.99 ± 0.0046 & 0.206 ± 0.046 & 0.117 ± 0.0085 & ± 0.28 & 89.0\\
+    \midrule
+    pH & 0.988 ± 0.0018 & 0.0232 ± 0.0019 & 0.0119 ± 0.00045 & ± 0.032 & 92.5\\
+    \midrule
+    $\mathrm{Na^+} (mg/l)$ & 0.982 ± 0.0034 & 9.01 ± 0.88 & 4.17 ± 0.22 & ± 11.0 & 90.8\\
+    \midrule
+    $\mathrm{Cl^-}$ (mg/l) & 0.982 ± 0.0054 & 1.96 ± 0.28 & 1.0 ± 0.066 & ± 2.3 & 89.7\\
+    \midrule
+    Blue-Green Algae [Phycoerythrin] (ppb) & 0.939 ± 0.017 & 3.12 ± 0.43 & 0.84 ± 0.065 & ± 1.8 & 91.4\\
+    \midrule
+    CDOM (ppb) & 0.934 ± 0.02 & 0.58 ± 0.093 & 0.219 ± 0.013 & ± 0.46 & 90.3\\
+    \midrule
+    Optical Brighteners (ppb) & 0.92 ± 0.015 & 0.11 ± 0.0092 & 0.0617 ± 0.0019 & ± 0.13 & 92.4\\
+    \midrule
+    $\mathrm{NO_3^-} (mg/l-N)$ & 0.89 ± 0.013 & 0.0575 ± 0.0036 & 0.0353 ± 0.00091 & ± 0.079 & 90.7\\
+    \midrule
+    Crude Oil (ppb) & 0.89 ± 0.037 & 0.55 ± 0.11 & 0.174 ± 0.019 & ± 0.3 & 89.2\\
+    \bottomrule
+  \end{tabularx}
+  \end{adjustwidth}
+\end{table}
+
 \subsubsection{Models Employed}
@@
 \begin{table}[H]
-\caption{This is a table caption.\label{tab:fit-results}}
+  \caption{Summary of fitting statistics for each target measurement.
+Values were evaluated using 10-fold cross validation on the training set.
+The estimated uncertainty is evaluated using conformal prediction so that a prediction $\hat{y}\pm \Delta y$ achieves 90\% coverage on the validation holdout set.
+The empirical coverage is the percentage of predictions in the holdout testing set that fall within the confidence interval determined by conformal prediction.
+\label{tab:fit-results}}
+  \begin{adjustwidth}{-\extralength}{0cm}
   \newcolumntype{C}{>{\centering\arraybackslash}X}
-\begin{tabularx}{\textwidth}{CCCCCC}
+  \begin{tabularx}{\fulllength}{CCCCCC}
     \toprule
-\textbf{Target (units)}	& \textbf{$\text{R}^2$}	& \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty (90\% CI)} & \textbf{Empirical Coverage (\%)}\\
+    \textbf{Target (units)} & \textbf{$\text{R}^2$} & \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty} & \textbf{Empirical Coverage (\%)}\\
     \midrule
-$\mathrm{Na}^+$     & 0.964 $\pm$ 0.006 & 8.10 $\pm$ 0.68 & 5.10 $\pm$ 0.26 & 11.7 & 88.5 \\
-Dissolved Oxygen    & 0.958 $\pm$ 0.005 & 0.119 $\pm$  & 5.10 $\pm$ 0.26 & 11.7 & 88.5 \\
+    Temperature (°C) & 0.999 ± 5.1e-5 & 0.0546 ± 0.0022 & 0.0316 ± 0.0015 & ± 0.084 & 89.7\\
+    \midrule
+    Conductivity ($\mu$S/cm) & 0.999 ± 0.00011 & 0.888 ± 0.067 & 0.497 ± 0.025 & ± 1.3 & 91.5\\
+    \midrule
+    $\mathrm{Ca}^{2+}$ (mg/l) & 0.999 ± 0.00031 & 0.544 ± 0.058 & 0.267 ± 0.013 & ± 0.72 & 89.9\\
+    \midrule
+    Dissolved Oxygen (mg/l) & 0.998 ± 0.00015 & 0.0931 ± 0.004 & 0.055 ± 0.0022 & ± 0.14 & 88.5\\
+    \midrule
+    Salinity (PSS) & 0.995 ± 0.00061 & 0.00124 ± 6.2e-5 & 0.000432 ± 2.6e-5 & ± 0.0009 & 90.1\\
+    \midrule
+    Tryptophan (ppb) & 0.99 ± 0.0046 & 0.206 ± 0.046 & 0.117 ± 0.0085 & ± 0.28 & 89.0\\
+    \midrule
+    pH & 0.988 ± 0.0018 & 0.0232 ± 0.0019 & 0.0119 ± 0.00045 & ± 0.032 & 92.5\\
+    \midrule
+    $\mathrm{Na^+} (mg/l)$ & 0.982 ± 0.0034 & 9.01 ± 0.88 & 4.17 ± 0.22 & ± 11.0 & 90.8\\
+    \midrule
+    $\mathrm{Cl^-}$ (mg/l) & 0.982 ± 0.0054 & 1.96 ± 0.28 & 1.0 ± 0.066 & ± 2.3 & 89.7\\
+    \midrule
+    Blue-Green Algae [Phycoerythrin] (ppb) & 0.939 ± 0.017 & 3.12 ± 0.43 & 0.84 ± 0.065 & ± 1.8 & 91.4\\
+    \midrule
+    CDOM (ppb) & 0.934 ± 0.02 & 0.58 ± 0.093 & 0.219 ± 0.013 & ± 0.46 & 90.3\\
+    \midrule
+    Optical Brighteners (ppb) & 0.92 ± 0.015 & 0.11 ± 0.0092 & 0.0617 ± 0.0019 & ± 0.13 & 92.4\\
+    \midrule
+    $\mathrm{NO_3^-} (mg/l-N)$ & 0.89 ± 0.013 & 0.0575 ± 0.0036 & 0.0353 ± 0.00091 & ± 0.079 & 90.7\\
+    \midrule
+    Crude Oil (ppb) & 0.89 ± 0.037 & 0.55 ± 0.11 & 0.174 ± 0.019 & ± 0.3 & 89.2\\
     \bottomrule
   \end{tabularx}
+  \end{adjustwidth}
 \end{table}

### 2023-12-28 paper/paper.tex
Updating paper methods section

@@
 % Full title of the paper (Capitalized)
-\Title{\textcolor{red}{Robot Team II: Electric Boogaloo}}
+\Title{\textcolor{red}{Leveraging Machine Learning to Characterize Aquatic Environments with an Autonomous Team of Sensing Sentinels }}
 
@@
 % Authors, for the paper (add full first names)
-\Author{John Waczak$^{\dagger}$\orcidA{}, Adam Aker, Lakitha O. H. Wijeratne, Shawhin Talebi, Bharana Fernando, David Schaefer, David J. Lary, $^{\dagger}$\orcidB{}*}
+\Author{John Waczak$^{\dagger}$\orcidA{}, Adam Aker, Lakitha O.
+H.
+Wijeratne, Shawhin Talebi, Bharana Fernando, Prabuddha Hathurusinghe, Mazhar Iqbal, David Schaefer, David J.
+Lary, $^{\dagger}$\orcidB{}*}
 
@@
 
+Each day over X terabytes of remote sensing data are collected fr
+
+Context
+
+Need
+
+Task
+
+Objective
+
 - First sentence about amount of remote sensing data generated per year w/ citation and a forecast for how much it will increase. 
@@
 
+\\
+
+In-situ measurements are expensive to collect and suffer from poor spatial coverage.
+Remote sensing data cover much wider areas but do not directly provide parameters needed for environmental assessments.
+Additionally, remote sensing data, particularly satellite based imagers, also suffer from long orbit-dependent site revisit times and can be easily occluded by the presence of clouds.
+This makes it incredibly challenging to collocate sufficient quantities of in-situ measurements with overlapping remote sensing imagery to enable their calibration.
+\textcolor{red}{(add reference to David's CDOM paper here...)}.
+To address this gap, we have developed an autonomous team of sensing sentinels combining a mobile uncrewed surface vessel (USV) with a unmanned aerial vehicle (UAV) which together rapidly collect hyperspectral imgaery \textit{and} comprehensive in-situ measurements to enable the estimation of key environmental parameters including concentrations of key constituents like CDOM, Crude Oils, Ions,as well as physical parameters like temperature, salinity, and dissolved oxygen.
+In our previous work we established a methodology for calibrating the hyperspectral imagery against reference measurements during a collection window \cite{robotTeam1}.
+In his study, we demonstrate that such models can be reliably trained using data collected from multiple observations....
+
 %The introduction should briefly place the study in a broad context and highlight why it is important.
@@
 
-\subsection{Autonomous Robotic Team}
-\subsubsection{Autonomous Boat: In-situ Sensing}
-\subsubsection{Autonomous Drone: Rapid Hyperspectral Imaging}
+In the study we employ a team of autonomous sensing sentinels, herein referred to as \textit{the robot team}, to enable the rapid characterization of aquatic environments.
+This team consists of two key sensing sentinels: An uncrewed surface vessel (USV) used to collect in-situ reference measurements, and an unmanned aerial vehicle (UAV) for performing rapid, wide-area surveys to gather remote sensing data products.
+Both platforms are coordinated using the open-source QGroundControl software for flight control and mission planning \cite{qgroundcontrol} and are equipped with high accuracy GPS and INS such that all collected data points are uniquely geolocated and time-stamped.
+Both the USV and UAV are equipped with long-range Ubiquiti 5 GHz LiteBeam airMAX WiFi to enable streaming of data products to a ground station with network attached storage providing redundancy.
+
+\subsection{USV: In-situ Measurements}
+
+The USV employed in the robot team is the Maritime Robotics Otter which features a flexible modular design and 20 hour battery life.
+The USV is equipped with an in-situ sensing payload utilizing a combination of Eureka Manta-40 multi-probes including fluorometers, ion selective electrodes, and other physical sensors which together enable the collection of comprehensive near-surface measurements including Colored Dissolved Organic Matter (CDOM), Crude Oil, Blue-Green Algae (phycoerythrin and phycocyanin), Chlorophyll-A, Tryptophan, $\mathrm{Na^+}$, $\mathrm{Ca^{2+}}$, $\mathrm{Cl^-}$, Temperature, Conductivity, and many others.
+The full list of measurements used in this study is given in Table~\ref{tab:fit-results}.
+Additionally, the USV is equipped with an ultra-sonic weather monitoring sensor for measuring air speed and direction as well as a a BioSonics MX Aquatic Habitat Echosounder sonar which are not utilized in this study.
+
+\subsection{UAV: Hyperspectral remote sensing}
+
+A Freefly Alta-X autonomous professional quad-copter was used as the UAV platform for the robotic team.
+The Alta-X is specifically designed to carry cameras featuring a payload of up to 35 lbs.
+We have equipped the UAV with a Resonon Pika XC2 Visible+Near-Infrared (VNIR) hyperspectral imager.
+For each image pixel, this camera samples 462 wavelengths ranging from 391 to 1,011 nm.
+Additionally, the UAV includes an upward facing Ocean Optics UV-Vis-NIR spectrometer with a cosine corrector to capture the incident downwelling irradiance spectrum.
+Data collection by the hyperspectral imager is controlled by an attached Intel NUC small-form-factor computer.
+A second \textit{processing} NUC is also included for onboard georectification and generation of data products.
+The collected hyperspectral images (HSI) are stored locally on a solid state drive which is simultaneously mounted by the processing computer.
+The configuration of the drone is shown in shown in Figure~\ref{fig:drone-components}.
 
@@
 \includegraphics[width=\columnwidth]{paper/figures/materials-and-methods/annotated-drone.pdf}
-\caption{These are the components of the drone. \label{fig:drone-components}}
+\caption{Configuration of the UAV: (\textbf{a}) the hyperspectral imager and acquisition computer.
+(\textbf{b}) the assembled UAV with secondary processing computer and (upward facing) downwelling irradiance spectrometer.
+\label{fig:drone-components}}
 \end{figure}
@@
 \subsection{Data Collection}
-\subsection{Georectification of Hyperspectral Imagery}
+
+For this study data were collected using the robot team at a site in north Texas across three observation periods in November and December of 2020.
+For each collection period the UAV first completed a wide survey of the lake capturing raw hyperspectral data cubes, downwelling irradiance spectra, and relevant position and orientation flight data.
+Subsequently, the the USV sampled across the lake, collecting in-situ reference measurements.
+These combined data form the basis from which we seek to develop machine learning models translating the UAV captured spectra into the target quantities as measured by the USV.
+To enable this modality, we must establish the processing procedure by which we account for the variability of the incident light illuminating the pond and transform the raw hyperspectral data cubes from their native \textit{imaging reference frame} to a chosen coordinate system compatible with the data collected by the USV.
+This procedure is illustrated in Figure~\ref{fig:hsi-pipeline}.
 
@@
 \centering
-\includegraphics[width=15.5cm]{paper/figures/materials-and-methods/pipeline-figure-2.pdf}
+\includegraphics[width=16cm]{paper/figures/materials-and-methods/pipeline-figure-2.pdf}
 \end{adjustwidth}
-\caption{This is a wide figure.\label{fig:hsi-pipeline}}
+\caption{Hyperspectral Image Processing: Hyperspectral datacubes are collected one scan-line at a time (left).
+By utilizing downwelling irradiance spectra we convert each pixel from spectral radiance to reflectance.
+By using orientation and position data from the on-board GPS and INS, we georeference each pixel to assign it a latitude and longitude on the ground.
+The final data product is a georectified hyperspectral reflectance data cube visualized at the right.
+\label{fig:hsi-pipeline}}
 \end{figure}
+
+The hyperspectral imager utilized in our robot team is in a so-called \textit{pushbroom} configuration, that is, each image captured by the drone is formed one scan-line at a time as the UAV flies.
+Each scan-line consists of 1600 pixels for which incoming light is diffracted into 462 wavelength bins.
+In the collection software a regular cutoff of 1000 lines is chosen so that each resulting \textit{image} forms a tensor of size 462$\times$1600$\times$1000 called a \textit{hyperspectral data cube}.
+Initially, the sampled spectra are in units of spectral radiance (measured in microflicks) however this does not account for the variability of incident light illuminating the water.
+To this end, we convert the hyperspectral data cubes into units of reflectance by utilizing the skyward-facing downwelling irradiance spectrometer (see Figure~\ref{fig:drone-components}).
+When our camera is normal to this surface, then the reflectance is given by
+\begin{equation}
+    R(\lambda) = \pi L(\lambda)/E(\lambda)
+\end{equation}
+where $L$ is the spectral radiance, $E$ is the downwelling irradiance, and a factor of $\pi$ steradians assumes the surface is Lambertian (diffuse) \cite{reflectance-conversion}.
+
+Having converted the hyperspectral data cube to units of reflectance, we must also georeference each pixel into geographic coordinate system so that each image pixel can be assigned a latitude and longitude cooresponding to the location on the ground from which it was sampled.
+During our three surveys, the UAV was flown at an altitude of ~50 m above the water.
+At this scale, the surface is essentially flat so that the hyperspectral datacube can be reliably georectified without the added need for a digital elevation map (DEM).
+We adopt the approach outlined in \cite{GeorectificationMuller, GeorectificationBaumker, GeorectificationMostafa} whereby each scanline is georeferenced using the known field of view (30.8 $\deg$) together with the position and orientation of the UAV as provided by the on-board GPS/INS.
+The resulting image is then re-sampled to a final output resolution.
+For these collections a resolution of 10 cm was utilized however this can be increased to reduce the processing time for real-time applications.
+The final result is a georectified hyperspectral reflectance data cube.
+In Figure~\ref{fig:hsi-infographic} we visualize one such data cube, highlighting a selection of exemplar pixel spectra from the scene as well as the incident downweling irradiance spectrum.
+A pseudo-color image is generated (plotted on the top of the datacube) to illustrate the scene.
 
@@
 \end{adjustwidth}
-\caption{This is a wide figure.\label{fig:hsi-infographic}}
+\caption{A georectified reflectance data cube is visualized (center) with the $\log10$-reflectance along the z axis and a pseudo-color image on the top.
+In the top left we visualize the downwelling irradiance spectrum (the incident light).
+The surrounding plots showcase exemplar pixel reflectance spectra for open water, dry grass, algae, and a rhodamine dye plume used to test the system.\label{fig:hsi-infographic}}
 \end{figure}
 
-\subsection{Machine Learning}
+\subsection{Machine Learning Methods}
+
 \subsubsection{Data Pre-processing and Feature Generation}
 Add a table of the Features we used here...
-
-\begin{table}[H]
-  \caption{Dervied spectral indices used as additional model filters. \label{tab:spectral-features}}
-  \begin{adjustwidth}{-\extralength}{0cm}
-  \newcolumntype{C}{>{\centering\arraybackslash}X}
-  \begin{tabularx}{\fulllength}{CCCCCC}
-    \toprule
-    \textbf{Target (units)} & \textbf{$\text{R}^2$} & \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty} & \textbf{Empirical Coverage (\%)}\\
-    \midrule
-    Temperature (°C) & 0.999 ± 5.1e-5 & 0.0546 ± 0.0022 & 0.0316 ± 0.0015 & ± 0.084 & 89.7\\
-    \midrule
-    Conductivity ($\mu$S/cm) & 0.999 ± 0.00011 & 0.888 ± 0.067 & 0.497 ± 0.025 & ± 1.3 & 91.5\\
-    \midrule
-    $\mathrm{Ca}^{2+}$ (mg/l) & 0.999 ± 0.00031 & 0.544 ± 0.058 & 0.267 ± 0.013 & ± 0.72 & 89.9\\
-    \midrule
-    Dissolved Oxygen (mg/l) & 0.998 ± 0.00015 & 0.0931 ± 0.004 & 0.055 ± 0.0022 & ± 0.14 & 88.5\\
-    \midrule
-    Salinity (PSS) & 0.995 ± 0.00061 & 0.00124 ± 6.2e-5 & 0.000432 ± 2.6e-5 & ± 0.0009 & 90.1\\
-    \midrule
-    Tryptophan (ppb) & 0.99 ± 0.0046 & 0.206 ± 0.046 & 0.117 ± 0.0085 & ± 0.28 & 89.0\\
-    \midrule
-    pH & 0.988 ± 0.0018 & 0.0232 ± 0.0019 & 0.0119 ± 0.00045 & ± 0.032 & 92.5\\
-    \midrule
-    $\mathrm{Na^+} (mg/l)$ & 0.982 ± 0.0034 & 9.01 ± 0.88 & 4.17 ± 0.22 & ± 11.0 & 90.8\\
-    \midrule
-    $\mathrm{Cl^-}$ (mg/l) & 0.982 ± 0.0054 & 1.96 ± 0.28 & 1.0 ± 0.066 & ± 2.3 & 89.7\\
-    \midrule
-    Blue-Green Algae [Phycoerythrin] (ppb) & 0.939 ± 0.017 & 3.12 ± 0.43 & 0.84 ± 0.065 & ± 1.8 & 91.4\\
-    \midrule
-    CDOM (ppb) & 0.934 ± 0.02 & 0.58 ± 0.093 & 0.219 ± 0.013 & ± 0.46 & 90.3\\
-    \midrule
-    Optical Brighteners (ppb) & 0.92 ± 0.015 & 0.11 ± 0.0092 & 0.0617 ± 0.0019 & ± 0.13 & 92.4\\
-    \midrule
-    $\mathrm{NO_3^-} (mg/l-N)$ & 0.89 ± 0.013 & 0.0575 ± 0.0036 & 0.0353 ± 0.00091 & ± 0.079 & 90.7\\
-    \midrule
-    Crude Oil (ppb) & 0.89 ± 0.037 & 0.55 ± 0.11 & 0.174 ± 0.019 & ± 0.3 & 89.2\\
-    \bottomrule
-  \end{tabularx}
-  \end{adjustwidth}
-\end{table}
 
@@
     Crude Oil (ppb) & 0.89 ± 0.037 & 0.55 ± 0.11 & 0.174 ± 0.019 & ± 0.3 & 89.2\\
+    \midrule
+    Chlorophyll A with Red Excitation ($\mu$g/l) & 0.728 ± 0.11 & 94.9 ± 37.0 & 17.0 ± 2.5 &  ± 31.0 & 91.1\\
+    \midrule
+    Chlorophyll A ($\mu$g/l) & 0.672 ± 0.17 & 1.96 ± 0.25 & 0.482 ± 0.044 &  ± 0.83 & 90.6\\
+    \midrule
+    Turbidity (FNU) & 0.616 ± 0.19 & 52.6 ± 23.0 & 7.62 ± 2.2 & ± 9.2 & 87.9\\
     \bottomrule
@@
 \subsection{Mapping}
-
-This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
-\subsection{Subsection}
-\subsubsection{Subsubsection}
-
-Bulleted lists look like this:
-\begin{itemize}
-\item	First bullet;
-\item	Second bullet;
-\item	Third bullet.
-\end{itemize}
-
-Numbered lists can be added as follows:
-\begin{enumerate}
-\item	First item; 
-\item	Second item;
-\item	Third item.
-\end{enumerate}
-
-The text continues here.
-
-\subsection{Figures, Tables and Schemes}
-
-All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
+\section{Discussion} \label{sec:discussion}
+
+\subsection{Limitations}
+
+\subsection{Data Product Streaming}
 
@@
 This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Patents}
-
-This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
 
@@
 
-\institutionalreview{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study.
-You might choose to exclude this statement if the study did not require ethical approval.
-Please note that the Editorial Office might ask you for further information.
-Please add “The study was conducted in accordance with the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving humans.
-OR “The animal study protocol was approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving animals.
-OR “Ethical review and approval were waived for this study due to REASON (please provide a detailed justification).” OR “Not applicable” for studies not involving humans or animals.}
+\institutionalreview{Not applicable}
 
-\informedconsent{Any research article describing a study involving humans should contain this statement.
-Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans.
-You might also choose to exclude this statement if the study did not involve humans.
-
-Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves).
-Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}
+\informedconsent{Not applicable}
 
@@
 
-\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflicts of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
-Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript; or in the decision to publish the results must be declared in this section.
-If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript; or in the decision to publish the results''.}
+\conflictsofinterest{The authors declare no conflicts of interest.}
 
@@
 %=====================================
-%\bibliography{your_external_BibTeX_file}
 
-%=====================================
-% References, variant B: internal bibliography
-%=====================================
-\begin{thebibliography}{999}
-% Reference 1
-\bibitem[Author1(year)]{ref-journal}
-Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
-% Reference 2
-\bibitem[Author2(year)]{ref-book1}
-Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
-% Reference 3
-\bibitem[Author3(year)]{ref-book2}
-Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
-% Reference 4
-\bibitem[Author4(year)]{ref-unpublish}
-Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
-% Reference 5
-\bibitem[Author5(year)]{ref-communication}
-Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
-% Reference 6
-\bibitem[Author6(year)]{ref-proceeding}
-Author 1, A.B.; Author 2, C.D.; Author 3, E.F.
-Title of presentation.
-In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
-% Reference 7
-\bibitem[Author7(year)]{ref-thesis}
-Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
-% Reference 8
-\bibitem[Author8(year)]{ref-url}
-Title of Site. Available online: URL (accessed on Day Month Year).
-\end{thebibliography}
+\bibliography{references.bib}
 

### 2024-01-02 3_feature-exploration.jl
updated training to remove CV

@@ -145,29 +145,46 @@ MODELS[:etr] = (;
 #                 )
 
 
-MODELS[:rfr] = (;
-                :longname => "Random Forest Regressor",
-                :savename => "RandomForestRegressor",
-                :packagename => "DecisionTree",
-                :suffix => "vanilla",
-                :mdl => RFR(n_subfeatures=-1, sampling_fraction=0.9, n_trees=150),
-                )
+# MODELS[:rfr] = (;
+#                  :longname => "Random Forest Regressor",
+#                  :savename => "RandomForestRegressor",
+#                  :packagename => "DecisionTree",
+#                  :suffix => "vanilla",
+#                  :mdl => RFR(n_subfeatures=-1, sampling_fraction=1.0, n_trees=150),
+#                  )
 
-MODELS[:rfr2] = (;
-                 :longname => "Random Forest Regressor",
-                 :savename => "RandomForestRegressor",
-                 :packagename => "DecisionTree",
-                 :suffix => "hpo1",
-                 :mdl => RFR(n_subfeatures=350, sampling_fraction=0.95, n_trees=85),
-                )
+# MODELS[:rfr0] = (;
+#                 :longname => "Random Forest Regressor",
+#                 :savename => "RandomForestRegressor",
+#                 :packagename => "DecisionTree",
+#                 :suffix => "vanilla",
+#                 :mdl => RFR(n_subfeatures=-1, sampling_fraction=0.9, n_trees=150),
+#                 )
 
-MODELS[:rfr3] = (;
-                 :longname => "Random Forest Regressor",
-                 :savename => "RandomForestRegressor",
-                 :packagename => "DecisionTree",
-                 :suffix => "hpo2",
-                 :mdl => RFR(n_subfeatures=350, sampling_fraction=0.95, n_trees=100),
-                 )
+# MODELS[:rfr1] = (;
+#                 :longname => "Random Forest Regressor",
+#                 :savename => "RandomForestRegressor",
+#                 :packagename => "DecisionTree",
+#                 :suffix => "vanilla_200",
+#                 :mdl => RFR(n_subfeatures=-1, sampling_fraction=0.9, n_trees=200),
+#                 )
+
+
+# MODELS[:rfr2] = (;
+#                  :longname => "Random Forest Regressor",
+#                  :savename => "RandomForestRegressor",
[…]

### 2024-01-02 3b_make-maps.jl

@@ -92,12 +92,12 @@ RFR = @load RandomForestRegressor pkg=DecisionTree
 ETR = @load EvoTreeRegressor pkg=EvoTrees
 
 model_collections = ["Full"]
-# suffixes = ["vanilla", "hpo1", "hpo2", "vanilla"]
-# ml_models = ["RandomForestRegressor", "RandomForestRegressor", "RandomForestRegressor", "EvoTreeRegressor"]
+suffixes = ["vanilla", "vanilla_200", "hpo1", "hpo2", "vanilla"]
+ml_models = ["RandomForestRegressor", "RandomForestRegressor", "RandomForestRegressor", "RandomForestRegressor", "EvoTreeRegressor"]
 
 
-suffixes = ["vanilla",]
-ml_models = ["RandomForestRegressor",]
+# suffixes = ["hpo1",]
+# ml_models = ["RandomForestRegressor",]
 
 
 
@@ -124,11 +124,16 @@ collection = "Full"
 
 
 for target ∈ targets_to_map
+
+    # target = :CDOM
+
     target_name = String(target)
     target_long = targets_dict[target][2]
     units = targets_dict[target][1]
 
     for i ∈ 1:length(h5_dates)
+        # i = 1
+
         h5_date = h5_dates[i]
         h5_files_to_use = h5_files[i]
 
@@ -141,6 +146,9 @@ for target ∈ targets_to_map
         longitudes = df_lat_long.longitudes
 
         for j ∈ 1:length(suffixes)
+            # suffixes
+            # j = 1
+
             suffix = suffixes[j]
             model = ml_models[j]
 

### 2024-01-02 3c_extra-plots.jl

@@ -2,12 +2,11 @@ using HDF5, CSV, DataFrames, JSON, Tables
 using MLJ, ConformalPrediction
 using Random, Statistics
 using ProgressMeter
-
-import CairoMakie as cmk
+using CairoMakie
 using MintsMakieRecipes
 
-cmk.set_theme!(mints_theme)
-cmk.update_theme!(
+set_theme!(mints_theme)
+update_theme!(
     figure_padding=30,
     Axis=(
         xticklabelsize=20,
@@ -25,6 +24,43 @@ cmk.update_theme!(
 
 include("./config.jl")
 include("./viz.jl")
-include("./sat-viz.jl")
 
 
+datapath = "/Users/johnwaczak/data/robot-team/supervised"
+
+
+
+
+
+df_1123 = CSV.read(joinpath(datapath, "11-23", "CDOM", "data", "X.csv"), DataFrame)
+df_1209 = CSV.read(joinpath(datapath, "12-09", "CDOM", "data", "X.csv"), DataFrame)
+df_1210 = CSV.read(joinpath(datapath, "12-10", "CDOM", "data", "X.csv"), DataFrame)
+
+
+names(df_1123)
+
+Σdownwelling_1123 = df_1123.Σdownwelling
+Σdownwelling_1209 = df_1209.Σdownwelling
+Σdownwelling_1210 = df_1210.Σdownwelling
+
+fig = Figure();
+ax = Axis(fig[1,1], xlabel="Total Downwelling Intensity");
+d = density!(ax, Σdownwelling_1123)
+d2 = density!(ax, Σdownwelling_1209)
+d3 = density!(ax, Σdownwelling_1210)
+
+
+fig
+
+Σdownwelling_1123
+Σdownwelling_1209
+Σdownwelling_1210
+
+h5_test_path = "/Users/johnwaczak/data/robot-team/processed/hsi/11-23/Scotty_1/Scotty_1-1.h5"
+@assert isfile(h5_test_path)
+
+h = h5open(h5_test_path, "r")
+Data = h["data-Δx_0.1/Data"][:,:,:];
+varnames = h["data-Δx_0.1/varnames"][:];
+
+Data[end-1,:,:]

### 2024-01-02 training-functions.jl

@@ -11,10 +11,10 @@ hpo_ranges = Dict("DecisionTree" => Dict("DecisionTreeRegressor" => [(hpname=:mi
                                                                       ],
                                          "RandomForestRegressor" => [
                                                                       #(hpname=:min_samples_leaf, lower=2, upper=100),
-                                                                      #(hpname=:max_depth, values=[-1, 2, 3, 5, 10, 20]),
-                                                                      (hpname=:n_subfeatures, lower=50, upper=450,),
+                                                                      (hpname=:max_depth, values=[-1, 3, 5, 7]),
+                                                                      (hpname=:n_subfeatures, lower=10, upper=100,),
                                                                       (hpname=:n_trees, lower=50, upper=250),
-                                                                      (hpname=:sampling_fraction, lower=0.75, upper=0.95)
+                                                                      #(hpname=:sampling_fraction, lower=0.75, upper=0.95)
                                                                       ],
                                           ),
                  "XGBoost" => Dict("XGBoostRegressor" => [(hpname=:num_round, lower=50, upper=100),
@@ -26,15 +26,17 @@ hpo_ranges = Dict("DecisionTree" => Dict("DecisionTreeRegressor" => [(hpname=:mi
                                                           (hpname=:alpha, lower=0.0, upper=100.0), # L1 regularization. Higher makes model more sparse
                                                           ],
                                    ),
-                  "EvoTrees" => Dict("EvoTreeRegressor" => [(hpname=:nrounds,lower=50, upper=100),
-                                                            (hpname=:nbins, lower=64, upper=255),
-                                                            (hpname=:eta, lower=0.01, upper=0.5),
-                                                            (hpname=:max_depth, lower=3, upper=8),
-                                                            (hpname=:rowsample, lower=0.65, upper=1.0),
[…]

### 2024-01-03 config.jl
added new indices

@@ -101,30 +101,70 @@ name_replacements["solar_elevation"] = "Solar Elevation"
 name_replacements["solar_zenith"] = "Solar Zenith"
 
 # add derived metrics
-name_replacements["mNDWI"] = "Modified Normalized Difference Water Index"
-name_replacements["NDVI"] = "Normalized Difference Vegetative Index"
+
+name_replacements["DVI"] = "Difference Vegetation Index"
+name_replacements["EVI"] = "Enhanced Vegetation Index"
+name_replacements["GEMI"] = "Global Environmental Monitoring Index"
+name_replacements["GARI"] = "Green Atmospherically Resistant Index"
+name_replacements["GCI"] = "Green Chlorophyll Index"
+name_replacements["GDVI"] = "Green Difference Vegetation Index"
+name_replacements["GLI"] = "Green Leaf Index"
+name_replacements["GNDVI"] = "Green Normalized Difference Vegetation Index"
+name_replacements["GOSAVI"] = "Green Optimized Soil Adjusted Vegetation Index"
+name_replacements["GRVI"] = "Green Ratio Vegetation Index"
+name_replacements["GSAVI"] = "Green Soil Adjusted Vegetation Index"
+name_replacements["IPVI"] = "Infrared Percentage Vegetation Index"
+name_replacements["LAI"] = "Leaf Area Index"
+name_replacements["LCI"] = "Leaf Chlorphyll Index"
+name_replacements["MNLI"] = "Modified Non-Linear Index"
+name_replacements["MSAVI2"] = "Modified Soil Adjusted Vegetation Index 2"
+name_replacements["MSR"] = "Modified Simple Ratio"
+name_replacements["NLI"] = "Non-Linear Index"
+name_replacements["NDVI"] = "Normalized Difference Vegetation Index"
+name_replacements["NPCI"] = "Normalized Pigment Chlorophyll Index"
+name_replacements["OSAVI"] = "Optimized Soil Ajusted Vegetation Index"
+name_replacements["RDVI"] = "Renormalized Difference Vegetation Index"
 name_replacements["SR"] = "Simple Ratio"
-name_replacements["EVI"] = "Enhanced Vegetative Index"
-name_replacements["AVRI"] = "Atmospherical Resistant Vegetative Index"
-name_replacements["NDVI_705"] = "Red Edge Normalized Difference Vegetation Index"
[…]

### 2024-01-03 1_make-datasets.jl
fixed typo and running for all models

@@ -109,7 +109,7 @@ satmap = get_background_satmap(w,e,s,n)
 
 
 # read in the datasets:
-function get_data(fpath; threshold=0.25)
+function get_data(fpath; threshold=0.3)
     df = DataFrame()
     feature_names = []
     target_names = []
@@ -132,7 +132,7 @@ function get_data(fpath; threshold=0.25)
     end
 
     # first select only those points that are identifiably "in" the water and deal with any rows with missing data
-    filter!(row -> row.mNDWI > threshold, df);
+    filter!(row -> row.NDWI1 > threshold, df);
     dropmissing!(df);
 
     # identify nan/inf columns

### 2024-01-03 2_exploratory-data-analysis.jl

@@ -33,8 +33,8 @@ include("./viz.jl")
 
 outpath = "/Users/johnwaczak/data/robot-team/supervised"
 
-# collections = ["11-23", "12-09", "12-10", "Full"]
-collections = ["11-23", "Full"]
+collections = ["11-23", "12-09", "12-10", "Full"]
+# collections = ["11-23", "Full"]
 
 
 

### 2024-01-03 3_feature-exploration.jl

@@ -145,13 +145,15 @@ MODELS[:etr] = (;
 #                 )
 
 
-# MODELS[:rfr] = (;
-#                  :longname => "Random Forest Regressor",
-#                  :savename => "RandomForestRegressor",
-#                  :packagename => "DecisionTree",
-#                  :suffix => "vanilla",
-#                  :mdl => RFR(n_subfeatures=-1, sampling_fraction=1.0, n_trees=150),
-#                  )
+MODELS[:rfr] = (;
+                 :longname => "Random Forest Regressor",
+                 :savename => "RandomForestRegressor",
+                 :packagename => "DecisionTree",
+                 :suffix => "vanilla",
+                 :mdl => RFR(n_subfeatures=-1, sampling_fraction=1.0, n_trees=150),
+                 )
+
+
 
 # MODELS[:rfr0] = (;
 #                 :longname => "Random Forest Regressor",
@@ -231,17 +233,6 @@ for collection ∈ collections
             try
                 T1 = now()
 
-                # train_folds(
-                #     Xtrain, ytrain,
-                #     Xtest, ytest,
-                #     model.longname, model.savename, model.mdl,
-                #     target_name, units, target_long,
-                #     outpath;
-                #     suffix=model.suffix,
-                #     run_occam=false,
-                # )
-
-
                 train_basic(
                     X, y,
                     idx_train, idx_test,
@@ -290,7 +281,10 @@ GC.gc()
 
 
 
-function make_summary_table(collection, savename, suffix)
+
+
+
+function make_summary_table(collection, savename, type, suffix)
     res_dicts = Dict[]
 
     for target in targets_to_try
@@ -298,7 +292,7 @@ function make_summary_table(collection, savename, suffix)
         target_long = targets_dict[target][2]
         units = targets_dict[target][1]
 
-        res_path = joinpath(datapath, collection, target_name, "models", savename, "default", savename*"__$(suffix).json")
+        res_path = joinpath(datapath, collection, target_name, "models", savename, type, savename*"__$(suffix).json")
 
         @assert ispath(res_path)
 
[…]

### 2024-01-03 config.jl

@@ -129,7 +129,7 @@ name_replacements["TDVI"] = "Transformed Difference Vegetation Index"
 name_replacements["TGI"] = "Triangular Greenness Index"
 name_replacements["VARI"] = "Visible Atmospherically Resistant Index"
 name_replacements["WDRVI"] = "Wide Dynamic Range Vegetation Index"
-name_replacements["ARVI"] = "Atmospherically Resistant Vegetation Index"
+name_replacements["AVRI"] = "Atmospherically Resistant Vegetation Index"
 name_replacements["MCARI"] = "Modified Chlorophyll Absorption Ratio Index"
 name_replacements["MCARI2"] = "Modified Chlorophyll Absorption Ratio Index Improved"
 name_replacements["MRENDVI"] = "Modified Red Edge Normalized Difference Vegetation Index"

### 2024-01-03 paper/paper.tex

@@
 
+somewhere we need to mention the limitations from \cite{robotTeam1} due to low spatial variablility in a single day's collection...
+We are demonstrating that by including multiple observations from different days, we can improve our modelling capabilities by representing a larger variety of incident lighting conditions and in-situ values.
+
 In-situ measurements are expensive to collect and suffer from poor spatial coverage.
@@
 
-In the study we employ a team of autonomous sensing sentinels, herein referred to as \textit{the robot team}, to enable the rapid characterization of aquatic environments.
+In the study we employ a team of autonomous sensing sentinels, hereafter referred to as \textit{the robot team}, to enable the rapid characterization of aquatic environments.
 This team consists of two key sensing sentinels: An uncrewed surface vessel (USV) used to collect in-situ reference measurements, and an unmanned aerial vehicle (UAV) for performing rapid, wide-area surveys to gather remote sensing data products.
@@
 The USV is equipped with an in-situ sensing payload utilizing a combination of Eureka Manta-40 multi-probes including fluorometers, ion selective electrodes, and other physical sensors which together enable the collection of comprehensive near-surface measurements including Colored Dissolved Organic Matter (CDOM), Crude Oil, Blue-Green Algae (phycoerythrin and phycocyanin), Chlorophyll-A, Tryptophan, $\mathrm{Na^+}$, $\mathrm{Ca^{2+}}$, $\mathrm{Cl^-}$, Temperature, Conductivity, and many others.
-The full list of measurements used in this study is given in Table~\ref{tab:fit-results}.
-Additionally, the USV is equipped with an ultra-sonic weather monitoring sensor for measuring air speed and direction as well as a a BioSonics MX Aquatic Habitat Echosounder sonar which are not utilized in this study.
+The full list of measurements used in this study is given in Table~\ref{tab:sensors}.
+Additionally, the USV is equipped with an ultra-sonic weather monitoring sensor for measuring air speed and direction as well as a a BioSonics MX Aquatic Habitat Echosounder sonar which are not explored in this study.
 
-\subsection{UAV: Hyperspectral remote sensing}
+% add table describing sensors here:
 
-A Freefly Alta-X autonomous professional quad-copter was used as the UAV platform for the robotic team.
+\begin{table}[H] 
+\caption{In-situ reference sensors modelled in this study.\label{tab:sensors}}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
+\begin{tabularx}{\textwidth}{CCC}
+\toprule
+\textbf{Sensor}	& \textbf{Units}	& \textbf{Sensor Type}\\
+\midrule
+Temperature		                    & $^{\circ}$C       & Thermistor \\
+Conductivity                        & $\mu$S/cm         & Four-Electrode Graphite Sensor \\
+Dissolved Oxygen                    & mg/l              & Optical Sensor\\
+Salinity                            & PSU               & Four-Electrode Graphite Sensor \\
+pH                                  & logarithmic (0-14)& Flowing-junction Reference Electrode\\
+Turbidity                           & FNU               & Ion-Selective Electrode \\
+$\mathrm{Ca^{2+}}$                  & mg/l              & Ion-Selective Electrode \\
+$\mathrm{Na^+}$                     & mg/l              & Ion-Selective Electrode \\
+$\mathrm{Cl^-}$                     & mg/l              & Ion-Selective Electrode \\
+$\mathrm{NO_3^-}$                   & mg/l as nitrogen  & Ion-Selective Electrode \\
+Tryptophan                          & ppb               & Fluorometer \\
+Blue-Green Algae (phycoerythrin)    & ppb               & Fluorometer \\
+CDOM                                & ppb               & Fluorometer \\
+Optical Brighteners                 & ppb               & Fluorometer \\
+Crude Oil                           & ppb               & Fluorometer \\
+Chlorophyll A                       & ppb               & Fluorometer \\
+Chlorophyll A (Red Excitation)      & ppb               & Fluorometer \\
+\bottomrule
+\end{tabularx}
+\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
+\end{table}
+
+\subsection{UAV: Hyperspectral Data Cubes}
+
+A Freefly Alta-X autonomous quadcopter was used as the UAV platform for the robotic team.
 The Alta-X is specifically designed to carry cameras featuring a payload of up to 35 lbs.
@@
 The collected hyperspectral images (HSI) are stored locally on a solid state drive which is simultaneously mounted by the processing computer.
-The configuration of the drone is shown in shown in Figure~\ref{fig:drone-components}.
+The configuration of the drone is shown in Figure~\ref{fig:drone-components}.
 
@@
 
-\subsection{Data Collection}
-
-For this study data were collected using the robot team at a site in north Texas across three observation periods in November and December of 2020.
-For each collection period the UAV first completed a wide survey of the lake capturing raw hyperspectral data cubes, downwelling irradiance spectra, and relevant position and orientation flight data.
-Subsequently, the the USV sampled across the lake, collecting in-situ reference measurements.
-These combined data form the basis from which we seek to develop machine learning models translating the UAV captured spectra into the target quantities as measured by the USV.
-To enable this modality, we must establish the processing procedure by which we account for the variability of the incident light illuminating the pond and transform the raw hyperspectral data cubes from their native \textit{imaging reference frame} to a chosen coordinate system compatible with the data collected by the USV.
+To effectively utilize the spectra collected by our UAV, we must account for the variability of the incident light illuminating the water and transform the raw hyperspectral data cubes from their native \textit{imaging reference frame} to a chosen coordinate system compatible with the data collected by the USV.
 This procedure is illustrated in Figure~\ref{fig:hsi-pipeline}.
@@
 \end{equation}
-where $L$ is the spectral radiance, $E$ is the downwelling irradiance, and a factor of $\pi$ steradians assumes the surface is Lambertian (diffuse) \cite{reflectance-conversion}.
+where $L$ is the spectral radiance, $E$ is the downwelling irradiance, and a factor of $\pi$ steradians resutls from assuming the water surface is Lambertian (diffuse) \cite{reflectance-conversion}.
+We will address the impact of this assumption in Section~\ref{sec:discussion}.
 
-Having converted the hyperspectral data cube to units of reflectance, we must also georeference each pixel into geographic coordinate system so that each image pixel can be assigned a latitude and longitude cooresponding to the location on the ground from which it was sampled.
+Having converted the hyperspectral data cube to units of reflectance, we must also georeference each pixel into geographic coordinate system so that each image pixel can be assigned a latitude and longitude corresponding to the location on the ground from which it was sampled.
 During our three surveys, the UAV was flown at an altitude of ~50 m above the water.
-At this scale, the surface is essentially flat so that the hyperspectral datacube can be reliably georectified without the added need for a digital elevation map (DEM).
-We adopt the approach outlined in \cite{GeorectificationMuller, GeorectificationBaumker, GeorectificationMostafa} whereby each scanline is georeferenced using the known field of view (30.8 $\deg$) together with the position and orientation of the UAV as provided by the on-board GPS/INS.
+At this scale, the surface is essentially flat so that the hyperspectral data cube can be reliably georectified without the need for an on-board digital elevation map (DEM).
+We adopt the approach outlined in \cite{GeorectificationMuller, GeorectificationBaumker, GeorectificationMostafa} whereby each scan-line is georeferenced using the known field of view (30.8 $\deg$) together with the position and orientation of the UAV as provided by the on-board GPS/INS.
+After a sequence of coordinate transformations, pixel coordinates are obtained in the relevant UTM zone (in meters).
 The resulting image is then re-sampled to a final output resolution.
-For these collections a resolution of 10 cm was utilized however this can be increased to reduce the processing time for real-time applications.
+For these collections a resolution of 10 cm was utilized, however this can be increased to reduce the processing time for real-time applications.
+Finally, the UTM coordinates are transformed to latitude and longitude for easy comparison with in-situ data collected by the USV.
 The final result is a georectified hyperspectral reflectance data cube.
-In Figure~\ref{fig:hsi-infographic} we visualize one such data cube, highlighting a selection of exemplar pixel spectra from the scene as well as the incident downweling irradiance spectrum.
-A pseudo-color image is generated (plotted on the top of the datacube) to illustrate the scene.
+In Figure~\ref{fig:hsi-infographic} we visualize one such data cube, highlighting a selection of exemplar pixel spectra from the scene as well as the incident downwelling irradiance spectrum.
+A pseudo-color image is generated (plotted on the top of the data cube) to illustrate the scene.
 
@@
 \end{figure}  
+The above processing pipeline was implemented using the Julia programming language, a just-in-time compiled language with native multi-theading support \cite{julia-1}.
+By running this pipeline on the on-board processing computer, we are able to process the collected hyperspectral data cubes in near real time.
+This feature is critical for time-sensitive applications where we need to quickly asses if an area is safe and can not afford to wait to download and post-process collected imagery after a flight.
+
+\subsection{Data Collection and Training Set Curation}
+
+Data were collected using the robot team at a site in north Texas across three observation periods in the fall of 2020.
+For each collection period, the UAV first completed a wide survey of the lake capturing hyperspectral data cubes.
+Subsequently, the the USV sampled across the lake, collecting in-situ reference measurements.
+Each of these reference measurements was then collocated with individual pixel spectra where the USV track overlapped with UAV pixels.
+These combined data form a tabular data set on which we seek use to train regression models; pixel spectra form input features and each separate USV sensor forms a distinct target variable.
+Together, this combined data set contains over 11,000 records.
+
+Each collection was performed near solar noon to maximize the amount of incident sunlight illuminating the water, however, to account for any potential variation in lighting conditions between data cubes, we augment the training set with additional features including the drone viewing geometry (roll, pitch, heading) and solar illumination geometry (solar azimuth, solar elevation, solar zenith) as wall as the total at-pixel intensity (before refelctance conversion) as well as the total downwelling intensity.
+Additional feature engineering is performed to add a combination of spectral indices like the normalized difference vegetation index (NDVI), modified normalized difference water index (mNDWI), simple ratio (SR), photochemical reflectance index (PRI), and more (see Appendix~\ref{appendix:spec-indices} for a full list of included spectral indices).
 
@@
 
-\subsubsection{Data Pre-processing and Feature Generation}
-Add a table of the Features we used here...
+For each of the 17 target variables listed in Table~\ref{tab:sensors}, data were randomly partitioned into a 90:10 training/testing split resulting 10,005 training points and 1,112 holdout testing points.
+Using the MLJ machine learning framework, a variety of machine learning models compatible with the regression task were identified \cite{MLJ1}.
+This selection of models included linear regression (and it's variations), Gaussian Process Regression, shallow Neural Networks, and decision tree based models.
+Out of this set, Random Forest Regression from \cite{decision-trees} and a native Julia implementation of gradient boosted trees were selected for their quick training time and high performance.
+Both random forests and gradient boosted trees are ensembling techniques based on individual decision tree regressors \cite{decision-trees, random-forest, gradient-boosting}.
 
-\subsubsection{Models Employed}
-Discuss random forests
-\subsubsection{Hyperparameter Optimization}
-Discuss the parameters we optimize and the evaluation strategy using 10-fold cross validation.
-
-\subsection{Uncertainty Quantification via Conformal Prediction}
+Each model was trained and hyperparameter optimized using 10-fold cross validation with a random hyperparameter search.
+Model performance was evaluated by computing out-of-fold values for the $R^2$ (coefficient of determination), as well as
+\begin{align}
+    \text{RMSE} &= \sqrt{\frac{\sum\limits_{i=1}^N (\hat{y}_i-y_i)^2}{N}}, \\
+    \text{MAE} &= \frac{\sum\limits_{i=1}^N \lvert \hat{y}_i - y_i \vert}{N},
+\end{align}
+where RMSE is the root-mean-square error, and MAE is the mean absolute error between true values $y_i$ and predictions $\hat{y}_i$.
+To assess the uncertainty of model predictions, we employ Inductive Conformal Prediction as described in \cite{conformal-prediction-1, conformal-prediction-2, conformal-prediction-3, conformal-prediction-4}.
+To do this, the training set is further partitioned so that we obtain an additional hold out set which we may call the \textit{calibration set}.
+We chose this split to achieve a 80:10:10 training, calibration, and testing ratios which results in a calibration set of ~1,000 records which \cite{conformal-prediction-2} suggest to be sufficient for most cases.
+First, the chosen model is trained on the training set.
+We then compute a set of nonconformity scores on the calibration set using an uncertainty heuristic, in this case, the absolute error
+\begin{equation}
+    s_i = s(X_i, y_i) = \lvert f(X_i) - y_i \rvert = \lvert \hat{y}_i - y_i \rvert
+\end{equation}
+where $f(X_i)=\hat{y}_i$ denotes the trained ML model applied to the $i^{th}$ calibration record.
+These n-many scores are sorted, and the interval half width $d$ is computed as the $\frac{\lceil(\alpha)(n+1) \rceil}{n}$ quantile of this set in order to achieve a coverage of $\alpha$ on the calibration set.
+Predictions intervals for new data are then formed as $f(X)\pm d$.
+For this study, we have chosen a coverage of $\alpha=0.9$.
 
@@
 
-\subsection{Modeling Results}
+The results of fitting our hyperparameter optimized models are listed in Table~\ref{tab:fit-results}.
+For each model, the $R^2$, RMSE, and MAE were evaluated using 10-fold cross validation.
+We observe considerable
 
@@
     \midrule
-    Tryptophan (ppb) & 0.99 ± 0.0046 & 0.206 ± 0.046 & 0.117 ± 0.0085 & ± 0.28 & 89.0\\
+    Tryptophan (ppb) & 0.989 ± 0.0046 & 0.206 ± 0.046 & 0.117 ± 0.0085 & ± 0.28 & 89.0\\
     \midrule
@@
     \midrule
-    Optical Brighteners (ppb) & 0.92 ± 0.015 & 0.11 ± 0.0092 & 0.0617 ± 0.0019 & ± 0.13 & 92.4\\
+    Optical Brighteners (ppb) & 0.920 ± 0.015 & 0.11 ± 0.0092 & 0.0617 ± 0.0019 & ± 0.13 & 92.4\\
     \midrule
-    $\mathrm{NO_3^-} (mg/l-N)$ & 0.89 ± 0.013 & 0.0575 ± 0.0036 & 0.0353 ± 0.00091 & ± 0.079 & 90.7\\
+    $\mathrm{NO_3^-} (mg/l-N)$ & 0.890 ± 0.013 & 0.0575 ± 0.0036 & 0.0353 ± 0.00091 & ± 0.079 & 90.7\\
     \midrule
-    Crude Oil (ppb) & 0.89 ± 0.037 & 0.55 ± 0.11 & 0.174 ± 0.019 & ± 0.3 & 89.2\\
+    Crude Oil (ppb) & 0.890 ± 0.037 & 0.55 ± 0.11 & 0.174 ± 0.019 & ± 0.3 & 89.2\\
     \midrule
@@
 
-\subsection{Mapping}
+\subsection{Physical Parameters}
 
 \begin{figure}[H]
-\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
-\caption{This is a figure.
-Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.\label{fig1}}
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=16.0cm]{paper/figures/results/fits/physical-fitres.pdf}
+\end{adjustwidth}
+\caption{A visualization of the fitresults for three of the physical parameters we modeled. On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:physical-fit}}
 \end{figure}
-\unskip
 
-\begin{table}[H] 
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
-\newcolumntype{C}{>{\centering\arraybackslash}X}
-\begin{tabularx}{\textwidth}{CCC}
-\toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-\midrule
-Entry 1		& Data			& Data\\
-Entry 2		& Data			& Data \textsuperscript{1}\\
-\bottomrule
-\end{tabularx}
-\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-\end{table}
+\begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=18.0cm]{paper/figures/results/fits/physical-ranking.pdf}
+\end{adjustwidth}
+\caption{Ranked feature importances for the same three physical parameter models.\label{fig:physical-fit}}
+\end{figure}
 
-The text continues here (Figure~\ref{fig2} and Table~\ref{tab2}).
+\subsection{Ion Measurements}
+
+\begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=16.0cm]{paper/figures/results/fits/ions-fitres.pdf}
+\end{adjustwidth}
+\caption{A visualization of the fitresults for three of the ion concentrations we modeled. On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:ions-fit}}
+\end{figure}
+
+\begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=18.0cm]{paper/figures/results/fits/ions-ranking.pdf}
+\end{adjustwidth}
+\caption{Ranked feature importances for the same three ion concentration models.\label{fig:ions-fit}}
+\end{figure}
+
+\subsection{Chemicals-of-Concern}
+
+\begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=16.0cm]{paper/figures/results/fits/chemical-fitres.pdf}
+\end{adjustwidth}
+\caption{A visualization of the fitresults for three of the chemical concentrations we modeled.
+On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:chemicals-fit}}
+\end{figure}
+
+\begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=18.0cm]{paper/figures/results/fits/chemical-ranking.pdf}
+\end{adjustwidth}
+\caption{Ranked feature importances for the same three chemical concentration models.\label{fig:chemicals-fit}}
+\end{figure}
+
+\subsection{Mapping}
 
@@
 \centering
-\includegraphics[width=15.5cm]{Definitions/logo-mdpi}
+\includegraphics[width=18.0cm]{paper/figures/results/map-combined.pdf}
 \end{adjustwidth}
-\caption{This is a wide figure.\label{fig2}}
+\caption{Maps generated by applying the ML model to hyperspectral data cubes.
+(\textbf{a}) The CDOM model applied to the 11-23 collection.
+(\textbf{b}) The CDOM model applied the the 12-09 collection.
+(\textbf{c}) the Crude Oil model applied to the 11-23 collection.
+(\textbf{d}) The Crude Oil model applied to the 12-09 collection.
+In each panel, boat data are overlaid as color-filled squares.
+We note that there is good agreement between estimated values at boat locations and the in-situ reference measurements.
+\label{fig:maps}}
 \end{figure}
-
-\begin{table}[H]
-\caption{This is a wide table.\label{tab2}}
-	\begin{adjustwidth}{-\extralength}{0cm}
-		\newcolumntype{C}{>{\centering\arraybackslash}X}
-		\begin{tabularx}{\fulllength}{CCCC}
-			\toprule
-			\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}     & \textbf{Title 4}\\
-			\midrule
-\multirow[m]{3}{*}{Entry 1 *}	& Data			& Data			& Data\\
-			  	                   & Data			& Data			& Data\\
-			             	      & Data			& Data			& Data\\
-                   \midrule
-\multirow[m]{3}{*}{Entry 2}    & Data			& Data			& Data\\
-			  	                  & Data			& Data			& Data\\
-			             	     & Data			& Data			& Data\\
-                   \midrule
-\multirow[m]{3}{*}{Entry 3}    & Data			& Data			& Data\\
-			  	                 & Data			& Data			& Data\\
-			             	    & Data			& Data			& Data\\
-                  \midrule
-\multirow[m]{3}{*}{Entry 4}   & Data			& Data			& Data\\
-			  	                 & Data			& Data			& Data\\
-			             	    & Data			& Data			& Data\\
-			\bottomrule
-		\end{tabularx}
-	\end{adjustwidth}
-	\noindent{\footnotesize{* Tables may have a footer.}}
-\end{table}
-
-%\begin{listing}[H]
-%\caption{Title of the listing}
-%\rule{\columnwidth}{1pt}
-%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
-%\rule{\columnwidth}{1pt}
-%\end{listing}
-
-Text.
-
-Text.
-
-\subsection{Formatting of Mathematical Components}
-
-This is the example 1 of equation:
-\begin{linenomath}
-\begin{equation}
-a = 1,
-\end{equation}
-\end{linenomath}
-the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
-%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
-This ensures correct linenumbering.
-The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
-
-This is the example 2 of equation:
-\begin{adjustwidth}{-\extralength}{0cm}
-\begin{equation}
-a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
-\end{equation}
-\end{adjustwidth}
-
-% Example of a page in landscape format (with table and table footnote).
-%\startlandscape
-%\begin{table}[H] %% Table in wide page
-%\caption{This is a very wide table.\label{tab3}}
-%	\begin{tabularx}{\textwidth}{CCCC}
-%		\toprule
-%		\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}	& \textbf{Title 4}\\
-%		\midrule
-%		Entry 1		& Data			& Data			& This cell has some longer content that runs over two lines.\\
-%		Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
-%		\bottomrule
-%	\end{tabularx}
-%	\begin{adjustwidth}{+\extralength}{0cm}
-%		\noindent\footnotesize{\textsuperscript{1} This is a table footnote.}
-%	\end{adjustwidth}
-%\end{table}
-%\finishlandscape
-
-Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
-%% Example of a theorem:
-\begin{Theorem}
-Example text of a theorem.
-\end{Theorem}
-
-The text continues here. Proofs must be formatted as follows:
-
-%% Example of a proof:
-\begin{proof}[Proof of Theorem 1]
-Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
-\end{proof}
-The text continues here.
 
@@
 \section{Discussion} \label{sec:discussion}
+
+However, the presence of DOM/POM (dissolved and particulate organic matter), decreases “blue” instrument sensitivity hindering the primary benefit of having a blue excitation fluorometer.
+The “red” chlorophyll sensor effectively eliminates interference effects from DOM/POM, by using a specific set of optics.
+Because these materials don’t absorb red excitation energy, but algae do, red excitation fluorometry is used to detect and estimate algal abundance free from DOM/POM interference.
+Note that although this optical setup is less sensitive for detecting eukaryotic algae, the errors associated with these interference materials may outweigh the increased sensitivity of blue excitation fluorometry.
+Also, red excitation fluorometry is significantly more sensitive to prokaryotic algae (blue-green or cyanobacteria), making it a favorable instrument for freshwater systems which are typically rich in DOM and blue-green algae.
 
@@
 \appendix
-\section[\appendixname~\thesection]{}
+\section[\appendixname~\thesection]{}\label{appendix:spec-indices}
 \subsection[\appendixname~\thesubsection]{}
-The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data.
-Mathematical proofs of results not central to the paper can be added as an appendix.
+
+For the following hyperspectral reflectance indices, we have made the following identifications:
+\begin{align}\label{eq:ref-bands}
+    R_b &= R(440 \text{ nm}) \\
+    R_g &= R(550 \text{ nm}) \\
+    R_b &= R(650 \text{ nm}) \\
+    R_{nir} &= R(860 \text{ nm}).
+\end{align}
+We also define $R_{swir} = R(1009 \text{ nm})$ as the \textit{almost}-SWIR band representing the infrared edge of the hyperspectral imager.
 
 \begin{table}[H]
-\caption{This is a table caption.\label{tab5}}
+\caption{Spectral indices used supplied as extra features to each ML model.
+For each index, $R_{\lambda}$ denotes the reflectance at wavelength $\lambda$ used to compute the index.
+$R_b$, $R_g$, etc are defined as in Eq~\ref{eq:ref-bands}.
+\label{tab:spec-indices}}
+\begin{adjustwidth}{-\extralength}{0cm}
     \newcolumntype{C}{>{\centering\arraybackslash}X}
-\begin{tabularx}{\textwidth}{CCC}
+    \begin{tabularx}{\fulllength}{CCC}
         \toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
+        \textbf{Spectral Index}	& \textbf{Acronym} & \textbf{Formula}\\
         \midrule
-Entry 1		& Data			& Data\\
-Entry 2		& Data			& Data\\
+        Difference Vegetation Index & DVI & $\dfrac{2.5(R_{nir} - R_r)}{R_{nir} + 6R_r - 7.5R_b + 1}$ \\
+        \midrule
+        Global Environmental Monitoring Index & GEMI* & $\text{eta}(1 - 0.25\,\text{eta}) - \dfrac{R_r - 1.125}{1 - R_r}$  \\
+        \midrule
+        Green Atmospherically Resistant Index & GARI** & $\dfrac{R_{nir} - (R_g - \gamma(R_b - R_r))}{R_{nir} + (R_g - \gamma (R_b - R_r))}$ \\
+        \midrule
+        Green Chlorophyll Index & GCI & $\dfrac{R_{nir}}{R_g} - 1$ \\
+        \midrule
+        Green Difference Vegetation Index & GDVI & $R_{nir} - R_g$ \\
+        \midrule
+        Green Leaf Index & GLI & $\dfrac{(R_g - R_r) + (R_g - R_b)}{2 R_g + R_r + R_b}$ \\
+        \midrule
+        Green Normalized Difference Vegetation Index & GNDVI & $\dfrac{R_{nir} - R_g}{R_{nir} + R_g}$ \\
+        \midrule 
+        Green Optimized Soil Adjusted Vegetation Index & GOSAVI & $\dfrac{R_{nir} - R_g}{R_{nir} + R_g + 0.16}$ \\
+        \midrule
+        Green Ratio Vegetation Index & GRVI & $\dfrac{R_{nir}}{R_g}$ \\
+        \midrule 
+        Green Soil Adjusted Vegetation Index & GSAVI & $\dfrac{1.5(R_{nir} - R_g)}{R_{nir} + R_g + 0.5}$ \\
+        \midrule
+        Infrared Percentage Vegetation Index & IPVI & $\dfrac{R_{nir}}{R_{nir} + R_r}$ \\
+        \midrule
+        Leaf Area Index & LAI & $3.618 \left(\dfrac{2.5 (R_{nir} - R_r)}{R_{nir} + 6R_{R_r} - 7.5 R_b + 1}\right) - 0.118$ \\
+        \midrule
+        Modified Non-Linear Index & MNLI & $\dfrac{1.5(R_{nir}^2 - R_r)}{R_{nir}^2 + R_r + 0.5}$ \\
+        \midrule
+        Modified Soil Adjusted Vegetation Index 2 & MSAVI2 & $\dfrac{2R_{nir} + 1 - \sqrt{(2R_{nir} + 1)^2 - 8(R_{nir} - R_r)}}{2}$ \\
+        \midrule
+        Modified Simple Ratio & MSR & $\dfrac{R_{nir}/R_r - 1}{\sqrt{R_{nir} / R_r} + 1}$ \\
+        \midrule
+        Non-Linear Index & NLI & $\dfrac{R_{nir}^2 - R_r}{R_{nir}^2 + R_r}$ \\
+        \midrule
+        Normalized Difference Vegetation Index & NDVI & $\dfrac{R_{nir} - R_r}{R_{nir} + R_r}$ \\
+        \midrule
+        Normalized Pigment Chlorophyll Index & NPCI & $\dfrac{R_{680} - R_{430}}{R_{680} + R_{430}}$ \\
+        \midrule
+        Optimized Soil Adjusted Vegetation Index & OSAVI & $\dfrac{R_{nir} - R_r}{R_{nir} + R_r + 0.16}$ \\
+        \midrule
+        Renormalized Difference Vegetation Index & RDVI & $\dfrac{R_{nir} - R_r}{\sqrt{R_{nir} + R_r}}$ \\
+        \midrule
+        Soil Adjusted Vegetation Index & SAVI & $\dfrac{1.5(R_{nir} - R_r)}{R_{nir} + R_r + 0.5}$ \\
+        \midrule 
+        Simple Ratio & SR & $\dfrac{R_{nir}}{R_r}$ \\
+        \midrule
+        Transformed Difference Vegetation Index & TDVI & $\dfrac{1.5R_{nir} - R_r}{\sqrt{R_{nir}^2 + R_r + 0.5}}$ \\
+        \midrule
+        Triangular Greenness Index & TGI & $\dfrac{(\lambda_r-\lambda_b)(R_r-R_g) - (\lambda_r-\lambda_g)(R_r - R_b)}{2}$ \\
+        \midrule
+        Visible Atmospherically Resistant Index & VARI & $\dfrac{R_g - R_r}{R_g + R_r - R_b}$ \\
         \bottomrule
     \end{tabularx}
+\end{adjustwidth}
+\noindent{\footnotesize{* $\text{eta} = 2(R_{nir}^2 - R_g^2) + 1.5R_{nir} + 0.5R_{r} $ \tab ** $\gamma =1.7$}}
 \end{table}
-
-\section[\appendixname~\thesection]{}
-All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.
 

### 2024-01-03 paper/supplementary-material/spectral-indices.qmd
moved table to supplementary material

---
title: "Supplementary Material:"
subtitle: "Hyperspectral Reflectance Indices"
date: "01-03-2024"
author: "John Waczak"
format:
    pdf:
        keep-tex: true
---

For the following hyperspectral reflectance indices, we have made the following identifications:

\begin{align}\label{eq:ref-bands}
\begin{split}
    R_b &= R(440 \text{ nm}) \\
    R_g &= R(550 \text{ nm}) \\
    R_b &= R(650 \text{ nm}) \\
    R_{nir} &= R(860 \text{ nm}).
\end{split}
\end{align}
We also define $R_{swir} = R(1009 \text{ nm})$ as the *almost*-SWIR band representing the infrared edge of the hyperspectral imager.

| **Spectral Index** | **Acronym** | **Formula** |
|---------|---|-----------|
| Difference Vegetation Index | DVI | $\dfrac{2.5(R_{nir} - R_r)}{R_{nir} + 6R_r - 7.5R_b + 1}$ |
| Global Environmental Monitoring Index | GEMI* | $\text{eta}(1 - 0.25\,\text{eta}) - \dfrac{R_r - 1.125}{1 - R_r}$ |
| Green Atmospherically Resistant Index | GARI** | $\dfrac{R_{nir} - (R_g - \gamma(R_b - R_r))}{R_{nir} + (R_g - \gamma (R_b - R_r))}$ |
| Green Chlorophyll Index | GCI | $\dfrac{R_{nir}}{R_g} - 1$ |
| Green Difference Vegetation Index | GDVI | $R_{nir} - R_g$ |
| Green Leaf Index | GLI | $\dfrac{(R_g - R_r) + (R_g - R_b)}{2 R_g + R_r + R_b}$ |
| Green Normalized Difference Vegetation Index | GNDVI | $\dfrac{R_{nir} - R_g}{R_{nir} + R_g}$ |
| Green Optimized Soil Adjusted Vegetation Index | GOSAVI | $\dfrac{R_{nir} - R_g}{R_{nir} + R_g + 0.16}$ |
| Green Ratio Vegetation Index | GRVI | $\dfrac{R_{nir}}{R_g}$ |
| Green Soil Adjusted Vegetation Index | GSAVI | $\dfrac{1.5(R_{nir} - R_g)}{R_{nir} + R_g + 0.5}$ |
| Infrared Percentage Vegetation Index | IPVI | $\dfrac{R_{nir}}{R_{nir} + R_r}$ |
| Leaf Area Index | LAI | $3.618 \left(\dfrac{2.5 (R_{nir} - R_r)}{R_{nir} + 6R_{R_r} - 7.5 R_b + 1}\right) - 0.118$ |
| Modified Non-Linear Index | MNLI | $\dfrac{1.5(R_{nir}^2 - R_r)}{R_{nir}^2 + R_r + 0.5}$ |
| Modified Soil Adjusted Vegetation Index 2 | MSAVI2 | $\dfrac{2R_{nir} + 1 - \sqrt{(2R_{nir} + 1)^2 - 8(R_{nir} - R_r)}}{2}$ |
| Modified Simple Ratio | MSR | $\dfrac{R_{nir}/R_r - 1}{\sqrt{R_{nir} / R_r} + 1}$ |
| Non-Linear Index | NLI | $\dfrac{R_{nir}^2 - R_r}{R_{nir}^2 + R_r}$ |
| Normalized Difference Vegetation Index | NDVI | $\dfrac{R_{nir} - R_r}{R_{nir} + R_r}$ |
| Normalized Pigment Chlorophyll Index | NPCI | $\dfrac{R_{680} - R_{430}}{R_{680} + R_{430}}$ |
| Optimized Soil Adjusted Vegetation Index | OSAVI | $\dfrac{R_{nir} - R_r}{R_{nir} + R_r + 0.16}$ |
| Renormalized Difference Vegetation Index | RDVI | $\dfrac{R_{nir} - R_r}{\sqrt{R_{nir} + R_r}}$ |
| Soil Adjusted Vegetation Index | SAVI | $\dfrac{1.5(R_{nir} - R_r)}{R_{nir} + R_r + 0.5}$ |
| Simple Ratio | SR | $\dfrac{R_{nir}}{R_r}$ |
| Transformed Difference Vegetation Index | TDVI | $\dfrac{1.5R_{nir} - R_r}{\sqrt{R_{nir}^2 + R_r + 0.5}}$ |
| Triangular Greenness Index | TGI | $\dfrac{(\lambda_r-\lambda_b)(R_r-R_g) - (\lambda_r-\lambda_g)(R_r - R_b)}{2}$ |
| Visible Atmospherically Resistant Index | VARI | $\dfrac{R_g - R_r}{R_g + R_r - R_b}$ |
| Wide Dynamic Range Vegetation Index | WDRVI | $\dfrac{0.2 R_{nir} - R_r}{0.2 * R_{nir} + R_r}$ |
| Atmospherically Resistant Vegetation Index | ARVI | $\dfrac{R_{800} - (R_{800} - 1(R_{450} - R_{680}))}{R_{800} + (R_{680} - 1 (R_{450} - R_{680}))}$ |
| Modified Chlorophyll Absorption Ratio Index | MCARI | $((R_{700} - R_{670}) - 2(R_{700} - R_{550}))\dfrac{R_{700}}{R_{670}}$ |
| Modified Chlorophyll Absorption Ratio Index Improved | MCARI2 | $\dfrac{1.5( 2.5(R_{800} - R_{670}) - 1.3 (R_{800} - R_{550}))}{\sqrt{(2R_{800} + 1)^2 - (6R_{800} - 5 \sqrt{R_{670}}) - 0.5}}$ |
| Modified Red Edge Normalized Difference Vegetation Index | MRENDVI | $\dfrac{R_{750} - R_{705}}{R_{750} + R_{705} - 2R_{445}}$ |
| Modified Red Edge Simple Ratio | MRESR | $\dfrac{R_{750} - R_{445}}{R_{705} - R_{445}}$ |
| Modified Triangular Vegetation Index | MTVI | $1.2 (1.2 (R_{800} - R_{550}) - 2.5 (R_{670} - R_{550}))$ |
| Red Edge Normalized Difference Vegetation Index | RENDVI | $\dfrac{R_{750} - R_{705}}{R_{750} + R_{705}}$ |
| Transformed Chlorophyll Absorption Reflectance Index | TCARI | $3\left((R_{700} - R_{670}) - 0.2(R_{700} - R_{550})\dfrac{R_{700}}{R_{670}}\right)$ |
| Triangular Vegetation Index | TVI | $0.5(120 (R_{750} - R_{550}) - 200 (R_{670} - R_{550}))$ |
| Vogelmann Red Edge Index 1 | VREI1 | $\dfrac{R_{740}}{R_{720}}$ |
| Vogelmann Red Edge Index 2 | VREI2 | $\dfrac{R_{734} - R_{747}}{R_{715} + R_{726}}$ |
| Vogelmann Red Edge Index 3 | VREI3 | $\dfrac{R_{734} - R_{747}}{R_{715} + R_{720}}$ |
| Photochemical Reflectance Index | PRI | $\dfrac{R_{531} - R_{570}}{R_{531} + R_{570}}$ |
| Structure Insensitive Pigment Index | SIPI | $\dfrac{R_{800} - R_{445}}{R_{800} + R_{680}}$ |
| Structure Independent Pigment Index | SIPI1 | $\dfrac{R_{445} - R_{800}}{R_{670} - R_{800}}$ |
| Plant Senescence Reflectance Index | PSRI | $\dfrac{R_{680} - R_{500}}{R_{750}}$ |
| Anthocyanin Reflectance Index 1 | ARI1 | $\dfrac{1}{R_{550}} - \dfrac{1}{R_{700}}$ |
| Anthocyanin Reflectance Index 2 | ARI2 | $\left(\dfrac{1}{R_{550}} - \dfrac{1}{R_{700}}\right)R_{800}$ |
| Carotenoid Reflectance Index 1 | CRI1 | $\dfrac{1}{R_{510}} - \dfrac{1}{R_{550}}$ |
| Carotenoid Reflectance Index 2 | CRI2 | $\dfrac{1}{R_{510}} - \dfrac{1}{R_{700}}$ |
| Normalized Difference Water Index 1 | NDWI1 | $\dfrac{R_g - R_{nir}}{R_g + R_{nir}}$ |
| Normalized Difference Water Index 2 | NDWI2 | $\dfrac{R_{nir} - R_{swir}}{R_{nir} + R_{swir}}$ |
| Modified Normalized Difference Water Index | MNDWI | $\dfrac{R_g - R_{swir}}{R_g + R_{swir}}$ |
| Water Band Index | WBI | $\dfrac{970}{900}$ |
| Anthocyanin Content Index | ACI | $\dfrac{R_g}{R_{nir}}$ |
| Chlorophyll Index Red Edge | CIre | $\dfrac{R_{nir}}{R_{705}} - 1$ |
| Modified Anthocyanin Reflectance Index | MARI | $\left(\dfrac{1}{R_{550}} - \dfrac{1}{R_{700}} \right)R_{nir}$ |
| Moisture Stress Index | MSI | $\dfrac{R_{swir}}{R_{nir}}$ |
| MERIS Terrestrial Chlorophyll Index | MTCI | $\dfrac{R_{753.75} - R_{708.75}}{R_{708.75} - R_{681.25}}$ |
| Normalzied Difference Infrared Index | NDII | $\dfrac{R_{nir} - R_{swir}}{R_{nir} + R_{swir}}$ |
| Normalized Difference Red Edge | NDRE | $\dfrac{R_{790} - R_{720}}{R_{790} + R_{720}}$ |
| Red Green Ratio Index | RGRI | $\dfrac{R_r}{R_g}$ |
| Red Edge Vegetation Stress Index | RVSI | $\dfrac{R_{714} + R_{752}}{2} - R_{733}$ |

: Spectral indices supplied as extra features to each ML model. For each index, $R_{\lambda}$ denotes the reflectance at wavelength $\lambda$ used to compute the index. $R_b$, $R_g$, etc are defined in Equation \ref{eq:ref-bands}.

### 2024-01-03 paper/paper.tex
added histogram for total downwelling intensity

@@
 \appendix
-\section[\appendixname~\thesection]{}\label{appendix:spec-indices}
-\subsection[\appendixname~\thesubsection]{}
-
-For the following hyperspectral reflectance indices, we have made the following identifications:
-\begin{align}\label{eq:ref-bands}
-    R_b &= R(440 \text{ nm}) \\
-    R_g &= R(550 \text{ nm}) \\
-    R_b &= R(650 \text{ nm}) \\
-    R_{nir} &= R(860 \text{ nm}).
-\end{align}
-We also define $R_{swir} = R(1009 \text{ nm})$ as the \textit{almost}-SWIR band representing the infrared edge of the hyperspectral imager.
-
-\begin{table}[H]
-\caption{Spectral indices used supplied as extra features to each ML model.
-For each index, $R_{\lambda}$ denotes the reflectance at wavelength $\lambda$ used to compute the index.
-$R_b$, $R_g$, etc are defined as in Eq~\ref{eq:ref-bands}.
-\label{tab:spec-indices}}
-\begin{adjustwidth}{-\extralength}{0cm}
-    \newcolumntype{C}{>{\centering\arraybackslash}X}
-    \begin{tabularx}{\fulllength}{CCC}
-        \toprule
-        \textbf{Spectral Index}	& \textbf{Acronym} & \textbf{Formula}\\
-        \midrule
-        Difference Vegetation Index & DVI & $\dfrac{2.5(R_{nir} - R_r)}{R_{nir} + 6R_r - 7.5R_b + 1}$ \\
-        \midrule
-        Global Environmental Monitoring Index & GEMI* & $\text{eta}(1 - 0.25\,\text{eta}) - \dfrac{R_r - 1.125}{1 - R_r}$  \\
-        \midrule
-        Green Atmospherically Resistant Index & GARI** & $\dfrac{R_{nir} - (R_g - \gamma(R_b - R_r))}{R_{nir} + (R_g - \gamma (R_b - R_r))}$ \\
-        \midrule
-        Green Chlorophyll Index & GCI & $\dfrac{R_{nir}}{R_g} - 1$ \\
-        \midrule
-        Green Difference Vegetation Index & GDVI & $R_{nir} - R_g$ \\
-        \midrule
-        Green Leaf Index & GLI & $\dfrac{(R_g - R_r) + (R_g - R_b)}{2 R_g + R_r + R_b}$ \\
-        \midrule
-        Green Normalized Difference Vegetation Index & GNDVI & $\dfrac{R_{nir} - R_g}{R_{nir} + R_g}$ \\
-        \midrule 
-        Green Optimized Soil Adjusted Vegetation Index & GOSAVI & $\dfrac{R_{nir} - R_g}{R_{nir} + R_g + 0.16}$ \\
-        \midrule
-        Green Ratio Vegetation Index & GRVI & $\dfrac{R_{nir}}{R_g}$ \\
-        \midrule 
-        Green Soil Adjusted Vegetation Index & GSAVI & $\dfrac{1.5(R_{nir} - R_g)}{R_{nir} + R_g + 0.5}$ \\
-        \midrule
-        Infrared Percentage Vegetation Index & IPVI & $\dfrac{R_{nir}}{R_{nir} + R_r}$ \\
-        \midrule
-        Leaf Area Index & LAI & $3.618 \left(\dfrac{2.5 (R_{nir} - R_r)}{R_{nir} + 6R_{R_r} - 7.5 R_b + 1}\right) - 0.118$ \\
-        \midrule
-        Modified Non-Linear Index & MNLI & $\dfrac{1.5(R_{nir}^2 - R_r)}{R_{nir}^2 + R_r + 0.5}$ \\
-        \midrule
-        Modified Soil Adjusted Vegetation Index 2 & MSAVI2 & $\dfrac{2R_{nir} + 1 - \sqrt{(2R_{nir} + 1)^2 - 8(R_{nir} - R_r)}}{2}$ \\
-        \midrule
-        Modified Simple Ratio & MSR & $\dfrac{R_{nir}/R_r - 1}{\sqrt{R_{nir} / R_r} + 1}$ \\
-        \midrule
-        Non-Linear Index & NLI & $\dfrac{R_{nir}^2 - R_r}{R_{nir}^2 + R_r}$ \\
-        \midrule
-        Normalized Difference Vegetation Index & NDVI & $\dfrac{R_{nir} - R_r}{R_{nir} + R_r}$ \\
-        \midrule
-        Normalized Pigment Chlorophyll Index & NPCI & $\dfrac{R_{680} - R_{430}}{R_{680} + R_{430}}$ \\
-        \midrule
-        Optimized Soil Adjusted Vegetation Index & OSAVI & $\dfrac{R_{nir} - R_r}{R_{nir} + R_r + 0.16}$ \\
-        \midrule
-        Renormalized Difference Vegetation Index & RDVI & $\dfrac{R_{nir} - R_r}{\sqrt{R_{nir} + R_r}}$ \\
-        \midrule
-        Soil Adjusted Vegetation Index & SAVI & $\dfrac{1.5(R_{nir} - R_r)}{R_{nir} + R_r + 0.5}$ \\
-        \midrule 
-        Simple Ratio & SR & $\dfrac{R_{nir}}{R_r}$ \\
-        \midrule
-        Transformed Difference Vegetation Index & TDVI & $\dfrac{1.5R_{nir} - R_r}{\sqrt{R_{nir}^2 + R_r + 0.5}}$ \\
-        \midrule
-        Triangular Greenness Index & TGI & $\dfrac{(\lambda_r-\lambda_b)(R_r-R_g) - (\lambda_r-\lambda_g)(R_r - R_b)}{2}$ \\
-        \midrule
-        Visible Atmospherically Resistant Index & VARI & $\dfrac{R_g - R_r}{R_g + R_r - R_b}$ \\
-        \bottomrule
-    \end{tabularx}
-\end{adjustwidth}
-\noindent{\footnotesize{* $\text{eta} = 2(R_{nir}^2 - R_g^2) + 1.5R_{nir} + 0.5R_{r} $ \tab ** $\gamma =1.7$}}
-\end{table}
+%% \section[\appendixname~\thesection]{}\label{appendix:spec-indices}
+%% \subsection[\appendixname~\thesubsection]{}
 

### 2024-01-03 3c_extra-plots.jl

@@ -1,7 +1,5 @@
-using HDF5, CSV, DataFrames, JSON, Tables
-using MLJ, ConformalPrediction
+using CSV, DataFrames, JSON, Tables
 using Random, Statistics
-using ProgressMeter
 using CairoMakie
 using MintsMakieRecipes
 
@@ -43,24 +41,33 @@ names(df_1123)
 Σdownwelling_1209 = df_1209.Σdownwelling
 Σdownwelling_1210 = df_1210.Σdownwelling
 
+nb1, _ = get_n_bins(Σdownwelling_1123)
+nb2, _ = get_n_bins(Σdownwelling_1209)
+nb3, _ = get_n_bins(Σdownwelling_1210)
+
+
 fig = Figure();
-ax = Axis(fig[1,1], xlabel="Total Downwelling Intensity");
-d = density!(ax, Σdownwelling_1123)
-d2 = density!(ax, Σdownwelling_1209)
-d3 = density!(ax, Σdownwelling_1210)
-
-
+ax = Axis(fig[1,1], xlabel="Downwelling Intensity (W/m²)", ylabel="count", title="Downwelling Intensity Variation");
+h1 = hist!(ax, Σdownwelling_1123, bins=nb1, color=(mints_colors[1], 0.7))
+h2 = hist!(ax, Σdownwelling_1209, bins=nb2, color=(mints_colors[2], 0.7))
+h3 = hist!(ax, Σdownwelling_1210, bins=nb3, color=(mints_colors[3], 0.7))
+leg = axislegend(ax, [h1, h2, h3], ["11-23", "12-09", "12-10"], position=:lt)
 fig
+
+save("./paper/figures/results/downwelling-hist.png", fig)
+save("./paper/figures/results/downwelling-hist.pdf", fig)
+
+
 
 Σdownwelling_1123
 Σdownwelling_1209
 Σdownwelling_1210
 
-h5_test_path = "/Users/johnwaczak/data/robot-team/processed/hsi/11-23/Scotty_1/Scotty_1-1.h5"
-@assert isfile(h5_test_path)
+# h5_test_path = "/Users/johnwaczak/data/robot-team/processed/hsi/11-23/Scotty_1/Scotty_1-1.h5"
+# @assert isfile(h5_test_path)
 
-h = h5open(h5_test_path, "r")
-Data = h["data-Δx_0.1/Data"][:,:,:];
[…]

### 2024-01-09 1_make-datasets.jl
added new figures

@@ -52,111 +52,137 @@ end
 
 
 inpaths = Dict(
-    "11-23" => "/Users/johnwaczak/data/robot-team/finalized/11-23",
-    "Full" => "/Users/johnwaczak/data/robot-team/finalized/Full",
-    "12-09" => "/Users/johnwaczak/data/robot-team/finalized/12-09",
-    "12-10" => "/Users/johnwaczak/data/robot-team/finalized/12-10",
+    "11-23" => Dict(
+        "Scotty_1" => "/Users/johnwaczak/data/robot-team/finalized/11-23/Scotty_1",
+        "Scotty_2" => "/Users/johnwaczak/data/robot-team/finalized/11-23/Scotty_2",
+    ),
+    "12-09" => Dict(
+        "NoDye_1" => "/Users/johnwaczak/data/robot-team/finalized/12-09/NoDye_1",
+        "NoDye_2" => "/Users/johnwaczak/data/robot-team/finalized/12-09/NoDye_2",
+    ),
+    "12-10" => Dict(
+        "NoDye_1" => "/Users/johnwaczak/data/robot-team/finalized/12-10/NoDye_1",
+        "NoDye_2" => "/Users/johnwaczak/data/robot-team/finalized/12-10/NoDye_2",
+    ),
 )
 
+
+dfs = Dict(
+    "11-23" => Dict(
+        "Scotty_1" => Dict(
+            "df" => DataFrame(),
+            "feature_names" => [],
+            "target_names" => [],
+        ),
+        "Scotty_2" => Dict(
+            "df" => DataFrame(),
+            "feature_names" => [],
+            "target_names" => [],
+        ),
+    ),
+    "12-09" => Dict(
+        "NoDye_1" => Dict(
+            "df" => DataFrame(),
+            "feature_names" => [],
+            "target_names" => [],
+        ),
+        "NoDye_2" => Dict(
+            "df" => DataFrame(),
+            "feature_names" => [],
+            "target_names" => [],
+        ),
+    ),
+    "12-10" => Dict(
+        "NoDye_1" => Dict(
+            "df" => DataFrame(),
+            "feature_names" => [],
+            "target_names" => [],
+        ),
+        "NoDye_2" => Dict(
+            "df" => DataFrame(),
+            "feature_names" => [],
+            "target_names" => [],
+        ),
+    ),
+)
+
+
 # inpath = "/Volumes/LabData/RobotTeam/finalized/Full"
-for (collection, path) in inpaths
[…]

### 2024-01-09 2_exploratory-data-analysis.jl

@@ -35,7 +35,7 @@ outpath = "/Users/johnwaczak/data/robot-team/supervised"
 
 collections = ["11-23", "12-09", "12-10", "Full"]
 # collections = ["11-23", "Full"]
-
+# collections = ["Full",]
 
 
 targets = String.(keys(targets_dict))

### 2024-01-09 3_feature-exploration.jl

@@ -153,20 +153,25 @@ MODELS[:rfr] = (;
                  :savename => "RandomForestRegressor",
                  :packagename => "DecisionTree",
                  :suffix => "vanilla",
-                 :mdl => RFR(n_subfeatures=-1, sampling_fraction=1.0, n_trees=150),
+                 :mdl => RFR(n_subfeatures=-1, sampling_fraction=0.85, n_trees=150, max_depth=20),
                  )
 
 
 
 # 5. Fit each of the models to different subsets of features.
 
-collections = ["11-23", "Full"]
-# collections = ["Full"]
+# collections = ["11-23", "Full"]
+collections = ["Full"]
 
 
 targets_to_try = [t for t in Symbol.(keys(targets_dict)) if !(t in [:TDS, :Salinity3490, :bg, :Br, :NH4, :Turb3488, :Turb3490])]
 
+# targets_to_try = [:bgm]
+
+
+
 # targets_to_try = [:CDOM,:CO]
+
 # targets_to_try = [:CDOM,]
 
 # targets_to_try = [:Chl]
@@ -204,7 +209,7 @@ for collection ∈ collections
                     target_name, units, target_long,
                     outpath;
                     suffix=model.suffix,
-                    nfolds=10,
+                    nfolds=6,
                 )
 
 
@@ -235,7 +240,7 @@ for collection ∈ collections
                     target_name, units, target_long,
                     model.mdl,
                     outpath;
-                    nfolds=10,
+                    nfolds=6,
                     nmodels=100,
                 )
 
@@ -332,7 +337,7 @@ function generate_tex_table(df)
         mae_str = string(round(row["MAE (mean)"], sigdigits=3)) * " ± " * string(round(row["MAE (std)"], sigdigits=3))
         # r_str = string(round(row["R (mean)"], sigdigits=3)) * " ± " * string(round(row["R (std)"], sigdigits=3))
         unc = " ± " * string(round(row["Estimated Uncertainty"], sigdigits=2))
-        cov = string(round(Int, row["Empirical Coverage"]*100))
+        cov = string(round(row["Empirical Coverage"]*100, digits=1))
 
         out = out * "    $(target_tex) & $(r2_str) & $(rmse_str) & $(mae_str) & $(unc) & $(cov)\\\\\n"
         out = out * "    \\midrule\n"
@@ -349,20 +354,16 @@ end
 
 
 
-collections[1]
[…]

### 2024-01-09 3b_make-maps.jl

@@ -58,7 +58,7 @@ end
 
 # let's open one and extract the data
 # create function to tell if the pixel is on land or not
-function in_water(Datacube, varnames; threshold=0.31)
+function in_water(Datacube, varnames; threshold=0.3)
     idx_ndwi = findfirst(varnames .== "NDWI1")
     return findall(Datacube[idx_ndwi,:,:] .> threshold)
 end
@@ -98,29 +98,29 @@ ETR = @load EvoTreeRegressor pkg=EvoTrees
 
 
 collection = "Full"
+day = "11-23"
+flight = "Scotty_2"
+
+
+day = "12-09"
+flight = "NoDye_1"
+
+
+# flight = "Scotty_1"
 
 # targets_to_map = [t for t in Symbol.(keys(targets_dict)) if !(t in [:TDS, :Salinity3490, :bg, :Br, :NH4, :Turb3488, :Turb3490, :TRYP])]
-#targets_to_map = [:CDOM, :CO, :SpCond, :HDO, :bgm, :Na, :Cl]
-targets_to_map = [:CDOM, :CO,]
+
+# targets_to_map = [:CDOM, :CO, :SpCond, :HDO, :bgm, :Na, :Cl, :Chl]
+targets_to_map = [:bgm]
+
+# targets_to_map = [:CDOM, :CO,]
 # targets_to_map = [:CDOM]
 
 # set up relevant paths
-hsi_11_23 = joinpath(hsipath, "11-23")
-hsi_12_09 = joinpath(hsipath, "12-09")
-hsi_12_10 = joinpath(hsipath, "12-10")
-
-h5_files_11_23 = sort_files_numerical!([joinpath(hsi_11_23, "Scotty_2", f) for f in readdir(joinpath(hsi_11_23, "Scotty_2")) if endswith(f, ".h5")])
-h5_files_11_23 = [f for f in h5_files_11_23 if !any(occursin.(["2-9", "2-16", "2-20", "2-21", "2-22", "2-23"], f))]
-h5_files_12_09 = sort_files_numerical!([joinpath(hsi_12_09, "NoDye_2", f) for f in readdir(joinpath(hsi_12_09, "NoDye_2")) if endswith(f, ".h5")])
-h5_files_12_10 = sort_files_numerical!([joinpath(hsi_12_10, "NoDye_2", f) for f in readdir(joinpath(hsi_12_10, "NoDye_2")) if endswith(f, ".h5")])
-
[…]

### 2024-01-09 3c_extra-plots.jl

@@ -47,10 +47,28 @@ nb3, _ = get_n_bins(Σdownwelling_1210)
 
 
 fig = Figure();
-ax = Axis(fig[1,1], xlabel="Downwelling Intensity (W/m²)", ylabel="count", title="Downwelling Intensity Variation");
+gl = GridLayout(fig[1,1]);
+
+ax_top = Axis(gl[1,1], title="Downwelling Intensity Variation");
+ax = Axis(gl[2,1], xlabel="Downwelling Intensity (W/m²)", ylabel="Counts", );
+
+linkxaxes!(ax_top, ax)
+
+hidedecorations!(ax_top)
+hidespines!(ax_top)
+
 h1 = hist!(ax, Σdownwelling_1123, bins=nb1, color=(mints_colors[1], 0.7))
 h2 = hist!(ax, Σdownwelling_1209, bins=nb2, color=(mints_colors[2], 0.7))
 h3 = hist!(ax, Σdownwelling_1210, bins=nb3, color=(mints_colors[3], 0.7))
+
+d1 = density!(ax_top, Σdownwelling_1123, color=(mints_colors[1], 0.25), strokecolor=(mints_colors[1], 0.75), strokewidth=3)
+d2 = density!(ax_top, Σdownwelling_1209, color=(mints_colors[2], 0.25), strokecolor=(mints_colors[2], 0.75), strokewidth=3)
+d3 = density!(ax_top, Σdownwelling_1210, color=(mints_colors[3], 0.25), strokecolor=(mints_colors[3], 0.75), strokewidth=3)
+
+rowsize!(gl, 1, Relative(0.15))
+rowgap!(gl, 1, Relative(0.001))
+ylims!(ax, 0, nothing)
+
 leg = axislegend(ax, [h1, h2, h3], ["11-23", "12-09", "12-10"], position=:lt)
 fig
 
@@ -59,15 +77,75 @@ save("./paper/figures/results/downwelling-hist.pdf", fig)
 
 
 
-Σdownwelling_1123
-Σdownwelling_1209
-Σdownwelling_1210
+# make another plot of the correlations between all targets to try and explain the
+# ability to predict physical parameters like salinity
 
-# h5_test_path = "/Users/johnwaczak/data/robot-team/processed/hsi/11-23/Scotty_1/Scotty_1-1.h5"
-# @assert isfile(h5_test_path)
+# load full dataset
+function get_targets(target)
[…]

### 2024-01-09 config.jl

@@ -19,9 +19,9 @@ targets_dict = Dict(
     :Na => ["mg/l", "Na⁺", 0.0],
     :OB => ["ppb", "Optical Brighteners", 0.0],
     :RefFuel => ["ppb", "Refined Fuels", 0.0],
-    :Salinity3488 => ["PSS", "Salinity (3488)"],
-    #:Salinity3489 => ["PSS", "Salinity (3489)"],
-    :Salinity3490 => ["PSS", "Salinity (3490)"],
+    :Salinity3488 => ["PSU", "Salinity"],
+    #:Salinity3489 => ["PSU", "Salinity (3489)"],
+    :Salinity3490 => ["PSU", "Salinity"],
     :SpCond => ["μS/cm", "Conductivity"],
     :TDS => ["mg/l", "Total Dissolved Solids", 0.0],
     :TRYP => ["ppb", "Tryptophan", 0.0],
@@ -31,8 +31,8 @@ targets_dict = Dict(
     :Turb3489 => ["FNU", "Turbidity"],
     :Turb3488 => ["FNU", "Turbidity"],
     :Turb3490 => ["FNU", "Turbidity"],
-    :bg => ["ppb", "Blue-Green Algae\nfresh water (Phycocyanin)", 0.0],
-    :bgm => ["ppb", "Blue-Green Algae\nsalt water (Phycoerythrin)", 0.0],
+    :bg => ["ppb", "Blue-Green Algae\n (Phycocyanin)", 0.0],
+    :bgm => ["ppb", "Blue-Green Algae\n (Phycoerythrin)", 0.0],
     :pH => ["", "pH", 0.0],
     :pH_mV => ["mV", "pH"],
 )
@@ -56,8 +56,8 @@ targets_latex= Dict(
     :Na => L"\mathrm{Na^+} (mg/l)",
     :OB => "Optical Brighteners (ppb)",
     :RefFuel => "Refined Fuels (ppb)",
-    :Salinity3488 => "Salinity (PSS)",
-    :Salinity3490 => "Salinity (PSS)",
+    :Salinity3488 => "Salinity (PSU)",
+    :Salinity3490 => "Salinity (PSU)",
     :SpCond => L"Conductivity ($\mu$S/cm)",
     :TDS => "Total Dissolved Solids (mg/l)",
     :TRYP => "Tryptophan (ppb)",
@@ -91,6 +91,7 @@ end
 name_replacements["roll"] = "Roll"
[…]

### 2024-01-09 training-functions.jl

@@ -186,59 +186,59 @@ function train_folds(
 
 
         # run occam
-        @info "\tRunning Occam Selection..."
-        N_features_to_use = [1,5,10,15,25,50,100]
-        r2_vals = Float64[]
-        rmse_vals = Float64[]
+        # @info "\tRunning Occam Selection..."
+        # N_features_to_use = [1,2,3,4,5,10,15,25,50,100]
+        # r2_vals = Float64[]
+        # rmse_vals = Float64[]
 
-        for N_features in N_features_to_use
-            @info "\tEvaluating models for $(N_features) features..."
-            fi_n = @view fi_df[1:N_features, :]
+        # for N_features in N_features_to_use
+        #     @info "\tEvaluating models for $(N_features) features..."
+        #     fi_n = @view fi_df[1:N_features, :]
 
-            try
-                pipe = Pipeline(
-                    selector=FeatureSelector(features=Symbol.(fi_n.feature_name)),
-                    model=mdl,
-                )
+        #     try
+        #         pipe = Pipeline(
+        #             selector=FeatureSelector(features=Symbol.(fi_n.feature_name)),
+        #             model=mdl,
+        #         )
 
 
-                mach = machine(pipe, Xtrain, ytrain)
-                cv = CV(nfolds=6, rng=rng)
+        #         mach = machine(pipe, Xtrain, ytrain)
+        #         cv = CV(nfolds=6, rng=rng)
 
-                e = evaluate!(
-                    mach,
-                    resampling=cv,
-                    measures=[rsq, rmse, mae, cor_coef]
-                )
+        #         e = evaluate!(
+        #             mach,
+        #             resampling=cv,
+        #             measures=[rsq, rmse, mae, cor_coef]
+        #         )
 
-                push!(r2_vals, mean(e.per_fold[1]))
-                push!(rmse_vals, mean(e.per_fold[2]))
+        #         push!(r2_vals, mean(e.per_fold[1]))
+        #         push!(rmse_vals, mean(e.per_fold[2]))
 
-            catch e
-                println(e)
-            end
-        end
+        #     catch e
+        #         println(e)
+        #     end
+        # end
 
-        # now let's plot the error as a function of number of features and pick the best
-        fig = Figure();
[…]

### 2024-01-09 paper/paper.tex

@@
 
-Each day over X terabytes of remote sensing data are collected fr
-
-Context
-
-Need
-
-Task
-
-Objective
+Each day over X terabytes of remote sensing data are collected from...
 
@@
 - Describe our work to create a robotic team which can do all of this...
-
-% https://gisgeography.com/hyperspectral-imaging/
-% https://hyperspectral.azavea.com/
-% https://sentinels.copernicus.eu/web/sentinel/user-guides/sentinel-1-sar/document-library/-/asset_publisher/1dO7RF5fJMbd/content/sentinel-high-level-operations-plan  <-- for amount of data produced by sentinel
-The main areas of usage for hyperspectral imagery can be categorized into 8 groups. This includes vegetation, agriculture, geology, soil, water resources, disaster, and land use.
-
-The underlying principle is that it improves any type of classification.
-For example, you can get more detail for geologic surface composition.
-The same is true for vegetation types, soil classes, and land cover too.
-
-Hyperspectral imaging helps identify pests for crop management.
-Water resources are about understanding bathymetry, water quality, and chemistry.
-And it’s been used for disaster management such as prevention and post-monitoring
-
-Step 1: Introduce your topic
-Step 2: Describe the background
-Step 3: Establish your research problem
-Step 4: Specify your objective(s)
-Step 5: Map out your paper
-
-The introduction should answer three important questions:
-1. What am I writing about?
-2. Why is it important?
-3. What do I want the reader to know about it?
-
-Step 1: Establish a Territory
-"In recent years..." or "researchers have become interested..."
-
-Step 2: Establish a Niche
-- Identify a gap that your research fills
 
@@
 
-\\
-
 somewhere we need to mention the limitations from \cite{robotTeam1} due to low spatial variablility in a single day's collection...
@@
 In his study, we demonstrate that such models can be reliably trained using data collected from multiple observations....
+
+- optically significant substances (OSS)
+- Colored dissolved organic matter (CDOM, also known as yellow substances, humic matter or gelbstoff) includes compounds produced during the decay of plant matter
+- Estimates concentrations of Chlorophyll-a, Total Suspended Solids, and the absorption coefficient of CDOM $a_{CDOM}(400)$ using Medium Resolution Imaging Spectrometer (MERIS) data during bloom in Gulf of Finland.
+They do this using band-ratio algorithms \cite{remote-sensing-finland}.
+-  We should note that band-ratio algroithms are impacted by atmospheric factors like the in-column aerosol distribution.
+- The amounts of aerosols (dust, haze, etc) and gases (ozone, water vapor, etc) present in the atmosphere vary spatially and temporally.
+These variations impact the estimation of water quality characteristics via remote sensing methods \cite{remote-sensing-finland}
+- However, when data from different dates and locations are compared and atmospheric correction is necessary \cite{remote-sensing-finland}.
+
+- Used a support vector machine (SVM) to classify hyperspectral images of vegetation acquired by a UAV and produced a high-resolution classification map \cite{uav-hsi-classification}.
+- Large misclassification occured in shaded areas
+
+For example, Garcia -Ruiz et al.
+(2013) conducted a UAV-based 56 aerial survey with multispectral cameras over a citrus orchard, and found that 57 UAV-based datasets yielded better classification accuracy than aircraft-based 58 datasets for diseased citrus trees.
+Moreover, Peña et al.
+(2013, 2015) applied 59 UAV-based multispectral imaging for the early detection of weed seedlings in 60 combination with object-based image analysis.
 
@@
 The results of fitting our hyperparameter optimized models are listed in Table~\ref{tab:fit-results}.
-For each model, the $R^2$, RMSE, and MAE were evaluated using 10-fold cross validation.
+For each model, the $R^2$, RMSE, and MAE were evaluated using 6-fold cross validation.
 We observe considerable
@@
   \caption{Summary of fitting statistics for each target measurement.
-Values were evaluated using 10-fold cross validation on the training set.
-The estimated uncertainty is evaluated using conformal prediction so that a prediction $\hat{y}\pm \Delta y$ achieves 90\% coverage on the validation holdout set.
-The empirical coverage is the percentage of predictions in the holdout testing set that fall within the confidence interval determined by conformal prediction.
+Models were evaluated using 6-fold cross validation on the training set.
+The estimated uncertainty is evaluated using conformal prediction so that a prediction $\hat{y}\pm \Delta y$ achieves 90\% coverage on the calibration holdout set.
+The empirical coverage is the percentage of predictions in the testing set that fall within the confidence interval determined by conformal prediction.
 \label{tab:fit-results}}
@@
     \midrule
-    Temperature (°C) & 0.999 ± 5.1e-5 & 0.0546 ± 0.0022 & 0.0316 ± 0.0015 & ± 0.084 & 89.7\\
+    Temperature (°C) & 1.0 ± 1.98e-5 & 0.0398 ± 0.00096 & 0.0267 ± 0.00055 &  ± 0.061 & 89.8\\
     \midrule
-    Conductivity ($\mu$S/cm) & 0.999 ± 0.00011 & 0.888 ± 0.067 & 0.497 ± 0.025 & ± 1.3 & 91.5\\
+    Conductivity ($\mu$S/cm) & 0.999 ± 2.17e-5 & 0.853 ± 0.0114 & 0.55 ± 0.00564 &  ± 1.3 & 89.8\\
     \midrule
-    $\mathrm{Ca}^{2+}$ (mg/l) & 0.999 ± 0.00031 & 0.544 ± 0.058 & 0.267 ± 0.013 & ± 0.72 & 89.9\\
+    $\mathrm{Ca}^{2+}$ (mg/l) & 0.999 ± 3.53e-5 & 0.423 ± 0.0101 & 0.243 ± 0.00552 &  ± 0.59 & 89.7\\
     \midrule
-    Dissolved Oxygen (mg/l) & 0.998 ± 0.00015 & 0.0931 ± 0.004 & 0.055 ± 0.0022 & ± 0.14 & 88.5\\
+    Dissolved Oxygen (mg/l) & 0.999 ± 3.17e-5 & 0.0705 ± 0.000984 & 0.0467 ± 0.000418 &  ± 0.11 & 89.8\\
     \midrule
-    Salinity (PSS) & 0.995 ± 0.00061 & 0.00124 ± 6.2e-5 & 0.000432 ± 2.6e-5 & ± 0.0009 & 90.1\\
+    Salinity (PSU) & 0.998 ± 0.000129 & 0.000759 ± 1.8e-5 & 0.000265 ± 6.1e-6 &  ± 0.00051 & 89.6\\
     \midrule
-    Tryptophan (ppb) & 0.989 ± 0.0046 & 0.206 ± 0.046 & 0.117 ± 0.0085 & ± 0.28 & 89.0\\
+    $\mathrm{Cl^-}$ (mg/l) & 0.994 ± 0.000441 & 1.15 ± 0.0418 & 0.578 ± 0.00534 &  ± 1.4 & 90.3\\
     \midrule
-    pH & 0.988 ± 0.0018 & 0.0232 ± 0.0019 & 0.0119 ± 0.00045 & ± 0.032 & 92.5\\
+    $\mathrm{Na^+} (mg/l)$ & 0.992 ± 0.000309 & 6.17 ± 0.134 & 2.85 ± 0.0536 &  ± 7.2 & 89.9\\
     \midrule
-    $\mathrm{Na^+} (mg/l)$ & 0.982 ± 0.0034 & 9.01 ± 0.88 & 4.17 ± 0.22 & ± 11.0 & 90.8\\
+    Tryptophan (ppb) & 0.991 ± 0.00038 & 0.188 ± 0.00404 & 0.112 ± 0.00149 &  ± 0.26 & 89.9\\
     \midrule
-    $\mathrm{Cl^-}$ (mg/l) & 0.982 ± 0.0054 & 1.96 ± 0.28 & 1.0 ± 0.066 & ± 2.3 & 89.7\\
+    pH & 0.991 ± 0.000327 & 0.0177 ± 0.000295 & 0.0109 ± 6.56e-5 &  ± 0.024 & 89.9\\
     \midrule
-    Blue-Green Algae [Phycoerythrin] (ppb) & 0.939 ± 0.017 & 3.12 ± 0.43 & 0.84 ± 0.065 & ± 1.8 & 91.4\\
+    Blue-Green Algae [Phycoerythrin] (ppb) & 0.981 ± 0.00186 & 1.72 ± 0.0947 & 0.608 ± 0.0218 &  ± 1.4 & 90.2\\
     \midrule
-    CDOM (ppb) & 0.934 ± 0.02 & 0.58 ± 0.093 & 0.219 ± 0.013 & ± 0.46 & 90.3\\
+    $\mathrm{NO_3^-} (mg/l-N)$ & 0.968 ± 0.00203 & 0.0308 ± 0.00113 & 0.0146 ± 0.000256 &  ± 0.043 & 89.9\\
     \midrule
-    Optical Brighteners (ppb) & 0.920 ± 0.015 & 0.11 ± 0.0092 & 0.0617 ± 0.0019 & ± 0.13 & 92.4\\
+    CDOM (ppb) & 0.966 ± 0.00228 & 0.464 ± 0.0195 & 0.144 ± 0.00449 &  ± 0.22 & 89.3\\
     \midrule
-    $\mathrm{NO_3^-} (mg/l-N)$ & 0.890 ± 0.013 & 0.0575 ± 0.0036 & 0.0353 ± 0.00091 & ± 0.079 & 90.7\\
+    Chlorophyll A ($\mu$g/l) & 0.924 ± 0.00645 & 1.29 ± 0.0667 & 0.359 ± 0.0079 &  ± 0.73 & 90.2\\
     \midrule
-    Crude Oil (ppb) & 0.890 ± 0.037 & 0.55 ± 0.11 & 0.174 ± 0.019 & ± 0.3 & 89.2\\
+    Optical Brighteners (ppb) & 0.915 ± 0.00406 & 0.118 ± 0.00169 & 0.0568 ± 0.000218 &  ± 0.1 & 89.8\\
     \midrule
-    Chlorophyll A with Red Excitation ($\mu$g/l) & 0.728 ± 0.11 & 94.9 ± 37.0 & 17.0 ± 2.5 &  ± 31.0 & 91.1\\
+    Chlorophyll A with Red Excitation ($\mu$g/l) & 0.909 ± 0.00794 & 77.6 ± 3.91 & 15.6 ± 0.418 &  ± 25.0 & 90.5\\
     \midrule
-    Chlorophyll A ($\mu$g/l) & 0.672 ± 0.17 & 1.96 ± 0.25 & 0.482 ± 0.044 &  ± 0.83 & 90.6\\
+    Crude Oil (ppb) & 0.906 ± 0.00606 & 0.588 ± 0.019 & 0.162 ± 0.00234 &  ± 0.23 & 89.7\\
     \midrule
-    Turbidity (FNU) & 0.616 ± 0.19 & 52.6 ± 23.0 & 7.62 ± 2.2 & ± 9.2 & 87.9\\
+    Turbidity (FNU) & 0.812 ± 0.0158 & 60.2 ± 2.61 & 6.98 ± 0.431 &  ± 3.4 & 89.5\\
     \bottomrule
@@
 
-\subsection{Chemicals-of-Concern}
+\subsection{Biochemical Measurements}
 
@@
 
+\begin{figure}[H]
+\includegraphics[width=10.5 cm]{paper/figures/results/downwelling-hist.pdf}
+\caption{Distribution of total downwelling intensity during each of the three HSI collection flights.
+The multi-modal nature of these distributions reflects the impact of the relative orientation of the drone to the sun as well as potential occlusion due to the presence of clouds.\label{fig:downwelling-hist}}
+\end{figure}
+
 \subsection{Data Product Streaming}
@@
 Future research directions may also be highlighted.
+
+\subsection{Extensions and Next Steps}
+
+The current implementation of conformal prediction utilized in these models estimates a fixed width confidence interval for all outputs.
+This could be improved by training a secondary \textit{residual} model on the errors produced by the base learner, that is, a model which predicts
+\begin{equation}
+    r(X) = \lvert f(X) - y \rvert = \lvert \hat{y} - y \rvert.
+\end{equation}
+In the conformal prediction framework, such a model could then be used to produce \textit{adaptive} uncertainty estimates using the augmented heuristic function
+\begin{equation}
+    S(X,y)  = \dfrac{\lvert \hat{y} - y \rvert }{r(X)}
+\end{equation}
+to produce scores on the calibration holdout set.
+With access to adaptive uncertainty estimates, we can then augment the navigation control for the USV to encourage data collection in regions of high model uncertainty.
+This would further optimize the data collection and calibration procedure at the expense of increased model training times.
 

### 2024-01-09 paper/paper.tex
Updates from Overleaf

@@
 - Large misclassification occured in shaded areas
+- \cite{uav-hsi-classification} calls these technqieus \textit{precision agriculture}
+- \cite{uav-hsi-classification-2} used a UAV aerial survey with multispectral cameras for citrus orchard classification
 
-For example, Garcia -Ruiz et al.
-(2013) conducted a UAV-based 56 aerial survey with multispectral cameras over a citrus orchard, and found that 57 UAV-based datasets yielded better classification accuracy than aircraft-based 58 datasets for diseased citrus trees.
-Moreover, Peña et al.
-(2013, 2015) applied 59 UAV-based multispectral imaging for the early detection of weed seedlings in 60 combination with object-based image analysis.
+- \cite{andres2018review}: \textit{Remote monitoring, via satellite assets and distributed in situ sensors, may help meet many of the challenges of information asymmetry and data gaps in developing countries, including unreliable (and time-consuming) survey data and reliance on spot checks to assess accurate reporting and performance.}
+- \cite{andres2018review}: \textit{(UAVs, or drones), are being used by researchers to map watersheds.
+Structure from Motion (SfM) three-dimensional point clouds can be derived from digital images collected on board UAVs, similar to the type of data produced by Light Detection and Ranging (LiDAR) technology [19].
+The technological development of UAVs and their ability to derive high-resolution 3D information (and with much lower operational and up-front costs than manned airborne platforms) and satellite imaging has made UAV image acquisition appealing in several applications.}
+
+- \cite{robert2017analysis} Used Landsat and MODIS data to estimate suspended particulate matter in the Sahelian (Sahel?) region in Africa. 
+- \cite{robert2017analysis} found near infrared bands are well suited for estimating turbidity and SPM up to $R^2=0.70$.
+- \cite{robert2017analysis} \textit{the strong and variable atmospheric load (aerosols and water vapor) were potentially challenging for a remote sensing approach.}
+
+- \cite{ross2019aquasat} constructed a dataset comprised of 600,000 paired observations of water quality and landsat reflectance for bodies across US from 1984-2019
+- Chlorophyll is a photosynthetically active pigment contained in all phytoplankton
+
+- \cite{lary2010artificial} Neural Networks and Support Vector Machines are popular choices for machine learning applications in remote sesnsing and geoscience
+
+- \cite{kaufman1992atmospherically} Developed the Atmospherically Resistant Vegetation Index (AVRI) for use in vegetation studies which takes advantage of blue band.
+It is reported to be 4-times less sensative to atmospheric effects than NDVI
+
+- \cite{chi2016big} NASA's Earth Science Data and Information System (ESDIS) holds 7.5 PB of data with ~7000 unique data sets.
+
+- Google Earth Engine's public data archive contains over 80 petabytes of data
+
+- \cite{garcia2013comparison} used a multi-band imager equipped UAV to identify citrus greening diseas (Huanglongbing) in Florida citrus trees.
+- Spatial resolution is easily controlled by adjusting the UAV flying altitude.
+
+- \cite{rostom2017evaluation} Evaluated water quality in an Egyptian lake using
 
@@
 
-However, the presence of DOM/POM (dissolved and particulate organic matter), decreases “blue” instrument sensitivity hindering the primary benefit of having a blue excitation fluorometer.
-The “red” chlorophyll sensor effectively eliminates interference effects from DOM/POM, by using a specific set of optics.
-Because these materials don’t absorb red excitation energy, but algae do, red excitation fluorometry is used to detect and estimate algal abundance free from DOM/POM interference.
-Note that although this optical setup is less sensitive for detecting eukaryotic algae, the errors associated with these interference materials may outweigh the increased sensitivity of blue excitation fluorometry.
-Also, red excitation fluorometry is significantly more sensitive to prokaryotic algae (blue-green or cyanobacteria), making it a favorable instrument for freshwater systems which are typically rich in DOM and blue-green algae.
+\subsection{Optically Active Components and Physio-Chemical Parameter Estimation}
+
+We can probably explain the inference of salinity, ion concentrations, etc as being directly related to the observed concentrations of chlorophyll, cdom, co, bgm, etc...
+which are all optically active (i.e.
+have absorption features spectral region of our hyperspectral imager).
+
+\begin{figure}[H]
+\includegraphics[width=10.5 cm]{paper/figures/results/target_correlations.pdf}
+\caption{\label{fig:target-correlations}}
+\end{figure}
+
+\subsection{Data Product Streaming}
 
@@
 \end{figure}
-
-\subsection{Data Product Streaming}
-
-Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
 

### 2024-01-11 3_feature-exploration.jl
tested permutation importance

@@ -34,14 +34,10 @@ using MLJBase: train_test_pairs
 using ConformalPrediction
 using JSON
 
-# using ShapML
-
 
 # for base model prediction:
 # using MLJModelInterface: reformat
 # predict(conf_model.model, mach.fitresult, reformat(conf_model.model, Xtest)...)
-
-
 
 
 # seed reproducible pseudo-random number generator

### 2024-01-11 3d_permutation-importance.jl

@@ -1,0 +1,190 @@
+using CSV, DataFrames
+using ProgressMeter
+using Statistics
+using Random
+
+using Dates
+using CairoMakie
+using MintsMakieRecipes
+
+set_theme!(mints_theme)
+update_theme!(
+    figure_padding=30,
+    Axis=(
+        xticklabelsize=20,
+        yticklabelsize=20,
+        xlabelsize=22,
+        ylabelsize=22,
+        titlesize=25,
+    ),
+    Colorbar=(
+        ticklabelsize=20,
+        labelsize=22
+    )
+)
+
+#using MLJ, Flux, ConformalPrediction
+using MLJ, Flux
+using MLJBase: train_test_pairs
+
+# add in ConformalPrediction via GitHub until my fix ships
+# using Pkg
+# Pkg.add(url="https://github.com/JuliaTrustworthyAI/ConformalPrediction.jl.git")
+using ConformalPrediction
+using JSON
+
+
+include("./config.jl")
+include("./viz.jl")
+include("./training-functions.jl")
+
+
+
+ETR = @load EvoTreeRegressor pkg=EvoTrees
+RFR = @load RandomForestRegressor pkg=DecisionTree
+
+
+
+
+# load the CDOM dataset and vanilla RFR & ETR models
+target = :CDOM
+target_name = String(target)
+target_long = targets_dict[target][2]
+units = targets_dict[target][1]
+
+collection = "Full"
+
+
+
+
+
+datapath = "/Users/johnwaczak/data/robot-team/supervised"
+data_path = joinpath(datapath, collection, target_name, "data")
+
+etr_path = joinpath(datapath, collection, target_name, "models", "EvoTreeRegressor", "default", "EvoTreeRegressor"*"__vanilla.jls")
+rfr_path = joinpath(datapath, collection, target_name, "models", "RandomForestRegressor", "default", "RandomForestRegressor"*"__vanilla.jls")
+
+@assert ispath(datapath)
+@assert ispath(data_path)
+@assert ispath(etr_path)
+@assert ispath(rfr_path)
+
+
+X = CSV.read(joinpath(data_path, "X.csv"), DataFrame)
+y = CSV.read(joinpath(data_path, "y.csv"), DataFrame)[:,1]
+idx_train = CSV.read(joinpath(data_path, "idx_train.csv"), DataFrame)[:,1]
[…]

### 2024-01-11 config.jl

@@ -125,6 +125,7 @@ name_replacements["NDVI"] = "Normalized Difference Vegetation Index"
 name_replacements["NPCI"] = "Normalized Pigment Chlorophyll Index"
 name_replacements["OSAVI"] = "Optimized Soil Ajusted Vegetation Index"
 name_replacements["RDVI"] = "Renormalized Difference Vegetation Index"
+name_replacements["SAVI"] = "Soil Adjusted Vegetation Index"
 name_replacements["SR"] = "Simple Ratio"
 name_replacements["TDVI"] = "Transformed Difference Vegetation Index"
 name_replacements["TGI"] = "Triangular Greenness Index"

### 2024-01-11 paper/paper.tex
Updates from Overleaf

@@
 
-The USV employed in the robot team is the Maritime Robotics Otter which features a flexible modular design and 20 hour battery life.
+The USV employed in the robot team is a Maritime Robotics Otter which features a modular design and 20 hour battery life.
 The USV is equipped with an in-situ sensing payload utilizing a combination of Eureka Manta-40 multi-probes including fluorometers, ion selective electrodes, and other physical sensors which together enable the collection of comprehensive near-surface measurements including Colored Dissolved Organic Matter (CDOM), Crude Oil, Blue-Green Algae (phycoerythrin and phycocyanin), Chlorophyll-A, Tryptophan, $\mathrm{Na^+}$, $\mathrm{Ca^{2+}}$, $\mathrm{Cl^-}$, Temperature, Conductivity, and many others.
-The full list of measurements used in this study is given in Table~\ref{tab:sensors}.
+The full list of measurements utilized in this study is given in Table~\ref{tab:sensors}.
 Additionally, the USV is equipped with an ultra-sonic weather monitoring sensor for measuring air speed and direction as well as a a BioSonics MX Aquatic Habitat Echosounder sonar which are not explored in this study.
@@
 \end{tabularx}
-\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
+% \noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
 \end{table}
@@
 Each scan-line consists of 1600 pixels for which incoming light is diffracted into 462 wavelength bins.
-In the collection software a regular cutoff of 1000 lines is chosen so that each resulting \textit{image} forms a tensor of size 462$\times$1600$\times$1000 called a \textit{hyperspectral data cube}.
+In the collection software, a regular cutoff of 1000 lines is chosen so that each resulting \textit{image} forms a array of size 462$\times$1600$\times$1000 called a \textit{hyperspectral data cube}.
 Initially, the sampled spectra are in units of spectral radiance (measured in microflicks) however this does not account for the variability of incident light illuminating the water.
@@
 \begin{equation}
-    R(\lambda) = \pi L(\lambda)/E(\lambda)
+    R(\lambda) = \pi L(\lambda)/E_d(\lambda)
 \end{equation}
-where $L$ is the spectral radiance, $E$ is the downwelling irradiance, and a factor of $\pi$ steradians resutls from assuming the water surface is Lambertian (diffuse) \cite{reflectance-conversion}.
+where $L$ is the spectral radiance, $E_d$ is the downwelling irradiance, and a factor of $\pi$ steradians results from assuming the water surface is Lambertian (diffuse) \cite{reflectance-conversion}.
 We will address the impact of this assumption in Section~\ref{sec:discussion}.
 
-Having converted the hyperspectral data cube to units of reflectance, we must also georeference each pixel into geographic coordinate system so that each image pixel can be assigned a latitude and longitude corresponding to the location on the ground from which it was sampled.
+Having converted the hyperspectral data cube to units of reflectance, we must also georeference each pixel into a geographic coordinate system so that each image pixel can be assigned a latitude and longitude corresponding to the location on the ground from which it was sampled.
 During our three surveys, the UAV was flown at an altitude of ~50 m above the water.
@@
 \end{figure}
+
 The above processing pipeline was implemented using the Julia programming language, a just-in-time compiled language with native multi-theading support \cite{julia-1}.
 By running this pipeline on the on-board processing computer, we are able to process the collected hyperspectral data cubes in near real time.
-This feature is critical for time-sensitive applications where we need to quickly asses if an area is safe and can not afford to wait to download and post-process collected imagery after a flight.
+This feature is critical for time-sensitive applications where we need to quickly asses if an area is safe and can not afford to wait to download and post-process collected imagery \textit{after} a flight.
 
@@
 Data were collected using the robot team at a site in north Texas across three observation periods in the fall of 2020.
-For each collection period, the UAV first completed a wide survey of the lake capturing hyperspectral data cubes.
+For each collection period, the UAV first completed two wide surveys of the lake capturing multiple hyperspectral data cubes.
 Subsequently, the the USV sampled across the lake, collecting in-situ reference measurements.
 Each of these reference measurements was then collocated with individual pixel spectra where the USV track overlapped with UAV pixels.
+To account for any time-delays in the values measured by the in-situ instruments and to account for the fact the the USV is larger than the final resolution of our resampled HSI, each in-siture measurent is associated with a 3$\times$3 grid of HSI pixels, that is, a 30 cm $\times$ 30 cm square.
 These combined data form a tabular data set on which we seek use to train regression models; pixel spectra form input features and each separate USV sensor forms a distinct target variable.
-Together, this combined data set contains over 11,000 records.
+Together, this combined data set contains over 130,000 records.
 
-Each collection was performed near solar noon to maximize the amount of incident sunlight illuminating the water, however, to account for any potential variation in lighting conditions between data cubes, we augment the training set with additional features including the drone viewing geometry (roll, pitch, heading) and solar illumination geometry (solar azimuth, solar elevation, solar zenith) as wall as the total at-pixel intensity (before refelctance conversion) as well as the total downwelling intensity.
-Additional feature engineering is performed to add a combination of spectral indices like the normalized difference vegetation index (NDVI), modified normalized difference water index (mNDWI), simple ratio (SR), photochemical reflectance index (PRI), and more (see Appendix~\ref{appendix:spec-indices} for a full list of included spectral indices).
+Each collection was performed near solar noon to maximize the amount of incident sunlight illuminating the water, however, to account for any potential variation in lighting conditions between data cubes, we augment the training set with additional features including the drone viewing geometry (roll, pitch, heading) and solar illumination geometry (solar azimuth, solar elevation, solar zenith) as well as the total at-pixel intensity (before refelctance conversion), the total downwelling intensity, and the drone altitude.
+Feature engineering is performed to add a additional spectral indices utilizing combinations of specific wavelength bands like the normalized difference vegetation index (NDVI), normalized difference water index (NDWI), simple ratio (SR), photochemical reflectance index (PRI), and more as described in \cite{envi_vegetation_indices, thenkabail2018hyperspectral,kaufman1992atmospherically, SpectralIndexWheat}.
+A comprehensive list of these added features is provided in supplementary table S1.
 
@@
 
-For each of the 17 target variables listed in Table~\ref{tab:sensors}, data were randomly partitioned into a 90:10 training/testing split resulting 10,005 training points and 1,112 holdout testing points.
+For each of the 17 target variables listed in Table~\ref{tab:sensors}, data were randomly partitioned into a 90:10 training/testing split resulting 120,350 training points and 13,372 holdout testing points.
 Using the MLJ machine learning framework, a variety of machine learning models compatible with the regression task were identified \cite{MLJ1}.
 This selection of models included linear regression (and it's variations), Gaussian Process Regression, shallow Neural Networks, and decision tree based models.
-Out of this set, Random Forest Regression from \cite{decision-trees} and a native Julia implementation of gradient boosted trees were selected for their quick training time and high performance.
+Out of this set, Random Forest Regression from \cite{decision-trees} and a native Julia implementation of gradient boosted tree regression from the EvoTrees package were selected for their quick training and inference times.
 Both random forests and gradient boosted trees are ensembling techniques based on individual decision tree regressors \cite{decision-trees, random-forest, gradient-boosting}.
+These tree-based methods also enable an impurity based ranking of the relative \textit{importance} of each feature to the target predictions as described in \cite{rfr-orig,rfr-importance-ranking}.
+We use these feature rankings to identify the most impactful features and perform feature selection and reduction.
 
-Each model was trained and hyperparameter optimized using 10-fold cross validation with a random hyperparameter search.
-Model performance was evaluated by computing out-of-fold values for the $R^2$ (coefficient of determination), as well as
+The training procedure for each model is as follow: First, the model is trained using 6-fold cross validation on the training set with default hyperparameters.
+Feature importances for the trained model are then computed and the top 25 features are identified.
+A second, reduced-feature model is then trained using the same 6-fold cross validation technique to ensure an improvement in model performance.
+Next, each model is hyperparameter optimized using a random parameter search.
+Model performance is evaluated by computing out-of-fold values for the $R^2$ (coefficient of determination), as well as
 \begin{align}
@@
 where RMSE is the root-mean-square error, and MAE is the mean absolute error between true values $y_i$ and predictions $\hat{y}_i$.
-To assess the uncertainty of model predictions, we employ Inductive Conformal Prediction as described in \cite{conformal-prediction-1, conformal-prediction-2, conformal-prediction-3, conformal-prediction-4}.
-To do this, the training set is further partitioned so that we obtain an additional hold out set which we may call the \textit{calibration set}.
-We chose this split to achieve a 80:10:10 training, calibration, and testing ratios which results in a calibration set of ~1,000 records which \cite{conformal-prediction-2} suggest to be sufficient for most cases.
-First, the chosen model is trained on the training set.
-We then compute a set of nonconformity scores on the calibration set using an uncertainty heuristic, in this case, the absolute error
+
+Having identified the model with the best out-of-fold performance, we proceed to train the final hyperparameter optimized model on the full training set.
+To assess the uncertainty of the final model's predictions, we employ Inductive Conformal Prediction as described in \cite{conformal-prediction-1, conformal-prediction-2, conformal-prediction-3, conformal-prediction-4}.
+To do this, the training set is further partitioned so that we obtain an additional validation hold out set with the split chosen to achieve a 80:10:10 training, validation, and testing ratio.
+This resulting validation set contains >10,000 records which \cite{conformal-prediction-2} suggests to be more than sufficient for most cases.
+
+The hyperparameter optimized model is trained on the full training set.
+We then compute a set of nonconformity scores on the validation set using an uncertainty heuristic, in this case, the absolute error
 \begin{equation}
@@
 Predictions intervals for new data are then formed as $f(X)\pm d$.
-For this study, we have chosen a coverage of $\alpha=0.9$.
+For this study, we have chosen a coverage of $\alpha=0.9$ corresponding to a 90\% confidence interval.
+Finally, each of these resulting hyperparameter optimized models is evaluated on the previously untouched testing set.
 
@@
 The empirical coverage is the percentage of predictions in the testing set that fall within the confidence interval determined by conformal prediction.
+The final column shows the best performing model.
 \label{tab:fit-results}}
@@
   \newcolumntype{C}{>{\centering\arraybackslash}X}
-  \begin{tabularx}{\fulllength}{CCCCCC}
+  \begin{tabularx}{\fulllength}{CCCCCCC}
     \toprule
-    \textbf{Target (units)} & \textbf{$\text{R}^2$} & \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty} & \textbf{Empirical Coverage (\%)}\\
+    \textbf{Target (units)} & \textbf{$\text{R}^2$} & \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty} & \textbf{Empirical Coverage (\%)} & \textbf{Model*}\\
     \midrule
-    Temperature (°C) & 1.0 ± 1.98e-5 & 0.0398 ± 0.00096 & 0.0267 ± 0.00055 &  ± 0.061 & 89.8\\
-    \midrule
+    Temperature (°C) & 1.0 ± 1.98e-5 & 0.0398 ± 0.00096 & 0.0267 ± 0.00055 &  ± 0.061 & 89.8 &\\
     Conductivity ($\mu$S/cm) & 0.999 ± 2.17e-5 & 0.853 ± 0.0114 & 0.55 ± 0.00564 &  ± 1.3 & 89.8\\
-    \midrule
     $\mathrm{Ca}^{2+}$ (mg/l) & 0.999 ± 3.53e-5 & 0.423 ± 0.0101 & 0.243 ± 0.00552 &  ± 0.59 & 89.7\\
-    \midrule
     Dissolved Oxygen (mg/l) & 0.999 ± 3.17e-5 & 0.0705 ± 0.000984 & 0.0467 ± 0.000418 &  ± 0.11 & 89.8\\
-    \midrule
     Salinity (PSU) & 0.998 ± 0.000129 & 0.000759 ± 1.8e-5 & 0.000265 ± 6.1e-6 &  ± 0.00051 & 89.6\\
-    \midrule
     $\mathrm{Cl^-}$ (mg/l) & 0.994 ± 0.000441 & 1.15 ± 0.0418 & 0.578 ± 0.00534 &  ± 1.4 & 90.3\\
-    \midrule
     $\mathrm{Na^+} (mg/l)$ & 0.992 ± 0.000309 & 6.17 ± 0.134 & 2.85 ± 0.0536 &  ± 7.2 & 89.9\\
-    \midrule
     Tryptophan (ppb) & 0.991 ± 0.00038 & 0.188 ± 0.00404 & 0.112 ± 0.00149 &  ± 0.26 & 89.9\\
-    \midrule
     pH & 0.991 ± 0.000327 & 0.0177 ± 0.000295 & 0.0109 ± 6.56e-5 &  ± 0.024 & 89.9\\
-    \midrule
     Blue-Green Algae [Phycoerythrin] (ppb) & 0.981 ± 0.00186 & 1.72 ± 0.0947 & 0.608 ± 0.0218 &  ± 1.4 & 90.2\\
-    \midrule
     $\mathrm{NO_3^-} (mg/l-N)$ & 0.968 ± 0.00203 & 0.0308 ± 0.00113 & 0.0146 ± 0.000256 &  ± 0.043 & 89.9\\
-    \midrule
     CDOM (ppb) & 0.966 ± 0.00228 & 0.464 ± 0.0195 & 0.144 ± 0.00449 &  ± 0.22 & 89.3\\
-    \midrule
     Chlorophyll A ($\mu$g/l) & 0.924 ± 0.00645 & 1.29 ± 0.0667 & 0.359 ± 0.0079 &  ± 0.73 & 90.2\\
-    \midrule
     Optical Brighteners (ppb) & 0.915 ± 0.00406 & 0.118 ± 0.00169 & 0.0568 ± 0.000218 &  ± 0.1 & 89.8\\
-    \midrule
     Chlorophyll A with Red Excitation ($\mu$g/l) & 0.909 ± 0.00794 & 77.6 ± 3.91 & 15.6 ± 0.418 &  ± 25.0 & 90.5\\
-    \midrule
     Crude Oil (ppb) & 0.906 ± 0.00606 & 0.588 ± 0.019 & 0.162 ± 0.00234 &  ± 0.23 & 89.7\\
-    \midrule
     Turbidity (FNU) & 0.812 ± 0.0158 & 60.2 ± 2.61 & 6.98 ± 0.431 &  ± 3.4 & 89.5\\
@@
   \end{adjustwidth}
+  \noindent{\footnotesize{* RFR = Random Forest Regressor, ETR = EvoTree Regressor}}
 \end{table}
@@
 %% optional
-%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}
+\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Table S1: Hyperspectral Reflectance Indices.}
 

### 2024-01-15 1_make-datasets.jl
updated with new bounds on targets

@@ -321,6 +321,13 @@ df_full = df_full[:, Not([:longitude, :latitude])]
 
 
 
+CSV.write(joinpath("/Users/johnwaczak/data/robot-team/finalized/Full/df_11_23.csv"), df_11_23)
+CSV.write(joinpath("/Users/johnwaczak/data/robot-team/finalized/Full/df_12_09.csv"), df_12_09)
+CSV.write(joinpath("/Users/johnwaczak/data/robot-team/finalized/Full/df_12_10.csv"), df_12_10)
+CSV.write(joinpath("/Users/johnwaczak/data/robot-team/finalized/Full/df_full.csv"), df_full)
+
+
+
 collections = ["11-23", "12-09", "12-10", "Full"]
 dfs_out = [df_11_23, df_12_09, df_12_10, df_full]
 dfs_latlong = [df_latlong_11_23, df_latlong_12_09, df_latlong_12_10, df_latlong_full]
@@ -363,15 +370,34 @@ for i in 1:length(collections)
         end
 
         (y,X) = make_datasets(df_out, target_name, feature_names)
-        idx_train, idx_test = partition(eachindex(y), 0.9, shuffle=true, rng=rng)
+
+
+        # get quantiles
+        if target in keys(target_ranges)
+            q_low = target_ranges[target][1]
+            q_high = target_ranges[target][2]
+        else
+            q_low = minimum(y)
+            q_high = maximum(y)
+        end
+
+        idx_to_use = findall(y .>= q_low .&& y .<= q_high)
+
+        X_out = X[idx_to_use, :]
+        y_out = y[idx_to_use]
+
+        df_latlong_out = df_latlong[idx_to_use, :]
+
+
+        idx_train, idx_test = partition(eachindex(y_out), 0.9, shuffle=true, rng=rng)
 
 
         CSV.write(joinpath(outpath_final, "idx_train.csv"), DataFrame(Dict(:idx => idx_train)))
         CSV.write(joinpath(outpath_final, "idx_test.csv"), DataFrame(Dict(:idx => idx_test)))
 
-        CSV.write(joinpath(outpath_final, "X.csv"), X)
-        CSV.write(joinpath(outpath_final, "y.csv"), DataFrame(Dict(target => y)))
-        CSV.write(joinpath(outpath_final, "lat_lon.csv"), df_latlong)
+        CSV.write(joinpath(outpath_final, "X.csv"), X_out)
[…]

### 2024-01-15 2_exploratory-data-analysis.jl

@@ -64,18 +64,6 @@ for collection in collections
         X = CSV.read(joinpath(data_path, "X.csv"), DataFrame)
         y = CSV.read(joinpath(data_path, "y.csv"), DataFrame)[:,1]
 
-        nbins = 1
-        bin_width = maximum(y) - minimum(y)
-        try
-            nbins, bin_width = get_n_bins(y)
-        catch e
-            println("Failed to find n_bins")
-            nbins = 30
-            bin_width = (maximum(y) - minimum(y))/nbins
-        end
-
-
-
 
         # compute correlation matrix between reflectances
         @info "\t\tcomputing inter-feature correlations"
@@ -114,14 +102,30 @@ for collection in collections
         # generate target histogram/distribution visualization
         @info "\t\tgenerating histogram..."
 
+        # y_hist = y[y .>= quantile(y,0.05) .&& y .<= quantile(y, 0.95)]
+        y_hist = y
+
+        nbins = 1
+        bin_width = maximum(y_hist) - minimum(y_hist)
+        try
+            nbins, bin_width = get_n_bins(y_hist)
+            @info "\t\t\tNbins=$(nbins)"
+            # nbins = minimum(nbins, 75)
+        catch e
+            println("Failed to find n_bins")
+            nbins = 30
+            bin_width = (maximum(y_hist) - minimum(y_hist))/nbins
+        end
+
         fig = Figure();
 
-        ax = Axis(fig[1,1], xlabel="$(pretty_name) ($(units))", ylabel="Counts", title="N bins = $(nbins), bin width=$(round(bin_width, digits=3))")
+        ax = Axis(fig[1,1], xlabel="$(pretty_name) ($(units))", ylabel="Counts") # , title="N bins = $(nbins), bin width=$(round(bin_width, digits=3))")
         ax2 = Axis(fig[1,1], yaxisposition=:right)
         linkxaxes!(ax, ax2)
 
-        h = hist!(ax, y; bins=nbins, color=(mints_colors[1], 0.75), normalization=:none)
-        d = density!(ax2, y[:,1], color=(mints_colors[2], 0.25), strokecolor=(mints_colors[2],0.75), strokewidth=3)
+        h = hist!(ax, y_hist; bins=nbins, color=(mints_colors[1], 0.75), normalization=:none)
[…]

### 2024-01-15 3_feature-exploration.jl

@@ -35,9 +35,12 @@ using ConformalPrediction
 using JSON
 
 
+
 # for base model prediction:
 # using MLJModelInterface: reformat
 # predict(conf_model.model, mach.fitresult, reformat(conf_model.model, Xtest)...)
+
+
 
 
 # seed reproducible pseudo-random number generator
@@ -160,16 +163,34 @@ MODELS[:rfr] = (;
 collections = ["Full"]
 
 
-targets_to_try = [t for t in Symbol.(keys(targets_dict)) if !(t in [:TDS, :Salinity3490, :bg, :Br, :NH4, :Turb3488, :Turb3490])]
+# targets_to_try = [t for t in Symbol.(keys(targets_dict)) if !(t in [:TDS, :Salinity3490, :bg, :Br, :NH4, :Turb3488, :Turb3490])]
+
+
+targets_to_try= [
+    :Temp3488,
+    :SpCond,
+    :Ca,
+    :HDO,
+    :Cl,
+    :Na,
+    :pH,
+    :bg,
+    :bgm,
+    :CDOM,
+    :Chl,
+    :OB,
+    :ChlRed,
+    :CO,
+    :Turb3489,
+    :RefFuel
+]
+
+
+
 
 # targets_to_try = [:bgm]
-
-
-
 # targets_to_try = [:CDOM,:CO]
-
 # targets_to_try = [:CDOM,]
-
 # targets_to_try = [:Chl]
 
 for collection ∈ collections
@@ -336,7 +357,6 @@ function generate_tex_table(df)
         cov = string(round(row["Empirical Coverage"]*100, digits=1))
 
         out = out * "    $(target_tex) & $(r2_str) & $(rmse_str) & $(mae_str) & $(unc) & $(cov)\\\\\n"
-        out = out * "    \\midrule\n"
     end
 
     out = out * "    \\bottomrule\n"

### 2024-01-15 3b_make-maps.jl

@@ -100,70 +100,172 @@ ETR = @load EvoTreeRegressor pkg=EvoTrees
 collection = "Full"
 day = "11-23"
 flight = "Scotty_2"
+# flight = "Scotty_1"
 
 
-day = "12-09"
-flight = "NoDye_1"
+# day = "12-09"
+# flight = "NoDye_1"
+
+
 
 
 # flight = "Scotty_1"
 
 # targets_to_map = [t for t in Symbol.(keys(targets_dict)) if !(t in [:TDS, :Salinity3490, :bg, :Br, :NH4, :Turb3488, :Turb3490, :TRYP])]
 
-# targets_to_map = [:CDOM, :CO, :SpCond, :HDO, :bgm, :Na, :Cl, :Chl]
-targets_to_map = [:bgm]
 
-# targets_to_map = [:CDOM, :CO,]
+# targets_to_map = [
+#     :Temp3488,
+#     :SpCond,
+#     :Ca,
+#     :HDO,
+#     :Cl,
+#     :Na,
+#     :pH,
+#     :bgm,
+#     :CDOM,
+#     :Chl,
+#     :OB,
+#     :ChlRed,
+#     :CO,
+#     :Turb3489
+# ]
+
+
+targets_to_map = [
+    :Temp3488,
+    :SpCond,
+    :Ca,
+    :HDO,
+    :Cl,
+    :Na,
+    :pH,
+    :bg,
+    :bgm,
+    :CDOM,
+    :Chl,
+    :OB,
+    :ChlRed,
+    :CO,
+    :Turb3489,
+#    :RefFuel,
+]
+
+#targets_to_map = [:HDO, :pH]
+
 # targets_to_map = [:CDOM]
+
 
 # set up relevant paths
 hsi_paths = joinpath(hsipath, day)
-h5_files = sort_files_numerical!([joinpath(hsi_paths, flight, f) for f in readdir(joinpath(hsi_paths, flight)) if endswith(f, ".h5")])
-h5_files_to_use = [f for f in h5_files if !(split(f, "/")[end] in bad_hsi_dict[day][flight])]
+
+# h5_files = sort_files_numerical!([joinpath(hsi_paths, flight, f) for f in readdir(joinpath(hsi_paths, flight)) if endswith(f, ".h5")])
+# h5_files_to_use = [f for f in h5_files if !(split(f, "/")[end] in bad_hsi_dict[day][flight])]
+
+
+flight = "Scotty_1"
[…]

### 2024-01-15 3c_extra-plots.jl

@@ -1,5 +1,5 @@
 using CSV, DataFrames, JSON, Tables
-using Random, Statistics
+using Random, Statistics, StatsBase
 using CairoMakie
 using MintsMakieRecipes
 
@@ -76,54 +76,98 @@ save("./paper/figures/results/downwelling-hist.png", fig)
 save("./paper/figures/results/downwelling-hist.pdf", fig)
 
 
-
 # make another plot of the correlations between all targets to try and explain the
 # ability to predict physical parameters like salinity
 
-# load full dataset
-function get_targets(target)
-    target_name = String.(target)
-
-    df_1123 = CSV.read(joinpath(datapath, "11-23", target_name, "data", "y.csv"), DataFrame)
-    df_1209 = CSV.read(joinpath(datapath, "12-09", target_name, "data", "y.csv"), DataFrame)
-    df_1210 = CSV.read(joinpath(datapath, "12-10", target_name, "data", "y.csv"), DataFrame)
-
-    return vcat(df_1123, df_1209, df_1210)
-end
-
-get_targets(:CDOM)
 
 
 
-targets_to_try = [t for t in Symbol.(keys(targets_dict)) if !(t in [:TDS, :Salinity3490, :bg, :Br, :NH4, :Turb3488, :Turb3490])]
 
-targets_to_try = [
+targets_to_try= [
     :Temp3488,
     :SpCond,
     :Ca,
     :HDO,
-    :Salinity3488,
     :Cl,
     :Na,
-    :TRYP,
     :pH,
+    :bg,
     :bgm,
-    :NO3,
     :CDOM,
     :Chl,
     :OB,
     :ChlRed,
     :CO,
-    :Turb3490
+    :Turb3489,
+    #:RefFuel
 ]
 
-df_targets = hcat([get_targets(t) for t in targets_to_try]...)
-
-names(df_targets)
 
 
+# df_1123 = CSV.read(joinpath("/Users/johnwaczak/data/robot-team/finalized/Full/df_11_23.csv"), DataFrame)
+# df_1209 = CSV.read(joinpath("/Users/johnwaczak/data/robot-team/finalized/Full/df_12_09.csv"), DataFrame)
+# df_1210 = CSV.read(joinpath("/Users/johnwaczak/data/robot-team/finalized/Full/df_12_10.csv"), DataFrame)
[…]

### 2024-01-15 3d_permutation-importance.jl

@@ -56,6 +56,9 @@ collection = "Full"
 
 
 
+target = :Turb3489
+target_name = String(target)
+
 
 
 datapath = "/Users/johnwaczak/data/robot-team/supervised"
@@ -75,6 +78,21 @@ y = CSV.read(joinpath(data_path, "y.csv"), DataFrame)[:,1]
 idx_train = CSV.read(joinpath(data_path, "idx_train.csv"), DataFrame)[:,1]
 idx_test= CSV.read(joinpath(data_path, "idx_test.csv"), DataFrame)[:,1]
 
+
+
+mean(y)
+median(y)
+extrema(y)
+std(y)
+
+fig,ax,d = density(y[y .< 10])
+xlims!(ax, 0, 10)
+fig
+
+quantile(y, 0.90)
+
+
+sum(y .> 100) ./ length(y)
 
 mach_etr = machine(etr_path)
 mach_rfr = machine(rfr_path)

### 2024-01-15 config.jl

@@ -33,11 +33,28 @@ targets_dict = Dict(
     :Turb3490 => ["FNU", "Turbidity"],
     :bg => ["ppb", "Blue-Green Algae\n (Phycocyanin)", 0.0],
     :bgm => ["ppb", "Blue-Green Algae\n (Phycoerythrin)", 0.0],
-    :pH => ["", "pH", 0.0],
+    :pH => ["0-14", "pH", 0.0],
     :pH_mV => ["mV", "pH"],
 )
 
-
+target_ranges = Dict(
+    :Temp3488 => (8.4, 14),
+    :SpCond => (784, 873),
+    :Ca => (0, 57),
+    :HDO => (8, 14),
+    :Cl => (0, 100),
+    :Na => (0, 401),
+    :pH => (7.9, 8.7),
+    :bg => (0, 10),
+    :bgm => (0, 40),
+    :CDOM => (12, 22),
+    :Chl => (0, 10),
+    :OB => (2.5, 5.1),
+    :ChlRed => (0, 50),
+    :CO => (20, 28.2),
+    :Turb3489 => (0, 100),
+    :RefFuel => (1.55, 2.4),
+)
 
 using LaTeXStrings
 

### 2024-01-15 training-functions.jl

@@ -938,70 +938,74 @@ function train_hpo(
     ytrain = @view y[idx_train]
     ytest = @view y[idx_test]
 
+    # only do hpo search if results don't already exist...
+    if !ispath(joinpath(path_to_use, "hp_defaults.json"))
+        @info "\tNo HPO Model found... running optimization."
+        # set up hyperparameter ranges
+        rs = []
+
+        # Either add allowed values or ranges for hyperparameters
+        for item in hpo_ranges[packagename][savename]
+            if :values ∈ keys(item)
+                push!(rs, range(mdl, item.hpname, values=item.values))
+            else
+                push!(rs, range(mdl, item.hpname, lower=item.lower, upper=item.upper))
+            end
+        end
 
 
-    # set up hyperparameter ranges
-    rs = []
+        @info "\tPerforming hyperparameter optimization..."
 
-    # Either add allowed values or ranges for hyperparameters
-    for item in hpo_ranges[packagename][savename]
-        if :values ∈ keys(item)
-            push!(rs, range(mdl, item.hpname, values=item.values))
-        else
-            push!(rs, range(mdl, item.hpname, lower=item.lower, upper=item.upper))
+
+        # search for hyperparameters without doing conformal prediction
+        tuning = RandomSearch(rng=rng)
+
+        tuning_pipe = TunedModel(
+            model=mdl,
+            range=rs,
+            tuning=tuning,
+            measures=[mae, rmse, rsq],
+            # resampling=[(idx_train, idx_test),],
+            resampling=CV(nfolds=6, rng=rng),
+            n=nmodels,
+            cache=false,
+        )
+
+        mach = machine(tuning_pipe, Xtrain, ytrain; cache=false)  # <- data leakage covered by resampling strategy above
+
+        @info "\tStarting training..."
+        fit!(mach) #, verbosity=0)
+
+        @info "\t...\tFinished training"
+
+        open(joinpath(path_to_use, "$(savename)__hpo.txt"), "w") do f
+            show(f,"text/plain", fitted_params(mach).best_model)
+            println(f, "\n")
+            println(f,"---------------------")
+            show(f,"text/plain", fitted_params(mach).best_fitted_params)
+            println(f,"\n")
+            println(f,"---------------------")
+            show(f,"text/plain", report(mach).best_history_entry)
+            println(f,"\n")
+        end
+
+
[…]

### 2024-01-15 3_feature-exploration.jl
adding permutation importance

@@ -341,9 +341,9 @@ function generate_tex_table(df)
     out = out * "  \\caption{This is a table caption.\\label{tab:fit-results}}\n"
     out = out * "  \\begin{adjustwidth}{-\\extralength}{0cm}\n"
     out = out * "  \\newcolumntype{C}{>{\\centering\\arraybackslash}X}\n"
-    out = out * "  \\begin{tabularx}{\\fulllength}{CCCCCC}\n"
+    out = out * "  \\begin{tabularx}{\\fulllength}{CCCCCCC}\n"
     out = out * "    \\toprule\n"
-    out = out * "    \\textbf{Target (units)} & \\textbf{\$\\text{R}^2\$} & \\textbf{RMSE} & \\textbf{MAE} & \\textbf{Estimated Uncertainty} & \\textbf{Empirical Coverage (\\%)}\\\\\n"
+    out = out * "    \\textbf{Target} & \\textbf{\$\\text{R}^2\$} & \\textbf{RMSE} & \\textbf{MAE} & \\textbf{Estimated Uncertainty} & \\textbf{Empirical Coverage (\\%)} & \\textbf{Best Model} \\\\\n"
     out = out * "    \\midrule\n"
 
     for row in eachrow(df)
@@ -355,8 +355,9 @@ function generate_tex_table(df)
         # r_str = string(round(row["R (mean)"], sigdigits=3)) * " ± " * string(round(row["R (std)"], sigdigits=3))
         unc = " ± " * string(round(row["Estimated Uncertainty"], sigdigits=2))
         cov = string(round(row["Empirical Coverage"]*100, digits=1))
+        winning_model = row["model"]
 
-        out = out * "    $(target_tex) & $(r2_str) & $(rmse_str) & $(mae_str) & $(unc) & $(cov)\\\\\n"
+        out = out * "    $(target_tex) & $(r2_str) & $(rmse_str) & $(mae_str) & $(unc) & $(cov) & $(winning_model)\\\\\n"
     end
 
     out = out * "    \\bottomrule\n"

### 2024-01-15 config.jl

@@ -59,35 +59,35 @@ target_ranges = Dict(
 using LaTeXStrings
 
 targets_latex= Dict(
-    :Br => L"$\mathrm{Br}^-$ (mg/l)",
-    :CDOM => "CDOM (ppb)",
-    :CO => "Crude Oil (ppb)",
-    :Ca => L"$\mathrm{Ca}^{2+}$ (mg/l)",
-    :Chl => L"Chlorophyll A ($\mu$g/l)",
-    :ChlRed => L"Chlorophyll A with Red Excitation ($\mu$g/l)",
-    :Cl => L"$\mathrm{Cl^-}$ (mg/l)",
-    :HDO => "Dissolved Oxygen (mg/l)",
-    :HDO_percent => "Dissolved Oxygen (\\% Sat)",
-    :NH4 => L"\mathrm{NH_4^+} (mg/l-N)",
-    :NO3 => L"\mathrm{NO_3^-} (mg/l-N)",
-    :Na => L"\mathrm{Na^+} (mg/l)",
-    :OB => "Optical Brighteners (ppb)",
-    :RefFuel => "Refined Fuels (ppb)",
-    :Salinity3488 => "Salinity (PSU)",
-    :Salinity3490 => "Salinity (PSU)",
-    :SpCond => L"Conductivity ($\mu$S/cm)",
-    :TDS => "Total Dissolved Solids (mg/l)",
-    :TRYP => "Tryptophan (ppb)",
-    :Temp3488 => "Temperature (°C)",
-    :Temp3489 => "Temperature (°C)",
-    :Temp3490 => "Temperature (°C)",
-    :Turb3489 => "Turbidity (FNU)",
-    :Turb3488 => "Turbidity (FNU)",
-    :Turb3490 => "Turbidity (FNU)",
-    :bg => "Blue-Green Algae [Phycocyanin] (ppb)",
-    :bgm => "Blue-Green Algae [Phycoerythrin] (ppb)",
+    :Br => L"$\mathrm{Br}^-$",
+    :CDOM => "CDOM",
+    :CO => "Crude Oil",
+    :Ca => L"$\mathrm{Ca}^{2+}$",
+    :Chl => L"Chlorophyll A",
+    :ChlRed => L"Chlorophyll A with Red Excitation",
+    :Cl => L"$\mathrm{Cl^-}$",
+    :HDO => "Dissolved Oxygen",
+    :HDO_percent => "Dissolved Oxygen",
+    :NH4 => L"\mathrm{NH_4^+}",
[…]

### 2024-01-15 training-functions.jl

@@ -63,6 +63,49 @@ hpo_ranges = Dict("DecisionTree" => Dict("DecisionTreeRegressor" => [(hpname=:mi
 cor_coef(yhat, y) = Statistics.cor(yhat, y)
 
 
+
+
+
+# note we are assuming that Xcal is a DataFrame
+function permutation_importance(mach, Xcal, ycal; score=rsq, ratio=false)
+    features = Symbol.(names(Xcal))
+    ycal_pred = predict(mach, Xcal)
+
+    # compute base score
+    s_base = score(ycal_pred, ycal)
+
+    fi_pairs = []
+    @showprogress for j in 1:ncol(Xcal)
+        # copy column so we can reset it after
+        col_orig = copy(Xcal[:, j])
+
+        # randomly permute the jth column
+        Xcal[:,j] = shuffle(Xcal[:, j])
+
+        # compute new score
+        s_perm = rsq(predict(mach, Xcal), ycal)
+
+        # importance is differe
+        imp = s_base - s_perm
+        if ratio
+            # if we want it as a ratio instead...
+            imp = s_perm/s_base
+        end
+
+        # add to list
+        push!(fi_pairs, features[j] => imp)
+
+        # reset random column back to normal
+        Xcal[:, j] = col_orig
+    end
+
+    return fi_pairs
+end
+
+
+
+
+
 function train_folds(
     X, y,
     idx_train, idx_test,
@@ -95,9 +138,13 @@ function train_folds(
 
 
     # fit the machine
-    Xtrain = @view X[idx_train,:]
-    ytrain = @view y[idx_train]
+    Xtrain = @view X[idx_train[10_001:end],:]
+    ytrain = @view y[idx_train[10_001:end]]
 
+    Xcal = @view X[idx_train[1:10_000],:]
+    ycal = @view y[idx_train[1:10_000]]
+
+    # split split off first 3000 for calibration
     Xtest = @view X[idx_test,:]
     ytest = @view y[idx_test]
 
@@ -138,189 +185,191 @@ function train_folds(
 
 
     # 2. Compute feature importances
-    if reports_feature_importances(mdl)
-        n_features = 25
+    # computing the permutation importance will work for any model
+#    if reports_feature_importances(mdl)
+    n_features = 25
 
-        @info "\tComputing feature importances"
-        rpt = report(mach);
+    @info "\tComputing feature importances"
+    # rpt = report(mach);
[…]

### 2024-01-15 paper/paper.tex

@@
 
-- \cite{rostom2017evaluation} Evaluated water quality in an Egyptian lake using
+- \cite{rostom2017evaluation} Modeled water quality in an Egyptian lake using reflectance data to predict concentrations of a variety of parameters and even some metals.
+
+- \cite{adao2017hyperspectral} \textit{The hyperspectral sensors’ ability for measuring hundreds of bands raises complexity when considering the sheer quantity of acquired data, whose usefulness depends on both calibration and corrective tasks occurring in pre- and post-flight stages.}
+
+- \cite{adao2017hyperspectral, padua2017uas} applications of UAV remote sensing data include: biomass estimation, disease monitoring, wildfire detection, forest preservation
+
+- \cite{adao2017hyperspectral} many applications require higher spectral fidelity of multispectral and hyperspectral imagers
+
+- \cite{adao2017hyperspectral} remote sensing spectrometry has involved applications like mineral exploration, landmine detection, agroforestry,
+
+- \cite{adao2017hyperspectral} spatial resolution of many remote sensing satellites is too coarse for some applications. Sentinel 2 provides up to 10 m resolution.
+
+- \cite{adao2017hyperspectral} no need for atmospheric corrections as in traditional remote sensing platforms.
+
+- \cite{arroyo2019implementation} UAV hyperspectral imaging system using a hexacopter equiped with a HSI with 288 sepctral bands with IMU-GNSS recorder.
+
+- \cite{koparan2018situ} used a hexacopter equiped with floatation equipment and in-situ sensors for Temperature, Conductivity, Dissolved Oxygen, and pH to autonomously collect data in water at many different locations.
+
+- \cite{gursoy2019investigating} perform water quality classification for a river using CHRIS/PROBA compact high resolution imaging spectrometer data
+
+- \cite{brezonik2005landsat} Uses multi-spectral satellite bands from Landsat to model water quality parameters Chlorophyll A and CDOM (Humic matter)
+
+- \cite{sagan2020monitoring} Successfully modelled conductivity, total dissolved solids, transparency, turbidity, depth, suspended particulate matter, and chlorophyll-a for a lake using high-spatial resolution remotely sensed multi-spectral imagery
+
+- \cite{ehmann2019monitoring} used two small UAVs with multispectral imagers to collect imagery for a river in Syracuse, NY across a variety of environmental conditions.
+They also collected in-situ turbidity measurements after each flight.
+They found red bands were strong predictors of turbidity
+
+- \cite{schiller1999neural} Used neural networks to approximate radiative transfer codes to predict concentrations of CDOM, phytoplankton pigment, and suspended matter using simulated bands of Medium Resolution Imaging Spectrometer.
+
+- \cite{brown2008neural} Use neural networks to calibrate NDVI from AVHRR (Advanced Very High Resolution Radiometer) to those from MODIS, i.e. sensor fusion.
+
+- \cite{paavel2011optical} found that CDOM was the main factor influencing light attenuation in coastal Baltic Waters.
+They analyzed in-situ data together with remote sensing data from MODIS and could predict CDOM but not Chlorphyll or suspended matter.
+
+- \cite{hruska2012radiometric} demonstrate the use of Resonon PIKA II hyperpsectral imager on a UAV (fixed wing) platform
+
+- \cite{belgiu2016random} random forests handle data dimensionality and multicolinearity for remote sensing domains and is fast \textit{and} insensitive to overfitting.
+Feature importance ranking is useful for dimensionality reduction, data selection, etc...
+
+- \cite{aurin2018remote}  presented Global Ocean Carbon Algorithm Database (GOCAD) developed from 500 oceanographic field campaigns over 30 years with in-situ reflectances \textit{and} coincident satellite imagery, CDOM absorption coefficients, spectral slopes, and other parameters.
+
+- \cite{topp2020research} "For low biomass, oligotrophic to mesotrophic waterbodies, the chl-a spectrum is characterized by a sun-induced fluorescence peak around 680 nm"
+
+- \cite{topp2020research} "Sources of CDOM can be either autochthonous (i.e., phytoplankton) or allochthonous (i.e., terrestrial carbon)."
+
+- \cite{topp2020research} "Similar to TSS, the reflectance spectra of waterbodies with varying concentrations of CDOM are highly dependent on the composition of other optically active constituents, and in certain areas can be complicated by the presence of colloidal iron, which shares similar optical properties [128]."
+
+- \cite{lu2021retrieval} utilized a hyperspectral imager to predict in situe measurements of Chlorophyll-a in a Chinese lake. Found that CatBoost was the best model.
+
+- \cite{austin1976index} The index of refraction of water is wavelength, temperature, pressure, and salinity dependent.
+
+-\cite{banerjee2020uav} "Near-earth spectroscopy from UAV-hyperspectral systems addresses the limitations of resolution, signal-to-noise ratio, and cloud cover from traditional satellite or airborne platforms."
+
+-\cite{kurihara2020unmanned} Another HSI equipped drone platform for precision agriculture
+
+-\cite{feng2015urban} ML using random forests to classify flooding from UAV imagery. Used feature importance rankings as well...
+
+-\cite{bonansea2019using} mapped secchi disk transparency using Landsat 8 and Sentinel-2A
+
+-\cite{laonamsai2023utilizing} Used hyperspectral indices to estimate erosion/deposition in Thailand river
 
@@
 The USV is equipped with an in-situ sensing payload utilizing a combination of Eureka Manta-40 multi-probes including fluorometers, ion selective electrodes, and other physical sensors which together enable the collection of comprehensive near-surface measurements including Colored Dissolved Organic Matter (CDOM), Crude Oil, Blue-Green Algae (phycoerythrin and phycocyanin), Chlorophyll-A, Tryptophan, $\mathrm{Na^+}$, $\mathrm{Ca^{2+}}$, $\mathrm{Cl^-}$, Temperature, Conductivity, and many others.
-The full list of measurements utilized in this study is given in Table~\ref{tab:sensors}.
+The full list of measurements utilized in this study is given in Table~\ref{tab:sensors} and are categorized into four distinct types: physical, ion, biochemical, and chemical.
 Additionally, the USV is equipped with an ultra-sonic weather monitoring sensor for measuring air speed and direction as well as a a BioSonics MX Aquatic Habitat Echosounder sonar which are not explored in this study.
@@
 \newcolumntype{C}{>{\centering\arraybackslash}X}
-\begin{tabularx}{\textwidth}{CCC}
+\begin{tabularx}{\textwidth}{CCCC}
 \toprule
-\textbf{Sensor}	& \textbf{Units}	& \textbf{Sensor Type}\\
+\textbf{Sensor}	& \textbf{Units} & \textbf{Sensor Type} & \textbf{Target Category}\\
 \midrule
-Temperature		                    & $^{\circ}$C       & Thermistor \\
-Conductivity                        & $\mu$S/cm         & Four-Electrode Graphite Sensor \\
-Dissolved Oxygen                    & mg/l              & Optical Sensor\\
-Salinity                            & PSU               & Four-Electrode Graphite Sensor \\
-pH                                  & logarithmic (0-14)& Flowing-junction Reference Electrode\\
-Turbidity                           & FNU               & Ion-Selective Electrode \\
-$\mathrm{Ca^{2+}}$                  & mg/l              & Ion-Selective Electrode \\
-$\mathrm{Na^+}$                     & mg/l              & Ion-Selective Electrode \\
-$\mathrm{Cl^-}$                     & mg/l              & Ion-Selective Electrode \\
-$\mathrm{NO_3^-}$                   & mg/l as nitrogen  & Ion-Selective Electrode \\
-Tryptophan                          & ppb               & Fluorometer \\
-Blue-Green Algae (phycoerythrin)    & ppb               & Fluorometer \\
-CDOM                                & ppb               & Fluorometer \\
-Optical Brighteners                 & ppb               & Fluorometer \\
-Crude Oil                           & ppb               & Fluorometer \\
-Chlorophyll A                       & ppb               & Fluorometer \\
-Chlorophyll A (Red Excitation)      & ppb               & Fluorometer \\
+Temperature		                    & $^{\circ}$C       & Thermistor  & Physical \\
+Conductivity                        & $\mu$S/cm         & Four-Electrode Graphite Sensor & Physical  \\
+Dissolved Oxygen                    & mg/l              & Optical Sensor & Physical \\
+pH                                  & logarithmic (0-14)& Flowing-junction Reference Electrode & Physical \\
+Turbidity                           & FNU               & Ion-Selective Electrode  & Physical \\
+$\mathrm{Ca^{2+}}$                  & mg/l              & Ion-Selective Electrode  & Ions \\
+$\mathrm{Cl^-}$                     & mg/l              & Ion-Selective Electrode & Ions \\
+$\mathrm{Na^+}$                     & mg/l              & Ion-Selective Electrode & Ions \\
+Blue-Green Algae (phycoerythrin)    & ppb               & Fluorometer & Biochemical \\
+CDOM                                & ppb               & Fluorometer & Biochemical \\
+Chlorophyll A                       & ppb               & Fluorometer & BioChemical \\
+Chlorophyll A (Red Excitation)      & ppb               & Fluorometer & BioChemical\\
+Optical Brighteners                 & ppb               & Fluorometer & Chemical \\
+Crude Oil                           & ppb               & Fluorometer & Chemical\\
+%Salinity                            & PSU               & Four-Electrode Graphite Sensor \\
+%$\mathrm{NO_3^-}$                   & mg/l as nitrogen  & Ion-Selective Electrode \\
 \bottomrule
@@
 At this scale, the surface is essentially flat so that the hyperspectral data cube can be reliably georectified without the need for an on-board digital elevation map (DEM).
-We adopt the approach outlined in \cite{GeorectificationMuller, GeorectificationBaumker, GeorectificationMostafa} whereby each scan-line is georeferenced using the known field of view (30.8 $\deg$) together with the position and orientation of the UAV as provided by the on-board GPS/INS.
+We adopt the approach outlined in \cite{GeorectificationMuller, GeorectificationBaumker, GeorectificationMostafa} whereby each scan-line is georeferenced using the known field of view (30.8 $\deg$) together with the position and orientation of the UAV as provided by the on-board GPS INS.
 After a sequence of coordinate transformations, pixel coordinates are obtained in the relevant UTM zone (in meters).
@@
 
-The results of fitting our hyperparameter optimized models are listed in Table~\ref{tab:fit-results}.
-For each model, the $R^2$, RMSE, and MAE were evaluated using 6-fold cross validation.
-We observe considerable
+Add description of the full dataset and relevant statistics... maybe add another table?
+
+The results of the model training procedure are outlined in Table~\ref{tab:fit-results}.
+Model performance is identified by the $R^2$, RMSE, and MAE out-of-fold estimates (mean $\pm$ standard deviation) of the final hyperparameter-optimized model with target variables ranked in descending order by the $R^2$ value.
+Additionally, we report the interval width that which yields a 90\% confidence interval on the holdout validation set.
+We then evaluate how the estimated uncertainty generalizes by computing the \textit{emprical coverage} on the holdout testing set, that is, we compute the percentage of predictions on the testing set that \textit{actually} fall within the desired 90\% interval.
 
@@
     \toprule
-    \textbf{Target (units)} & \textbf{$\text{R}^2$} & \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty} & \textbf{Empirical Coverage (\%)} & \textbf{Model*}\\
+    \textbf{Target} & \textbf{$\text{R}^2$} & \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty} & \textbf{Empirical Coverage (\%)} & \textbf{Model*}\\
     \midrule
-    Temperature (°C) & 1.0 ± 1.98e-5 & 0.0398 ± 0.00096 & 0.0267 ± 0.00055 &  ± 0.061 & 89.8 &\\
-    Conductivity ($\mu$S/cm) & 0.999 ± 2.17e-5 & 0.853 ± 0.0114 & 0.55 ± 0.00564 &  ± 1.3 & 89.8\\
-    $\mathrm{Ca}^{2+}$ (mg/l) & 0.999 ± 3.53e-5 & 0.423 ± 0.0101 & 0.243 ± 0.00552 &  ± 0.59 & 89.7\\
-    Dissolved Oxygen (mg/l) & 0.999 ± 3.17e-5 & 0.0705 ± 0.000984 & 0.0467 ± 0.000418 &  ± 0.11 & 89.8\\
-    Salinity (PSU) & 0.998 ± 0.000129 & 0.000759 ± 1.8e-5 & 0.000265 ± 6.1e-6 &  ± 0.00051 & 89.6\\
-    $\mathrm{Cl^-}$ (mg/l) & 0.994 ± 0.000441 & 1.15 ± 0.0418 & 0.578 ± 0.00534 &  ± 1.4 & 90.3\\
-    $\mathrm{Na^+} (mg/l)$ & 0.992 ± 0.000309 & 6.17 ± 0.134 & 2.85 ± 0.0536 &  ± 7.2 & 89.9\\
-    Tryptophan (ppb) & 0.991 ± 0.00038 & 0.188 ± 0.00404 & 0.112 ± 0.00149 &  ± 0.26 & 89.9\\
-    pH & 0.991 ± 0.000327 & 0.0177 ± 0.000295 & 0.0109 ± 6.56e-5 &  ± 0.024 & 89.9\\
-    Blue-Green Algae [Phycoerythrin] (ppb) & 0.981 ± 0.00186 & 1.72 ± 0.0947 & 0.608 ± 0.0218 &  ± 1.4 & 90.2\\
-    $\mathrm{NO_3^-} (mg/l-N)$ & 0.968 ± 0.00203 & 0.0308 ± 0.00113 & 0.0146 ± 0.000256 &  ± 0.043 & 89.9\\
-    CDOM (ppb) & 0.966 ± 0.00228 & 0.464 ± 0.0195 & 0.144 ± 0.00449 &  ± 0.22 & 89.3\\
-    Chlorophyll A ($\mu$g/l) & 0.924 ± 0.00645 & 1.29 ± 0.0667 & 0.359 ± 0.0079 &  ± 0.73 & 90.2\\
-    Optical Brighteners (ppb) & 0.915 ± 0.00406 & 0.118 ± 0.00169 & 0.0568 ± 0.000218 &  ± 0.1 & 89.8\\
-    Chlorophyll A with Red Excitation ($\mu$g/l) & 0.909 ± 0.00794 & 77.6 ± 3.91 & 15.6 ± 0.418 &  ± 25.0 & 90.5\\
-    Crude Oil (ppb) & 0.906 ± 0.00606 & 0.588 ± 0.019 & 0.162 ± 0.00234 &  ± 0.23 & 89.7\\
-    Turbidity (FNU) & 0.812 ± 0.0158 & 60.2 ± 2.61 & 6.98 ± 0.431 &  ± 3.4 & 89.5\\
+    Temperature & 1.0 ± 1.98e-5 & 0.0398 ± 0.00096 & 0.0267 ± 0.00055 &  ± 0.061 & 89.8 & ETR \\
+    Conductivity & 0.999 ± 2.17e-5 & 0.853 ± 0.0114 & 0.55 ± 0.00564 &  ± 1.3 & 89.8 & ETR \\
+    $\mathrm{Ca}^{2+}$ & 0.999 ± 3.53e-5 & 0.423 ± 0.0101 & 0.243 ± 0.00552 &  ± 0.59 & 89.7 & ETR \\
+    Dissolved Oxygen & 0.999 ± 3.17e-5 & 0.0705 ± 0.000984 & 0.0467 ± 0.000418 &  ± 0.11 & 89.8 & ETR \\
+    $\mathrm{Cl^-}$ & 0.994 ± 0.000441 & 1.15 ± 0.0418 & 0.578 ± 0.00534 &  ± 1.4 & 90.3 & RFR \\
+    $\mathrm{Na^+}$ & 0.992 ± 0.000309 & 6.17 ± 0.134 & 2.85 ± 0.0536 &  ± 7.2 & 89.9 & RFR \\
+    pH & 0.991 ± 0.000327 & 0.0177 ± 0.000295 & 0.0109 ± 6.56e-5 &  ± 0.024 & 89.9 & ETR \\
+    Blue-Green Algae & 0.981 ± 0.00186 & 1.72 ± 0.0947 & 0.608 ± 0.0218 &  ± 1.4 & 90.2 & ETR \\
+    CDOM & 0.966 ± 0.00228 & 0.464 ± 0.0195 & 0.144 ± 0.00449 &  ± 0.22 & 89.3 & RFR \\
+    Chlorophyll A & 0.924 ± 0.00645 & 1.29 ± 0.0667 & 0.359 ± 0.0079 &  ± 0.73 & 90.2 & ETR\\
+    Optical Brighteners & 0.915 ± 0.00406 & 0.118 ± 0.00169 & 0.0568 ± 0.000218 &  ± 0.1 & 89.8 & RFR \\
+    Chlorophyll A with Red Excitation & 0.909 ± 0.00794 & 77.6 ± 3.91 & 15.6 ± 0.418 &  ± 25.0 & 90.5 & ETR \\
+    Crude Oil & 0.906 ± 0.00606 & 0.588 ± 0.019 & 0.162 ± 0.00234 &  ± 0.23 & 89.7 & RFR \\
+    Turbidity & 0.812 ± 0.0158 & 60.2 ± 2.61 & 6.98 ± 0.431 &  ± 3.4 & 89.5 & RFR\\
     \bottomrule
@@
 \end{table}
+
+From Table~\ref{tab:fit-results}, it is clear that neither the random forest model nor the gradient boosted tree model is superior for all targets.
+We see that the empirical coverage achieved by the inferred confidence interval is within 1\% of our desired coverage for each target modelled.
+This indicates that the uncertainties obtained by the conformal prediction procedure are reliable, at least within the extremes of the collected dataset.
+
+To further understand the differences in model performance between the target variables, we can consider the difference between the RMSE and MAE scores.
+Because the MAE is less sensitive to impacts from outliers than the RMSE, any large difference between the two is a good indication that model performance has been degraded by outliers.
+Indeed for turbidity, the worst performing model in the collection, there is an order of magnitude difference between the two.
+This is easily explained upon confirmation that ~3\% of data points had values greater than 100 FNU despite a median value of 1.34 FNU.
+
+The advantage of combining multiple datsets is clear, particularly for target variables like Chlorophyll which show unimodal distributions within each collection period.
+As there is only slight variation within a single collection, combining multiple collections with different mean values dramatically improves the capability of a model to identify variations...
+yada yada yada
+
+discuss distribution of values each day and identify variables which had mostly constant values between all three days (and so were highly impaced by the presece of outliers)...
 
@@
 
-\subsection{Ion Measurements}
+\subsection{Ions}
 
@@
 
-\subsection{Biochemical Measurements}
+\subsection{Biochemical Parameters}
 
@@
 \end{figure}
+
+\subsection{Chemical Parameters}
 

### 2024-01-16 3_feature-exploration.jl
finished training

@@ -379,6 +379,8 @@ dfs = [
 ]
 
 
+dfs[2][:, 1:3]
+dfs[end][:, 1:3]
 
 model_ids = ["etr occam", "etr hpo", "rfr occam", "rfr hpo"]
 

### 2024-01-17 paper/paper.tex

--- 2024-01-11 paper/paper.tex
@@
 % Full title of the paper (Capitalized)
-\Title{\textcolor{red}{Leveraging Machine Learning to Characterize Aquatic Environments with an Autonomous Team of Sensing Sentinels }}
+\Title{\textcolor{red}{Leveraging Machine Learning to Characterize Water Quality with an Autonomous Team of Sensing Sentinels }}
 
@@
 
-Each day over X terabytes of remote sensing data are collected from...
+% Overview and Remote Sensing
 
-- First sentence about amount of remote sensing data generated per year w/ citation and a forecast for how much it will increase. 
-- Second sentence about the lack of in-situ reference data (this is the limitation we can fill) 
-- Further limitations of current remote sensing data products (spectral resolution, spatial resolution, observation frequency)
-- Discuss newly launched and and soon-to-be-launched satellites with HSI capabilities
-- Discuss use of multi-sepctral imagery for environmental studies
-    - Generation of spectral indices like the NDVI and others which have shown to be helpful for environmental characterization
-    - Cite David's previous CDOM paper that used the Atlantic shipping data.
-- Discuss use of ML in remote sensing/environmental assessment applications.
-Here, the possibilities are limited by the availability of high-quality reference data which is why many remote sensing ML models employ unsupervised methods to enable pixel classification (i.e.
-surface type, cloudiness fraction, etc...)
-- Outline need for in-situ reference data to calibrate HSI data products
-- Autonomous teams are perfect for this application due to their transportability, rapid deployment, and elastic configuration
-- Give examples of drone use for smart agriculture, etc... 
-- Give examples of autonomous boat use for water studies, cleanup, etc... 
-- Describe our work to create a robotic team which can do all of this...
+% Water Quality
 
-In (cite last robot team paper) we outlined a paradigmatic approach to the generation of remote sensing data sets for water-based environmental studies by employing a coordinated team of autonomous sensing sentinels.
-In this paper, we demonstrate the use of this platform across multiple observation periods...
+% UAVs
 
-Remote sensing data products
+% Machine Learning
 
-Hyper-spectral imagery
+% Our Approach
+- Most remote sensing data products are from multi-spectral imagers, i.e. LANDSAT, MODIS, ETC... 
+    - multispectral imagers have limited spectral resolution 
+    - Much progress has been made in the development of spectral indices
+    - It can be challenging to directly associate these to desired measurements, rather we typically just track the index (without use of in-situ data), or generate classifications that can be challenging to interpret (i.e.
+good vs acceptable vs poor air/water quality)
+- Existing hyperspectral imagers do not have global coverage, but many are on the way EnMAP
+    - AVRIS was used in a plane 
+    - Regardless, the increased data volume due to improved spectral resolution has an impact on the rate at which data are registered, processed, and transferred
+- In situ measurements are expensive and challenging to collect
+    - Existing in-situ data often require collection in the field and analysis back in the lab
+    - In-situ measurements tend to have poor spatial resolution and volume (~10-100 of measurements per site)
+    - Collection and analysis is slow. At best, we can have fixed location sensors which stream their data
+- Retrieval of water quality parameters from remote sensing data requires the existence of co-aligned imagery
+    - This could never be "real time" due to satellite revisit times (usual 1/day) 
+    - remote sensing imagery are easily occluded by clouds and are impacted by atmospheric effects due to aerosols (dust) and gasses (ozone, water vapor, etc). 
+- UAVs provided an excellent solution allowing for improved spatial resolution easily controlled by flight altitude
+    - Much less expensive
+    - Can rapidly survey wide areas that are hard to reach with conventional reference instruments
+    - Can be equipped with many instruments including hyperspectral imagers
+    - Can enable rapid development of relevant spectral indices by \textit{brining the spectrometer to the problem}
+- UAVs alone are not a complete solution as we still suffer from an insufficient sampling density of in-situ reference data
+    - The ideal solution is to use a team of autonomous sensing sentinels including a UAV to provide the hyperspectral imagery complemented by additional sentinels for collecting in-situ reference data
+    - In this team, an uncrewed survey vehicle (USV), i.e. a boat is equipped with a suite of reference instruments. 
+    - These instruments provide the ground truth data used to map reflectance measurements made by the UAV directly to the water quality parameters we actually care about.
+- In our previous work, we devised and implemented such a team \cite{robotTeam1}. 
+    - Prevously we showcased how the team can work for a single collection in the field 
+    - In this work, we demonstrate how combining data from multiple collections allows the ML models to learn the representation of a wider range of target concentrations under a variety of lighting conditions.
+        - This is clearly beneficial when single-day collections are uni-modal.
+That is, for targets that show little variation within a single collection, there is a significant benefit to combining multiple days of observations
+        - This is successful even for collections with complicated distributions.
+    - For use in near-real time safety assessments it's important that the proposed architecture be both fast and accurate
+        - We describe the implementation of a rapid georectification procedure that can run \textit{on the UAV}
+        - The selected ML models achieve a balance of both training time \textit{and} inference time allowing us to rapidly deploy the models
+        - We additionally include a characterization of ML model uncertainty (which is typically lacking) using Conformal Prediction
+        - Key reflectance features that impact model performance can be quickly identifed using permutation importance
+            - This is less biased than typical tree-based impurity methods 
+            - This is also model agnostic (can be applied to any black-box model) 
+            - This is easily interpretable: we measure the impact on model performance ($R^2$ value) when a feature is randomly permuted and all others remain the same.
+The change in $R^2$ value tells us how sensivie the final model is to each feature
+            - This can aid the generation of new spectral indices as well as allow for reduced model size while maximizing performance, i.e. an Occam's razor approach. 
+    - we showcase maps generated using the trained ML models
 
-Launched and soon-to-be-launched HSI satellites
+% The shrinking size of multispectral and hyperspectral imagers has enabled their inclusion as the payload of multi-rotor Unmanned Aerial Vehicles (quadcopters, hexacopters, etc.).
+These platforms are able to address the shortcoming of remote sensing imagery, namely poor spatial resolution and atmospheric interference effects due to aerosols, dust, water vapor, etc by flying close to the ground.
+Further, UAVs can be taken \textit{to the reference sensors} to better facilitate collocation with reference data.
+However,
 
-Generation of in-situe reference measurements for the calibration of remote sensing data products
-
-Drone based applications of hyper-spectral imagers
-
-Autonomous robotic teams (cite our previous paper)
-
-Overview of what we demonstrate here...
-
-somewhere we need to mention the limitations from \cite{robotTeam1} due to low spatial variablility in a single day's collection...
-We are demonstrating that by including multiple observations from different days, we can improve our modelling capabilities by representing a larger variety of incident lighting conditions and in-situ values.
-
-In-situ measurements are expensive to collect and suffer from poor spatial coverage.
+% In-situ measurements are expensive to collect and suffer from poor spatial coverage.
 Remote sensing data cover much wider areas but do not directly provide parameters needed for environmental assessments.
@@
 In his study, we demonstrate that such models can be reliably trained using data collected from multiple observations....
-
-- optically significant substances (OSS)
-- Colored dissolved organic matter (CDOM, also known as yellow substances, humic matter or gelbstoff) includes compounds produced during the decay of plant matter
-- Estimates concentrations of Chlorophyll-a, Total Suspended Solids, and the absorption coefficient of CDOM $a_{CDOM}(400)$ using Medium Resolution Imaging Spectrometer (MERIS) data during bloom in Gulf of Finland.
-They do this using band-ratio algorithms \cite{remote-sensing-finland}.
--  We should note that band-ratio algroithms are impacted by atmospheric factors like the in-column aerosol distribution.
-- The amounts of aerosols (dust, haze, etc) and gases (ozone, water vapor, etc) present in the atmosphere vary spatially and temporally.
-These variations impact the estimation of water quality characteristics via remote sensing methods \cite{remote-sensing-finland}
-- However, when data from different dates and locations are compared and atmospheric correction is necessary \cite{remote-sensing-finland}.
-
-- Used a support vector machine (SVM) to classify hyperspectral images of vegetation acquired by a UAV and produced a high-resolution classification map \cite{uav-hsi-classification}.
-- Large misclassification occured in shaded areas
-- \cite{uav-hsi-classification} calls these technqieus \textit{precision agriculture}
-- \cite{uav-hsi-classification-2} used a UAV aerial survey with multispectral cameras for citrus orchard classification
-
-- \cite{andres2018review}: \textit{Remote monitoring, via satellite assets and distributed in situ sensors, may help meet many of the challenges of information asymmetry and data gaps in developing countries, including unreliable (and time-consuming) survey data and reliance on spot checks to assess accurate reporting and performance.}
-- \cite{andres2018review}: \textit{(UAVs, or drones), are being used by researchers to map watersheds.
-Structure from Motion (SfM) three-dimensional point clouds can be derived from digital images collected on board UAVs, similar to the type of data produced by Light Detection and Ranging (LiDAR) technology [19].
-The technological development of UAVs and their ability to derive high-resolution 3D information (and with much lower operational and up-front costs than manned airborne platforms) and satellite imaging has made UAV image acquisition appealing in several applications.}
-
-- \cite{robert2017analysis} Used Landsat and MODIS data to estimate suspended particulate matter in the Sahelian (Sahel?) region in Africa. 
-- \cite{robert2017analysis} found near infrared bands are well suited for estimating turbidity and SPM up to $R^2=0.70$.
-- \cite{robert2017analysis} \textit{the strong and variable atmospheric load (aerosols and water vapor) were potentially challenging for a remote sensing approach.}
-
-- \cite{ross2019aquasat} constructed a dataset comprised of 600,000 paired observations of water quality and landsat reflectance for bodies across US from 1984-2019
-- Chlorophyll is a photosynthetically active pigment contained in all phytoplankton
-
-- \cite{lary2010artificial} Neural Networks and Support Vector Machines are popular choices for machine learning applications in remote sesnsing and geoscience
-
-- \cite{kaufman1992atmospherically} Developed the Atmospherically Resistant Vegetation Index (AVRI) for use in vegetation studies which takes advantage of blue band.
-It is reported to be 4-times less sensative to atmospheric effects than NDVI
-
-- \cite{chi2016big} NASA's Earth Science Data and Information System (ESDIS) holds 7.5 PB of data with ~7000 unique data sets.
-
-- Google Earth Engine's public data archive contains over 80 petabytes of data
-
-- \cite{garcia2013comparison} used a multi-band imager equipped UAV to identify citrus greening diseas (Huanglongbing) in Florida citrus trees.
-- Spatial resolution is easily controlled by adjusting the UAV flying altitude.
-
-- \cite{rostom2017evaluation} Evaluated water quality in an Egyptian lake using
 
@@
 \newcolumntype{C}{>{\centering\arraybackslash}X}
-\begin{tabularx}{\textwidth}{CCC}
+\begin{tabularx}{\textwidth}{CCCC}
 \toprule
-\textbf{Sensor}	& \textbf{Units}	& \textbf{Sensor Type}\\
+\textbf{Sensor}	& \textbf{Units} & \textbf{Sensor Type} & \textbf{Target Category}\\
 \midrule
-Temperature		                    & $^{\circ}$C       & Thermistor \\
-Conductivity                        & $\mu$S/cm         & Four-Electrode Graphite Sensor \\
-Dissolved Oxygen                    & mg/l              & Optical Sensor\\
-Salinity                            & PSU               & Four-Electrode Graphite Sensor \\
-pH                                  & logarithmic (0-14)& Flowing-junction Reference Electrode\\
-Turbidity                           & FNU               & Ion-Selective Electrode \\
-$\mathrm{Ca^{2+}}$                  & mg/l              & Ion-Selective Electrode \\
-$\mathrm{Na^+}$                     & mg/l              & Ion-Selective Electrode \\
-$\mathrm{Cl^-}$                     & mg/l              & Ion-Selective Electrode \\
-$\mathrm{NO_3^-}$                   & mg/l as nitrogen  & Ion-Selective Electrode \\
-Tryptophan                          & ppb               & Fluorometer \\
-Blue-Green Algae (phycoerythrin)    & ppb               & Fluorometer \\
-CDOM                                & ppb               & Fluorometer \\
-Optical Brighteners                 & ppb               & Fluorometer \\
-Crude Oil                           & ppb               & Fluorometer \\
-Chlorophyll A                       & ppb               & Fluorometer \\
-Chlorophyll A (Red Excitation)      & ppb               & Fluorometer \\
+Temperature		                    & $^{\circ}$C       & Thermistor  & Physical \\
+Conductivity                        & $\mu$S/cm         & Four-Electrode Graphite Sensor & Physical  \\
+%Dissolved Oxygen                    & mg/l              & Optical Sensor & Physical \\
+pH                                  & logarithmic (0-14)& Flowing-junction Reference Electrode & Physical \\
+Turbidity                           & FNU               & Ion-Selective Electrode  & Physical \\
+$\mathrm{Ca^{2+}}$                  & mg/l              & Ion-Selective Electrode  & Ions \\
+$\mathrm{Cl^-}$                     & mg/l              & Ion-Selective Electrode & Ions \\
+$\mathrm{Na^+}$                     & mg/l              & Ion-Selective Electrode & Ions \\
+Blue-Green Algae (phycoerythrin)    & ppb               & Fluorometer & Biochemical \\
+CDOM                                & ppb               & Fluorometer & Biochemical \\
+Chlorophyll A                       & ppb               & Fluorometer & BioChemical \\
+Chlorophyll A (Red Excitation)      & ppb               & Fluorometer & BioChemical\\
+Optical Brighteners                 & ppb               & Fluorometer & Chemical \\
+Crude Oil                           & ppb               & Fluorometer & Chemical\\
+%Salinity                            & PSU               & Four-Electrode Graphite Sensor \\
+%$\mathrm{NO_3^-}$                   & mg/l as nitrogen  & Ion-Selective Electrode \\
 \bottomrule
@@
     \toprule
-    \textbf{Target (units)} & \textbf{$\text{R}^2$} & \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty} & \textbf{Empirical Coverage (\%)} & \textbf{Model*}\\
+    \textbf{Target} & \textbf{$\text{R}^2$} & \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty} & \textbf{Empirical Coverage (\%)} & \textbf{Best Model} \\
     \midrule
-    Temperature (°C) & 1.0 ± 1.98e-5 & 0.0398 ± 0.00096 & 0.0267 ± 0.00055 &  ± 0.061 & 89.8 &\\
-    Conductivity ($\mu$S/cm) & 0.999 ± 2.17e-5 & 0.853 ± 0.0114 & 0.55 ± 0.00564 &  ± 1.3 & 89.8\\
-    $\mathrm{Ca}^{2+}$ (mg/l) & 0.999 ± 3.53e-5 & 0.423 ± 0.0101 & 0.243 ± 0.00552 &  ± 0.59 & 89.7\\
-    Dissolved Oxygen (mg/l) & 0.999 ± 3.17e-5 & 0.0705 ± 0.000984 & 0.0467 ± 0.000418 &  ± 0.11 & 89.8\\
-    Salinity (PSU) & 0.998 ± 0.000129 & 0.000759 ± 1.8e-5 & 0.000265 ± 6.1e-6 &  ± 0.00051 & 89.6\\
-    $\mathrm{Cl^-}$ (mg/l) & 0.994 ± 0.000441 & 1.15 ± 0.0418 & 0.578 ± 0.00534 &  ± 1.4 & 90.3\\
-    $\mathrm{Na^+} (mg/l)$ & 0.992 ± 0.000309 & 6.17 ± 0.134 & 2.85 ± 0.0536 &  ± 7.2 & 89.9\\
-    Tryptophan (ppb) & 0.991 ± 0.00038 & 0.188 ± 0.00404 & 0.112 ± 0.00149 &  ± 0.26 & 89.9\\
-    pH & 0.991 ± 0.000327 & 0.0177 ± 0.000295 & 0.0109 ± 6.56e-5 &  ± 0.024 & 89.9\\
-    Blue-Green Algae [Phycoerythrin] (ppb) & 0.981 ± 0.00186 & 1.72 ± 0.0947 & 0.608 ± 0.0218 &  ± 1.4 & 90.2\\
-    $\mathrm{NO_3^-} (mg/l-N)$ & 0.968 ± 0.00203 & 0.0308 ± 0.00113 & 0.0146 ± 0.000256 &  ± 0.043 & 89.9\\
-    CDOM (ppb) & 0.966 ± 0.00228 & 0.464 ± 0.0195 & 0.144 ± 0.00449 &  ± 0.22 & 89.3\\
-    Chlorophyll A ($\mu$g/l) & 0.924 ± 0.00645 & 1.29 ± 0.0667 & 0.359 ± 0.0079 &  ± 0.73 & 90.2\\
-    Optical Brighteners (ppb) & 0.915 ± 0.00406 & 0.118 ± 0.00169 & 0.0568 ± 0.000218 &  ± 0.1 & 89.8\\
-    Chlorophyll A with Red Excitation ($\mu$g/l) & 0.909 ± 0.00794 & 77.6 ± 3.91 & 15.6 ± 0.418 &  ± 25.0 & 90.5\\
-    Crude Oil (ppb) & 0.906 ± 0.00606 & 0.588 ± 0.019 & 0.162 ± 0.00234 &  ± 0.23 & 89.7\\
-    Turbidity (FNU) & 0.812 ± 0.0158 & 60.2 ± 2.61 & 6.98 ± 0.431 &  ± 3.4 & 89.5\\
+    Temperature & 1.0 ± 6.04e-6 & 0.0289 ± 0.000466 & 0.0162 ± 0.00016 &  ± 0.039 & 90.3 & RFR\\
+    $Conductivity$ & 1.0 ± 1.54e-5 & 0.574 ± 0.0128 & 0.322 ± 0.00579 &  ± 0.76 & 90.6 & RFR\\
+    $\mathrm{Ca}^{2+}$ & 1.0 ± 1.06e-5 & 0.285 ± 0.00357 & 0.137 ± 0.00224 &  ± 0.33 & 89.8 & RFR\\
+    %Dissolved Oxygen & 0.999 ± 2.63e-5 & 0.054 ± 0.00114 & 0.0303 ± 0.000534 &  ± 0.08 & 89.9 & RFR\\
+    $\mathrm{Cl^-}$ & 0.995 ± 0.000196 & 0.895 ± 0.0202 & 0.516 ± 0.00759 &  ± 1.2 & 90.1 & RFR\\
+    Blue-Green Algae (Phycoerythrin) & 0.995 ± 0.000601 & 0.783 ± 0.0489 & 0.287 ± 0.00959 &  ± 0.73 & 89.3 & RFR\\
+    pH & 0.994 ± 0.000288 & 0.0145 ± 0.000304 & 0.00739 ± 9.49e-5 &  ± 0.017 & 89.5 & RFR\\
+    $\mathrm{Na^+}$ & 0.993 ± 0.000229 & 6.16 ± 0.102 & 2.83 ± 0.0303 &  ± 7.3 & 90.0 & RFR\\
+    CDOM & 0.965 ± 0.00352 & 0.248 ± 0.0142 & 0.0921 ± 0.0024 &  ± 0.15 & 89.9 & RFR\\
+    Crude Oil & 0.949 ± 0.00267 & 0.247 ± 0.00597 & 0.0935 ± 0.00114 &  ± 0.17 & 89.8 & RFR\\
+    Optical Brighteners & 0.943 ± 0.00122 & 0.0806 ± 0.0014 & 0.0481 ± 0.000416 &  ± 0.095 & 89.8 & RFR\\
+    $Chlorophyll A$ & 0.908 ± 0.00664 & 0.37 ± 0.00934 & 0.131 ± 0.00228 &  ± 0.27 & 89.2 & RFR\\
+    Turbidity & 0.897 ± 0.00611 & 3.13 ± 0.084 & 0.736 ± 0.0156 &  ± 1.1 & 89.8 & RFR \\
+    Blue-Green Algae (Phycocyanin) & 0.708 ± 0.00689 & 0.749 ± 0.0129 & 0.446 ± 0.00405 &  ± 0.93 & 89.8 & RFR\\
     \bottomrule

### 2024-01-17 3c_extra-plots.jl
updated figure to use correct variables

@@ -86,19 +86,17 @@ save("./paper/figures/results/downwelling-hist.pdf", fig)
 targets_to_try= [
     :Temp3488,
     :SpCond,
+    :pH,
+    :Turb3489,
     :Ca,
-    :HDO,
     :Cl,
     :Na,
-    :pH,
     :bg,
     :bgm,
     :CDOM,
     :Chl,
     :OB,
-    :ChlRed,
     :CO,
-    :Turb3489,
     #:RefFuel
 ]
 
@@ -179,9 +177,9 @@ fig = Figure();
 ax = Axis(
     fig[1,1],
     xticks=var_ticks,
-    xticklabelsize=15,
+    xticklabelsize=14,
     yticks=var_ticks,
-    yticklabelsize=15,
+    yticklabelsize=13,
     xticklabelrotation=π/2,
     yreversed = true,
     xgridvisible=false,

### 2024-01-17 3d_permutation-importance.jl

@@ -79,6 +79,7 @@ idx_train = CSV.read(joinpath(data_path, "idx_train.csv"), DataFrame)[:,1]
 idx_test= CSV.read(joinpath(data_path, "idx_test.csv"), DataFrame)[:,1]
 
 
+ncol(X)
 
 mean(y)
 median(y)

### 2024-01-17 training-functions.jl

@@ -10,10 +10,10 @@ hpo_ranges = Dict("DecisionTree" => Dict("DecisionTreeRegressor" => [(hpname=:mi
                                                                       (hpname=:post_prune, values=[false, true])
                                                                       ],
                                          "RandomForestRegressor" => [
-                                                                      (hpname=:min_samples_leaf, lower=1, upper=100),
+                                                                      #(hpname=:min_samples_leaf, lower=1, upper=100),
                                                                       #(hpname=:max_depth, values=[-1, 3, 5, 7]),
                                                                       #(hpname=:n_subfeatures, lower=10, upper=100,),
-                                                                      #(hpname=:n_trees, lower=50, upper=200),
+                                                                      (hpname=:n_trees, lower=50, upper=200),
                                                                       (hpname=:sampling_fraction, lower=0.8, upper=1.0)
                                                                       ],
                                           ),

### 2024-01-17 paper/paper.tex
Updates from Overleaf

@@
 
+In our previous work, we developed a robotic team comprised of...
+We showed that using this team, hyperspectral imagery collected by the UAV can be calibrated against in-situ reference measurements collected by the USV to enable the rapid generation of wide area surveys for a variety of water quality parameters \cite{robotTeam1}.
+In this study, we expand on this previous work to demonstrate that by combining observations across multiple distinct collections, we can improve our machine learning models...
+
 % The shrinking size of multispectral and hyperspectral imagers has enabled their inclusion as the payload of multi-rotor Unmanned Aerial Vehicles (quadcopters, hexacopters, etc.).
@@
 
-In the study we employ a team of autonomous sensing sentinels, hereafter referred to as \textit{the robot team}, to enable the rapid characterization of aquatic environments.
+In this study we employ a team of autonomous sensing sentinels, hereafter referred to as \textit{the robot team}, to enable the rapid characterization of aquatic environments.
 This team consists of two key sensing sentinels: An uncrewed surface vessel (USV) used to collect in-situ reference measurements, and an unmanned aerial vehicle (UAV) for performing rapid, wide-area surveys to gather remote sensing data products.
-Both platforms are coordinated using the open-source QGroundControl software for flight control and mission planning \cite{qgroundcontrol} and are equipped with high accuracy GPS and INS such that all collected data points are uniquely geolocated and time-stamped.
+Both platforms are coordinated using the open-source QGroundControl software for flight control and mission planning and are equipped with high accuracy GPS and INS such that all collected data points are uniquely geolocated and time-stamped \cite{qgroundcontrol}.
 Both the USV and UAV are equipped with long-range Ubiquiti 5 GHz LiteBeam airMAX WiFi to enable streaming of data products to a ground station with network attached storage providing redundancy.
@@
 The USV employed in the robot team is a Maritime Robotics Otter which features a modular design and 20 hour battery life.
-The USV is equipped with an in-situ sensing payload utilizing a combination of Eureka Manta-40 multi-probes including fluorometers, ion selective electrodes, and other physical sensors which together enable the collection of comprehensive near-surface measurements including Colored Dissolved Organic Matter (CDOM), Crude Oil, Blue-Green Algae (phycoerythrin and phycocyanin), Chlorophyll-A, Tryptophan, $\mathrm{Na^+}$, $\mathrm{Ca^{2+}}$, $\mathrm{Cl^-}$, Temperature, Conductivity, and many others.
-The full list of measurements utilized in this study is given in Table~\ref{tab:sensors} and are categorized into four distinct types: physical, ion, biochemical, and chemical.
+The USV is equipped with an in-situ sensing payload consisting of a combination of Eureka Manta-40 multi-probes including fluorometers, ion selective electrodes, and other physical sensors which together enable the collection of comprehensive near-surface measurements including Colored Dissolved Organic Matter (CDOM), Crude Oil, Blue-Green Algae (phycoerythrin and phycocyanin), Chlorophyll-A, $\mathrm{Na^+}$, $\mathrm{Ca^{2+}}$, $\mathrm{Cl^-}$, Temperature, Conductivity, and many others.
+The full list of measurements utilized in this study is given in Table~\ref{tab:sensors} and are categorized into four distinct types: physical measurements, ion measurements, biochemical measurements, and chemical measurements.
 Additionally, the USV is equipped with an ultra-sonic weather monitoring sensor for measuring air speed and direction as well as a a BioSonics MX Aquatic Habitat Echosounder sonar which are not explored in this study.
@@
 Blue-Green Algae (phycoerythrin)    & ppb               & Fluorometer & Biochemical \\
+Blue-Green Algae (phycocyanin)      & ppb               & Fluorometer & BioChemical \\
 CDOM                                & ppb               & Fluorometer & Biochemical \\
 Chlorophyll A                       & ppb               & Fluorometer & BioChemical \\
-Chlorophyll A (Red Excitation)      & ppb               & Fluorometer & BioChemical\\
 Optical Brighteners                 & ppb               & Fluorometer & Chemical \\
@@
 \end{table}
+
+As shown in Table~\ref{tab:sensors}, the physical parameter and ion sensors are largely based on different configurations of electrodes while the chemical and biochemical parameters are all optically active substances enabling their determination by fluorometry.
+The pigments phycoerythrin and phycocyanin are used to determine blue-green algae content which together with chlorophyll-a enables us to asses the distribution of photosynthetic life.
+Additionally, we also measure the concentration of colored dissolved organic matter (CDOM) which impacts light penetration and serves as a primary source of bioavailable carbon.
+Crude oil (natural petroleum) and optical brightener concentrations are also measured with fluorometers and are relevant for identifying sources of industrial contamination or natural seepage.
 
@@
 To this end, we convert the hyperspectral data cubes into units of reflectance by utilizing the skyward-facing downwelling irradiance spectrometer (see Figure~\ref{fig:drone-components}).
-When our camera is normal to this surface, then the reflectance is given by
+When our camera is normal to the water surface, then the reflectance is given by
 \begin{equation}
@@
 The resulting image is then re-sampled to a final output resolution.
-For these collections a resolution of 10 cm was utilized, however this can be increased to reduce the processing time for real-time applications.
-Finally, the UTM coordinates are transformed to latitude and longitude for easy comparison with in-situ data collected by the USV.
+For these collections a resolution of 10 cm was utilized, however this can be adjusted to optimize the processing time and final resolution for real-time applications.
+Finally, the obtained pixel UTM coordinates are transformed to latitude and longitude for easy comparison with in-situ data collected by the USV.
 The final result is a georectified hyperspectral reflectance data cube.
@@
 Each of these reference measurements was then collocated with individual pixel spectra where the USV track overlapped with UAV pixels.
-To account for any time-delays in the values measured by the in-situ instruments and to account for the fact the the USV is larger than the final resolution of our resampled HSI, each in-siture measurent is associated with a 3$\times$3 grid of HSI pixels, that is, a 30 cm $\times$ 30 cm square.
-These combined data form a tabular data set on which we seek use to train regression models; pixel spectra form input features and each separate USV sensor forms a distinct target variable.
-Together, this combined data set contains over 130,000 records.
+To account for any time lag in the values measured by the in-situ instruments and to account for the USV size in comparison to the data cube spatial resolution, each in-situ measurement is associated with a 3$\times$3 grid of HSI pixels, that is, a 30 cm $\times$ 30 cm square.
+These combined data form the tabular data set on which we train regression models; pixel spectra form input features and each separate USV sensor forms a distinct target variable.
 
 Each collection was performed near solar noon to maximize the amount of incident sunlight illuminating the water, however, to account for any potential variation in lighting conditions between data cubes, we augment the training set with additional features including the drone viewing geometry (roll, pitch, heading) and solar illumination geometry (solar azimuth, solar elevation, solar zenith) as well as the total at-pixel intensity (before refelctance conversion), the total downwelling intensity, and the drone altitude.
-Feature engineering is performed to add a additional spectral indices utilizing combinations of specific wavelength bands like the normalized difference vegetation index (NDVI), normalized difference water index (NDWI), simple ratio (SR), photochemical reflectance index (PRI), and more as described in \cite{envi_vegetation_indices, thenkabail2018hyperspectral,kaufman1992atmospherically, SpectralIndexWheat}.
+Further feature engineering is performed to add a additional spectral indices which utilize combinations of specific wavelength bands like the normalized difference vegetation index (NDVI), normalized difference water index (NDWI), simple ratio (SR), photochemical reflectance index (PRI), and more as described in \cite{envi_vegetation_indices, thenkabail2018hyperspectral,kaufman1992atmospherically, SpectralIndexWheat}.
 A comprehensive list of these added features is provided in supplementary table S1.
+The final dataset includes a total of 526 features (462 reflectance bands plus 64 additional features) with over 120,000 records.
 
@@
 
-For each of the 17 target variables listed in Table~\ref{tab:sensors}, data were randomly partitioned into a 90:10 training/testing split resulting 120,350 training points and 13,372 holdout testing points.
+For each of the 13 target variables listed in Table~\ref{tab:sensors}, data were randomly partitioned into a 90:10 training/testing split.
 Using the MLJ machine learning framework, a variety of machine learning models compatible with the regression task were identified \cite{MLJ1}.
 This selection of models included linear regression (and it's variations), Gaussian Process Regression, shallow Neural Networks, and decision tree based models.
-Out of this set, Random Forest Regression from \cite{decision-trees} and a native Julia implementation of gradient boosted tree regression from the EvoTrees package were selected for their quick training and inference times.
-Both random forests and gradient boosted trees are ensembling techniques based on individual decision tree regressors \cite{decision-trees, random-forest, gradient-boosting}.
-These tree-based methods also enable an impurity based ranking of the relative \textit{importance} of each feature to the target predictions as described in \cite{rfr-orig,rfr-importance-ranking}.
-We use these feature rankings to identify the most impactful features and perform feature selection and reduction.
+Out of this set, the Random Forest Regressor (RFR) model from \cite{decision-trees} was selected for its relatively quick training and inference times.
+Random forests are an ensembling technique based on the bagged predictions of individual decision tree regressors trained using the CART algorithm with each individual tree trained on a random subset of features \textit{and} a random subset of training records \cite{decision-trees, random-forest}.
 
-The training procedure for each model is as follow: First, the model is trained using 6-fold cross validation on the training set with default hyperparameters.
-Feature importances for the trained model are then computed and the top 25 features are identified.
-A second, reduced-feature model is then trained using the same 6-fold cross validation technique to ensure an improvement in model performance.
-Next, each model is hyperparameter optimized using a random parameter search.
-Model performance is evaluated by computing out-of-fold values for the $R^2$ (coefficient of determination), as well as
+As reflectance values in adjacent wavelength bins tend to correlate with each other, and therefore, may not necessarily contribute additional information content to the final model, it is desirable to evaluate the relative importance of each feature to the predictions of our trained models.
+This is useful both for identifying the most relevant parameters as well as for performing feature selection to reduce the final model size and optimize inference time.
+By default, tree-based methods like the RFR allow for an impurity based ranking as described in \cite{rfr-orig, rfr-importance-ranking}.
+However, these methods have been shown to be biased towards high cardinality and correlated features \cite{strobl2008conditional}.
+We therefore choose to use the model-agnostic permutation importance as described by \cite{parr2018beware}.
+To do this, we further partition the training dataset resulting in an 80:10:10 split with 80\% of points used for model training, 10\% of points used for validation and feature importance determination, and the final 10\% held out as an independent testing dataset.
+The importance for the $j^{\text{th}}$ feature is then computed as
+\begin{equation}
+    \text{Imp}_j = R^2(f(X_{\text{val}}), y_{\text{val}}) - R^2(f(X_{\text{val}}^{(j)}), y_{\text{val}})
+\end{equation}
+where $(X_{\text{val}}, y_{\text{val}})$ is the validation set, $f(\cdot)$ is the trained model, $R^2(\cdot, \cdot)$ is the coefficient of determination, and $X_{\text{val}}^{(j)}$ is validation feature set with the $j^{th}$ column randomly permuted.
+The permutation importance is therefore understood as the decrease in model performance when the $j^{th}$ feature is replaced by random values from the validation set.
+
+To assess the uncertainty of the final model's predictions, we employ Inductive Conformal Prediction as described in \cite{conformal-prediction-1, conformal-prediction-2, conformal-prediction-3, conformal-prediction-4}.
+To do this, we compute a set of nonconformity scores of the trained model on the validation set using an uncertainty heuristic, in this case, the absolute error
+\begin{equation}
+    s_i = s(X_i, y_i) = \lvert f(X_i) - y_i \rvert = \lvert \hat{y}_i - y_i \rvert
+\end{equation}
+where $f(X_i)=\hat{y}_i$ denotes the trained ML model applied to the $i^{th}$ calibration record.
+These n-many scores are sorted, and the interval half width $d$ is computed as the $\frac{\lceil(1-\alpha)(n+1) \rceil}{n}$ quantile of this set in order to achieve a coverage of $1-\alpha$ on the calibration set.
+Predictions intervals for new data are then formed as $f(X)\pm d$.
+For this study, we have chosen $\alpha=0.1$ for a coverage corresponding to a 90\% confidence interval.
+
+Using these tools, the training procedure for each model is as follows: First, the model is trained using 6-fold cross validation on the training set with default hyperparameters.
+Feature importances and for the trained model are then computed and the top 25 features are identified.
+A second, reduced-feature model is then trained using the same 6-fold cross validation scheme.
+Next, each model is hyperparameter optimized using a random parameter search over the number of tees and sampling fraction.
+Model performance is evaluated by computing out-of-fold values for the coefficient of determination, as well as
 \begin{align}
@@
 
-Having identified the model with the best out-of-fold performance, we proceed to train the final hyperparameter optimized model on the full training set.
-To assess the uncertainty of the final model's predictions, we employ Inductive Conformal Prediction as described in \cite{conformal-prediction-1, conformal-prediction-2, conformal-prediction-3, conformal-prediction-4}.
-To do this, the training set is further partitioned so that we obtain an additional validation hold out set with the split chosen to achieve a 80:10:10 training, validation, and testing ratio.
-This resulting validation set contains >10,000 records which \cite{conformal-prediction-2} suggests to be more than sufficient for most cases.
-
-The hyperparameter optimized model is trained on the full training set.
-We then compute a set of nonconformity scores on the validation set using an uncertainty heuristic, in this case, the absolute error
-\begin{equation}
-    s_i = s(X_i, y_i) = \lvert f(X_i) - y_i \rvert = \lvert \hat{y}_i - y_i \rvert
-\end{equation}
-where $f(X_i)=\hat{y}_i$ denotes the trained ML model applied to the $i^{th}$ calibration record.
-These n-many scores are sorted, and the interval half width $d$ is computed as the $\frac{\lceil(\alpha)(n+1) \rceil}{n}$ quantile of this set in order to achieve a coverage of $\alpha$ on the calibration set.
-Predictions intervals for new data are then formed as $f(X)\pm d$.
-For this study, we have chosen a coverage of $\alpha=0.9$ corresponding to a 90\% confidence interval.
+Having identified the model with the best out-of-fold performance, we proceed to train the final hyperparameter optimized model on the full training set with associated uncertainty estimated using conformal prediction.
 Finally, each of these resulting hyperparameter optimized models is evaluated on the previously untouched testing set.
+Additionally, we visualize the scatter diagram and quantile-quantile plot to visualize model performance across the distribution of testing data.
 
@@
 
-Add description of the full dataset and relevant statistics... maybe add another table?
+The final dataset combining observations from each of the three separate collections contains more than 120,000 individual records.
 
-The results of the model training procedure are outlined in Table~\ref{tab:fit-results}.
+\begin{figure}[H]
+\includegraphics[width=10.5 cm]{paper/figures/results/target_correlations.pdf}
+\caption{\label{fig:target-correlations}}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[width=10.5 cm]{paper/figures/results/downwelling-hist.pdf}
+\caption{Distribution of total downwelling intensity during each of the three HSI collection flights.
+The multi-modal nature of these distributions reflects the impact of the relative orientation of the drone to the sun as well as potential occlusion due to the presence of clouds.\label{fig:downwelling-hist}}
+\end{figure}
+
+The results of the model training procedure are presented in Table~\ref{tab:fit-results}.
 Model performance is identified by the $R^2$, RMSE, and MAE out-of-fold estimates (mean $\pm$ standard deviation) of the final hyperparameter-optimized model with target variables ranked in descending order by the $R^2$ value.
-Additionally, we report the interval width that which yields a 90\% confidence interval on the holdout validation set.
+The small variation in values across folds confirms that the reported performance is independent of how the training set was sampled.
+Additionally, we report the interval width which yields a 90\% confidence interval on the holdout validation set as determiend by the conformal prediction procedure.
 We then evaluate how the estimated uncertainty generalizes by computing the \textit{emprical coverage} on the holdout testing set, that is, we compute the percentage of predictions on the testing set that \textit{actually} fall within the desired 90\% interval.
@@
   \newcolumntype{C}{>{\centering\arraybackslash}X}
-  \begin{tabularx}{\fulllength}{CCCCCCC}
+  \begin{tabularx}{\fulllength}{CCCCCC}
     \toprule
-    \textbf{Target} & \textbf{$\text{R}^2$} & \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty} & \textbf{Empirical Coverage (\%)} & \textbf{Best Model} \\
+    \textbf{Target} & \textbf{$\text{R}^2$} & \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty} & \textbf{Empirical Coverage (\%)} \\
     \midrule
-    Temperature & 1.0 ± 6.04e-6 & 0.0289 ± 0.000466 & 0.0162 ± 0.00016 &  ± 0.039 & 90.3 & RFR\\
-    $Conductivity$ & 1.0 ± 1.54e-5 & 0.574 ± 0.0128 & 0.322 ± 0.00579 &  ± 0.76 & 90.6 & RFR\\
-    $\mathrm{Ca}^{2+}$ & 1.0 ± 1.06e-5 & 0.285 ± 0.00357 & 0.137 ± 0.00224 &  ± 0.33 & 89.8 & RFR\\
-    %Dissolved Oxygen & 0.999 ± 2.63e-5 & 0.054 ± 0.00114 & 0.0303 ± 0.000534 &  ± 0.08 & 89.9 & RFR\\
-    $\mathrm{Cl^-}$ & 0.995 ± 0.000196 & 0.895 ± 0.0202 & 0.516 ± 0.00759 &  ± 1.2 & 90.1 & RFR\\
-    Blue-Green Algae (Phycoerythrin) & 0.995 ± 0.000601 & 0.783 ± 0.0489 & 0.287 ± 0.00959 &  ± 0.73 & 89.3 & RFR\\
-    pH & 0.994 ± 0.000288 & 0.0145 ± 0.000304 & 0.00739 ± 9.49e-5 &  ± 0.017 & 89.5 & RFR\\
-    $\mathrm{Na^+}$ & 0.993 ± 0.000229 & 6.16 ± 0.102 & 2.83 ± 0.0303 &  ± 7.3 & 90.0 & RFR\\
-    CDOM & 0.965 ± 0.00352 & 0.248 ± 0.0142 & 0.0921 ± 0.0024 &  ± 0.15 & 89.9 & RFR\\
-    Crude Oil & 0.949 ± 0.00267 & 0.247 ± 0.00597 & 0.0935 ± 0.00114 &  ± 0.17 & 89.8 & RFR\\
-    Optical Brighteners & 0.943 ± 0.00122 & 0.0806 ± 0.0014 & 0.0481 ± 0.000416 &  ± 0.095 & 89.8 & RFR\\
-    $Chlorophyll A$ & 0.908 ± 0.00664 & 0.37 ± 0.00934 & 0.131 ± 0.00228 &  ± 0.27 & 89.2 & RFR\\
-    Turbidity & 0.897 ± 0.00611 & 3.13 ± 0.084 & 0.736 ± 0.0156 &  ± 1.1 & 89.8 & RFR \\
-    Blue-Green Algae (Phycocyanin) & 0.708 ± 0.00689 & 0.749 ± 0.0129 & 0.446 ± 0.00405 &  ± 0.93 & 89.8 & RFR\\
+    Temperature & 1.0 ± 6.04e-6 & 0.0289 ± 0.000466 & 0.0162 ± 0.00016 &  ± 0.039 & 90.3 \\
+    $Conductivity$ & 1.0 ± 1.54e-5 & 0.574 ± 0.0128 & 0.322 ± 0.00579 &  ± 0.76 & 90.6 \\
+    $\mathrm{Ca}^{2+}$ & 1.0 ± 1.06e-5 & 0.285 ± 0.00357 & 0.137 ± 0.00224 &  ± 0.33 & 89.8 \\
+    $\mathrm{Cl^-}$ & 0.995 ± 0.000196 & 0.895 ± 0.0202 & 0.516 ± 0.00759 &  ± 1.2 & 90.1 \\
+    Blue-Green Algae (Phycoerythrin) & 0.995 ± 0.000601 & 0.783 ± 0.0489 & 0.287 ± 0.00959 &  ± 0.73 & 89.3 \\
+    pH & 0.994 ± 0.000288 & 0.0145 ± 0.000304 & 0.00739 ± 9.49e-5 &  ± 0.017 & 89.5 \\
+    $\mathrm{Na^+}$ & 0.993 ± 0.000229 & 6.16 ± 0.102 & 2.83 ± 0.0303 &  ± 7.3 & 90.0 \\
+    CDOM & 0.965 ± 0.00352 & 0.248 ± 0.0142 & 0.0921 ± 0.0024 &  ± 0.15 & 89.9 \\
+    Crude Oil & 0.949 ± 0.00267 & 0.247 ± 0.00597 & 0.0935 ± 0.00114 &  ± 0.17 & 89.8 \\
+    Optical Brighteners & 0.943 ± 0.00122 & 0.0806 ± 0.0014 & 0.0481 ± 0.000416 &  ± 0.095 & 89.8 \\
+    $Chlorophyll A$ & 0.908 ± 0.00664 & 0.37 ± 0.00934 & 0.131 ± 0.00228 &  ± 0.27 & 89.2 \\
+    Turbidity & 0.897 ± 0.00611 & 3.13 ± 0.084 & 0.736 ± 0.0156 &  ± 1.1 & 89.8 \\
+    Blue-Green Algae (Phycocyanin) & 0.708 ± 0.00689 & 0.749 ± 0.0129 & 0.446 ± 0.00405 &  ± 0.93 & 89.8 \\
     \bottomrule
@@
   \end{adjustwidth}
-  \noindent{\footnotesize{* RFR = Random Forest Regressor, ETR = EvoTree Regressor}}
 \end{table}
 
-From Table~\ref{tab:fit-results}, it is clear that neither the random forest model nor the gradient boosted tree model is superior for all targets.
-We see that the empirical coverage achieved by the inferred confidence interval is within 1\% of our desired coverage for each target modelled.
+From Table~\ref{tab:fit-results},  we see that the empirical coverage achieved by the inferred confidence interval evaluated on the independent test set is within 1\% of our desired coverage for each target modelled.
 This indicates that the uncertainties obtained by the conformal prediction procedure are reliable, at least within the extremes of the collected dataset.
@@
 \centering
-\includegraphics[width=16.0cm]{paper/figures/results/fits/physical-fitres.pdf}
+\includegraphics[width=16.0cm]{paper/figures/results/fits/physical-fitres.png}
 \end{adjustwidth}
@@
 
+Explanation for goodness of fit: index of refraction is temperature and salinity dependent
+
 \begin{figure}[H]
@@
 \centering
-\includegraphics[width=16.0cm]{paper/figures/results/fits/ions-fitres.pdf}
+\includegraphics[width=16.0cm]{paper/figures/results/fits/ions-fitres.png}
 \end{adjustwidth}
@@
 
+\begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=18.0cm]{paper/figures/results/maps/ions.pdf}
+\end{adjustwidth}
+\caption{ \label{fig:map-phys-chem}}
+\end{figure}
+
 \subsection{Biochemical Parameters}
@@
 \centering
-\includegraphics[width=16.0cm]{paper/figures/results/fits/chemical-fitres.pdf}
+\includegraphics[width=16.0cm]{paper/figures/results/fits/chemical-fitres.png}
 \end{adjustwidth}
@@
 
-\subsection{Chemical Parameters}
-
-\subsection{Mapping}
-
-% Example of a figure that spans the whole page width. The same concept works for tables, too.
 \begin{figure}[H]
@@
 \centering
-\includegraphics[width=18.0cm]{paper/figures/results/map-combined.pdf}
+\includegraphics[width=18.0cm]{paper/figures/results/maps/biochemical.pdf}
 \end{adjustwidth}
-\caption{Maps generated by applying the ML model to hyperspectral data cubes.
+\caption{ \label{fig:map-phys-chem}}
+\end{figure}
+
+\subsection{Chemical Parameters}
+
+\begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=16.0cm]{paper/figures/results/fits/chemical-fitres.png}
+\end{adjustwidth}
+\caption{A visualization of the fitresults for three of the chemical concentrations we modeled.
+On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:chemicals-fit}}
+\end{figure}
+
+\begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=18.0cm]{paper/figures/results/fits/chemical-ranking.pdf}
+\end{adjustwidth}
+\caption{Ranked feature importances for the same three chemical concentration models.\label{fig:chemicals-fit}}
+\end{figure}
+
+\begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=18.0cm]{paper/figures/results/maps/physical-chemical.pdf}
+\end{adjustwidth}
+\caption{ \label{fig:map-phys-chem}}
+\end{figure}
+
+% Example of a figure that spans the whole page width. The same concept works for tables, too.
+%\begin{figure}[H]
+%\begin{adjustwidth}{-\extralength}{0cm}
+%\centering
+%\includegraphics[width=18.0cm]{paper/figures/results/map-combined.pdf}
+%\end{adjustwidth}
+%\caption{Maps generated by applying the ML model to hyperspectral data cubes.
 (\textbf{a}) The CDOM model applied to the 11-23 collection.
@@
 \label{fig:maps}}
-\end{figure}
+%\end{figure}
 
@@
 \section{Discussion} \label{sec:discussion}
-
-\subsection{Optically Active Components and Physio-Chemical Parameter Estimation}
 
@@
 
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{paper/figures/results/target_correlations.pdf}
-\caption{\label{fig:target-correlations}}
-\end{figure}
-
 \subsection{Data Product Streaming}
@@
 \subsection{Limitations}
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{paper/figures/results/downwelling-hist.pdf}
-\caption{Distribution of total downwelling intensity during each of the three HSI collection flights.
-The multi-modal nature of these distributions reflects the impact of the relative orientation of the drone to the sun as well as potential occlusion due to the presence of clouds.\label{fig:downwelling-hist}}
-\end{figure}
 

### 2024-01-19 3b_make-maps.jl
updated pdfs

@@ -156,6 +156,9 @@ targets_to_map = [
 # targets_to_map = [:CDOM]
 
 
+targets_to_map = [:pH]
+
+
 # set up relevant paths
 hsi_paths = joinpath(hsipath, day)
 
@@ -217,7 +220,8 @@ color_clims= Dict(
         # "12-09" => (210, 350),
     ),
     "pH" => Dict(
-        "11-23" => (8.0, 8.25),
+        "11-23" => (7.95, 8.5),
+        #"11-23" => (7.95, 8.65),
         "12-09" => (8.2, 8.6),
     ),
     "bg" => Dict(
@@ -259,7 +263,7 @@ color_clims= Dict(
         # "12-09" => (23.0, 25.0),
     ),
     "Turb3489" => Dict(
-        "11-23" => (1,3),
+        "11-23" => (1,25),
         "12-09" => (1,3),
     ),
     "RefFuel" => Dict(
@@ -350,7 +354,7 @@ for target ∈ targets_to_map
 
 
         fig_tot = cmk.Figure(px_per_unit=5);
-        ax_tot = cmk.Axis(fig_tot[1,1], xlabel="longitude", ylabel="latitude", title="Collection Date: $(h5_date)");
+        ax_tot = cmk.Axis(fig_tot[1,1], xlabel="Longitude", ylabel="Latitude", title="Collection Date: $(h5_date)");
         bg_tot = cmk.heatmap!(ax_tot, satmap.w..satmap.e, satmap.s..satmap.n, satmap.img);
 
         q_01 = quantile(y, 0.01)
@@ -383,7 +387,7 @@ for target ∈ targets_to_map
             map_name = split(split(h5path, "/")[end], ".")[1]
 
             fig = cmk.Figure();
-            ax = cmk.Axis(fig[1,1], xlabel="longitude", ylabel="latitude");
+            ax = cmk.Axis(fig[1,1], xlabel="Longitude", ylabel="Latitude");
             bg = cmk.heatmap!(ax, satmap.w..satmap.e, satmap.s..satmap.n, satmap.img);
 
             X_hsi, Y, ij_water, Latitudes, Longitudes = get_data_for_pred(h5path, names(X))

### 2024-01-19 paper/paper.tex
Updates from Overleaf

@@
 % Full title of the paper (Capitalized)
-\Title{\textcolor{red}{Leveraging Machine Learning to Characterize Water Quality with an Autonomous Team of Sensing Sentinels }}
+\Title{\textcolor{red}{Leveraging Machine Learning to Characterize Water Quality with an Autonomous Team of Sensing Sentinels}}
 
@@
 \begin{figure}[H]
-\includegraphics[width=10.5 cm]{paper/figures/results/target_correlations.pdf}
+\includegraphics[width=0.75\columnwidth]{paper/figures/results/target_correlations.pdf}
 \caption{\label{fig:target-correlations}}
@@
 \begin{figure}[H]
-\includegraphics[width=10.5 cm]{paper/figures/results/downwelling-hist.pdf}
+\includegraphics[width=0.75\columnwidth]{paper/figures/results/downwelling-hist.pdf}
 \caption{Distribution of total downwelling intensity during each of the three HSI collection flights.
@@
     Temperature & 1.0 ± 6.04e-6 & 0.0289 ± 0.000466 & 0.0162 ± 0.00016 &  ± 0.039 & 90.3 \\
-    $Conductivity$ & 1.0 ± 1.54e-5 & 0.574 ± 0.0128 & 0.322 ± 0.00579 &  ± 0.76 & 90.6 \\
+    Conductivity & 1.0 ± 1.54e-5 & 0.574 ± 0.0128 & 0.322 ± 0.00579 &  ± 0.76 & 90.6 \\
     $\mathrm{Ca}^{2+}$ & 1.0 ± 1.06e-5 & 0.285 ± 0.00357 & 0.137 ± 0.00224 &  ± 0.33 & 89.8 \\
@@
 
-The advantage of combining multiple datsets is clear, particularly for target variables like Chlorophyll which show unimodal distributions within each collection period.
-As there is only slight variation within a single collection, combining multiple collections with different mean values dramatically improves the capability of a model to identify variations...
-yada yada yada
+For each type, discuss:
+- Data Distribution (unimodal, multimodal, spatial variability within each day)
+- Fit results (parameter regions where performance is poor)
+- Feature importance rankings 
+- Maps
+- Can we explain the quality of fit? e.g. target is optically active, correlates with an optically active substance, or has some other physical explanation
 
-discuss distribution of values each day and identify variables which had mostly constant values between all three days (and so were highly impaced by the presece of outliers)...
-
-\subsection{Physical Parameters}
+\subsection{Biochemical Parameters}
 
 \begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
+%\begin{adjustwidth}{-\extralength}{0cm}
 \centering
-\includegraphics[width=16.0cm]{paper/figures/results/fits/physical-fitres.png}
-\end{adjustwidth}
-\caption{A visualization of the fitresults for three of the physical parameters we modeled. On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:physical-fit}}
+%\includegraphics[width=16.0cm]{paper/figures/results/fits/biochemical-fitres.png}
+\includegraphics[width=\columnwidth]{paper/figures/results/fits/biochemical-fitres.pdf}
+%\end{adjustwidth}
+\caption{Scatter plots (left) and quantile-quantile plots (right) for the final hyperparameter optimized models for the biochemical targets Blue-green algae (phycoerythrin), CDOM, Chlorophyll-A, and Blue-green algae (phycocyanin).
+\label{fig:biochem-fit}}
 \end{figure}
@@
 \centering
-\includegraphics[width=18.0cm]{paper/figures/results/fits/physical-ranking.pdf}
+\includegraphics[width=18.0cm]{paper/figures/results/fits/biochemical-ranking.pdf}
 \end{adjustwidth}
-\caption{Ranked feature importances for the same three physical parameter models.\label{fig:physical-fit}}
-\end{figure}
-
-\subsection{Ions}
-
-Explanation for goodness of fit: index of refraction is temperature and salinity dependent
-
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
-\centering
-\includegraphics[width=16.0cm]{paper/figures/results/fits/ions-fitres.png}
-\end{adjustwidth}
-\caption{A visualization of the fitresults for three of the ion concentrations we modeled. On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:ions-fit}}
-\end{figure}
-
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
-\centering
-\includegraphics[width=18.0cm]{paper/figures/results/fits/ions-ranking.pdf}
-\end{adjustwidth}
-\caption{Ranked feature importances for the same three ion concentration models.\label{fig:ions-fit}}
-\end{figure}
-
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
-\centering
-\includegraphics[width=18.0cm]{paper/figures/results/maps/ions.pdf}
-\end{adjustwidth}
-\caption{ \label{fig:map-phys-chem}}
-\end{figure}
-
-\subsection{Biochemical Parameters}
-
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
-\centering
-\includegraphics[width=16.0cm]{paper/figures/results/fits/chemical-fitres.png}
-\end{adjustwidth}
-\caption{A visualization of the fitresults for three of the chemical concentrations we modeled.
-On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:chemicals-fit}}
-\end{figure}
-
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
-\centering
-\includegraphics[width=18.0cm]{paper/figures/results/fits/chemical-ranking.pdf}
-\end{adjustwidth}
-\caption{Ranked feature importances for the same three chemical concentration models.\label{fig:chemicals-fit}}
+\caption{Ranked feature importances for the same three chemical concentration models.\label{fig:biochem-fi}}
 \end{figure}
@@
 \centering
-\includegraphics[width=16.0cm]{paper/figures/results/fits/chemical-fitres.png}
+\includegraphics[width=16.0cm]{paper/figures/results/fits/chemical-fitres.pdf}
 \end{adjustwidth}
@@
 \end{adjustwidth}
-\caption{Ranked feature importances for the same three chemical concentration models.\label{fig:chemicals-fit}}
+\caption{Ranked feature importances for the same three chemical concentration models.\label{fig:chemicals-fi}}
 \end{figure}
@@
 \includegraphics[width=18.0cm]{paper/figures/results/maps/physical-chemical.pdf}
+\end{adjustwidth}
+\caption{ \label{fig:map-phys-chem}}
+\end{figure}
+
+\subsection{Physical Parameters}
+
+\begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=16.0cm]{paper/figures/results/fits/physical-fitres.pdf}
+\end{adjustwidth}
+\caption{A visualization of the fitresults for three of the physical parameters we modeled. On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:physical-fit}}
+\end{figure}
+
+\begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=18.0cm]{paper/figures/results/fits/physical-ranking.pdf}
+\end{adjustwidth}
+\caption{Ranked feature importances for the same three physical parameter models.\label{fig:physical-fi}}
+\end{figure}
+
+\subsection{Ions}
+
+Explanation for goodness of fit: index of refraction is temperature and salinity dependent
+
+\begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=16.0cm]{paper/figures/results/fits/ions-fitres.pdf}
+\end{adjustwidth}
+\caption{A visualization of the fitresults for three of the ion concentrations we modeled. On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:ions-fit}}
+\end{figure}
+
+\begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=18.0cm]{paper/figures/results/fits/ions-ranking.pdf}
+\end{adjustwidth}
+\caption{Ranked feature importances for the same three ion concentration models.\label{fig:ions-fi}}
+\end{figure}
+
+\begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=18.0cm]{paper/figures/results/maps/ions.pdf}
 \end{adjustwidth}
@@
 
-We can probably explain the inference of salinity, ion concentrations, etc as being directly related to the observed concentrations of chlorophyll, cdom, co, bgm, etc...
-which are all optically active (i.e.
-have absorption features spectral region of our hyperspectral imager).
+The advantage of combining multiple datsets is clear, particularly for target variables like Chlorophyll which show unimodal distributions within each collection period.
+As there is only slight variation within a single collection, combining multiple collections with different mean values dramatically improves the capability of a model to identify variations...
+yada yada yada
 

### 2024-01-23 paper/paper.tex
updated paper text

--- 2024-01-17 paper/paper.tex
@@
 %=================================================================
-\documentclass[journal,article,submit,pdftex,moreauthors]{Definitions/mdpi}
+\documentclass[sensors,article,submit,pdftex,moreauthors]{Definitions/mdpi}
 
@@
 % Full title of the paper (Capitalized)
-\Title{\textcolor{red}{Leveraging Machine Learning to Characterize Water Quality with an Autonomous Team of Sensing Sentinels }}
+ \Title{\textcolor{red}{Characterizing Water Quality with an Autonomous Robotic Team Employing Comprehensive In-Situ Sensing, Hyperspectral Imaging, Machine Learning, and Conformal Prediction}}
+%\Title{\textcolor{red}{Towards Real-Time Water Quality Characterization Using an Autonomous Robotic Team Employing Comprehensive In-Situ Sensing, Hyperspectral Imaging, and Conformal Prediction}}
 
 % MDPI internal command: Title for citation in the left column
-\TitleCitation{Robot Team II: Electric Boogaloo}
+%\TitleCitation{Robot Team II: Electric Boogaloo}
+\TitleCitation{\textcolor{red}{Characterizing Water Quality with an Autonomous Robotic Team Employing Comprehensive In-Situ Sensing, Hyperspectral Imaging, Machine Learning, and Conformal Prediction}}
 
@@
 % Authors, for the paper (add full first names)
-\Author{John Waczak$^{\dagger}$\orcidA{}, Adam Aker, Lakitha O.
-H.
-Wijeratne, Shawhin Talebi, Bharana Fernando, Prabuddha Hathurusinghe, Mazhar Iqbal, David Schaefer, David J.
-Lary, $^{\dagger}$\orcidB{}*}
+\Author{John Waczak\orcidA{}, Adam Aker, Lakitha O. H. Wijeratne, Shawhin Talebi, Bharana Fernando, Prabuddha Hathurusinghe, Mazhar Iqbal, Matthew Lary, David Schaefer, David J. Lary\orcidB{}*}
 
@@
 % MDPI internal command: Authors, for citation in the left column
-\AuthorCitation{Waczak, J.; Lary, D.; Lastname, F.}
+\AuthorCitation{\textcolor{red}{Waczak, J. et al.}}
 % If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
@@
 % Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{%
-Hanson Center for Space Sciences, University of Texas at Dallas, Richardson, TX 75080, USA\
-}
+\address[1]{%
+Hanson Center for Space Sciences, University of Texas at Dallas, Richardson, TX 75080, USA;  John.Waczak@utdallas.edu (J.W.); Adam.Aker@utdallas.edu (A.A.); lhw150030@utdallas.edu (L.O.H.W.); Shawhin.Talebi@utdallas.edu  (S.T.); ashen.fernando@utdallas.edu  (B.F.); prabuddhamadusanka.hathurusinghedewage@utdallas.edu (P.H.); mazhar.iqbal@utdallas.edu (M.I.); mdlary@me.com~(M.D.L.); captdaveschaefer@gmail.com (D.S.); david.lary@utdallas.edu (D.J.L.)}
+\corres{\hangafter=1 \hangindent=1.05em \hspace{-0.82em} Correspondence: {David.Lary@utdallas.edu}}
 
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{\textcolor{red}{Advances in hyperspectral imaging technology are enabling significant improvements in the spectral resolution of remote sensing data products with a plethora of new satellites either in development or soon to be launched.
-Utilizing hyperspectral data for environmental assessment requires high quality in-situ data that is both difficult to collect and difficult to align with remote sensing data products due to orbital-dependent revisit times and occlusion by weather and cloud cover.
-In this study, present the results of a series of surveys.}}
-
-% A robust characterization of model uncertainties is critical for any time-sensitive or dangerous application...To that end we employ a combination of model stacking together with Conformal Prediction by which we are able to blend together a variety of ML models while simultaneously estimating confidence intervals for the resulting predictions.
+\abstract{\textcolor{red}{
+Inland waters pose a unique challenge for water quality measurement by remote sensing techniques due to their complicated spectral features and small-scale variability.
+At the same time, collecting the high-quality reference data needed to calibrate remote sensing data products is both time-consuming and expensive.
+In this study, we present further development of a robotic team composed of an uncrewed surface vessel (USV) providing in-situ reference measurements and an unmanned aerial vehicle (UAV) equipped with a hyperspectral imager.
+Together, this team is able to address the limitations of existing approaches by enabling the simultaneous collection of comprehensive in-situ data together with high resolution hyperspectral imagery.
+We showcase the capabilities of this team using data collected in a North Texas pond during three observations in the Fall of 2020.
+Machine learning models for 13 parameters are trained using the dataset of paired in-situ measurements and coincident reflectance spectra.
+Using conformal prediction we  estimate 90\% confidence intervals for the output of each trained model.
+Maps generated by applying the models to the collected imagery reveal the small-scale spatial variability within the pond.
+Additionally, computing the permutation importance for each reflectance bin provides further insight into the relevant spectral features associated with each measurement.
+}}
 
@@
 % Keywords
-\keyword{\textcolor{red}{Hyperspectral Imaging; Machine Learning; Robotic Teams; UAV;}}
+\keyword{Water Quality; Robotic Teams; Hyperspectral Imaging; Machine Learning; Conformal Prediction}
 
@@
 
-% Overview and Remote Sensing
+For decades, remote sensing imagery have been used for environmental monitoring with applications ranging from resource mapping, land type classification, and urban growth assessment to wildfire tracking, natural disaster tracking, and many more \cite{cohen2004landsat, melesse2007remote, allison2016airborne, joyce2009review, robert2017analysis}.
+Among these applications, the retrieval of water quality parameters from remote sensing imagery remains challenging due to the difficulty of obtaining in-situ reference data coincident with available satellite imagery.
+Many studies have shown success modeling relevant water quality parameters such as colored dissolved organic matter (CDOM), cholorophyll-a, and total suspended sediment concentrations by using combinations of spectral bands from terrestrial remote sensing satellites.
+However, the in-situ reference data used in these studies typically require the time-consuming collection of individual samples for lab analysis or continuous monitoring at fixed sites \cite{brezonik2005landsat, paavel2011optical, gursoy2019investigating, bonansea2019using, sagan2020monitoring, remote-sensing-finland}.
 
-% Water Quality
+Much effort has recently gone into the curation of comprehensive datasets combining water quality records with decades of satellite imagery to enable the development of new methods for water quality estimation.
+For example, Aurin et al.
+curated over 30 years of oceanographic field campaign data with associated coincident satellite imagery \cite{aurin2018remote}.
+Similarly, Ross et al.
+have combined over 600,000 records of dissolved organic carbon, chlorophyll-a, and other water quality parameters together with historical reflectance data from Landsat for the period of 1984-2019 \cite{ross2019aquasat}.
+With a sufficient quantity of data, machine learning methods can augment traditional approaches using reflectance band ratios to enable estimation of water quality metrics and perform water quality classification \cite{schiller1999neural, brown2008neural, lary2010artificial, feng2015urban,belgiu2016random}.
+However, the low spatial and spectral resolution of available multi-band remote sensing satellites makes it difficult to analyze inland waters with small features and complicated spectral signatures.
+Additionally, the long revisit times of these satellites limits their use for real-time monitoring, for example, during oil spills \cite{fingas2017review}.
 
-% UAVs
+Advances in multispectral and hyperspectral imaging technology have considerably reduced their size making it possible to incorporate these cameras into the payload of autonomous aerial vehicles (UAV) such as quadcopters, hexacopters, and other drones \cite{hruska2012radiometric}.
+By controlling the altitude during flight, UAVs can produce imagery with pixels at the centimeter scale and limit the need for complicated atmospheric corrections to account for scattering by atmospheric aerosols and gases \cite{adao2017hyperspectral,banerjee2020uav}.
+Already, UAVs equipped with multi- and hyperspectral imagers are being utilized in a variety of domains to great effect including biomass estimation, forest management, precision agriculture, and now, water quality monitoring \cite{adao2017hyperspectral, padua2017uas,arroyo2019implementation,kurihara2020unmanned,ehmann2019monitoring, lu2021retrieval}.
 
-% Machine Learning
+Despite the increased spectral and spatial resolution afforded by UAV platforms, these improvements alone are unable to address the limited spatial resolution of in-situ reference data.
+To address this gap and enable real-time comprehensive water quality sensing, we have developed a robotic team composed of an autonomous uncrewed surface vessel (USV) equipped with a collection of reference grade instruments together with an UAV carrying a hyperspectral imager \cite{robotTeam1}.
+By incorporating these reference instruments on a maneuverable USV platform, we are able to rapidly collect large volumes of water quality data for a variety of physical, biochemical, and chemical parameters.
+Critically, the USV enables the collection of reference data with significantly improved spatial resolution compared to other approaches.
+These in-situ measurements then provide the ground-truth data used to train machine learning models which map reflectance spectra captured by the hyperspectral imager to the desired water quality parameters.
 
-% Our Approach
-- Most remote sensing data products are from multi-spectral imagers, i.e. LANDSAT, MODIS, ETC... 
-    - multispectral imagers have limited spectral resolution 
-    - Much progress has been made in the development of spectral indices
-    - It can be challenging to directly associate these to desired measurements, rather we typically just track the index (without use of in-situ data), or generate classifications that can be challenging to interpret (i.e.
-good vs acceptable vs poor air/water quality)
-- Existing hyperspectral imagers do not have global coverage, but many are on the way EnMAP
-    - AVRIS was used in a plane 
-    - Regardless, the increased data volume due to improved spectral resolution has an impact on the rate at which data are registered, processed, and transferred
-- In situ measurements are expensive and challenging to collect
-    - Existing in-situ data often require collection in the field and analysis back in the lab
-    - In-situ measurements tend to have poor spatial resolution and volume (~10-100 of measurements per site)
-    - Collection and analysis is slow. At best, we can have fixed location sensors which stream their data
-- Retrieval of water quality parameters from remote sensing data requires the existence of co-aligned imagery
-    - This could never be "real time" due to satellite revisit times (usual 1/day) 
-    - remote sensing imagery are easily occluded by clouds and are impacted by atmospheric effects due to aerosols (dust) and gasses (ozone, water vapor, etc). 
-- UAVs provided an excellent solution allowing for improved spatial resolution easily controlled by flight altitude
-    - Much less expensive
-    - Can rapidly survey wide areas that are hard to reach with conventional reference instruments
-    - Can be equipped with many instruments including hyperspectral imagers
-    - Can enable rapid development of relevant spectral indices by \textit{brining the spectrometer to the problem}
-- UAVs alone are not a complete solution as we still suffer from an insufficient sampling density of in-situ reference data
-    - The ideal solution is to use a team of autonomous sensing sentinels including a UAV to provide the hyperspectral imagery complemented by additional sentinels for collecting in-situ reference data
-    - In this team, an uncrewed survey vehicle (USV), i.e. a boat is equipped with a suite of reference instruments. 
-    - These instruments provide the ground truth data used to map reflectance measurements made by the UAV directly to the water quality parameters we actually care about.
-- In our previous work, we devised and implemented such a team \cite{robotTeam1}. 
-    - Prevously we showcased how the team can work for a single collection in the field 
-    - In this work, we demonstrate how combining data from multiple collections allows the ML models to learn the representation of a wider range of target concentrations under a variety of lighting conditions.
-        - This is clearly beneficial when single-day collections are uni-modal.
-That is, for targets that show little variation within a single collection, there is a significant benefit to combining multiple days of observations
-        - This is successful even for collections with complicated distributions.
-    - For use in near-real time safety assessments it's important that the proposed architecture be both fast and accurate
-        - We describe the implementation of a rapid georectification procedure that can run \textit{on the UAV}
-        - The selected ML models achieve a balance of both training time \textit{and} inference time allowing us to rapidly deploy the models
-        - We additionally include a characterization of ML model uncertainty (which is typically lacking) using Conformal Prediction
-        - Key reflectance features that impact model performance can be quickly identifed using permutation importance
-            - This is less biased than typical tree-based impurity methods 
-            - This is also model agnostic (can be applied to any black-box model) 
-            - This is easily interpretable: we measure the impact on model performance ($R^2$ value) when a feature is randomly permuted and all others remain the same.
-The change in $R^2$ value tells us how sensivie the final model is to each feature
-            - This can aid the generation of new spectral indices as well as allow for reduced model size while maximizing performance, i.e. an Occam's razor approach. 
-    - we showcase maps generated using the trained ML models
+In this study, we expand on our previous work by demonstrating the capabilities of this coordinated robot team using data collected at a pond in North Texas across three separate days in the Fall of 2020.
+Specifically, we showcase the ability to accurately predict physical parameters such as temperature, conductivity, pH, and turbidity, as well as biochemical constituents including blue-green algae pigments, CDOM, and chlorophyll-a, in addition to concentrations of crude oils, optical brighteners, and a variety of ions.
+Further, the considerable size of the collected dataset allows us to quantify the uncertainty in the resulting machine learning models by using techniques from conformal prediction.
+This methodology addresses the shortcomings of existing approaches by facilitating rapid, real-time data collection coupled with on board hyperspectral image processing and machine learning model deployment with uncertainty quantification.
 
-In our previous work, we developed a robotic team comprised of...
-We showed that using this team, hyperspectral imagery collected by the UAV can be calibrated against in-situ reference measurements collected by the USV to enable the rapid generation of wide area surveys for a variety of water quality parameters \cite{robotTeam1}.
-In this study, we expand on this previous work to demonstrate that by combining observations across multiple distinct collections, we can improve our machine learning models...
-
-% The shrinking size of multispectral and hyperspectral imagers has enabled their inclusion as the payload of multi-rotor Unmanned Aerial Vehicles (quadcopters, hexacopters, etc.).
-These platforms are able to address the shortcoming of remote sensing imagery, namely poor spatial resolution and atmospheric interference effects due to aerosols, dust, water vapor, etc by flying close to the ground.
-Further, UAVs can be taken \textit{to the reference sensors} to better facilitate collocation with reference data.
-However,
-
-% In-situ measurements are expensive to collect and suffer from poor spatial coverage.
-Remote sensing data cover much wider areas but do not directly provide parameters needed for environmental assessments.
-Additionally, remote sensing data, particularly satellite based imagers, also suffer from long orbit-dependent site revisit times and can be easily occluded by the presence of clouds.
-This makes it incredibly challenging to collocate sufficient quantities of in-situ measurements with overlapping remote sensing imagery to enable their calibration.
-\textcolor{red}{(add reference to David's CDOM paper here...)}.
-To address this gap, we have developed an autonomous team of sensing sentinels combining a mobile uncrewed surface vessel (USV) with a unmanned aerial vehicle (UAV) which together rapidly collect hyperspectral imgaery \textit{and} comprehensive in-situ measurements to enable the estimation of key environmental parameters including concentrations of key constituents like CDOM, Crude Oils, Ions,as well as physical parameters like temperature, salinity, and dissolved oxygen.
-In our previous work we established a methodology for calibrating the hyperspectral imagery against reference measurements during a collection window \cite{robotTeam1}.
-In his study, we demonstrate that such models can be reliably trained using data collected from multiple observations....
-
-%The introduction should briefly place the study in a broad context and highlight why it is important.
-It should define the purpose of the work and its significance.
-The current state of the research field should be reviewed carefully and key publications cited.
-Please highlight controversial and diverging hypotheses when necessary.
-Finally, briefly mention the main aim of the work and highlight the principal conclusions.
-As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
-Citing a journal paper \cite{ref-journal}.
-Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}.
-Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
+% critical to this approach
 
@@
 
-In this study we employ a team of autonomous sensing sentinels, hereafter referred to as \textit{the robot team}, to enable the rapid characterization of aquatic environments.
-This team consists of two key sensing sentinels: An uncrewed surface vessel (USV) used to collect in-situ reference measurements, and an unmanned aerial vehicle (UAV) for performing rapid, wide-area surveys to gather remote sensing data products.
-Both platforms are coordinated using the open-source QGroundControl software for flight control and mission planning and are equipped with high accuracy GPS and INS such that all collected data points are uniquely geolocated and time-stamped \cite{qgroundcontrol}.
-Both the USV and UAV are equipped with long-range Ubiquiti 5 GHz LiteBeam airMAX WiFi to enable streaming of data products to a ground station with network attached storage providing redundancy.
+ The robotic team employed in this study consists of two key sensing sentinels: An uncrewed surface vessel (USV) used to collect in-situ reference measurements, and an unmanned aerial vehicle (UAV) for performing rapid, wide-area surveys to gather remote sensing data products.
+Both platforms are coordinated using the open-source QGroundControl software for flight control and mission planning and are equipped with high accuracy GPS and INS such that all collected data points are uniquely geo-located and time-stamped \cite{qgroundcontrol}.
+Both the USV and UAV include long-range Ubiquiti 5 GHz LiteBeam airMAX WiFi to enable streaming of data products to a ground station with network attached storage providing redundancy.
 
@@
 The USV is equipped with an in-situ sensing payload consisting of a combination of Eureka Manta-40 multi-probes including fluorometers, ion selective electrodes, and other physical sensors which together enable the collection of comprehensive near-surface measurements including Colored Dissolved Organic Matter (CDOM), Crude Oil, Blue-Green Algae (phycoerythrin and phycocyanin), Chlorophyll-A, $\mathrm{Na^+}$, $\mathrm{Ca^{2+}}$, $\mathrm{Cl^-}$, Temperature, Conductivity, and many others.
-The full list of measurements utilized in this study is given in Table~\ref{tab:sensors} and are categorized into four distinct types: physical measurements, ion measurements, biochemical measurements, and chemical measurements.
+The full list of measurements utilized in this study is given in Table~\ref{tab:sensors} and is categorized into four distinct types: physical measurements, ion measurements, biochemical measurements, and chemical measurements.
 Additionally, the USV is equipped with an ultra-sonic weather monitoring sensor for measuring air speed and direction as well as a a BioSonics MX Aquatic Habitat Echosounder sonar which are not explored in this study.
@@
 \newcolumntype{C}{>{\centering\arraybackslash}X}
-\begin{tabularx}{\textwidth}{CCCC}
+\begin{tabularx}{\textwidth}{CCCCC}
 \toprule
-\textbf{Sensor}	& \textbf{Units} & \textbf{Sensor Type} & \textbf{Target Category}\\
+\textbf{Sensor}	& \textbf{Units} & Resolution & \textbf{Sensor Type} & \textbf{Target Category}\\
 \midrule
-Temperature		                    & $^{\circ}$C       & Thermistor  & Physical \\
-Conductivity                        & $\mu$S/cm         & Four-Electrode Graphite Sensor & Physical  \\
-%Dissolved Oxygen                    & mg/l              & Optical Sensor & Physical \\
-pH                                  & logarithmic (0-14)& Flowing-junction Reference Electrode & Physical \\
-Turbidity                           & FNU               & Ion-Selective Electrode  & Physical \\
-$\mathrm{Ca^{2+}}$                  & mg/l              & Ion-Selective Electrode  & Ions \\
-$\mathrm{Cl^-}$                     & mg/l              & Ion-Selective Electrode & Ions \\
-$\mathrm{Na^+}$                     & mg/l              & Ion-Selective Electrode & Ions \\
-Blue-Green Algae (phycoerythrin)    & ppb               & Fluorometer & Biochemical \\
-Blue-Green Algae (phycocyanin)      & ppb               & Fluorometer & BioChemical \\
-CDOM                                & ppb               & Fluorometer & Biochemical \\
-Chlorophyll A                       & ppb               & Fluorometer & BioChemical \\
-Optical Brighteners                 & ppb               & Fluorometer & Chemical \\
-Crude Oil                           & ppb               & Fluorometer & Chemical\\
-%Salinity                            & PSU               & Four-Electrode Graphite Sensor \\
-%$\mathrm{NO_3^-}$                   & mg/l as nitrogen  & Ion-Selective Electrode \\
+Temperature		                    & $^{\circ}$C        & 0.01  & Thermistor                           & Physical \\
+Conductivity                        & $\mu$S/cm          & 0.01  & Four-Electrode Graphite Sensor       & Physical  \\
+pH                                  & logarithmic (0-14) & 0.01  & Flowing-junction Reference Electrode & Physical \\
+Turbidity                           & FNU                & 0.01  & Ion-Selective Electrode              & Physical \\
+$\mathrm{Ca^{2+}}$                  & mg/l               & 0.1   & Ion-Selective Electrode              & Ions \\
+$\mathrm{Cl^-}$                     & mg/l               & 0.1   & Ion-Selective Electrode              & Ions \\
+$\mathrm{Na^+}$                     & mg/l               & 0.1   & Ion-Selective Electrode              & Ions \\
+Blue-Green Algae (phycoerythrin)    & ppb                & 0.01  & Fluorometer                          & Biochemical \\
+Blue-Green Algae (phycocyanin)      & ppb                & 0.01  & Fluorometer                          & BioChemical \\
+CDOM                                & ppb                & 0.01  & Fluorometer                          & Biochemical \\
+Chlorophyll A                       & ppb                & 0.01  & Fluorometer                          & BioChemical \\
+Optical Brighteners                 & ppb                & 0.01  & Fluorometer                          & Chemical \\
+Crude Oil                           & ppb                & 0.01  & Fluorometer                          & Chemical\\
 \bottomrule
@@
 As shown in Table~\ref{tab:sensors}, the physical parameter and ion sensors are largely based on different configurations of electrodes while the chemical and biochemical parameters are all optically active substances enabling their determination by fluorometry.
-The pigments phycoerythrin and phycocyanin are used to determine blue-green algae content which together with chlorophyll-a enables us to asses the distribution of photosynthetic life.
+The pigments phycoerythrin and phycocyanin are used to determine blue-green algae content which together with chlorophyll-a enables us to asses the distribution of photosynthetic life in the pond.
 Additionally, we also measure the concentration of colored dissolved organic matter (CDOM) which impacts light penetration and serves as a primary source of bioavailable carbon.
@@
 \centering
-\includegraphics[width=16cm]{paper/figures/materials-and-methods/pipeline-figure-2.pdf}
+\includegraphics[width=14cm]{paper/figures/materials-and-methods/pipeline-figure-2.pdf}
 \end{adjustwidth}
-\caption{Hyperspectral Image Processing: Hyperspectral datacubes are collected one scan-line at a time (left).
+\caption{Hyperspectral Image Processing: Hyperspectral data cubes are collected one scan-line at a time (left).
 By utilizing downwelling irradiance spectra we convert each pixel from spectral radiance to reflectance.
@@
 In the collection software, a regular cutoff of 1000 lines is chosen so that each resulting \textit{image} forms a array of size 462$\times$1600$\times$1000 called a \textit{hyperspectral data cube}.
-Initially, the sampled spectra are in units of spectral radiance (measured in microflicks) however this does not account for the variability of incident light illuminating the water.
+Initially, the captured spectra are in units of spectral radiance (measured in microflicks) however this does not account for the variability of incident light illuminating the water.
 To this end, we convert the hyperspectral data cubes into units of reflectance by utilizing the skyward-facing downwelling irradiance spectrometer (see Figure~\ref{fig:drone-components}).
-When our camera is normal to the water surface, then the reflectance is given by
+When the camera is normal to the water's surface, the reflectance is given by
 \begin{equation}
@@
 The final result is a georectified hyperspectral reflectance data cube.
-In Figure~\ref{fig:hsi-infographic} we visualize one such data cube, highlighting a selection of exemplar pixel spectra from the scene as well as the incident downwelling irradiance spectrum.
+In Figure~\ref{fig:hsi-infographic} we visualize one such data cube, highlighting a selection of exemplar pixel spectra as well as the incident downwelling irradiance spectrum.
 A pseudo-color image is generated (plotted on the top of the data cube) to illustrate the scene.
@@
 The above processing pipeline was implemented using the Julia programming language, a just-in-time compiled language with native multi-theading support \cite{julia-1}.
-By running this pipeline on the on-board processing computer, we are able to process the collected hyperspectral data cubes in near real time.
+By running this pipeline on the on board computer, we are able to process the collected hyperspectral data cubes in near real time.
 This feature is critical for time-sensitive applications where we need to quickly asses if an area is safe and can not afford to wait to download and post-process collected imagery \textit{after} a flight.
 
-\subsection{Data Collection and Training Set Curation}
+\subsection{Data Collection}
 
-Data were collected using the robot team at a site in north Texas across three observation periods in the fall of 2020.
-For each collection period, the UAV first completed two wide surveys of the lake capturing multiple hyperspectral data cubes.
-Subsequently, the the USV sampled across the lake, collecting in-situ reference measurements.
+Data were collected using the robot team at a site in North Texas across three observation periods in the fall of 2020.
+For each collection period, the UAV first completed a wide survey of the pond capturing multiple hyperspectral data cubes.
+Subsequently, the the USV sampled across the pond, collecting in-situ reference measurements.
 Each of these reference measurements was then collocated with individual pixel spectra where the USV track overlapped with UAV pixels.
-To account for any time lag in the values measured by the in-situ instruments and to account for the USV size in comparison to the data cube spatial resolution, each in-situ measurement is associated with a 3$\times$3 grid of HSI pixels, that is, a 30 cm $\times$ 30 cm square.
+To account for any time lag in the values measured by the in-situ instruments and to account for the USV size in comparison to the data cube's spatial resolution, each in-situ measurement is associated with a 3$\times$3 grid of HSI pixels, that is, a 30 cm $\times$ 30 cm square.
 These combined data form the tabular data set on which we train regression models; pixel spectra form input features and each separate USV sensor forms a distinct target variable.
 
-Each collection was performed near solar noon to maximize the amount of incident sunlight illuminating the water, however, to account for any potential variation in lighting conditions between data cubes, we augment the training set with additional features including the drone viewing geometry (roll, pitch, heading) and solar illumination geometry (solar azimuth, solar elevation, solar zenith) as well as the total at-pixel intensity (before refelctance conversion), the total downwelling intensity, and the drone altitude.
-Further feature engineering is performed to add a additional spectral indices which utilize combinations of specific wavelength bands like the normalized difference vegetation index (NDVI), normalized difference water index (NDWI), simple ratio (SR), photochemical reflectance index (PRI), and more as described in \cite{envi_vegetation_indices, thenkabail2018hyperspectral,kaufman1992atmospherically, SpectralIndexWheat}.
+Each collection was performed near solar noon to maximize the amount of incident sunlight illuminating the water, however, to account for any potential variation in lighting conditions between data cubes, we augment the training set with additional features including the drone viewing geometry (roll, pitch, heading) and solar illumination geometry (solar azimuth, solar elevation, solar zenith) as well as the total at-pixel intensity before reflectance conversion, the total downwelling intensity, and the drone altitude.
+Further feature engineering is performed to add additional spectral indices which utilize combinations of specific wavelength bands like the normalized difference vegetation index (NDVI), normalized difference water index (NDWI), simple ratio (SR), photochemical reflectance index (PRI), and more as outlined in \cite{envi_vegetation_indices, thenkabail2018hyperspectral,kaufman1992atmospherically, SpectralIndexWheat}.
 A comprehensive list of these added features is provided in supplementary table S1.
@@
 
-As reflectance values in adjacent wavelength bins tend to correlate with each other, and therefore, may not necessarily contribute additional information content to the final model, it is desirable to evaluate the relative importance of each feature to the predictions of our trained models.
+As reflectance values in adjacent wavelength bins tend to correlate with each other, and therefore, may not necessarily contribute additional information content to the final model, it is desirable to evaluate the relative importance of each feature to the final predictions of our trained models.
 This is useful both for identifying the most relevant parameters as well as for performing feature selection to reduce the final model size and optimize inference time.
-By default, tree-based methods like the RFR allow for an impurity based ranking as described in \cite{rfr-orig, rfr-importance-ranking}.
+By default, tree-based methods like the RFR allow for an impurity based ranking as described in \cite{random-forest, rfr-importance-ranking}.
 However, these methods have been shown to be biased towards high cardinality and correlated features \cite{strobl2008conditional}.
@@
 
-Using these tools, the training procedure for each model is as follows: First, the model is trained using 6-fold cross validation on the training set with default hyperparameters.
-Feature importances and for the trained model are then computed and the top 25 features are identified.
-A second, reduced-feature model is then trained using the same 6-fold cross validation scheme.
-Next, each model is hyperparameter optimized using a random parameter search over the number of tees and sampling fraction.
-Model performance is evaluated by computing out-of-fold values for the coefficient of determination, as well as
+Using these tools, the training procedure for each model is as follows: First, the model is trained using 6-fold cross validation on the training set with default hyperparameter values.
+Feature importances for the trained model are then computed and the top 25 features are identified.
+A second, model is then trained using the same 6-fold cross validation scheme with \textit{only} these 25 most important features together with hyperparameter optimization using a random parameter search over the number of tees and sampling fraction.
+Model performance is evaluated by computing out-of-fold values for the coefficient of determination, as well as the
 \begin{align}
@@
 Having identified the model with the best out-of-fold performance, we proceed to train the final hyperparameter optimized model on the full training set with associated uncertainty estimated using conformal prediction.
-Finally, each of these resulting hyperparameter optimized models is evaluated on the previously untouched testing set.
-Additionally, we visualize the scatter diagram and quantile-quantile plot to visualize model performance across the distribution of testing data.
+Each final model is then evaluated on the previously untouched testing set.
+We visualize model performance across the distribution of testing data with a scatter diagram and quantile-quantile plot for which successful model predictions should lie close to a 1:1 line.
+
+These trained models can then easily be deployed on the on board processing computer so that during subsequent surveys, target concentrations can be inferred as imagery are collected and processed.
+The application of each model to the collected hyperspectral data cubes results in a map of the distribution of each water quality parameter across the pond.
 
@@
 The final dataset combining observations from each of the three separate collections contains more than 120,000 individual records.
+The collection on 11-23 covered the largest spatial extent across the pond, however due to flight time constraints resulting from the payload size, imagery from adjacent flight tracks did not overlap resulting in slight gaps.
+The collections on 12-09 and 12-10 were adjusted to reduce this gap, resulting in a more uniform coverage across a smaller spatial extent.
 
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{paper/figures/results/target_correlations.pdf}
-\caption{\label{fig:target-correlations}}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{paper/figures/results/downwelling-hist.pdf}
+\begin{figure}
+\includegraphics[width=0.7\columnwidth]{paper/figures/results/downwelling-hist.pdf}
 \caption{Distribution of total downwelling intensity during each of the three HSI collection flights.
@@
 
+The variability of incident lighting conditions for each collection is visualized in Figure~\ref{fig:downwelling-hist} where the distribution of the total downwelling intensity measured by the downwelling irradiance spectrometer across all hyperspectral data cubes is visualized.
+Despite performing all UAV flights near solar noon, there was a difference in minimum solar zenith angle between collections due to the time of year.
+Additionally, there was some slight cloudiness during the 12-09 and 12-10 collections.
+
 The results of the model training procedure are presented in Table~\ref{tab:fit-results}.
-Model performance is identified by the $R^2$, RMSE, and MAE out-of-fold estimates (mean $\pm$ standard deviation) of the final hyperparameter-optimized model with target variables ranked in descending order by the $R^2$ value.
+Model performance is identified by the $R^2$, RMSE, and MAE out-of-fold estimates (mean $\pm$ standard deviation) of the final hyperparameter-optimized model on the training set with target variables ranked in descending order by the $R^2$ value and separated by sensor type (physical parameters, ions, biochemical parameters, and chemical parameters).
 The small variation in values across folds confirms that the reported performance is independent of how the training set was sampled.
-Additionally, we report the interval width which yields a 90\% confidence interval on the holdout validation set as determiend by the conformal prediction procedure.
-We then evaluate how the estimated uncertainty generalizes by computing the \textit{emprical coverage} on the holdout testing set, that is, we compute the percentage of predictions on the testing set that \textit{actually} fall within the desired 90\% interval.
+Additionally, we report the interval width which yields a 90\% confidence interval on the holdout validation set as determined by the conformal prediction procedure.
+We then evaluate how the estimated uncertainty generalizes by computing the \textit{emprical coverage} on the holdout testing set, that is, we compute the percentage of predictions on the testing set that \textit{actually} fall within the estimated 90\% confidence interval.
 
-\begin{table}[H]
+\begin{table}
   \caption{Summary of fitting statistics for each target measurement.
 Models were evaluated using 6-fold cross validation on the training set.
-The estimated uncertainty is evaluated using conformal prediction so that a prediction $\hat{y}\pm \Delta y$ achieves 90\% coverage on the calibration holdout set.
-The empirical coverage is the percentage of predictions in the testing set that fall within the confidence interval determined by conformal prediction.
-The final column shows the best performing model.
+The estimated uncertainty is evaluated so that a prediction $\hat{y}\pm \Delta y$ achieves 90\% coverage on the calibration holdout set.
+The empirical coverage is the percentage of predictions in the testing set that fall within the inferred confidence interval.
 \label{tab:fit-results}}
@@
   \newcolumntype{C}{>{\centering\arraybackslash}X}
-  \begin{tabularx}{\fulllength}{CCCCCC}
+  \begin{tabularx}{\fulllength}{CCCCCCC}
     \toprule
-    \textbf{Target} & \textbf{$\text{R}^2$} & \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty} & \textbf{Empirical Coverage (\%)} \\
+    \textbf{Target} & \textbf{Units} & \textbf{$\text{R}^2$} & \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty} & \textbf{Empirical Coverage (\%)} \\
     \midrule
-    Temperature & 1.0 ± 6.04e-6 & 0.0289 ± 0.000466 & 0.0162 ± 0.00016 &  ± 0.039 & 90.3 \\
-    $Conductivity$ & 1.0 ± 1.54e-5 & 0.574 ± 0.0128 & 0.322 ± 0.00579 &  ± 0.76 & 90.6 \\
-    $\mathrm{Ca}^{2+}$ & 1.0 ± 1.06e-5 & 0.285 ± 0.00357 & 0.137 ± 0.00224 &  ± 0.33 & 89.8 \\
-    $\mathrm{Cl^-}$ & 0.995 ± 0.000196 & 0.895 ± 0.0202 & 0.516 ± 0.00759 &  ± 1.2 & 90.1 \\
-    Blue-Green Algae (Phycoerythrin) & 0.995 ± 0.000601 & 0.783 ± 0.0489 & 0.287 ± 0.00959 &  ± 0.73 & 89.3 \\
-    pH & 0.994 ± 0.000288 & 0.0145 ± 0.000304 & 0.00739 ± 9.49e-5 &  ± 0.017 & 89.5 \\
-    $\mathrm{Na^+}$ & 0.993 ± 0.000229 & 6.16 ± 0.102 & 2.83 ± 0.0303 &  ± 7.3 & 90.0 \\
-    CDOM & 0.965 ± 0.00352 & 0.248 ± 0.0142 & 0.0921 ± 0.0024 &  ± 0.15 & 89.9 \\
-    Crude Oil & 0.949 ± 0.00267 & 0.247 ± 0.00597 & 0.0935 ± 0.00114 &  ± 0.17 & 89.8 \\
-    Optical Brighteners & 0.943 ± 0.00122 & 0.0806 ± 0.0014 & 0.0481 ± 0.000416 &  ± 0.095 & 89.8 \\
-    $Chlorophyll A$ & 0.908 ± 0.00664 & 0.37 ± 0.00934 & 0.131 ± 0.00228 &  ± 0.27 & 89.2 \\
-    Turbidity & 0.897 ± 0.00611 & 3.13 ± 0.084 & 0.736 ± 0.0156 &  ± 1.1 & 89.8 \\
-    Blue-Green Algae (Phycocyanin) & 0.708 ± 0.00689 & 0.749 ± 0.0129 & 0.446 ± 0.00405 &  ± 0.93 & 89.8 \\
+    Temperature & $^{\circ}$C & 1.0 ± 6.04e-6 & 0.0289 ± 0.000466 & 0.0162 ± 0.00016 &  ± 0.039 & 90.3 \\
+    Conductivity & $\mu$S/cm & 1.0 ± 1.54e-5 & 0.574 ± 0.0128 & 0.322 ± 0.00579 &  ± 0.76 & 90.6 \\
+    pH & 0-14 & 0.994 ± 0.000288 & 0.0145 ± 0.000304 & 0.00739 ± 9.49e-5 &  ± 0.017 & 89.5 \\
+    Turbidity & FNU & 0.897 ± 0.00611 & 3.13 ± 0.084 & 0.736 ± 0.0156 &  ± 1.1 & 89.8 \\
+    \midrule
+    $\mathrm{Ca}^{2+}$ & mg/l & 1.0 ± 1.06e-5 & 0.285 ± 0.00357 & 0.137 ± 0.00224 &  ± 0.33 & 89.8 \\
+    $\mathrm{Cl^-}$ & mg/l & 0.995 ± 0.000196 & 0.895 ± 0.0202 & 0.516 ± 0.00759 &  ± 1.2 & 90.1 \\
+    $\mathrm{Na^+}$ & mg/l &0.993 ± 0.000229 & 6.16 ± 0.102 & 2.83 ± 0.0303 &  ± 7.3 & 90.0 \\
+    \midrule
+    Blue-Green Algae (Phycoerythrin) & ppb & 0.995 ± 0.000601 & 0.783 ± 0.0489 & 0.287 ± 0.00959 &  ± 0.73 & 89.3 \\
+    CDOM & ppb &  0.965 ± 0.00352 & 0.248 ± 0.0142 & 0.0921 ± 0.0024 &  ± 0.15 & 89.9 \\
+    Chlorophyll A & ppb & 0.908 ± 0.00664 & 0.37 ± 0.00934 & 0.131 ± 0.00228 &  ± 0.27 & 89.2 \\
+    Blue-Green Algae (Phycocyanin) & ppb & 0.708 ± 0.00689 & 0.749 ± 0.0129 & 0.446 ± 0.00405 &  ± 0.93 & 89.8 \\
+    \midrule
+    Crude Oil & ppb & 0.949 ± 0.00267 & 0.247 ± 0.00597 & 0.0935 ± 0.00114 &  ± 0.17 & 89.8 \\
+    Optical Brighteners & ppb & 0.943 ± 0.00122 & 0.0806 ± 0.0014 & 0.0481 ± 0.000416 &  ± 0.095 & 89.8 \\
     \bottomrule
@@
 From Table~\ref{tab:fit-results},  we see that the empirical coverage achieved by the inferred confidence interval evaluated on the independent test set is within 1\% of our desired coverage for each target modelled.
-This indicates that the uncertainties obtained by the conformal prediction procedure are reliable, at least within the extremes of the collected dataset.
+This indicates that the uncertainties obtained by the conformal prediction procedure are reliable, at least within the bounds of the collected dataset.
+We also note that in all cases, the inferred model uncertainties are larger than resolution of the in-situ sensors.
+This lends further credence to the inferred uncertainty estimates as we should not expect to be able have lower uncertainty than the smallest resolvable difference in reference sensor measurements.
 
-To further understand the differences in model performance between the target variables, we can consider the difference between the RMSE and MAE scores.
-Because the MAE is less sensitive to impacts from outliers than the RMSE, any large difference between the two is a good indication that model performance has been degraded by outliers.
-Indeed for turbidity, the worst performing model in the collection, there is an order of magnitude difference between the two.
-This is easily explained upon confirmation that ~3\% of data points had values greater than 100 FNU despite a median value of 1.34 FNU.
+To further examine the differences in model performance between the target variables, we can consider the difference between the RMSE and MAE scores.
+The MAE is less sensitive to impacts from outliers than the RMSE, and as a consequence, any large difference between the two is indicative of impacts due to the distribution of target values.
+Indeed, this is the case for turbidity, for which almost all measurements were below 10 FNU with only a small fraction of observations from a small area near the shore.
+The rest of the models all show a mean per-fold RMSE value with size comparable to the mean per-fold MAE.
 
-The advantage of combining multiple datsets is clear, particularly for target variables like Chlorophyll which show unimodal distributions within each collection period.
-As there is only slight variation within a single collection, combining multiple collections with different mean values dramatically improves the capability of a model to identify variations...
-yada yada yada
-
-discuss distribution of values each day and identify variables which had mostly constant values between all three days (and so were highly impaced by the presece of outliers)...
+In the remainder of this section, we compare the models within each target category.
 
@@
 
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
+The physical parameters included temperature, conductivity, pH, and turbidity.
+In the combined dataset, the distributions for temperature and conductivity had two distinct, non-overlapping regions corresponding to the measurements from 11-23 and the measurements from 12-09 and 12-10, respectively.
+The pH value of the pond was slightly alkaline showing a multi-modal spatial distribution with values ranging from 8.0 to 8.6.
+As mentioned above, the pond water was very clear for each observation period with most turbidity values ranging between 1 and 3 FNU and very few above 10.
+
+The results of the hyperparameter optimized RFR fits are shown in Figure~\ref{fig:physical-fit}.
+Temperature and conductivity show the best performance on the independent training set with $R^2$ values of 1.0 (to 3 decimal places).
+Similarly, the pH model achieves an excellent fit with most predictions falling close to the 1:1 line.
+The quantile-quantile plots for these three models further confirm that the distributions of true and predicted values match.
+The turbidity model also achieves a strong fit with an $R^2$ value of 0.905.
+The scatter diagram and quantile-quantile plot for this target show that the model performance degrades with larger values where deviation in the predicted distribution is apparent past 25 FNU.
+
+\begin{figure}
 \centering
-\includegraphics[width=16.0cm]{paper/figures/results/fits/physical-fitres.png}
-\end{adjustwidth}
-\caption{A visualization of the fitresults for three of the physical parameters we modeled. On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:physical-fit}}
+\includegraphics[width=\columnwidth]{paper/figures/results/fits/physical-fitres.png}
+\caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the physical parameters measured by the USV.\label{fig:physical-fit}}
 \end{figure}
 
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
+The permutation importance of the top 25 features for each of the physical parameter models is shown in Figure~\ref{fig:physical-fi}.
+All four models show a strong dependence on the solar illumination geometry (solar azimuth, elevation, solar zenith) as well as the viewing geometry (pitch, altitude, heading, etc.).
+All four models also include the total downwelling intensity and the total pixel intensity as highly important features.
+The temperature, conductivity, and pH models all include red to infrared reflectance bins and a combination of spectral indices within their most important features.
+Finally, the turbidity model depends mostly on blue wavelengths from 462 to 496 nm and did not include any spectral indices amongst the 25 most important features.
+
+\begin{figure}
 \centering
-\includegraphics[width=18.0cm]{paper/figures/results/fits/physical-ranking.pdf}
-\end{adjustwidth}
-\caption{Ranked feature importances for the same three physical parameter models.\label{fig:physical-fit}}
+\includegraphics[width=\columnwidth]{paper/figures/results/fits/physical-ranking.pdf}
+\caption{Ranked permutation importance for each feature in the physical parameter models.
+Permutation importance measured the decrease in model $R^2$ value after replacing each feature in the prediction set with a random permutation of its values.\label{fig:physical-fi}}
+\end{figure}
+
+By applying the trained models to the full hypserspectral data cubes, we can produce maps of the distribution of the target parameters as in Figure~\ref{fig:map-physical}.
+Here we have chosen to show the map produced from the imagery collected during the 11-23 collection period as they showcase the largest spatial extent.
+The temperature map shows lower values near the shore which is to be expected as the air temperature was below the water temperature.
+The temperature, conductivity, and pH maps all show a distinction between the main body of water and the alcove to the east which receives little flow from the main body.
+The turbidity map confirms that the water is largely clear, with elevated levels near the shore.
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{paper/figures/results/maps/physical.pdf}
+\caption{Maps generated by applying each of the physical parameter models to the hyperspectral data cubes collected on 11-23.
+Overlaid over the predictions are color-filled squares showing the associated in-situ reference data for the same collection period.
+The size of the squares has been exaggerated for the visualization.
+We note that there is good agreement between the model predictions and the reference data.
+\label{fig:map-physical}}
 \end{figure}
@@
 
-Explanation for goodness of fit: index of refraction is temperature and salinity dependent
+The measured ions include $\mathrm{Ca}^{2+}$, $\mathrm{Cl}^{-}$, and $\mathrm{Na}^{+}$.
+All three measurements showed multi-modal spatial distributions throughout the pond on each of the three collections.
+The scatter diagrams and quantile-quantile plots for the resulting fits are shown in Figure~\ref{fig:ions-fit}.
+All three models achieved excellent fits with $R^2$ values of 1.0, 0.996, and 0.993 on the independent testing set respectively.
+Further, there is no clear decrease in model performance for low or high concentrations, rather, for $\textrm{Cl}^{-}$ and $\textrm{Na}^{+}$, the model have the most difficulty in the middle of the target distributions.
 
-\begin{figure}[H]
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{paper/figures/results/fits/ions-fitres.png}
+\caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the ion measurements made by the USV.\label{fig:ions-fit}}
+\end{figure}
+
+The permutation importance ranking for the top 25 features for each of the ion models is shown in Figure~\ref{fig:ions-fi}.
+Here we see that all three models depend on the solar illumination and viewing geometries as well as the total downwelling intensity and the total pixel intensity measured at the hyperspectral imager.
+All three models utilize a combination of spectral indices which combine green, red, and infrared reflectance bins.
+The $\textrm{Ca}^{+}$ and $\textrm{Cl}^{-}$ models depend on specific red wavelengths from 740 to 769 nm.
+$\textrm{Cl}^{-}$ and $\textrm{Na}^{+}$ also depend on green and yellow reflectance bins from 541 to 589 nanometers.
+
+\begin{figure}
 \begin{adjustwidth}{-\extralength}{0cm}
 \centering
-\includegraphics[width=16.0cm]{paper/figures/results/fits/ions-fitres.png}
+\includegraphics[width=18 cm]{paper/figures/results/fits/ions-ranking.pdf}
 \end{adjustwidth}
-\caption{A visualization of the fitresults for three of the ion concentrations we modeled. On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:ions-fit}}
+\caption{Ranked permutation importance for the top 25 features of the ion models.
+The permutation importance measures the decrease in model $R^2$ value when each feature is replaced by a random permutation of its values.\label{fig:ions-fi}}
 \end{figure}
 
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
+The maps produced by applying the fitted models to the hyperspectral data cubes for 11-23 are shown in Figure~\ref{fig:map-ions}.
+Both positive ions $\mathrm{Ca}^{2+}$ and $\mathrm{Na}^{+}$ show high concentrations in the north-west portion of the pond with lower values in the alcove on the eastern side.
+The positive ion concentrations also appear to decrease near the shore.
+The negative ion $\mathrm{Cl}^{-}$ shows the opposite distribution with larger values in the alcove to the east and lowest values on the western side of the pond.
+The $\mathrm{Cl}^{-}$ ion concentration also appears to increase near the shore.
+
+\begin{figure}
 \centering
-\includegraphics[width=18.0cm]{paper/figures/results/fits/ions-ranking.pdf}
-\end{adjustwidth}
-\caption{Ranked feature importances for the same three ion concentration models.\label{fig:ions-fit}}
-\end{figure}
-
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
-\centering
-\includegraphics[width=18.0cm]{paper/figures/results/maps/ions.pdf}
-\end{adjustwidth}
-\caption{ \label{fig:map-phys-chem}}
+\includegraphics[width=\columnwidth]{paper/figures/results/maps/ions.pdf}
+\caption{Maps generated by applying the trained ion models to the data cubes collected on 11-23.
+Overlaid on the maps are the in-situ reference measurements for the same collection period.
+The size of the squares has been exaggerated for the visualization.
+We note that there is good agreement between the generated map and the reference data.
+\label{fig:map-ions}}
 \end{figure}
@@
 
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
+The measured biochemical parameters include the pigments phycoerythrin, phycocyanin, and chlorophyll-a, as well as CDOM.
+Phycoerythrin and phycocyanin are both present in blue-green alagae and chlorophyll-a is a found in all photosynthetic organisms except bacteria.
+In the combined dataset, the three pigments showed multi-modal distributions separated by collection day with little spatial variation within the individual collection.
+CDOM showed a variable spatial distribution throughout the pond between the main water body and the eastern alcove on 11-23.
+
+The results of the RFR fits for the biochemical parameters are shown in Figure~\ref{fig:biochem-fit}.
+Phycoerythrin showed the best model performance with an $R^2$ value of 0.995 on the training set.
+Both CDOM and chlorophyll-a acheived good performance with $R^2$ values of 0.967 and 0.917 on the training set.
+The quantile-quantile plots indicate that the model for CDOM degrades for values below 16 ppb where data are sparse.
+The chlrophyll-a model shows the opposite trend with poorer performance for concentrations above 5 ppb for which there are very few records.
+The phycocyanin model had the lowest performance of the biochemical sensors with an $R^2$ value of 0.727 with model predictions rapidly decreasing in quality for concentrations above 3 ppb.
+
+\begin{figure}
 \centering
-\includegraphics[width=16.0cm]{paper/figures/results/fits/chemical-fitres.png}
-\end{adjustwidth}
-\caption{A visualization of the fitresults for three of the chemical concentrations we modeled.
-On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:chemicals-fit}}
+\includegraphics[width=\columnwidth]{paper/figures/results/fits/biochemical-fitres.png}
+\caption{Scatter plots (left) and quantile-quantile plots (right) for the final hyperparameter optimized models for the biochemical targets blue-green algae (phycoerythrin), CDOM, chlorophyll-a, and blue-green algae (phycocyanin).
+\label{fig:biochem-fit}}
 \end{figure}
 
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
+The permutation importance ranking of the top 25 features of each biochemical model are shown in Figure~\ref{fig:biochem-fi}.
+Again, all four models include the solar illumination and viewing geometries amongst their most important features as well as the total downwelling intensity and total pixel intensity at the imager.
+Additionally, all four models include some vegetation indices amgonst the top features which utilize combinations of blue, green, yellow, red, and infrared reflectance bands.
+The phycoerythrin model shows a preference for green reflectance bins from 544 to 556 nm while the phycocyanin model prefers blue and red reflectance bins.
+The CDOM model utilizes mostly red reflectance values while the chlorophyll-a model includes red, green, and blue reflectance bins.
+
+\begin{figure}
 \centering
-\includegraphics[width=18.0cm]{paper/figures/results/fits/chemical-ranking.pdf}
-\end{adjustwidth}
-\caption{Ranked feature importances for the same three chemical concentration models.\label{fig:chemicals-fit}}
+\includegraphics[width=\columnwidth]{paper/figures/results/fits/biochemical-ranking.pdf}
+\caption{Ranked permutation importance for each feature in the trained biochemical models.
+The permutation importance measures the decrease in model $R^2$ value after replacing each feature with a random permutation of its values.\label{fig:biochem-fi}}
 \end{figure}
 
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
+The maps generated for the 11-23 collection by applying the trained biochemical parameter models are shown in Figure~\ref{fig:map-biochem}.
+The three pigments all show low concentrations in the body of water with elevated levels near the shore.
+The CDOM distribution shows spatial variability with increased values in the eastern alcove similar to the separation seen in the maps for temperature, conductivity, $\textrm{Ca}^{2+}$, $\textrm{Cl}^{-}$, and $\textrm{Na}^{+}$.
+
+\begin{figure}
 \centering
-\includegraphics[width=18.0cm]{paper/figures/results/maps/biochemical.pdf}
-\end{adjustwidth}
-\caption{ \label{fig:map-phys-chem}}
+\includegraphics[width=\columnwidth]{paper/figures/results/maps/biochemical.pdf}
+\caption{Maps generated by applying the trained biochemical parameter models to the data cubes collected on 11-23.
+Overlaid are the in-situ reference data for the same collection period.
+The size of the squares has been exaggerated for the visualization.
+We note there is good agreement between the predicted map and the reference data.
+\label{fig:map-biochem}}
 \end{figure}
@@
 
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
+The final two models to consider are for the measured chemical parameters: crude oil (CO) and optical brighteners (OB).
+The crude oil measurement includes natural, unprocessed petroleum while optical brighteners consist of whitening agents often added to products like soaps, detergents, and cleaning agents.
+Both the crude oil and optical brightener measurements show multi-modal spatial distributions across each collection period.
+The scatter diagrams and quantile-quantile plots for the fitted models are shown in Figure~\ref{fig:chemicals-fit}.
+Both models achieve good performance with $R^2$ values of 0.957 and 0.941 for CO and OB on the holdout testing set.
+The perfomance of the CO model degrades for concentrations below 24 ppb for which there are few records.
+Similarly the OB model shows worse performance for concentrations below roughly 3.5 ppb.
+
+\begin{figure}
 \centering
-\includegraphics[width=16.0cm]{paper/figures/results/fits/chemical-fitres.png}
-\end{adjustwidth}
-\caption{A visualization of the fitresults for three of the chemical concentrations we modeled.
-On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:chemicals-fit}}
+\includegraphics[width=\columnwidth]{paper/figures/results/fits/chemical-fitres.png}
+\caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the the chemical parameters measured by the USV.\label{fig:chemicals-fit}}
 \end{figure}
 
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
+The ranked permutation importances of the top 25 features for each model are shown in Figure~\ref{fig:chemicals-fi}.
+Both models rank the solar illumination and viewing geometries together with the total downwelling intensity and total pixel intensities amongst the top features.
+Both models include a combination of spectral indices utilizing blue, green, yellow, red, and infrared reflectance bins.
+Additionally, the CO model includes green-yellow reflectances from 539 to 589 nm as well as red reflectances from 749 to 769 nm.
+The OB model includes a yellow reflectance at 584.6 nm as well as red reflectance bins.
+
+\begin{figure}
 \centering
-\includegraphics[width=18.0cm]{paper/figures/results/fits/chemical-ranking.pdf}
-\end{adjustwidth}
-\caption{Ranked feature importances for the same three chemical concentration models.\label{fig:chemicals-fit}}
+\includegraphics[width=\columnwidth]{paper/figures/results/fits/chemical-ranking.pdf}
+\caption{Ranked permutation importance for for the top 25 features of the chemical models.
+The permutation importance measures the deacrease in model $R^2$ value after replacing each feature in the prediction set with a random permutation of its values.\label{fig:chemicals-fi}}
 \end{figure}
 
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
+The maps generated by applying the CO and OB models to the 11-23 data cubes are shown in Figure ~\ref{fig:map-chem}.
+Both models show a distinct spatial distribution with elevated values in the eastern alcove of the pond similar to the distribution of CDOM in Figure~\ref{fig:map-biochem}
+
+\begin{figure}
 \centering
-\includegraphics[width=18.0cm]{paper/figures/results/maps/physical-chemical.pdf}
-\end{adjustwidth}
-\caption{ \label{fig:map-phys-chem}}
+\includegraphics[width=\columnwidth]{paper/figures/results/maps/chemical.pdf}
+\caption{Maps generated by applying the trained chemical parameter models to the hyperspectral data cubes collected on 11-23.
+Overlaid are color-filled squares showing the in-situ reference data for the same collection period.
+The size of the squares is exaggerated for the visualization.
+We note that there is good agreement between the model predictions and reference data.\label{fig:map-chem}}
 \end{figure}
@@
 
-We can probably explain the inference of salinity, ion concentrations, etc as being directly related to the observed concentrations of chlorophyll, cdom, co, bgm, etc...
-which are all optically active (i.e.
-have absorption features spectral region of our hyperspectral imager).
+In this paper, we have validated the methodology introduced in our previous work\cite{robotTeam1}. Specifically, we demonstrate that by using an autonomous team of sensing sentinels we can
+\begin{enumerate}
+    \item Rapidly acquire large volumes in in-situ reference data points for a variety of relevant water quality parameters including physical measurements such as temperature, pH, and conductivity as well as ion concentrations, chemicals such as crude oil, and relevant biochemical parameters such as blue-green algae pigments, chlorophyll-a, and CDOM.
+    \item Simultaneously collect hyperspectral remote sensing imagery using an UAV.
+    \item Rapidly process the captured imagery into georectified reflectance data cubes.
+    \item Train machine learning models to map captured reflectance spectra to the water quality parameters measured by the reference sensors.
+    \item Apply the trained models to rapidly map large bodies of water and identify areas of interest.
+\end{enumerate}
+Additionally, we have demonstrated that we can extend this methodology in two new ways: First, we have shown that it is possible to combine the datasets from separate collection periods and successfully train models using \textit{all} of the records despite variability in incident lighting conditions that impact the assumptions made in the reflectance conversion of captured hyperspectral data cubes.
+Second, we have shown that by leveraging the large amount of collected data, we can simultaneously train the machine learning models and quantify their prediction uncertainties by utilizing conformal predictions.
 
-\subsection{Data Product Streaming}
+As Figure~\ref{fig:downwelling-hist} indicates, there is variation in the total downwelling intensity between images collected in the same day \textit{and} between each separate collection period despite acquiring the imagery consistently near solar noon.
+These within collection variations are due to a combination of the stability of the UAV (on which the upward facing downwelling irradiance spectrometer is mounted) together with the occasional interference of clouds.
+Moreover, the assumption that the water's surface can be treated as Lambertian is clearly violated when the water is not perfectly still.
+Despite the potential impact of these limitations on the quality of the resulting reflectance data cubes, the smoothness of the maps generated by our models suggests that we have provided sufficient context by including the relevant solar illumination and viewing geometries as additional features in the final data set.
+This fact is reinforced by the position of these variables s the most important features for \textit{each} of the estimated water quality parameters.
+So long as we are primarily interested in these values and not the reflectances themselves, we are able to successfully account for these lighting effects.
 
-\subsection{Limitations}
+With respect to the real time deployment of these models in the field, we note that training a reduced feature model without further hyperparameter optimization takes roughly 1 minute per target variable of interest using the processing computer included on the UAV.
+This means that in principle, the requisite training data can be collected by the USV, hyperspectral imagery can be acquired and processed into reflectance data cubes by the UAV, the resulting datasets can be combined to identify coincindent records, and this collection can then be used to train machine learning models and generate maps as in Figure~\ref{fig:map-biochem} all while the investigators are still in the field.
+Analyzing these resulting maps enables areas of interest to be readily pinpointed as was demonstrated by the identification of elevated crude oil, optical brighteners, and CDOM in the eastern alcove of the pond on 11-23.
+Having identified a region of interest, the USV can then be sent to collect additional reference data and confirm the presence of any spill, bloom, or other source.
 
-\subsection{Extensions and Next Steps}
-
-The current implementation of conformal prediction utilized in these models estimates a fixed width confidence interval for all outputs.
-This could be improved by training a secondary \textit{residual} model on the errors produced by the base learner, that is, a model which predicts
-\begin{equation}
-    r(X) = \lvert f(X) - y \rvert = \lvert \hat{y} - y \rvert.
-\end{equation}
-In the conformal prediction framework, such a model could then be used to produce \textit{adaptive} uncertainty estimates using the augmented heuristic function
-\begin{equation}
-    S(X,y)  = \dfrac{\lvert \hat{y} - y \rvert }{r(X)}
-\end{equation}
-to produce scores on the calibration holdout set.
-With access to adaptive uncertainty estimates, we can then augment the navigation control for the USV to encourage data collection in regions of high model uncertainty.
-This would further optimize the data collection and calibration procedure at the expense of increased model training times.
+Beyond the potential applications of this robot team for direct water quality monitoring, the combination of reference instruments together with easily co-located hyperspectral imagery provides fertile ground for the development of new spectral indices targeted towards specific water quality parameters.
+In this paper, we have shown how permutation importance ranking for the trained machine learning models enables a straight forward interpretation of the relative value of each reflectance bin to the final model predictions.
+In future work, we plan to utilize this information to construct new combinations of spectral bands which can be readily transferred to remote sensing platforms equipped with hyperspectral imagers such as the German EnMAP mission.
 
@@
 
-This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
+In this study we address the two key limitations of current remote sensing approaches to characterizing water quality, namely, the limited spatial, spectral, and temporal resolution provided by existing satellite platforms and the lack of comprehensive, highly resolved in-situ data needed to validate remote sensing data products.
+By equipping an autonomous USV with a suite of reference sensors, we are able to collect significantly more data than existing approaches that rely on the collection of individual samples for lab analysis or are constrained to continuous sensing at fixed sites.
+Utilizing an autonomous UAV equipped with a hyperspectral imager in tandem with the USV allows us to rapidly generate aligned datasets which can be used to train machine learning models which map measured reflectance spectra to the desired water quality parameters of interest.
+Furthermore, by virtue of collecting large training datasets we are able to simultaneously estimate the uncertainty of our trained models using conformal prediction.
+This addresses the lack of uncertainty quantification in traditional machine learning approaches.
+Finally, the rapid hyperspectral data cube processing pipeline employed on board the UAV makes it possible to deploy these trained models in order to rapidly generate maps of the desired target variables across entire bodies of water.
+The rapid turnaround time from data collection to model deployment is critical for real time water quality assessment and threat identification.
 
@@
 
-\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''.
-Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}
+\funding{This research was funded by the following grants: The Texas National Security Network
+Excellence Fund award for Environmental Sensing Security Sentinels. SOFWERX award for Machine
+Learning for Robotic Team. Support from the University of Texas at Dallas Office of Sponsored
+Programs, Dean of Natural Sciences and Mathematics, and Chair of the Physics Department are gratefully acknowledged.}
 
@@
 
-\dataavailability{We encourage all authors of articles published in MDPI journals to share their research data.
-In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study.
-Where no new data were created, or where data is unavailable due to privacy or ethical restrictions, a statement is still required.
-Suggested Data Availability Statements are available in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}.}
+\dataavailability{The raw data supporting the conclusions of this article will be made available by the authors on request.}
 
@@
 
-\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections.
-This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}
+\acknowledgments{Don MacLaughlin, Scotty MacLaughlin and the City of Plano, TX, are gratefully acknowledged for allowing us to deploy the autonomous robot team on their property.
+Christopher Simmons is gratefully acknowledged for his computational support.
+Annette Rogers is gratefully acknowledged for support with arranging insurance coverage.
+Steven Lyles is gratefully acknowledged for support in arranging a secure place for the robot team.
+The authors acknowledge the OIT-Cyberinfrastructure Research Computing group at the University of Texas at Dallas and the TRECIS CC* Cyberteam (NSF #2019135) for providing HPC resources that contributed to this research.
+\textcolor{red}{Dr.
+Lary had a person to acknowledge that suggested the sensors to use...}}
 
@@
 \begin{tabular}{@{}ll}
-MDPI & Multidisciplinary Digital Publishing Institute\\
-DOAJ & Directory of open access journals\\
-TLA & Three letter acronym\\
-LD & Linear dichroism
+ML & Machine Learning \\
+USV & Uncrewed Surface Vessel \\
+UAV & Unmanned Aerial Vehicle \\
+CDOM & Colored Dissolved Organic Matter \\
+CO & Crude Oil \\ 
+OB & Optical Brighteners \\
+FNU & Formazin Nephelometric Unit \\
+RFR & Random Forest Regressor \\
+RMSE & Root mean square error \\ 
+MAE & Mean absolute error \\
+RENDVI & Red-edge normalized difference vegetation index
 \end{tabular}

### 2024-01-24 paper/paper.tex
Updates from Overleaf

@@
 \address[1]{%
-Hanson Center for Space Sciences, University of Texas at Dallas, Richardson, TX 75080, USA;  John.Waczak@utdallas.edu (J.W.); Adam.Aker@utdallas.edu (A.A.); lhw150030@utdallas.edu (L.O.H.W.); Shawhin.Talebi@utdallas.edu  (S.T.); ashen.fernando@utdallas.edu  (B.F.); prabuddhamadusanka.hathurusinghedewage@utdallas.edu (P.H.); mazhar.iqbal@utdallas.edu (M.I.); mdlary@me.com~(M.D.L.); captdaveschaefer@gmail.com (D.S.); david.lary@utdallas.edu (D.J.L.)}
+Hanson Center for Space Sciences, University of Texas at Dallas, Richardson, TX 75080, USA;  John.Waczak@utdallas.edu (J.W.); Adam.Aker@utdallas.edu (A.A.); lhw150030@utdallas.edu (L.O.H.W.); shawhintalebi@gmail.com (S.T.); ashen.fernando@utdallas.edu  (B.F.); prabuddhamadusanka.hathurusinghedewage@utdallas.edu (P.H.); mazhar.iqbal@utdallas.edu (M.I.); mdlary@me.com~(M.D.L.); captdaveschaefer@gmail.com (D.S.); david.lary@utdallas.edu (D.J.L.)}
 \corres{\hangafter=1 \hangindent=1.05em \hspace{-0.82em} Correspondence: {David.Lary@utdallas.edu}}
@@
 \abstract{\textcolor{red}{
-Inland waters pose a unique challenge for water quality measurement by remote sensing techniques due to their complicated spectral features and small-scale variability.
+Inland waters pose a unique challenge for water quality monitoring by remote sensing techniques due to their complicated spectral features and small-scale variability.
 At the same time, collecting the high-quality reference data needed to calibrate remote sensing data products is both time-consuming and expensive.
-In this study, we present further development of a robotic team composed of an uncrewed surface vessel (USV) providing in-situ reference measurements and an unmanned aerial vehicle (UAV) equipped with a hyperspectral imager.
+In this study, we present the further development of a robotic team composed of an uncrewed surface vessel (USV) providing in-situ reference measurements and an unmanned aerial vehicle (UAV) equipped with a hyperspectral imager.
 Together, this team is able to address the limitations of existing approaches by enabling the simultaneous collection of comprehensive in-situ data together with high resolution hyperspectral imagery.
-We showcase the capabilities of this team using data collected in a North Texas pond during three observations in the Fall of 2020.
+We showcase the capabilities of this team using data collected in a North Texas pond across three observations in the Fall of 2020.
 Machine learning models for 13 parameters are trained using the dataset of paired in-situ measurements and coincident reflectance spectra.
-Using conformal prediction we  estimate 90\% confidence intervals for the output of each trained model.
-Maps generated by applying the models to the collected imagery reveal the small-scale spatial variability within the pond.
-Additionally, computing the permutation importance for each reflectance bin provides further insight into the relevant spectral features associated with each measurement.
+These models are able to successfully estimate physical parameters including temperature, conductivity, pH, and turbidity as well as the concentrations of blue-green algae, colored dissolved organic matter (CDOM), chlorophyll-a, crude oil, optical brighteners, and the ions $\mathrm{Ca}^{2+}$, $\mathrm{Cl}^{-}$, and $\mathrm{Na}^{+}$.
+We extend the training procedure to utilize conformal prediction in order to  estimate 90\% confidence intervals for the output of each trained model.
+Maps generated by applying each trained model to the collected imagery reveal the small-scale spatial variability within the pond.
+Additionally, the permutation importance computed for each feature of the trained models highlights the spectral features relevant to each water quality parameter.
 }}
@@
 
-Much effort has recently gone into the curation of comprehensive datasets combining water quality records with decades of satellite imagery to enable the development of new methods for water quality estimation.
+Much effort has recently gone into the curation of comprehensive datasets combining water quality records with decades of satellite imagery to enable the development of new methods for water quality monitoring.
 For example, Aurin et al.
@@
 This methodology addresses the shortcomings of existing approaches by facilitating rapid, real-time data collection coupled with on board hyperspectral image processing and machine learning model deployment with uncertainty quantification.
+The resulting models are small enough to be deployed on board the UAV to enable real time streaming of data products to the ground.
+This approach drastically reduces the time from data collection to insight.
 
@@
 Additionally, we have demonstrated that we can extend this methodology in two new ways: First, we have shown that it is possible to combine the datasets from separate collection periods and successfully train models using \textit{all} of the records despite variability in incident lighting conditions that impact the assumptions made in the reflectance conversion of captured hyperspectral data cubes.
-Second, we have shown that by leveraging the large amount of collected data, we can simultaneously train the machine learning models and quantify their prediction uncertainties by utilizing conformal predictions.
+Second, we have shown that by leveraging the large amount of collected data, we can simultaneously train the machine learning models and quantify their prediction uncertainties by utilizing conformal prediction.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
-The following statements should be used ``Conceptualization, X.X.
-and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y.
-and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y.
-All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation.
-Authorship must be limited to those who have contributed substantially to the work~reported.}
+\authorcontributions{
+Conceptualization, D.J.L.; methodology, J.L.W.
+and D.J.L; software, J.L.W; field deployment and preparation, J.L.W, A.A., L.O.H.W., S.T.
+B.F., P.H., M.I., M.L., D.S., and D.J.L.; validation, J.L.W.; formal analysis, J.L.W.; investigation J.L.W.; resources, D.J.L.; data curation, J.L.W., A.A., L.O.H.W., and D.J.L; writing---original draft preparation, J.L.W.; writing---review and editing, J.L.W.
+and D.J.L; visualization, J.L.W; supervision, D.J.L; project administration, D.J.L; funding acquisition, D.J.L.; All authors have read and agreed to the published version of the manuscript.
+}
 

### 2024-02-19 paper/paper.tex
updates from David before submission

@@
 %=================================================================
-\documentclass[sensors,article,submit,pdftex,moreauthors]{Definitions/mdpi}
+\documentclass[remotesensing,article,submit,pdftex,moreauthors]{Definitions/mdpi}
 
@@
 % Full title of the paper (Capitalized)
- \Title{\textcolor{red}{Characterizing Water Quality with an Autonomous Robotic Team Employing Comprehensive In-Situ Sensing, Hyperspectral Imaging, Machine Learning, and Conformal Prediction}}
+ \Title{Characterizing Water Composition with an Autonomous Robotic Team Employing Comprehensive In-Situ Sensing, Hyperspectral Imaging, Machine Learning, and Conformal Prediction}
 %\Title{\textcolor{red}{Towards Real-Time Water Quality Characterization Using an Autonomous Robotic Team Employing Comprehensive In-Situ Sensing, Hyperspectral Imaging, and Conformal Prediction}}
@@
 %\TitleCitation{Robot Team II: Electric Boogaloo}
-\TitleCitation{\textcolor{red}{Characterizing Water Quality with an Autonomous Robotic Team Employing Comprehensive In-Situ Sensing, Hyperspectral Imaging, Machine Learning, and Conformal Prediction}}
+\TitleCitation{Characterizing Water Composition with an Autonomous Robotic Team Employing Comprehensive In-Situ Sensing, Hyperspectral Imaging, Machine Learning, and Conformal Prediction}
 
@@
 % MDPI internal command: Authors, for citation in the left column
-\AuthorCitation{\textcolor{red}{Waczak, J. et al.}}
+\AuthorCitation{Waczak, J. et al.}
 % If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{\textcolor{red}{
+\abstract{
 Inland waters pose a unique challenge for water quality monitoring by remote sensing techniques due to their complicated spectral features and small-scale variability.
-At the same time, collecting the high-quality reference data needed to calibrate remote sensing data products is both time-consuming and expensive.
-In this study, we present the further development of a robotic team composed of an uncrewed surface vessel (USV) providing in-situ reference measurements and an unmanned aerial vehicle (UAV) equipped with a hyperspectral imager.
-Together, this team is able to address the limitations of existing approaches by enabling the simultaneous collection of comprehensive in-situ data together with high resolution hyperspectral imagery.
-We showcase the capabilities of this team using data collected in a North Texas pond across three observations in the Fall of 2020.
-Machine learning models for 13 parameters are trained using the dataset of paired in-situ measurements and coincident reflectance spectra.
-These models are able to successfully estimate physical parameters including temperature, conductivity, pH, and turbidity as well as the concentrations of blue-green algae, colored dissolved organic matter (CDOM), chlorophyll-a, crude oil, optical brighteners, and the ions $\mathrm{Ca}^{2+}$, $\mathrm{Cl}^{-}$, and $\mathrm{Na}^{+}$.
-We extend the training procedure to utilize conformal prediction in order to  estimate 90\% confidence intervals for the output of each trained model.
-Maps generated by applying each trained model to the collected imagery reveal the small-scale spatial variability within the pond.
-Additionally, the permutation importance computed for each feature of the trained models highlights the spectral features relevant to each water quality parameter.
-}}
+At the same time, collecting the high-quality reference data needed to calibrate remote sensing data products is both time consuming and expensive.
+In this study, we present the further development of a robotic team composed of an uncrewed surface vessel (USV) providing in situ reference measurements and an unmanned aerial vehicle (UAV) equipped with a hyperspectral imager.
+Together, this team is able to address the limitations of existing approaches by enabling the simultaneous collection of comprehensive in situ data together with high-resolution hyperspectral imagery.
+We showcase the capabilities of this team using data collected in a north Texas pond during three collections in the fall of 2020.
+Machine learning models for 13 variables are trained using the data set of paired in situ measurements and coincident reflectance spectra.
+These models can successfully estimate physical variables, including temperature, conductivity, pH, and turbidity, as well as the concentrations of blue-green algae, colored dissolved organic matter (CDOM), chlorophyll-a, crude oil, optical brighteners and the ions $\mathrm{Ca}^{2+}$, $\mathrm{Cl}^{-}$, and $\mathrm{Na}^{+}$.
+We extend the training procedure to utilize conformal prediction to estimate 90\% confidence intervals for the output of each trained model.
+The maps generated by applying each trained model to the collected images reveal the small-scale spatial variability within the pond.
+Additionally, the permutation importance computed for each feature of the trained models highlights the spectral features relevant to each water quality variable.
+}
 
@@
 
-For decades, remote sensing imagery have been used for environmental monitoring with applications ranging from resource mapping, land type classification, and urban growth assessment to wildfire tracking, natural disaster tracking, and many more \cite{cohen2004landsat, melesse2007remote, allison2016airborne, joyce2009review, robert2017analysis}.
-Among these applications, the retrieval of water quality parameters from remote sensing imagery remains challenging due to the difficulty of obtaining in-situ reference data coincident with available satellite imagery.
-Many studies have shown success modeling relevant water quality parameters such as colored dissolved organic matter (CDOM), cholorophyll-a, and total suspended sediment concentrations by using combinations of spectral bands from terrestrial remote sensing satellites.
-However, the in-situ reference data used in these studies typically require the time-consuming collection of individual samples for lab analysis or continuous monitoring at fixed sites \cite{brezonik2005landsat, paavel2011optical, gursoy2019investigating, bonansea2019using, sagan2020monitoring, remote-sensing-finland}.
+For decades, remote sensing imagery has been used for environmental monitoring with applications ranging from resource mapping, land type classification, and urban growth assessment to wildfire tracking, natural disaster tracking, and many more \cite{cohen2004landsat, melesse2007remote, allison2016airborne, joyce2009review, robert2017analysis}.
+Among these applications, the retrieval of water quality variables from remote sensing imagery remains challenging due to the difficulty of obtaining in situ reference data that coincide with available satellite imagery.
+Many studies have shown success modeling relevant water quality variables such as colored dissolved organic matter (CDOM), cholorophyll-a, and total suspended sediment concentrations by using combinations of spectral bands from terrestrial remote sensing satellites.
+However, the in situ reference data used in these studies typically require the time-consuming collection of individual samples for lab analysis or continuous monitoring at fixed sites \cite{brezonik2005landsat, paavel2011optical, gursoy2019investigating, bonansea2019using, sagan2020monitoring, remote-sensing-finland}.
 
-Much effort has recently gone into the curation of comprehensive datasets combining water quality records with decades of satellite imagery to enable the development of new methods for water quality monitoring.
+Much effort has recently been spent on the curation of comprehensive datasets that combine water quality records with decades of satellite imagery to enable the development of new methods for monitoring water quality.
 For example, Aurin et al.
@@
 Similarly, Ross et al.
-have combined over 600,000 records of dissolved organic carbon, chlorophyll-a, and other water quality parameters together with historical reflectance data from Landsat for the period of 1984-2019 \cite{ross2019aquasat}.
+have combined more than 600,000 records of dissolved organic carbon, chlorophyll-a and other variables of water quality together with Landsat historical reflectance data for the period 1984--2019 \cite{ross2019aquasat}.
 With a sufficient quantity of data, machine learning methods can augment traditional approaches using reflectance band ratios to enable estimation of water quality metrics and perform water quality classification \cite{schiller1999neural, brown2008neural, lary2010artificial, feng2015urban,belgiu2016random}.
-However, the low spatial and spectral resolution of available multi-band remote sensing satellites makes it difficult to analyze inland waters with small features and complicated spectral signatures.
-Additionally, the long revisit times of these satellites limits their use for real-time monitoring, for example, during oil spills \cite{fingas2017review}.
+However, the low spatial and spectral resolution of available multiband remote sensing satellites makes it difficult to analyze inland waters with small spatial features and complicated spectral signatures.
+Furthermore, the long return times of these satellites limit their use for real-time monitoring, for example, during oil spills \cite{fingas2017review}.
 
-Advances in multispectral and hyperspectral imaging technology have considerably reduced their size making it possible to incorporate these cameras into the payload of autonomous aerial vehicles (UAV) such as quadcopters, hexacopters, and other drones \cite{hruska2012radiometric}.
-By controlling the altitude during flight, UAVs can produce imagery with pixels at the centimeter scale and limit the need for complicated atmospheric corrections to account for scattering by atmospheric aerosols and gases \cite{adao2017hyperspectral,banerjee2020uav}.
-Already, UAVs equipped with multi- and hyperspectral imagers are being utilized in a variety of domains to great effect including biomass estimation, forest management, precision agriculture, and now, water quality monitoring \cite{adao2017hyperspectral, padua2017uas,arroyo2019implementation,kurihara2020unmanned,ehmann2019monitoring, lu2021retrieval}.
+Advances in multispectral and hyperspectral imaging technology have considerably reduced their size, making it possible to incorporate these cameras into the payload of autonomous aerial vehicles (UAVs) such as quadcopters, hexacopters, and other drones \cite{hruska2012radiometric}.
+By controlling altitude during flight, UAVs can produce imagery with pixels at the centimeter scale and limit the need for complicated atmospheric corrections to account for scattering by atmospheric aerosols and gases \cite{adao2017hyperspectral,banerjee2020uav}.
+Already, UAVs equipped with multispectral and hyperspectral imagers are being used in a variety of domains to great effect, including biomass estimation, forest management, precision agriculture, and now water quality monitoring \cite{adao2017hyperspectral, padua2017uas,arroyo2019implementation,kurihara2020unmanned,ehmann2019monitoring, lu2021retrieval}.
 
-Despite the increased spectral and spatial resolution afforded by UAV platforms, these improvements alone are unable to address the limited spatial resolution of in-situ reference data.
-To address this gap and enable real-time comprehensive water quality sensing, we have developed a robotic team composed of an autonomous uncrewed surface vessel (USV) equipped with a collection of reference grade instruments together with an UAV carrying a hyperspectral imager \cite{robotTeam1}.
-By incorporating these reference instruments on a maneuverable USV platform, we are able to rapidly collect large volumes of water quality data for a variety of physical, biochemical, and chemical parameters.
+Despite the increased spectral and spatial resolution afforded by UAV platforms, these improvements alone cannot address the limited spatial resolution of in situ reference data.
+To address this gap and enable comprehensive real-time water quality detection, we have developed a robotic team composed of an autonomous uncrewed surface vessel (USV) equipped with a collection of reference grade instruments together with a UAV carrying a hyperspectral imager \cite{robotTeam1}.
+By incorporating these reference instruments on a maneuverable USV platform, we are able to rapidly collect large volumes of water quality data for a variety of physical, biochemical, and chemical variables.
 Critically, the USV enables the collection of reference data with significantly improved spatial resolution compared to other approaches.
-These in-situ measurements then provide the ground-truth data used to train machine learning models which map reflectance spectra captured by the hyperspectral imager to the desired water quality parameters.
+These in situ measurements then provide the ground-truth data used to train machine learning models which map reflectance spectra captured by the hyperspectral imager to the desired water quality variables.
 
-In this study, we expand on our previous work by demonstrating the capabilities of this coordinated robot team using data collected at a pond in North Texas across three separate days in the Fall of 2020.
-Specifically, we showcase the ability to accurately predict physical parameters such as temperature, conductivity, pH, and turbidity, as well as biochemical constituents including blue-green algae pigments, CDOM, and chlorophyll-a, in addition to concentrations of crude oils, optical brighteners, and a variety of ions.
-Further, the considerable size of the collected dataset allows us to quantify the uncertainty in the resulting machine learning models by using techniques from conformal prediction.
-This methodology addresses the shortcomings of existing approaches by facilitating rapid, real-time data collection coupled with on board hyperspectral image processing and machine learning model deployment with uncertainty quantification.
-The resulting models are small enough to be deployed on board the UAV to enable real time streaming of data products to the ground.
+In this study, we expand on our previous work by demonstrating the capabilities of this coordinated robot team using data collected at a pond in North Texas over three separate days in the fall of 2020.
+Specifically, we show the ability to accurately predict physical variables such as temperature, conductivity, pH, and turbidity, as well as biochemical constituents, including blue-green algae pigments, CDOM, and chlorophyll-a, in addition to concentrations of crude oils, optical brighteners, and a variety of ions.
+In addition, the considerable size of the collected data set allows us to quantify the uncertainty in the resulting machine learning models by using conformal prediction techniques.
+This methodology addresses the shortcomings of existing approaches by facilitating rapid, real-time data collection coupled with on-board hyperspectral image processing and machine learning model deployment with uncertainty quantification.
+The resulting models are small enough to be deployed on board the UAV to enable real-time streaming of data products to the ground.
 This approach drastically reduces the time from data collection to insight.
@@
 
- The robotic team employed in this study consists of two key sensing sentinels: An uncrewed surface vessel (USV) used to collect in-situ reference measurements, and an unmanned aerial vehicle (UAV) for performing rapid, wide-area surveys to gather remote sensing data products.
-Both platforms are coordinated using the open-source QGroundControl software for flight control and mission planning and are equipped with high accuracy GPS and INS such that all collected data points are uniquely geo-located and time-stamped \cite{qgroundcontrol}.
+ The robotic team employed in this study consists of two key sensing sentinels: An uncrewed surface vessel (USV) used to collect in situ reference measurements, and an unmanned aerial vehicle (UAV) for performing rapid, wide-area surveys to gather remote sensing data products.
+Both platforms are coordinated using open source QGroundControl software for flight control and mission planning and are equipped with high-accuracy GPS and INS such that all data points collected are uniquely geolocated and time-stamped \cite{qgroundcontrol}.
 Both the USV and UAV include long-range Ubiquiti 5 GHz LiteBeam airMAX WiFi to enable streaming of data products to a ground station with network attached storage providing redundancy.
@@
 The USV employed in the robot team is a Maritime Robotics Otter which features a modular design and 20 hour battery life.
-The USV is equipped with an in-situ sensing payload consisting of a combination of Eureka Manta-40 multi-probes including fluorometers, ion selective electrodes, and other physical sensors which together enable the collection of comprehensive near-surface measurements including Colored Dissolved Organic Matter (CDOM), Crude Oil, Blue-Green Algae (phycoerythrin and phycocyanin), Chlorophyll-A, $\mathrm{Na^+}$, $\mathrm{Ca^{2+}}$, $\mathrm{Cl^-}$, Temperature, Conductivity, and many others.
+The USV is equipped with an in situ sensing payload consisting of a combination of Eureka Manta-40 multiprobes including fluorometers, ion selective electrodes, and other physical sensors that together enable the collection of comprehensive near-surface measurements including Colored Dissolved Organic Matter (CDOM), Crude Oil, Blue-Green Algae (phycoerythrin and phycocyanin), Chlorophyll A, $\mathrm{Na^+}$, $\mathrm{Ca^{2+}}$, $\mathrm{Cl^-}$, Temperature, Conductivity, and many others.
 The full list of measurements utilized in this study is given in Table~\ref{tab:sensors} and is categorized into four distinct types: physical measurements, ion measurements, biochemical measurements, and chemical measurements.
-Additionally, the USV is equipped with an ultra-sonic weather monitoring sensor for measuring air speed and direction as well as a a BioSonics MX Aquatic Habitat Echosounder sonar which are not explored in this study.
+Additionally, the USV is equipped with an ultrasonic weather monitoring sensor for measuring air speed and direction, as well as a BioSonics MX Aquatic Habitat Echosounder sonar, which are not explored in this study.
 
@@
 Blue-Green Algae (phycoerythrin)    & ppb                & 0.01  & Fluorometer                          & Biochemical \\
-Blue-Green Algae (phycocyanin)      & ppb                & 0.01  & Fluorometer                          & BioChemical \\
+Blue-Green Algae (phycocyanin)      & ppb                & 0.01  & Fluorometer                          & Biochemical \\
 CDOM                                & ppb                & 0.01  & Fluorometer                          & Biochemical \\
-Chlorophyll A                       & ppb                & 0.01  & Fluorometer                          & BioChemical \\
+Chlorophyll A                       & ppb                & 0.01  & Fluorometer                          & Biochemical \\
 Optical Brighteners                 & ppb                & 0.01  & Fluorometer                          & Chemical \\
@@
 
-As shown in Table~\ref{tab:sensors}, the physical parameter and ion sensors are largely based on different configurations of electrodes while the chemical and biochemical parameters are all optically active substances enabling their determination by fluorometry.
-The pigments phycoerythrin and phycocyanin are used to determine blue-green algae content which together with chlorophyll-a enables us to asses the distribution of photosynthetic life in the pond.
-Additionally, we also measure the concentration of colored dissolved organic matter (CDOM) which impacts light penetration and serves as a primary source of bioavailable carbon.
+As shown in Table~\ref{tab:sensors}, the physical measurements and ion sensors are largely based on different electrode configurations, while the chemical and biochemical measurements are all optically significant in UV and visible light, enabling their determination by fluorometry.
+The pigments phycoerythrin and phycocyanin are used to determine the blue-green algae content, which together with chlorophyll-a enable us to assess the distribution of photosynthetic life in the pond.
+In addition, we also measured the concentration of colored dissolved organic matter (CDOM), which impacts light penetration and serves as a primary source of bioavailable carbon.
 Crude oil (natural petroleum) and optical brightener concentrations are also measured with fluorometers and are relevant for identifying sources of industrial contamination or natural seepage.
@@
 
-A Freefly Alta-X autonomous quadcopter was used as the UAV platform for the robotic team.
-The Alta-X is specifically designed to carry cameras featuring a payload of up to 35 lbs.
+A Freefly Alta-X autonomous quadcopter was used as a UAV platform for the robotic team.
+The Alta-X is specifically designed to carry cameras that have a payload of up to 35 lbs.
 We have equipped the UAV with a Resonon Pika XC2 Visible+Near-Infrared (VNIR) hyperspectral imager.
@@
 Additionally, the UAV includes an upward facing Ocean Optics UV-Vis-NIR spectrometer with a cosine corrector to capture the incident downwelling irradiance spectrum.
-Data collection by the hyperspectral imager is controlled by an attached Intel NUC small-form-factor computer.
-A second \textit{processing} NUC is also included for onboard georectification and generation of data products.
-The collected hyperspectral images (HSI) are stored locally on a solid state drive which is simultaneously mounted by the processing computer.
+Data collection by the hyperspectral imager is controlled by an attached Intel NUC small-form factor computer.
+A second processing NUC is also included for onboard georectification and generation of data products.
+The collected hyperspectral images (HSIs) are stored locally on a solid state drive which is simultaneously mounted by the processing computer.
 The configuration of the drone is shown in Figure~\ref{fig:drone-components}.
@@
 
-To effectively utilize the spectra collected by our UAV, we must account for the variability of the incident light illuminating the water and transform the raw hyperspectral data cubes from their native \textit{imaging reference frame} to a chosen coordinate system compatible with the data collected by the USV.
+To effectively utilize the spectra collected by our UAV, we must account for the variability of the incident light that illuminates the water and transform the raw hyperspectral data cubes from their native \textit{imaging reference frame} to a chosen coordinate system compatible with the data collected by the USV.
 This procedure is illustrated in Figure~\ref{fig:hsi-pipeline}.
@@
 
-The hyperspectral imager utilized in our robot team is in a so-called \textit{pushbroom} configuration, that is, each image captured by the drone is formed one scan-line at a time as the UAV flies.
-Each scan-line consists of 1600 pixels for which incoming light is diffracted into 462 wavelength bins.
+The hyperspectral imager utilized in our robot team is in a so-called \textit{pushbroom} configuration, that is, each image captured by the drone is formed one scan line at a time as the UAV flies.
+Each scan line consists of 1600 pixels for which incoming light is diffracted into 462 wavelength bins.
 In the collection software, a regular cutoff of 1000 lines is chosen so that each resulting \textit{image} forms a array of size 462$\times$1600$\times$1000 called a \textit{hyperspectral data cube}.
-Initially, the captured spectra are in units of spectral radiance (measured in microflicks) however this does not account for the variability of incident light illuminating the water.
-To this end, we convert the hyperspectral data cubes into units of reflectance by utilizing the skyward-facing downwelling irradiance spectrometer (see Figure~\ref{fig:drone-components}).
-When the camera is normal to the water's surface, the reflectance is given by
+Initially, the captured spectra are in units of spectral radiance (measured in microflicks); however, this does not account for the variability of incident light illuminating the water.
+To this end, we convert the hyperspectral data cubes into units of reflectance utilizing the skyward-facing downwelling irradiance spectrometer (see Figure~\ref{fig:drone-components}).
+When the camera is normal to the water surface, the reflectance is given by
 \begin{equation}
@@
 where $L$ is the spectral radiance, $E_d$ is the downwelling irradiance, and a factor of $\pi$ steradians results from assuming the water surface is Lambertian (diffuse) \cite{reflectance-conversion}.
-We will address the impact of this assumption in Section~\ref{sec:discussion}.
 
@@
 During our three surveys, the UAV was flown at an altitude of ~50 m above the water.
-At this scale, the surface is essentially flat so that the hyperspectral data cube can be reliably georectified without the need for an on-board digital elevation map (DEM).
-We adopt the approach outlined in \cite{GeorectificationMuller, GeorectificationBaumker, GeorectificationMostafa} whereby each scan-line is georeferenced using the known field of view (30.8 $\deg$) together with the position and orientation of the UAV as provided by the on-board GPS INS.
-After a sequence of coordinate transformations, pixel coordinates are obtained in the relevant UTM zone (in meters).
+At this scale, the surface is essentially flat, so that the hyperspectral data cube can be reliably georectified without the need for an on-board digital elevation map (DEM).
+We adopt the approach outlined in \cite{GeorectificationMuller, GeorectificationBaumker, GeorectificationMostafa} whereby each scan line is georeferenced using the known field of view (30.8 $\deg$) together with the position and orientation of the UAV as provided by the on-board GPS/INS.
+After a sequence of coordinate transformations, the pixel coordinates are obtained in the relevant UTM zone (in meters).
 The resulting image is then re-sampled to a final output resolution.
-For these collections a resolution of 10 cm was utilized, however this can be adjusted to optimize the processing time and final resolution for real-time applications.
-Finally, the obtained pixel UTM coordinates are transformed to latitude and longitude for easy comparison with in-situ data collected by the USV.
+For these collections, a resolution of 10 cm was utilized, however, this can be adjusted to optimize the processing time and final resolution for real-time applications.
+Finally, the UTM pixel coordinates obtained are transformed to latitude and longitude for easy comparison with in situ data collected by the USV.
 The final result is a georectified hyperspectral reflectance data cube.
-In Figure~\ref{fig:hsi-infographic} we visualize one such data cube, highlighting a selection of exemplar pixel spectra as well as the incident downwelling irradiance spectrum.
+In Figure~\ref{fig:hsi-infographic} we visualize one of such data cubes, highlighting a selection of exemplar pixel spectra as well as the incident downward irradiance spectrum.
 A pseudo-color image is generated (plotted on the top of the data cube) to illustrate the scene.
@@
 By running this pipeline on the on board computer, we are able to process the collected hyperspectral data cubes in near real time.
-This feature is critical for time-sensitive applications where we need to quickly asses if an area is safe and can not afford to wait to download and post-process collected imagery \textit{after} a flight.
+This feature is critical for time-sensitive applications where we need to quickly assess if an area is safe and can not afford to wait to download and post-process collected imagery after a flight.
 
@@
 
-Data were collected using the robot team at a site in North Texas across three observation periods in the fall of 2020.
-For each collection period, the UAV first completed a wide survey of the pond capturing multiple hyperspectral data cubes.
-Subsequently, the the USV sampled across the pond, collecting in-situ reference measurements.
-Each of these reference measurements was then collocated with individual pixel spectra where the USV track overlapped with UAV pixels.
-To account for any time lag in the values measured by the in-situ instruments and to account for the USV size in comparison to the data cube's spatial resolution, each in-situ measurement is associated with a 3$\times$3 grid of HSI pixels, that is, a 30 cm $\times$ 30 cm square.
-These combined data form the tabular data set on which we train regression models; pixel spectra form input features and each separate USV sensor forms a distinct target variable.
+Data were collected using the robot team at a site in North Texas during three observation periods in the fall of 2020.
+For each collection period, the UAV first completed a broad survey of the pond, capturing multiple hyperspectral data cubes.
+Subsequently, the USV sampled across the pond, collecting in situ reference measurements.
+Each of these reference measurements was then collocated with individual pixel spectra, where the USV track overlapped with UAV pixels.
+To account for any time lag in the values measured by the in situ instruments and to account for the USV size in comparison to the data cube's spatial resolution, each in-situ measurement is associated with a 3$\times$3 grid of HSI pixels, that is, a 30 cm $\times$ 30 cm square.
+These combined data form the tabular data set on which we train regression models; pixel spectra form input features, and each separate USV sensor forms a distinct target variable.
 
-Each collection was performed near solar noon to maximize the amount of incident sunlight illuminating the water, however, to account for any potential variation in lighting conditions between data cubes, we augment the training set with additional features including the drone viewing geometry (roll, pitch, heading) and solar illumination geometry (solar azimuth, solar elevation, solar zenith) as well as the total at-pixel intensity before reflectance conversion, the total downwelling intensity, and the drone altitude.
-Further feature engineering is performed to add additional spectral indices which utilize combinations of specific wavelength bands like the normalized difference vegetation index (NDVI), normalized difference water index (NDWI), simple ratio (SR), photochemical reflectance index (PRI), and more as outlined in \cite{envi_vegetation_indices, thenkabail2018hyperspectral,kaufman1992atmospherically, SpectralIndexWheat}.
-A comprehensive list of these added features is provided in supplementary table S1.
+Each collection was performed near solar noon to maximize the amount of incident sunlight illuminating the water; however, to account for any potential variation in lighting conditions between data cubes, we augment the training set with additional features including the drone viewing geometry (roll, pitch, heading) and solar illumination geometry (solar azimuth, solar elevation, solar zenith) as well as the total at-pixel intensity before reflectance conversion, the total downwelling intensity, and the drone altitude.
+Further feature engineering is performed to add additional spectral indices that utilize combinations of specific wavelength bands such as the normalized difference vegetation index (NDVI), normalized difference water index (NDWI), simple ratio (SR), photochemical reflectance index (PRI) and more, as outlined in \cite{envi_vegetation_indices, thenkabail2018hyperspectral,kaufman1992atmospherically, SpectralIndexWheat}.
+A comprehensive list of these added features is provided in Supplementary Table S1.
 The final dataset includes a total of 526 features (462 reflectance bands plus 64 additional features) with over 120,000 records.
@@
 
-For each of the 13 target variables listed in Table~\ref{tab:sensors}, data were randomly partitioned into a 90:10 training/testing split.
+For each of the 13 target variables listed in Table~\ref{tab:sensors}, the data was randomly partitioned into a 90:10 training/testing split.
 Using the MLJ machine learning framework, a variety of machine learning models compatible with the regression task were identified \cite{MLJ1}.
-This selection of models included linear regression (and it's variations), Gaussian Process Regression, shallow Neural Networks, and decision tree based models.
+This selection of models included linear regression (and it's variations), Gaussian process regression, shallow neural networks, and decision tree-based models.
 Out of this set, the Random Forest Regressor (RFR) model from \cite{decision-trees} was selected for its relatively quick training and inference times.
-Random forests are an ensembling technique based on the bagged predictions of individual decision tree regressors trained using the CART algorithm with each individual tree trained on a random subset of features \textit{and} a random subset of training records \cite{decision-trees, random-forest}.
+Random forests are an ensembling technique based on bagged predictions of individual decision tree regressors trained using the CART algorithm with each individual tree trained on a random subset of features \textit{and} a random subset of training records \cite{decision-trees, random-forest}.
 
-As reflectance values in adjacent wavelength bins tend to correlate with each other, and therefore, may not necessarily contribute additional information content to the final model, it is desirable to evaluate the relative importance of each feature to the final predictions of our trained models.
-This is useful both for identifying the most relevant parameters as well as for performing feature selection to reduce the final model size and optimize inference time.
-By default, tree-based methods like the RFR allow for an impurity based ranking as described in \cite{random-forest, rfr-importance-ranking}.
+As reflectance values in adjacent wavelength bins tend to correlate with each other and, therefore, may not necessarily contribute additional information content to the final model, it is desirable to evaluate the relative importance of each feature to the final predictions of our trained models.
+This is useful both for identifying the most relevant features and for performing feature selection to reduce the final model size and optimize the inference time.
+By default, tree-based methods, such as the RFR allow for an impurity-based ranking as described in \cite{random-forest, rfr-importance-ranking}.
 However, these methods have been shown to be biased towards high cardinality and correlated features \cite{strobl2008conditional}.
-We therefore choose to use the model-agnostic permutation importance as described by \cite{parr2018beware}.
-To do this, we further partition the training dataset resulting in an 80:10:10 split with 80\% of points used for model training, 10\% of points used for validation and feature importance determination, and the final 10\% held out as an independent testing dataset.
-The importance for the $j^{\text{th}}$ feature is then computed as
+Therefore, we choose to use the model-agnostic permutation importance as described by \cite{parr2018beware}.
+To do this, we further partition the training data set, resulting in an 80:10:10 split with 80\% of points used for model training, 10\% of points used for validation and determination of feature importance, and the final 10\% held out as an independent test data set.
+The importance of the $j^{\text{th}}$ feature is then computed as
 \begin{equation}
@@
 where $f(X_i)=\hat{y}_i$ denotes the trained ML model applied to the $i^{th}$ calibration record.
-These n-many scores are sorted, and the interval half width $d$ is computed as the $\frac{\lceil(1-\alpha)(n+1) \rceil}{n}$ quantile of this set in order to achieve a coverage of $1-\alpha$ on the calibration set.
-Predictions intervals for new data are then formed as $f(X)\pm d$.
+These n-many scores are sorted, and the half width of the interval $d$ is calculated as the $\frac{\lceil(1-\alpha)(n+1) \rceil}{n}$ quantile of this set in order to achieve a coverage of $1-\alpha$ on the calibration set.
+Prediction intervals for new data are then formed as $f(X)\pm d$.
 For this study, we have chosen $\alpha=0.1$ for a coverage corresponding to a 90\% confidence interval.
 
-Using these tools, the training procedure for each model is as follows: First, the model is trained using 6-fold cross validation on the training set with default hyperparameter values.
-Feature importances for the trained model are then computed and the top 25 features are identified.
-A second, model is then trained using the same 6-fold cross validation scheme with \textit{only} these 25 most important features together with hyperparameter optimization using a random parameter search over the number of tees and sampling fraction.
+Using these tools, the training procedure for each model is as follows: First, the model is trained using six-fold cross-validation on the training set with default hyperparameter values.
+Feature importances for the trained model are then computed, and the top 25 features are identified.
+A second model is then trained using the same 6-fold cross-validation scheme with \textit{ only} these 25 most important features together with hyperparameter optimization using a random parameter search over the number of trees and sampling fraction.
 Model performance is evaluated by computing out-of-fold values for the coefficient of determination, as well as the
@@
 Having identified the model with the best out-of-fold performance, we proceed to train the final hyperparameter optimized model on the full training set with associated uncertainty estimated using conformal prediction.
-Each final model is then evaluated on the previously untouched testing set.
+Then each final model is evaluated on the previously untouched testing set.
 We visualize model performance across the distribution of testing data with a scatter diagram and quantile-quantile plot for which successful model predictions should lie close to a 1:1 line.
 
-These trained models can then easily be deployed on the on board processing computer so that during subsequent surveys, target concentrations can be inferred as imagery are collected and processed.
-The application of each model to the collected hyperspectral data cubes results in a map of the distribution of each water quality parameter across the pond.
+These trained models can then easily be deployed on the on-board processing computer so that during subsequent surveys, target concentrations can be inferred as imagery are collected and processed.
+The application of each model to the collected hyperspectral data cubes results in a map of the distribution of each water quality variable across the pond.
 
@@
 
-The final dataset combining observations from each of the three separate collections contains more than 120,000 individual records.
-The collection on 11-23 covered the largest spatial extent across the pond, however due to flight time constraints resulting from the payload size, imagery from adjacent flight tracks did not overlap resulting in slight gaps.
-The collections on 12-09 and 12-10 were adjusted to reduce this gap, resulting in a more uniform coverage across a smaller spatial extent.
+The final data set that combined observations from each of the three separate collections contains more than 120,000 individual records.
+The collection on 11-23-2020 covered the largest spatial extent across the pond, however, due to flight time constraints resulting from the payload size, imagery from adjacent flight tracks did not overlap, resulting in slight gaps.
+The collections on 12-09-2020 and 12-10-2020 were adjusted to reduce this gap, resulting in a more uniform coverage over a smaller spatial extent.
 
@@
 The results of the model training procedure are presented in Table~\ref{tab:fit-results}.
-Model performance is identified by the $R^2$, RMSE, and MAE out-of-fold estimates (mean $\pm$ standard deviation) of the final hyperparameter-optimized model on the training set with target variables ranked in descending order by the $R^2$ value and separated by sensor type (physical parameters, ions, biochemical parameters, and chemical parameters).
+The performance of the model is identified by the $R^2$, RMSE, and MAE out-of-fold estimates (mean $\pm$ standard deviation) of the final hyperparameter optimized model in the training set with the target variables ranked in descending order by the $R^2$ value and separated by sensor type (physical variables, ions, biochemical variables, and chemical variables).
 The small variation in values across folds confirms that the reported performance is independent of how the training set was sampled.
-Additionally, we report the interval width which yields a 90\% confidence interval on the holdout validation set as determined by the conformal prediction procedure.
-We then evaluate how the estimated uncertainty generalizes by computing the \textit{emprical coverage} on the holdout testing set, that is, we compute the percentage of predictions on the testing set that \textit{actually} fall within the estimated 90\% confidence interval.
+Furthermore, we report the interval width that yields a 90\% confidence interval on the holdout validation set determined by the conformal prediction procedure.
+We then evaluate how the estimated uncertainty generalizes by computing the \textit{emprical coverage} on the holdout testing set, that is, we compute the percentage of predictions in the test set that \textit{actually} fall within the estimated 90\% confidence interval.
 
@@
 
-From Table~\ref{tab:fit-results},  we see that the empirical coverage achieved by the inferred confidence interval evaluated on the independent test set is within 1\% of our desired coverage for each target modelled.
-This indicates that the uncertainties obtained by the conformal prediction procedure are reliable, at least within the bounds of the collected dataset.
-We also note that in all cases, the inferred model uncertainties are larger than resolution of the in-situ sensors.
-This lends further credence to the inferred uncertainty estimates as we should not expect to be able have lower uncertainty than the smallest resolvable difference in reference sensor measurements.
+From Table~\ref{tab:fit-results},  we see that the empirical coverage achieved by the inferred confidence interval evaluated in the independent test set is within 1\% of our desired coverage for each target modeled.
+This indicates that the uncertainties obtained by the conformal prediction procedure are reliable, at least within the bounds of the collected data set.
+We also note that in all cases, the inferred model uncertainties are larger than the resolution of the in-situ sensors.
+This lends further credence to the inferred uncertainty estimates as we should not expect to be able to have lower uncertainty than the smallest resolvable difference in reference sensor measurements.
 
 To further examine the differences in model performance between the target variables, we can consider the difference between the RMSE and MAE scores.
-The MAE is less sensitive to impacts from outliers than the RMSE, and as a consequence, any large difference between the two is indicative of impacts due to the distribution of target values.
+The MAE is less sensitive to outlier impacts than the RMSE, and, as a consequence, any large difference between the two is indicative of impacts due to the distribution of target values.
 Indeed, this is the case for turbidity, for which almost all measurements were below 10 FNU with only a small fraction of observations from a small area near the shore.
-The rest of the models all show a mean per-fold RMSE value with size comparable to the mean per-fold MAE.
+The rest of the models all show a mean perfold RMSE value with size comparable to the mean per-fold MAE.
 
@@
 
-\subsection{Physical Parameters}
+\subsection{Physical Variables}
 
-The physical parameters included temperature, conductivity, pH, and turbidity.
-In the combined dataset, the distributions for temperature and conductivity had two distinct, non-overlapping regions corresponding to the measurements from 11-23 and the measurements from 12-09 and 12-10, respectively.
-The pH value of the pond was slightly alkaline showing a multi-modal spatial distribution with values ranging from 8.0 to 8.6.
-As mentioned above, the pond water was very clear for each observation period with most turbidity values ranging between 1 and 3 FNU and very few above 10.
+Physical variables included temperature, conductivity, pH, and turbidity.
+In the combined dataset, the distributions for temperature and conductivity had two distinct, nonoverlapping regions corresponding to the measurements from 11-23 and the measurements from 12-09 and 12-10, respectively.
+The pH value of the pond was slightly alkaline, showing a multimodal spatial distribution with values ranging from 8.0 to 8.6.
+As mentioned above, the pond water was very clear for each observation period, with most turbidity values ranging between 1 and 3 FNU and very few above 10.
 
 The results of the hyperparameter optimized RFR fits are shown in Figure~\ref{fig:physical-fit}.
-Temperature and conductivity show the best performance on the independent training set with $R^2$ values of 1.0 (to 3 decimal places).
-Similarly, the pH model achieves an excellent fit with most predictions falling close to the 1:1 line.
-The quantile-quantile plots for these three models further confirm that the distributions of true and predicted values match.
-The turbidity model also achieves a strong fit with an $R^2$ value of 0.905.
+Temperature and conductivity show the best performance in the independent training set with $R^2$ values of 1.0 (to 3 decimal places).
+Similarly, the pH model achieves an excellent fit, with most predictions falling close to the 1:1 line.
+Quantile-quantile plots for these three models further confirm that the distributions of true and predicted values match.
+The turbidity model also achieves a strong fit with a $R^2$ value of 0.905.
 The scatter diagram and quantile-quantile plot for this target show that the model performance degrades with larger values where deviation in the predicted distribution is apparent past 25 FNU.
@@
 \includegraphics[width=\columnwidth]{paper/figures/results/fits/physical-fitres.png}
-\caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the physical parameters measured by the USV.\label{fig:physical-fit}}
+\caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the physical variables measured by the USV.\label{fig:physical-fit}}
 \end{figure}
 
-The permutation importance of the top 25 features for each of the physical parameter models is shown in Figure~\ref{fig:physical-fi}.
+The permutation importance of the top 25 features for each of the models of the physical variables is shown in Figure~\ref{fig:physical-fi}.
 All four models show a strong dependence on the solar illumination geometry (solar azimuth, elevation, solar zenith) as well as the viewing geometry (pitch, altitude, heading, etc.).
 All four models also include the total downwelling intensity and the total pixel intensity as highly important features.
-The temperature, conductivity, and pH models all include red to infrared reflectance bins and a combination of spectral indices within their most important features.
-Finally, the turbidity model depends mostly on blue wavelengths from 462 to 496 nm and did not include any spectral indices amongst the 25 most important features.
+The temperature, conductivity, and pH models all include red-to-infrared reflectance bins and a combination of spectral indices within their most important features.
+Finally, the turbidity model relies mainly on blue wavelengths from 462 to 496 nm and did not include any spectral indices amongst the 25 most important features.
 
@@
 \includegraphics[width=\columnwidth]{paper/figures/results/fits/physical-ranking.pdf}
-\caption{Ranked permutation importance for each feature in the physical parameter models.
+\caption{Ranked permutation importance for each feature in the physical variable models.
 Permutation importance measured the decrease in model $R^2$ value after replacing each feature in the prediction set with a random permutation of its values.\label{fig:physical-fi}}
@@
 
-By applying the trained models to the full hypserspectral data cubes, we can produce maps of the distribution of the target parameters as in Figure~\ref{fig:map-physical}.
-Here we have chosen to show the map produced from the imagery collected during the 11-23 collection period as they showcase the largest spatial extent.
-The temperature map shows lower values near the shore which is to be expected as the air temperature was below the water temperature.
-The temperature, conductivity, and pH maps all show a distinction between the main body of water and the alcove to the east which receives little flow from the main body.
+By applying the trained models to the full hyperspectral data cubes, we can produce maps of the distribution of the target variables as in Figure~\ref{fig:map-physical}.
+Here we have chosen to show the map produced from the imagery collected during the 11-23 collection period, as they showcase the largest spatial extent.
+The temperature map shows lower values near the shore, which is to be expected as the air temperature was below the water temperature.
+The temperature, conductivity, and pH maps all show a distinction between the main body of water and the alcove to the east, which receives little flow from the main body.
 The turbidity map confirms that the water is largely clear, with elevated levels near the shore.
@@
 \includegraphics[width=\columnwidth]{paper/figures/results/maps/physical.pdf}
-\caption{Maps generated by applying each of the physical parameter models to the hyperspectral data cubes collected on 11-23.
+\caption{Maps generated by applying each of the physical variable models to the hyperspectral data cubes collected on 11-23.
 Overlaid over the predictions are color-filled squares showing the associated in-situ reference data for the same collection period.
@@
 The measured ions include $\mathrm{Ca}^{2+}$, $\mathrm{Cl}^{-}$, and $\mathrm{Na}^{+}$.
-All three measurements showed multi-modal spatial distributions throughout the pond on each of the three collections.
-The scatter diagrams and quantile-quantile plots for the resulting fits are shown in Figure~\ref{fig:ions-fit}.
-All three models achieved excellent fits with $R^2$ values of 1.0, 0.996, and 0.993 on the independent testing set respectively.
-Further, there is no clear decrease in model performance for low or high concentrations, rather, for $\textrm{Cl}^{-}$ and $\textrm{Na}^{+}$, the model have the most difficulty in the middle of the target distributions.
+All three measurements showed multimodal spatial distributions throughout the pond on each of the three collections.
+The scatter diagrams and quantile-quantile graphs for the resulting fits are shown in Figure~\ref{fig:ions-fit}.
+All three models achieved excellent fits with $R^2$ values of 1.0, 0.996, and 0.993 on the independent testing set, respectively.
+Furthermore, there is no clear decrease in model performance for low or high concentrations; rather, for $\textrm{Cl}^{-}$ and $\textrm{Na}^{+}$, the models have the most difficulty in the middle of the target distributions.
 
@@
 
-The permutation importance ranking for the top 25 features for each of the ion models is shown in Figure~\ref{fig:ions-fi}.
-Here we see that all three models depend on the solar illumination and viewing geometries as well as the total downwelling intensity and the total pixel intensity measured at the hyperspectral imager.
-All three models utilize a combination of spectral indices which combine green, red, and infrared reflectance bins.
-The $\textrm{Ca}^{+}$ and $\textrm{Cl}^{-}$ models depend on specific red wavelengths from 740 to 769 nm.
-$\textrm{Cl}^{-}$ and $\textrm{Na}^{+}$ also depend on green and yellow reflectance bins from 541 to 589 nanometers.
+The permutation importance ranking for the top 25 features of each of the ion models is shown in Figure~\ref{fig:ions-fi}.
+Here, we see that all three models depend on the solar illumination and viewing geometries as well as the total downwelling intensity and the total pixel intensity measured at the hyperspectral imager.
+All three models utilize a combination of spectral indices that combine green, red, and infrared reflectance bins.
+The $\textrm{Ca}^{+}$ and $\textrm{Cl}^{-}$ models depend on specific red wavelengths of 740 to 769 nm.
+$\textrm{Cl}^{-}$ and $\textrm{Na}^{+}$ also depend on green and yellow reflectance bins of 541 to 589 nanometers.
 
@@
 The maps produced by applying the fitted models to the hyperspectral data cubes for 11-23 are shown in Figure~\ref{fig:map-ions}.
-Both positive ions $\mathrm{Ca}^{2+}$ and $\mathrm{Na}^{+}$ show high concentrations in the north-west portion of the pond with lower values in the alcove on the eastern side.
-The positive ion concentrations also appear to decrease near the shore.
+Both positive ions $\mathrm{Ca}^{2+}$ and $\mathrm{Na}^{+}$ show high concentrations in the northwest portion of the pond with lower values in the alcove on the eastern side.
+Positive ion concentrations also appear to decrease near the shore.
 The negative ion $\mathrm{Cl}^{-}$ shows the opposite distribution with larger values in the alcove to the east and lowest values on the western side of the pond.
@@
 
-\subsection{Biochemical Parameters}
+\subsection{Biochemical Variables}
 
-The measured biochemical parameters include the pigments phycoerythrin, phycocyanin, and chlorophyll-a, as well as CDOM.
-Phycoerythrin and phycocyanin are both present in blue-green alagae and chlorophyll-a is a found in all photosynthetic organisms except bacteria.
-In the combined dataset, the three pigments showed multi-modal distributions separated by collection day with little spatial variation within the individual collection.
+The measured biochemical variables include the pigments phycoerythrin, phycocyanin, and chlorophyll-a, as well as CDOM.
+Phycoerythrin and phycocyanin are both present in blue-green algae, and chlorophyll-a is found in all photosynthetic organisms except bacteria.
+In the combined dataset, the three pigments showed multimodal distributions separated by collection day with little spatial variation within the individual collection.
 CDOM showed a variable spatial distribution throughout the pond between the main water body and the eastern alcove on 11-23.
 
-The results of the RFR fits for the biochemical parameters are shown in Figure~\ref{fig:biochem-fit}.
-Phycoerythrin showed the best model performance with an $R^2$ value of 0.995 on the training set.
-Both CDOM and chlorophyll-a acheived good performance with $R^2$ values of 0.967 and 0.917 on the training set.
-The quantile-quantile plots indicate that the model for CDOM degrades for values below 16 ppb where data are sparse.
+The results of the RFR fits for the biochemical variables are shown in Figure~\ref{fig:biochem-fit}.
+Phycoerythrin showed the best model performance with an $R^2$ value of 0.995 in the training set.
+Both CDOM and chlorophyll-a achieved good performance with $R^2$ values of 0.967 and 0.917 in the training set.
+Quantile-quantile plots indicate that the CDOM model degrades for values below 16 ppb, where data is sparse.
 The chlrophyll-a model shows the opposite trend with poorer performance for concentrations above 5 ppb for which there are very few records.
-The phycocyanin model had the lowest performance of the biochemical sensors with an $R^2$ value of 0.727 with model predictions rapidly decreasing in quality for concentrations above 3 ppb.
+The phycocyanin model had the lowest performance of biochemical sensors with a $R^2$ value of 0.727 and the model predictions rapidly decreased in quality for concentrations greater than 3 ppb.
 
@@
 
-The permutation importance ranking of the top 25 features of each biochemical model are shown in Figure~\ref{fig:biochem-fi}.
+The permutation importance ranking of the top 25 features of each biochemical model is shown in Figure~\ref{fig:biochem-fi}.
 Again, all four models include the solar illumination and viewing geometries amongst their most important features as well as the total downwelling intensity and total pixel intensity at the imager.
-Additionally, all four models include some vegetation indices amgonst the top features which utilize combinations of blue, green, yellow, red, and infrared reflectance bands.
+Additionally, all four models include some vegetation indices amongst the top features, which utilize combinations of blue, green, yellow, red, and infrared reflectance bands.
 The phycoerythrin model shows a preference for green reflectance bins from 544 to 556 nm while the phycocyanin model prefers blue and red reflectance bins.
-The CDOM model utilizes mostly red reflectance values while the chlorophyll-a model includes red, green, and blue reflectance bins.
+The CDOM model uses mainly red reflectance values, whereas the chlorophyll-a model includes red, green, and blue reflectance bins.
 
@@
 
-The maps generated for the 11-23 collection by applying the trained biochemical parameter models are shown in Figure~\ref{fig:map-biochem}.
-The three pigments all show low concentrations in the body of water with elevated levels near the shore.
-The CDOM distribution shows spatial variability with increased values in the eastern alcove similar to the separation seen in the maps for temperature, conductivity, $\textrm{Ca}^{2+}$, $\textrm{Cl}^{-}$, and $\textrm{Na}^{+}$.
+The maps generated for the 11-23 collection by applying trained biochemical models are shown in Figure~\ref{fig:map-biochem}.
+The three pigments show low concentrations in the body of water with elevated levels near the shore.
+The CDOM distribution shows spatial variability with higher values in the eastern alcove similar to the separation seen in the maps for temperature, conductivity, $\textrm{Ca}^{2+}$, $\textrm{Cl}^{-}$, and $\textrm{Na}^{+}$.
 
@@
 \includegraphics[width=\columnwidth]{paper/figures/results/maps/biochemical.pdf}
-\caption{Maps generated by applying the trained biochemical parameter models to the data cubes collected on 11-23.
+\caption{Maps generated by applying the trained biochemical models to the data cubes collected on 11-23.
 Overlaid are the in-situ reference data for the same collection period.
@@
 
-\subsection{Chemical Parameters}
+\subsection{Chemical Variables}
 
-The final two models to consider are for the measured chemical parameters: crude oil (CO) and optical brighteners (OB).
-The crude oil measurement includes natural, unprocessed petroleum while optical brighteners consist of whitening agents often added to products like soaps, detergents, and cleaning agents.
+The final two models to consider are for the measured chemical concentrations of crude oil (CO) and optical brighteners (OB).
+The crude oil measurement includes natural unprocessed petroleum, whereas optical brighteners consist of whitening agents that are often added to products such as soaps, detergents, and cleaning agents.
 Both the crude oil and optical brightener measurements show multi-modal spatial distributions across each collection period.
-The scatter diagrams and quantile-quantile plots for the fitted models are shown in Figure~\ref{fig:chemicals-fit}.
-Both models achieve good performance with $R^2$ values of 0.957 and 0.941 for CO and OB on the holdout testing set.
-The perfomance of the CO model degrades for concentrations below 24 ppb for which there are few records.
-Similarly the OB model shows worse performance for concentrations below roughly 3.5 ppb.
+Scatter diagrams and quantile-quantile plots for the fitted models are shown in Figure~\ref{fig:chemicals-fit}.
+Both models achieve good performance with $R^2$ values of 0.957 and 0.941 for CO and OB on the holdout test set.
+The performance of the CO model degrades for concentrations below 24 ppb for which there are few records.
+Similarly, the OB model shows worse performance for concentrations below roughly 3.5 ppb.
 
@@
 \includegraphics[width=\columnwidth]{paper/figures/results/fits/chemical-fitres.png}
-\caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the the chemical parameters measured by the USV.\label{fig:chemicals-fit}}
+\caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the chemical variables measured by the USV.\label{fig:chemicals-fit}}
 \end{figure}
@@
 Both models rank the solar illumination and viewing geometries together with the total downwelling intensity and total pixel intensities amongst the top features.
-Both models include a combination of spectral indices utilizing blue, green, yellow, red, and infrared reflectance bins.
+Both models include a combination of spectral indices using blue, green, yellow, red, and infrared reflectance bins.
 Additionally, the CO model includes green-yellow reflectances from 539 to 589 nm as well as red reflectances from 749 to 769 nm.
-The OB model includes a yellow reflectance at 584.6 nm as well as red reflectance bins.
+The OB model includes a yellow reflectance at 584.6 nm and red reflectance bins.
 
@@
 The maps generated by applying the CO and OB models to the 11-23 data cubes are shown in Figure ~\ref{fig:map-chem}.
-Both models show a distinct spatial distribution with elevated values in the eastern alcove of the pond similar to the distribution of CDOM in Figure~\ref{fig:map-biochem}
+Both models show a distinct spatial distribution with elevated values in the eastern alcove of the pond similar to the CDOM distribution in Figure~\ref{fig:map-biochem}
 
@@
 \includegraphics[width=\columnwidth]{paper/figures/results/maps/chemical.pdf}
-\caption{Maps generated by applying the trained chemical parameter models to the hyperspectral data cubes collected on 11-23.
+\caption{Maps generated by applying the trained chemical variable models to the hyperspectral data cubes collected on 11-23.
 Overlaid are color-filled squares showing the in-situ reference data for the same collection period.
@@
 
-In this paper, we have validated the methodology introduced in our previous work\cite{robotTeam1}. Specifically, we demonstrate that by using an autonomous team of sensing sentinels we can
+In this paper, we have validated the methodology introduced in our previous work\cite{robotTeam1}. Specifically, we demonstrate that by using an autonomous team of sensing sentinels, we can
 \begin{enumerate}
-    \item Rapidly acquire large volumes in in-situ reference data points for a variety of relevant water quality parameters including physical measurements such as temperature, pH, and conductivity as well as ion concentrations, chemicals such as crude oil, and relevant biochemical parameters such as blue-green algae pigments, chlorophyll-a, and CDOM.
+    \item Rapidly acquire large volumes in in-situ reference data points for a variety of relevant water quality variables including physical measurements such as temperature, pH, and conductivity as well as ion concentrations, chemicals such as crude oil, and relevant biochemical variables such as blue-green algae pigments, chlorophyll-a, and CDOM.
     \item Simultaneously collect hyperspectral remote sensing imagery using an UAV.
-    \item Rapidly process the captured imagery into georectified reflectance data cubes.
-    \item Train machine learning models to map captured reflectance spectra to the water quality parameters measured by the reference sensors.
-    \item Apply the trained models to rapidly map large bodies of water and identify areas of interest.
+    \item Rapidly process captured imagery into georectified reflectance data cubes.
+    \item Train machine learning models to map captured reflectance spectra to water quality variables measured by reference sensors.
+    \item Apply trained models to rapidly map large bodies of water and identify areas of interest.
 \end{enumerate}
-Additionally, we have demonstrated that we can extend this methodology in two new ways: First, we have shown that it is possible to combine the datasets from separate collection periods and successfully train models using \textit{all} of the records despite variability in incident lighting conditions that impact the assumptions made in the reflectance conversion of captured hyperspectral data cubes.
-Second, we have shown that by leveraging the large amount of collected data, we can simultaneously train the machine learning models and quantify their prediction uncertainties by utilizing conformal prediction.
+Additionally, we have demonstrated that we can extend this methodology in two new ways.
+First, we have shown that it is possible to combine data sets from separate collection periods and successfully train models using \textit{all} of the records despite variability in incident lighting conditions that affects the assumptions made in the reflectance conversion of captured hyperspectral data cubes.
+Second, we have shown that by leveraging the large amount of data collected, we can simultaneously train machine learning models and quantify their prediction uncertainties by utilizing conformal prediction.
 
-As Figure~\ref{fig:downwelling-hist} indicates, there is variation in the total downwelling intensity between images collected in the same day \textit{and} between each separate collection period despite acquiring the imagery consistently near solar noon.
-These within collection variations are due to a combination of the stability of the UAV (on which the upward facing downwelling irradiance spectrometer is mounted) together with the occasional interference of clouds.
+As Figure~\ref{fig:downwelling-hist} indicates, there is variation in the total downwelling intensity between images collected on the same day \textit{and} between each separate collection period despite acquiring the imagery consistently near solar noon.
+These within-collection variations are due to a combination of the stability of the UAV (on which the upward facing downwelling irradiance spectrometer is mounted) together with the occasional interference of clouds.
 Moreover, the assumption that the water's surface can be treated as Lambertian is clearly violated when the water is not perfectly still.
 Despite the potential impact of these limitations on the quality of the resulting reflectance data cubes, the smoothness of the maps generated by our models suggests that we have provided sufficient context by including the relevant solar illumination and viewing geometries as additional features in the final data set.
-This fact is reinforced by the position of these variables s the most important features for \textit{each} of the estimated water quality parameters.
-So long as we are primarily interested in these values and not the reflectances themselves, we are able to successfully account for these lighting effects.
+This fact is reinforced by the position of these variables as the most important features for \textit{each} of the estimated water quality variables.
+As long as we are primarily interested in these values and not the reflectances themselves, we are able to successfully account for these lighting effects.
 
-With respect to the real time deployment of these models in the field, we note that training a reduced feature model without further hyperparameter optimization takes roughly 1 minute per target variable of interest using the processing computer included on the UAV.
-This means that in principle, the requisite training data can be collected by the USV, hyperspectral imagery can be acquired and processed into reflectance data cubes by the UAV, the resulting datasets can be combined to identify coincindent records, and this collection can then be used to train machine learning models and generate maps as in Figure~\ref{fig:map-biochem} all while the investigators are still in the field.
-Analyzing these resulting maps enables areas of interest to be readily pinpointed as was demonstrated by the identification of elevated crude oil, optical brighteners, and CDOM in the eastern alcove of the pond on 11-23.
+With respect to the real-time deployment of these models in the field, we note that training a reduced feature model without further hyperparameter optimization takes roughly 1 minute per target variable of interest using the processing computer included on the UAV.
+This means that in principle the necessary training data can be collected by the USV, hyperspectral imagery can be acquired and processed into reflectance data cubes by the UAV, the resulting data sets can be combined to identify coincindent records, and this collection can then be used to train machine learning models and generate maps as in Figure~\ref{fig:map-biochem} all while the investigators are still in the field.
+Analyzing these resulting maps enables areas of interest to be readily pinpointed, as demonstrated by the identification of elevated crude oil, optical brighteners, and CDOM in the eastern alcove of the pond on 11-23.
 Having identified a region of interest, the USV can then be sent to collect additional reference data and confirm the presence of any spill, bloom, or other source.
 
-Beyond the potential applications of this robot team for direct water quality monitoring, the combination of reference instruments together with easily co-located hyperspectral imagery provides fertile ground for the development of new spectral indices targeted towards specific water quality parameters.
-In this paper, we have shown how permutation importance ranking for the trained machine learning models enables a straight forward interpretation of the relative value of each reflectance bin to the final model predictions.
+Beyond the potential applications of this robot team for direct water quality monitoring, the combination of reference instruments together with easily co-located hyperspectral imagery provides fertile ground for the development of new spectral indices targeted towards specific water quality variables.
+In this paper, we have shown how permutation importance ranking for trained machine learning models enables a straightforward interpretation of the relative value of each reflectance bin to the final model predictions.
 In future work, we plan to utilize this information to construct new combinations of spectral bands which can be readily transferred to remote sensing platforms equipped with hyperspectral imagers such as the German EnMAP mission.
@@
 
-In this study we address the two key limitations of current remote sensing approaches to characterizing water quality, namely, the limited spatial, spectral, and temporal resolution provided by existing satellite platforms and the lack of comprehensive, highly resolved in-situ data needed to validate remote sensing data products.
-By equipping an autonomous USV with a suite of reference sensors, we are able to collect significantly more data than existing approaches that rely on the collection of individual samples for lab analysis or are constrained to continuous sensing at fixed sites.
-Utilizing an autonomous UAV equipped with a hyperspectral imager in tandem with the USV allows us to rapidly generate aligned datasets which can be used to train machine learning models which map measured reflectance spectra to the desired water quality parameters of interest.
-Furthermore, by virtue of collecting large training datasets we are able to simultaneously estimate the uncertainty of our trained models using conformal prediction.
+In this study, we address the two key limitations of current remote sensing approaches to characterizing water quality, namely the limited spatial, spectral, and temporal resolution provided by existing satellite platforms and the lack of comprehensive, highly resolved in-situ data needed to validate remote sensing data products.
+By equipping an autonomous USV with a suite of reference sensors, we can collect significantly more data than existing approaches that rely on the collection of individual samples for lab analysis or are constrained to continuous sensing at fixed sites.
+Utilizing an autonomous UAV equipped with a hyperspectral imager in tandem with the USV allows us to rapidly generate aligned datasets which can be used to train machine learning models which map measured reflectance spectra to the desired water quality variables of interest.
+Furthermore, by virtue of collecting large training datasets, we are able to simultaneously estimate the uncertainty of our trained models using conformal prediction.
 This addresses the lack of uncertainty quantification in traditional machine learning approaches.
 Finally, the rapid hyperspectral data cube processing pipeline employed on board the UAV makes it possible to deploy these trained models in order to rapidly generate maps of the desired target variables across entire bodies of water.
-The rapid turnaround time from data collection to model deployment is critical for real time water quality assessment and threat identification.
+The rapid turnaround time from data collection to model deployment is critical for real-time water quality assessment and threat identification.
 
@@
 
-\funding{This research was funded by the following grants: The Texas National Security Network
-Excellence Fund award for Environmental Sensing Security Sentinels. SOFWERX award for Machine
-Learning for Robotic Team. Support from the University of Texas at Dallas Office of Sponsored
-Programs, Dean of Natural Sciences and Mathematics, and Chair of the Physics Department are gratefully acknowledged.}
+\funding{
+This research was funded by the following grants: The Texas National Security Network Excellence Fund award for Environmental Sensing Security Sentinels.
+SOFWERX award for Machine Learning for Robotic Team and NSF Award OAC-2115094.
+Support from the University of Texas at Dallas Office of Sponsored Programs, Dean of Natural Sciences and Mathematics, and Chair of the Physics Department is gratefully acknowledged.
+TRECIS CC* Cyberteam (NSF #2019135), NSF OAC-2115094 Award, and EPA P3 grant number 84057001-0.
+}
 
@@
 \acknowledgments{Don MacLaughlin, Scotty MacLaughlin and the City of Plano, TX, are gratefully acknowledged for allowing us to deploy the autonomous robot team on their property.
+Dr.
 Christopher Simmons is gratefully acknowledged for his computational support.
-Annette Rogers is gratefully acknowledged for support with arranging insurance coverage.
+We thank Dr.
+Antonio Mannino for his advice in selecting the robotic boat sensing suite.
+Annette Rogers is gratefully acknowledged for support in arranging insurance coverage.
 Steven Lyles is gratefully acknowledged for support in arranging a secure place for the robot team.
-The authors acknowledge the OIT-Cyberinfrastructure Research Computing group at the University of Texas at Dallas and the TRECIS CC* Cyberteam (NSF #2019135) for providing HPC resources that contributed to this research.
-\textcolor{red}{Dr.
-Lary had a person to acknowledge that suggested the sensors to use...}}
+The authors acknowledge the OIT-Cyberinfrastructure Research Computing group at the University of Texas at Dallas and the TRECIS CC* Cyberteam (NSF #2019135) for providing HPC resources that contributed to this research, the NSF OAC-2115094 Award, and EPA P3 grant number 84057001-0.}
 
@@
 \begin{tabular}{@{}ll}
+GPS & Global Positioning System \\ 
+INS & Inertial Navigation System \\
+UTM & Universal Transverse Mercator \\
+UV & Ultraviolet \\
 ML & Machine Learning \\

### 2024-02-19 paper/paper.tex
updated with latest version of the text

@@
 Steven Lyles is gratefully acknowledged for support in arranging a secure place for the robot team.
-The authors acknowledge the OIT-Cyberinfrastructure Research Computing group at the University of Texas at Dallas and the TRECIS CC* Cyberteam (NSF #2019135) for providing HPC resources that contributed to this research, the NSF OAC-2115094 Award, and EPA P3 grant number 84057001-0.}
+The authors acknowledge the OIT-Cyberinfrastructure Research Computing group at the University of Texas at Dallas and the TRECIS CC* Cyberteam (NSF #2019135) for providing HPC resources that contributed to this research, NSF OAC-2115094 Award, and EPA P3 grant number 84057001-0.}
 

### 2024-02-19 old/make_slurm_scripts.jl

@@ -30,8 +30,6 @@ function make_slurm_jobs(;script_to_run="5a__hpo_DecisionTreeRegressor.jl", base
         open(basename*String(target)*".slurm", "w") do f
             println(f, file_text)
         end
-
-
     end
 end
 

### 2024-02-19 paper/paper.tex
Updates from Overleaf

@@
 
-The USV employed in the robot team is a Maritime Robotics Otter which features a modular design and 20 hour battery life.
-The USV is equipped with an in situ sensing payload consisting of a combination of Eureka Manta-40 multiprobes including fluorometers, ion selective electrodes, and other physical sensors that together enable the collection of comprehensive near-surface measurements including Colored Dissolved Organic Matter (CDOM), Crude Oil, Blue-Green Algae (phycoerythrin and phycocyanin), Chlorophyll A, $\mathrm{Na^+}$, $\mathrm{Ca^{2+}}$, $\mathrm{Cl^-}$, Temperature, Conductivity, and many others.
-The full list of measurements utilized in this study is given in Table~\ref{tab:sensors} and is categorized into four distinct types: physical measurements, ion measurements, biochemical measurements, and chemical measurements.
+\begin{figure}
+\includegraphics[width=\columnwidth]{paper/figures/materials-and-methods/annotated-boat.pdf}
+\caption{ Configuration of the USV: (\textbf{a}) Frontal view of the USV showing the Eureka Manta+40 Multiprobes mounted on the underside of the boat.
+(\textbf{b}) The USV deployed in the water.\label{fig:boat-components}}
+\end{figure}
+
+The USV employed in the robot team is a Maritime Robotics Otter equipped with an in situ sensing payload consisting of a combination of Eureka Manta+40 multiprobes.
+These sensors include fluorometers, ion selective electrodes, and other physical sensors and are mounted on the underside of boat as illustrated in Figure~\ref{fig:boat-components}.
+Together this sensor array enables the collection of comprehensive near-surface measurements including Colored Dissolved Organic Matter (CDOM), Crude Oil, Blue-Green Algae (phycoerythrin and phycocyanin), Chlorophyll A, $\mathrm{Na^+}$, $\mathrm{Ca^{2+}}$, $\mathrm{Cl^-}$, Temperature, Conductivity, and many others.
+The full list of measurements utilized in this study is outlined in Table~\ref{tab:sensors} and is categorized into four distinct types: physical measurements, ion measurements, biochemical measurements, and chemical measurements.
 Additionally, the USV is equipped with an ultrasonic weather monitoring sensor for measuring air speed and direction, as well as a BioSonics MX Aquatic Habitat Echosounder sonar, which are not explored in this study.
@@
 \begin{table}[H] 
-\caption{In-situ reference sensors modelled in this study.\label{tab:sensors}}
+\caption{In-situ reference sensors utilized in this study.\label{tab:sensors}}
 \newcolumntype{C}{>{\centering\arraybackslash}X}
@@
 For each of the 13 target variables listed in Table~\ref{tab:sensors}, the data was randomly partitioned into a 90:10 training/testing split.
-Using the MLJ machine learning framework, a variety of machine learning models compatible with the regression task were identified \cite{MLJ1}.
+Using Julia's MLJ (Machine Learning Julia) package, a variety of machine learning models compatible with the regression task were identified \cite{MLJ1}.
 This selection of models included linear regression (and it's variations), Gaussian process regression, shallow neural networks, and decision tree-based models.
-Out of this set, the Random Forest Regressor (RFR) model from \cite{decision-trees} was selected for its relatively quick training and inference times.
-Random forests are an ensembling technique based on bagged predictions of individual decision tree regressors trained using the CART algorithm with each individual tree trained on a random subset of features \textit{and} a random subset of training records \cite{decision-trees, random-forest}.
+Out of this set, the Random Forest Regressor (RFR) model from \cite{decision-trees} was selected for use in this study due to its relatively quick training and inference times.
+Random forests are an ensembling technique based on bagged predictions of individual decision tree regressors trained using the classification and regression trees (CART) algorithm.
+Each individual tree in a RFR is trained on a random subset of features \textit{and} a random subset of training records \cite{decision-trees, random-forest}.
 
@@
 In this paper, we have shown how permutation importance ranking for trained machine learning models enables a straightforward interpretation of the relative value of each reflectance bin to the final model predictions.
-In future work, we plan to utilize this information to construct new combinations of spectral bands which can be readily transferred to remote sensing platforms equipped with hyperspectral imagers such as the German EnMAP mission.
+In future work, we plan to utilize this information to construct new combinations of spectral bands which can be readily extended for use remote sensing platforms equipped with hyperspectral imagers.
+\textcolor{red}{The recently launched Environmental Mapping and Analysis Program (EnMAP) is one such example which includes over 91 spectral bands in the VNIR that overlap with our hyperspectral imager \cite{Storch2023TheEI}.}
 

### 2024-02-20 3b_make-maps.jl
updated figures to include a 30 m scale bar

@@ -39,6 +39,14 @@ if !ispath(mapspath)
 end
 
 
+# see https://en.wikipedia.org/wiki/Geographic_coordinate_system#Latitude_and_longitude
+# for detail
+ϕ_scale = 33.70093
+m_per_deg = 111412.84*cosd(ϕ_scale) - 93.5*cosd(3*ϕ_scale) + 0.118 * cosd(5*ϕ_scale)
+λ_scale_l = -97.7166
+λ_scale_r = λ_scale_l + 30/m_per_deg
+
+
 
 w= -97.717472
 n= 33.703572
@@ -47,6 +55,15 @@ e= -97.712413
 
 
 satmap = get_background_satmap(w,e,s,n)
+
+# fig = cmk.Figure();
+# ax = cmk.Axis(fig[1,1])
+# cmk.heatmap!(ax, satmap.w..satmap.e, satmap.s..satmap.n, satmap.img);
+# cmk.xlims!(ax, -97.7168, -97.7125)
+# cmk.ylims!(ax, 33.70075, 33.7035)
+
+# fig
+
 
 
 # let's add a function to sort them into numerical order
@@ -151,12 +168,12 @@ targets_to_map = [
 #    :RefFuel,
 ]
 
-#targets_to_map = [:HDO, :pH]
+# targets_to_map = [:HDO, :pH]
 
 # targets_to_map = [:CDOM]
 
 
-targets_to_map = [:pH]
+# targets_to_map = [:pH]
 
 
 # set up relevant paths
@@ -425,6 +442,10 @@ for target ∈ targets_to_map
             cmk.xlims!(ax, -97.7168, -97.7125)
             cmk.ylims!(ax, 33.70075, 33.7035)
 
+            # add 30 meter scale bar
+            cmk.lines!(ax, [λ_scale_l, λ_scale_r], [ϕ_scale, ϕ_scale], color=:white, linewidth=5)
+            cmk.text!(ax, λ_scale_l, ϕ_scale - 0.0001, text = "30 m", color=:white, fontsize=12, font=:bold)
+
             cb = cmk.Colorbar(fig[1,2], label="$(target_long) ($(units))", colorrange=clims, colormap=cm, lowclip = cm[1], highclip = cm[end])
 
             fig
@@ -435,6 +456,11 @@ for target ∈ targets_to_map
 
         cmk.xlims!(ax_tot, -97.7168, -97.7125)
         cmk.ylims!(ax_tot, 33.70075, 33.7035)
+
[…]

### 2024-02-23 paper/paper.tex
updated text

@@
 Together, this team is able to address the limitations of existing approaches by enabling the simultaneous collection of comprehensive in situ data together with high-resolution hyperspectral imagery.
-We showcase the capabilities of this team using data collected in a north Texas pond during three collections in the fall of 2020.
+We showcase the capabilities of this team using data collected in a north Texas pond during three collections in 2020.
 Machine learning models for 13 variables are trained using the data set of paired in situ measurements and coincident reflectance spectra.
@@
 We extend the training procedure to utilize conformal prediction to estimate 90\% confidence intervals for the output of each trained model.
-The maps generated by applying each trained model to the collected images reveal the small-scale spatial variability within the pond.
+Maps generated by applying each trained model to the collected images reveal the small-scale spatial variability within the pond.
 Additionally, the permutation importance computed for each feature of the trained models highlights the spectral features relevant to each water quality variable.
@@
 
-For decades, remote sensing imagery has been used for environmental monitoring with applications ranging from resource mapping, land type classification, and urban growth assessment to wildfire tracking, natural disaster tracking, and many more \cite{cohen2004landsat, melesse2007remote, allison2016airborne, joyce2009review, robert2017analysis}.
+For decades, remote sensing imagery has been used for environmental monitoring with applications ranging from resource mapping, land type classification, and urban growth assessment to wildfire tracking, natural disaster tracking, and many more \cite{melesse2007remote, joyce2009review}.
 Among these applications, the retrieval of water quality variables from remote sensing imagery remains challenging due to the difficulty of obtaining in situ reference data that coincide with available satellite imagery.
@@
 
-Much effort has recently been spent on the curation of comprehensive datasets that combine water quality records with decades of satellite imagery to enable the development of new methods for monitoring water quality.
+Much effort has recently been spent on the curation of comprehensive datasets combining water quality records with decades of satellite imagery to enable the development of new methods for monitoring water quality.
 For example, Aurin et al.
@@
 have combined more than 600,000 records of dissolved organic carbon, chlorophyll-a and other variables of water quality together with Landsat historical reflectance data for the period 1984--2019 \cite{ross2019aquasat}.
-With a sufficient quantity of data, machine learning methods can augment traditional approaches using reflectance band ratios to enable estimation of water quality metrics and perform water quality classification \cite{schiller1999neural, brown2008neural, lary2010artificial, feng2015urban,belgiu2016random}.
+With a sufficient quantity of data, machine learning methods can augment traditional approaches using reflectance band ratios to enable estimation of water quality variables and perform water quality classification \cite{schiller1999neural, brown2008neural, lary2010artificial, feng2015urban,belgiu2016random}.
 However, the low spatial and spectral resolution of available multiband remote sensing satellites makes it difficult to analyze inland waters with small spatial features and complicated spectral signatures.
@@
 Despite the increased spectral and spatial resolution afforded by UAV platforms, these improvements alone cannot address the limited spatial resolution of in situ reference data.
-To address this gap and enable comprehensive real-time water quality detection, we have developed a robotic team composed of an autonomous uncrewed surface vessel (USV) equipped with a collection of reference grade instruments together with a UAV carrying a hyperspectral imager \cite{robotTeam1}.
+To address this gap and enable comprehensive real-time water quality \textcolor{red}{detection}, we have developed a robotic team composed of an autonomous uncrewed surface vessel (USV) equipped with a collection of reference grade instruments together with a UAV carrying a hyperspectral imager \cite{robotTeam1}.
 By incorporating these reference instruments on a maneuverable USV platform, we are able to rapidly collect large volumes of water quality data for a variety of physical, biochemical, and chemical variables.
@@
 
-In this study, we expand on our previous work by demonstrating the capabilities of this coordinated robot team using data collected at a pond in North Texas over three separate days in the fall of 2020.
+In this study, we expand on our previous work by demonstrating the capabilities of this coordinated robot team using data collected at a pond in North Texas over three separate days in 2020.
 Specifically, we show the ability to accurately predict physical variables such as temperature, conductivity, pH, and turbidity, as well as biochemical constituents, including blue-green algae pigments, CDOM, and chlorophyll-a, in addition to concentrations of crude oils, optical brighteners, and a variety of ions.
@@
 This approach drastically reduces the time from data collection to insight.
+
+\textcolor{red}{The primary goal of this study is to demonstrate the capabilities of a coordinated robotic team combining in situ sensing together with hyperspectral imaging for the rapid characterization of water composition.
+Specifically, we seek to address the primary challenge of acquiring remote sensing data products coincident with reference measurements that are critical for the retrieval of water composition and water quality parameters.
+By bringing together
+- there are three key goals in this study: The first is to demonstrate the variety of water quality and composition variables that can be predicted from our collected hypserspectral imager.
+The second is to demonstrate that hyperspectral imagery from multiple observations can by combined despite variability in lighting conditions, and the third is to introduce a method for uncertainty quantification which is crucial for the evaluation of model predictions.
+}
 
@@
 
-\begin{figure}
+\begin{figure}[t!]
 \includegraphics[width=\columnwidth]{paper/figures/materials-and-methods/annotated-boat.pdf}
@@
 
-\begin{table}[H] 
+\begin{table}[t!] 
 \caption{In-situ reference sensors utilized in this study.\label{tab:sensors}}
@@
 
-As shown in Table~\ref{tab:sensors}, the physical measurements and ion sensors are largely based on different electrode configurations, while the chemical and biochemical measurements are all optically significant in UV and visible light, enabling their determination by fluorometry.
-The pigments phycoerythrin and phycocyanin are used to determine the blue-green algae content, which together with chlorophyll-a enable us to assess the distribution of photosynthetic life in the pond.
+As shown in Table~\ref{tab:sensors}, the physical measurements and ion sensors are largely based on different electrode configurations, while the chemical and biochemical measurements are all optically significant in UV and visible light, enabling their determination by fluorometry \cite{de2007ion,trees2002fluorometric,tillman2017evaluation}.
+The pigments phycoerythrin and phycocyanin are used to determine the blue-green algae content, which together with chlorophyll-a enable us to assess the distribution of photosynthetic life in the pond \cite{Brient2008APP, boyer2009phytoplankton}.
 In addition, we also measured the concentration of colored dissolved organic matter (CDOM), which impacts light penetration and serves as a primary source of bioavailable carbon.
-Crude oil (natural petroleum) and optical brightener concentrations are also measured with fluorometers and are relevant for identifying sources of industrial contamination or natural seepage.
+Crude oil (natural petroleum) and optical brightener concentrations are also measured with fluorometers and are relevant for identifying sources of industrial contamination, natural seepage, and sewage \cite{brown2003review,cao2009evaluation}.
+
+\textcolor{red}{Should we add something here about non-optically active substances?}
 
@@
 
-\begin{figure}[H]
+\begin{figure}[b!]
 \includegraphics[width=\columnwidth]{paper/figures/materials-and-methods/annotated-drone.pdf}
+\vspace{-0.2in}
 \caption{Configuration of the UAV: (\textbf{a}) the hyperspectral imager and acquisition computer.
@@
 
-\begin{figure}[H]
+\begin{figure}[t!]
 \begin{adjustwidth}{-\extralength}{0cm}
 \centering
+\vspace{-0.2in}
 \includegraphics[width=14cm]{paper/figures/materials-and-methods/pipeline-figure-2.pdf}
 \end{adjustwidth}
+\vspace{-0.2in}
 \caption{Hyperspectral Image Processing: Hyperspectral data cubes are collected one scan-line at a time (left).
@@
 
-\begin{figure}[H]
+\begin{figure}[t!]
 \begin{adjustwidth}{-\extralength}{0cm}
 \centering
+\vspace{-0.2in}
 \includegraphics[width=15.5cm]{paper/figures/materials-and-methods/HyperSpectralInfoGraphic.pdf}
@@
 
-Data were collected using the robot team at a site in North Texas during three observation periods in the fall of 2020.
+Data were collected using the robot team at a site in North Texas during three observations on 11-23-2020, 12-09-2020, and 12-10-2020.
 For each collection period, the UAV first completed a broad survey of the pond, capturing multiple hyperspectral data cubes.
@@
 
-Each collection was performed near solar noon to maximize the amount of incident sunlight illuminating the water; however, to account for any potential variation in lighting conditions between data cubes, we augment the training set with additional features including the drone viewing geometry (roll, pitch, heading) and solar illumination geometry (solar azimuth, solar elevation, solar zenith) as well as the total at-pixel intensity before reflectance conversion, the total downwelling intensity, and the drone altitude.
+Each collection was performed near solar noon to maximize the amount of incident sunlight illuminating the water.
+For the site in North Texas, this corresponded to average solar zenith angles of 54.9$^{\circ}$, 56.7$^{\circ}$, and 56.75$^{\circ}$ for 11-23-202, 12-09-2020, and 12-10-2020 respectively.
+Given the hyperspectral imager acquires data cubes at nadir, there was little concern for effects due to sunglint.
+However, to account for any potential variation in lighting conditions between data cubes, we augment the training set with additional features including the drone viewing geometry (roll, pitch, heading) and solar illumination geometry (solar azimuth, solar elevation, solar zenith) as well as the total at-pixel intensity before reflectance conversion, the total downwelling intensity, and the drone altitude.
 Further feature engineering is performed to add additional spectral indices that utilize combinations of specific wavelength bands such as the normalized difference vegetation index (NDVI), normalized difference water index (NDWI), simple ratio (SR), photochemical reflectance index (PRI) and more, as outlined in \cite{envi_vegetation_indices, thenkabail2018hyperspectral,kaufman1992atmospherically, SpectralIndexWheat}.
@@
 For each of the 13 target variables listed in Table~\ref{tab:sensors}, the data was randomly partitioned into a 90:10 training/testing split.
-Using Julia's MLJ (Machine Learning Julia) package, a variety of machine learning models compatible with the regression task were identified \cite{MLJ1}.
-This selection of models included linear regression (and it's variations), Gaussian process regression, shallow neural networks, and decision tree-based models.
-Out of this set, the Random Forest Regressor (RFR) model from \cite{decision-trees} was selected for use in this study due to its relatively quick training and inference times.
+To model the data, we chose to use the Random Forest Regressor (RFR) as implemented in the Machine Learning Framework for Julia package,  MLJ \cite{MLJ1}.
 Random forests are an ensembling technique based on bagged predictions of individual decision tree regressors trained using the classification and regression trees (CART) algorithm.
-Each individual tree in a RFR is trained on a random subset of features \textit{and} a random subset of training records \cite{decision-trees, random-forest}.
+Each tree in a RFR is trained on a random subset of features \textit{and} a random subset of training records \cite{decision-trees, random-forest}.
+Random Forests are particularly attractive due to their fast training and inference times.
+Furthermore, studies continue to observe that tree-based models like the Random Forest remain superior for tabular datasets \cite{grinsztajn2022tree, shwartz2022tabular}.
 
-As reflectance values in adjacent wavelength bins tend to correlate with each other and, therefore, may not necessarily contribute additional information content to the final model, it is desirable to evaluate the relative importance of each feature to the final predictions of our trained models.
-This is useful both for identifying the most relevant features and for performing feature selection to reduce the final model size and optimize the inference time.
+As reflectance values in adjacent wavelength bins tend to correlate with each other and, therefore, may not necessarily contribute additional information content to the final model, it is desirable to evaluate the relative importance of each feature to the trained model predictions.
+This is useful both for identifying the most relevant features and for performing feature selection to reduce the final model size.
 By default, tree-based methods, such as the RFR allow for an impurity-based ranking as described in \cite{random-forest, rfr-importance-ranking}.
@@
 Therefore, we choose to use the model-agnostic permutation importance as described by \cite{parr2018beware}.
-To do this, we further partition the training data set, resulting in an 80:10:10 split with 80\% of points used for model training, 10\% of points used for validation and determination of feature importance, and the final 10\% held out as an independent test data set.
+To do this, we further partition the training data set, resulting in an 80:10:10 split with 80\% of points used for model training, 10\% of points used for validation and determination of feature importance, and the final 10\% held out as an independent testing set.
 The importance of the $j^{\text{th}}$ feature is then computed as
@@
 
-To assess the uncertainty of the final model's predictions, we employ Inductive Conformal Prediction as described in \cite{conformal-prediction-1, conformal-prediction-2, conformal-prediction-3, conformal-prediction-4}.
-To do this, we compute a set of nonconformity scores of the trained model on the validation set using an uncertainty heuristic, in this case, the absolute error
+To assess the uncertainty of the final model's predictions, we employed Inductive Conformal Prediction as described in \cite{conformal-prediction-1, conformal-prediction-2, conformal-prediction-3, conformal-prediction-4}.
+To do this, we computed a set of nonconformity scores of the trained model on the validation set using an uncertainty heuristic, in this case, the absolute error
 \begin{equation}
@@
 where $f(X_i)=\hat{y}_i$ denotes the trained ML model applied to the $i^{th}$ calibration record.
-These n-many scores are sorted, and the half width of the interval $d$ is calculated as the $\frac{\lceil(1-\alpha)(n+1) \rceil}{n}$ quantile of this set in order to achieve a coverage of $1-\alpha$ on the calibration set.
+These n-many scores are sorted, and the interval half width, $d$, is calculated as the $\frac{\lceil(1-\alpha)(n+1) \rceil}{n}$ quantile of this set in order to achieve a coverage of $1-\alpha$ on the calibration set.
 Prediction intervals for new data are then formed as $f(X)\pm d$.
-For this study, we have chosen $\alpha=0.1$ for a coverage corresponding to a 90\% confidence interval.
+For this study, we chose $\alpha=0.1$ for a coverage corresponding to a 90\% confidence interval.
 
-Using these tools, the training procedure for each model is as follows: First, the model is trained using six-fold cross-validation on the training set with default hyperparameter values.
-Feature importances for the trained model are then computed, and the top 25 features are identified.
-A second model is then trained using the same 6-fold cross-validation scheme with \textit{ only} these 25 most important features together with hyperparameter optimization using a random parameter search over the number of trees and sampling fraction.
-Model performance is evaluated by computing out-of-fold values for the coefficient of determination, as well as the
+Using these tools, the training procedure for each model was as follows: First, each model was trained using six-fold cross-validation on the full 526-feature training set with default hyperparameter values.
+Feature importances for the trained model were then computed, and the top 25 features were identified.
+A second model was then trained using the same 6-fold cross-validation scheme with \textit{only} these 25 most important features together with hyperparameter optimization using a random search over the number of trees and sampling fraction.
+The number of trees was optimized as it has a significant impact on both model performance and inference time.
+The sampling ratio determines the fraction of training records that each individual tree is exposed to during training.
+Tuning this parameter helps limit overfitting by increasing the diversity trees in the ensemble.
+Additionally, we chose to fix the maximum tree depth to 20 to control the final model size such that each trained model can fit in-memory on the on board UAV processing computer.
+The remaining hyperparameters were left to their default values in order to constrain the total optimization space.
+The performance of each model was evaluated by computing out-of-fold scores for the coefficient of determination, as well as the
 \begin{align}
@@
 \end{align}
-where RMSE is the root-mean-square error, and MAE is the mean absolute error between true values $y_i$ and predictions $\hat{y}_i$.
+where RMSE is the root-mean-square error, and MAE is the mean absolute error between true measurements $y_i$ and predictions $\hat{y}_i$.
 
-Having identified the model with the best out-of-fold performance, we proceed to train the final hyperparameter optimized model on the full training set with associated uncertainty estimated using conformal prediction.
-Then each final model is evaluated on the previously untouched testing set.
+Having identified the model with the best out-of-fold performance, we proceeded to train the final hyperparameter optimized model on the full training set with associated uncertainty estimated using conformal prediction.
+Then each final model was evaluated on the previously untouched testing set.
 We visualize model performance across the distribution of testing data with a scatter diagram and quantile-quantile plot for which successful model predictions should lie close to a 1:1 line.
@@
 These trained models can then easily be deployed on the on-board processing computer so that during subsequent surveys, target concentrations can be inferred as imagery are collected and processed.
-The application of each model to the collected hyperspectral data cubes results in a map of the distribution of each water quality variable across the pond.
+The application of each model to the collected hyperspectral data cubes results in a map of the distribution of the water composition across the pond.
 
@@
 
-\begin{figure}
+\begin{figure}[t!]
+\vspace{-0.2in}
 \includegraphics[width=0.7\columnwidth]{paper/figures/results/downwelling-hist.pdf}
+\vspace{-0.2in}
 \caption{Distribution of total downwelling intensity during each of the three HSI collection flights.
@@
 
-\begin{table}
+\begin{table}[t!]
   \caption{Summary of fitting statistics for each target measurement.
@@
 
-\begin{figure}
+\begin{figure}[p]
 \centering
@@
 
-\begin{figure}
+\begin{figure}[t!]
 \centering
+\vspace{-0.2in}
 \includegraphics[width=\columnwidth]{paper/figures/results/fits/physical-ranking.pdf}
@@
 
-\begin{figure}
+\begin{figure}[t!]
 \centering
@@
 
+% \cite{cohen2004landsat, melesse2007remote, allison2016airborne, joyce2009review, robert2017analysis}
+
+\textcolor{red}{test
+- We need to discuss how we are building on the original paper. 
+- The key advancements are a demonstration of more optically active substances that can be successfully modelled from the HSIs 
+- The ability to model physical parameters that are not considered to be optically active in the sense that they have uniquelly identifiable absorption features (ions, etc...) 
+- The ability to successfully combine mutliple observations
+    - This is particularly noteworthy as there was significant variation in total downwelling intensity between the separate collections which could introduce bias between reflectance values measured on separate days
+    - Key result is that by incorporating the relevant information (solar illumination geometry and viewing geometry) we are able to successfully account for these biases and produce models that are consistent between multiple observation periods
+- Estimation of uncertainty using conformal prediction
+- The trained models are small enough so as to be deployable on the UAV for real time processing
+
+- part one: overview of method and description of how we are able to collect comparable data quantities which traditionally require decades i.e.
+Aurin et al.
+We can also mention how existing approaches using HSI on UAV platforms suffer from a lack of comprehensive in-situ data needed to reliably calibrate the (machine learning) data products.
+By creating a coordinated team with both autonomous in situ data collection and rapid HSI acquisition by a UAV we effectively bridge this gap by enabling the precise collection of collocated data points.
+- part two: We extend our previous work in three key ways: first we model significantly more target variables, second we confirm that it is possible to utilize imagery from multiple collections despite the impact of light variability so long as we appropriately augment the data to include illumination and viewing geometry, third we implemented a method for robust uncertainty quantification by using conformal prediction so that we can evaluate the certainty of our trained models.
+- finally we can comment on limitations, extensions, and future work
+    - Limitation: total area surveyed is determined by battery life (suggestion --> multiple drones) 
+    - Limitation: predictions of trained tree-based models are litmied by the range of available data.
+To extend the model to be sensitive across a broader range of values/concentrations, we need to collect more training data.
+However we have demonstrated that data from disparate observations can be combined despite the limitations of lighting variability.
+Indeed it is preciesly the fact that we are interested in the water composition and not the absolute reflectance values themselves that makes this possible because so long as we include enough descriptive variables which capture the lighting dynamics, we can account for differences in ambient lighting conditions between observations.
+}
+
 In this paper, we have validated the methodology introduced in our previous work\cite{robotTeam1}. Specifically, we demonstrate that by using an autonomous team of sensing sentinels, we can
@@
 \appendix
-%% \section[\appendixname~\thesection]{}\label{appendix:spec-indices}
+\section[\appendixname~\thesection]{}\label{Model Hyperparameters}
 %% \subsection[\appendixname~\thesubsection]{}
+\begin{table}[H] 
+\caption{Hyperparameter values for the final models.\label{tab5}}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
+\begin{tabularx}{\textwidth}{CCCCCCC}
+\toprule
+\textbf{Target}	& \textbf{Number of Trees}	& \textbf{Sampling Ratio} & \textbf{Maximum tree depth} & \textbf{Number of Subfeatures} & \textbf{Minimum samples per leaf} & \textbf{Minimum samples per split}\\
+\midrule
+Temperature & 153 & 0.979 & 20 & 5 & 1 & 2 \\
+Conductivity & 153 & 0.979 & 20 & 5 & 1 & 2\\
+pH & 153 & 0.979 & 20 & 5 & 1 & 2\\
+Turbidity & 153 & 0.979 & 20 & 5 & 1 & 2\\
+$\mathrm{Ca}^{2+}$ & 153 & 0.979 & 20 & 5 & 1 & 2\\
+$\mathrm{Cl^-}$ & 153 & 0.979 & 20 & 5 & 1 & 2\\
+$\mathrm{Na^+}$ & 153 & 0.979 & 20 & 5 & 1 & 2\\
+Blue-Green Algae (Phycoerythrin) & 153 & 0.979 & 20 & 5 & 1 & 2\\
+CDOM & 153 & 0.979 & 20 & 5 & 1 & 2\\
+Chlorophyll A & 153 & 0.979 & 20 & 5 & 1 & 2\\
+Blue-Green Algae (Phycocyanin) & 153 & 0.979 & 20 & 5 & 1 & 2\\
+Crude Oil & 153 & 0.979 & 20 & 5 & 1 & 2\\
+Optical Brighteners & 153 & 0.979 & 20 & 5 & 1 & 2\\
+\bottomrule
+\end{tabularx}
+\end{table}
 

### 2024-02-23 paper/paper.tex
Updates from Overleaf

@@
 
-For decades, remote sensing imagery has been used for environmental monitoring with applications ranging from resource mapping, land type classification, and urban growth assessment to wildfire tracking, natural disaster tracking, and many more \cite{melesse2007remote, joyce2009review}.
-Among these applications, the retrieval of water quality variables from remote sensing imagery remains challenging due to the difficulty of obtaining in situ reference data that coincide with available satellite imagery.
-Many studies have shown success modeling relevant water quality variables such as colored dissolved organic matter (CDOM), cholorophyll-a, and total suspended sediment concentrations by using combinations of spectral bands from terrestrial remote sensing satellites.
-However, the in situ reference data used in these studies typically require the time-consuming collection of individual samples for lab analysis or continuous monitoring at fixed sites \cite{brezonik2005landsat, paavel2011optical, gursoy2019investigating, bonansea2019using, sagan2020monitoring, remote-sensing-finland}.
+For decades, remote sensing imagery have been used for environmental monitoring with applications ranging from resource mapping, land type classification, and urban growth assessment to wildfire monitoring, natural disaster tracking, and many more \cite{melesse2007remote, joyce2009review}.
+Among these applications, the retrieval of water quality variables from remote sensing imagery remains challenging due to the difficulty of obtaining in situ reference data coincident with available satellite imagery.
+Traditional approaches to obtain these data have relied on serendipitous satellite passes over fixed sensing sites or sensor-equipped vessels.
+As a consequence, curating comprehensive datasets can require decades of observations \cite{aurin2018remote, ross2019aquasat}.
+This poses a significant challenge for assessing natural and anthropogenic changes to water composition in real time.
 
-Much effort has recently been spent on the curation of comprehensive datasets combining water quality records with decades of satellite imagery to enable the development of new methods for monitoring water quality.
-For example, Aurin et al.
-curated over 30 years of oceanographic field campaign data with associated coincident satellite imagery \cite{aurin2018remote}.
-Similarly, Ross et al.
-have combined more than 600,000 records of dissolved organic carbon, chlorophyll-a and other variables of water quality together with Landsat historical reflectance data for the period 1984--2019 \cite{ross2019aquasat}.
-With a sufficient quantity of data, machine learning methods can augment traditional approaches using reflectance band ratios to enable estimation of water quality variables and perform water quality classification \cite{schiller1999neural, brown2008neural, lary2010artificial, feng2015urban,belgiu2016random}.
+Where datasets have been compiled, many studies have shown success extracting optically active water quality variables such as colored dissolved organic matter (CDOM), chlorophyll-a, and suspended sediment concentration by using combinations of spectral bands from from remote sensing satellites \cite{remote-sensing-finland,bonansea2015using}.
+These approaches can be further augmented by machine learning methods which consist of nonlinear and non-parametric models designed to learn representations of functions directly from data \cite{sagan2020monitoring}.
+For example Petersen et al.
+utilized a deep neural network to successfully estimate blue-green algae, chlorophyal-a, CDOM, as well as the optically in-active
+
+which are often related indirectly to optically active variables.
+
+which  \cite{sagan2020monitoring, peterson2020deep}
+
+can augment traditional approaches using reflectance band ratios to enable estimation of water quality variables and perform water quality classification \cite{schiller1999neural, brown2008neural, lary2010artificial, feng2015urban,belgiu2016random}.
+
 However, the low spatial and spectral resolution of available multiband remote sensing satellites makes it difficult to analyze inland waters with small spatial features and complicated spectral signatures.
@@
 Advances in multispectral and hyperspectral imaging technology have considerably reduced their size, making it possible to incorporate these cameras into the payload of autonomous aerial vehicles (UAVs) such as quadcopters, hexacopters, and other drones \cite{hruska2012radiometric}.
-By controlling altitude during flight, UAVs can produce imagery with pixels at the centimeter scale and limit the need for complicated atmospheric corrections to account for scattering by atmospheric aerosols and gases \cite{adao2017hyperspectral,banerjee2020uav}.
+
+Bringing the imaging technology closer to the ground enables UAVs to address the spectral, spatial, and temporal shortcomings of remote sensing satellites.
+
+Controlling altitude during flight, UAVs can produce imagery with pixels at the centimeter scale and limit the need for complicated atmospheric corrections to account for scattering by atmospheric aerosols and gases \cite{adao2017hyperspectral,banerjee2020uav}.
 Already, UAVs equipped with multispectral and hyperspectral imagers are being used in a variety of domains to great effect, including biomass estimation, forest management, precision agriculture, and now water quality monitoring \cite{adao2017hyperspectral, padua2017uas,arroyo2019implementation,kurihara2020unmanned,ehmann2019monitoring, lu2021retrieval}.
+Despite the increased spectral and spatial resolution afforded by UAV platforms, these improvements alone cannot address the limited spatial resolution of in situ reference data.
 
-Despite the increased spectral and spatial resolution afforded by UAV platforms, these improvements alone cannot address the limited spatial resolution of in situ reference data.
 To address this gap and enable comprehensive real-time water quality \textcolor{red}{detection}, we have developed a robotic team composed of an autonomous uncrewed surface vessel (USV) equipped with a collection of reference grade instruments together with a UAV carrying a hyperspectral imager \cite{robotTeam1}.
@@
 
- The robotic team employed in this study consists of two key sensing sentinels: An uncrewed surface vessel (USV) used to collect in situ reference measurements, and an unmanned aerial vehicle (UAV) for performing rapid, wide-area surveys to gather remote sensing data products.
+ The robotic team presented in this study consists of two key sensing sentinels: An uncrewed surface vessel (USV) used to collect in situ reference measurements, and an unmanned aerial vehicle (UAV) for performing rapid, wide-area surveys to gather remote sensing data products.
 Both platforms are coordinated using open source QGroundControl software for flight control and mission planning and are equipped with high-accuracy GPS and INS such that all data points collected are uniquely geolocated and time-stamped \cite{qgroundcontrol}.
@@
 \textcolor{red}{Should we add something here about non-optically active substances?}
+\textcolor{blue}{Good idea if you have something}
 
@@
 
-\begin{figure}[b!]
+\begin{figure}[t!]
+\vspace{-0.3in}
 \includegraphics[width=\columnwidth]{paper/figures/materials-and-methods/annotated-drone.pdf}
-\vspace{-0.2in}
+\vspace{-0.3in}
 \caption{Configuration of the UAV: (\textbf{a}) the hyperspectral imager and acquisition computer.
@@
 
-\begin{figure}[t!]
+\begin{figure}[b!]
 \begin{adjustwidth}{-\extralength}{0cm}
 \centering
-\vspace{-0.2in}
+\vspace{-0.4in}
 \includegraphics[width=14cm]{paper/figures/materials-and-methods/pipeline-figure-2.pdf}
 \end{adjustwidth}
-\vspace{-0.2in}
+\vspace{-0.4in}
 \caption{Hyperspectral Image Processing: Hyperspectral data cubes are collected one scan-line at a time (left).
@@
 Initially, the captured spectra are in units of spectral radiance (measured in microflicks); however, this does not account for the variability of incident light illuminating the water.
-To this end, we convert the hyperspectral data cubes into units of reflectance utilizing the skyward-facing downwelling irradiance spectrometer (see Figure~\ref{fig:drone-components}).
+To this end, we convert the hyperspectral data cubes into units of reflectance utilizing the skyward-facing downwelling irradiance spectrometer.
 When the camera is normal to the water surface, the reflectance is given by
@@
 At this scale, the surface is essentially flat, so that the hyperspectral data cube can be reliably georectified without the need for an on-board digital elevation map (DEM).
-We adopt the approach outlined in \cite{GeorectificationMuller, GeorectificationBaumker, GeorectificationMostafa} whereby each scan line is georeferenced using the known field of view (30.8 $\deg$) together with the position and orientation of the UAV as provided by the on-board GPS/INS.
+We adopt the approach outlined in \cite{GeorectificationMuller, GeorectificationBaumker, GeorectificationMostafa} whereby each scan line is georeferenced using the known field of view (30.8$^\circ$) together with the position and orientation of the UAV as provided by the on-board GPS/INS.
 After a sequence of coordinate transformations, the pixel coordinates are obtained in the relevant UTM zone (in meters).
@@
 \centering
-\vspace{-0.2in}
+\vspace{-0.3in}
 \includegraphics[width=15.5cm]{paper/figures/materials-and-methods/HyperSpectralInfoGraphic.pdf}
@@
 
-The above processing pipeline was implemented using the Julia programming language, a just-in-time compiled language with native multi-theading support \cite{julia-1}.
+The above processing pipeline was implemented using the Julia programming language, a just-in-time compiled language with native multi-threading support \cite{julia-1}.
 By running this pipeline on the on board computer, we are able to process the collected hyperspectral data cubes in near real time.
@@
 
-The final data set that combined observations from each of the three separate collections contains more than 120,000 individual records.
-The collection on 11-23-2020 covered the largest spatial extent across the pond, however, due to flight time constraints resulting from the payload size, imagery from adjacent flight tracks did not overlap, resulting in slight gaps.
-The collections on 12-09-2020 and 12-10-2020 were adjusted to reduce this gap, resulting in a more uniform coverage over a smaller spatial extent.
+The final data set of combined observations from each of the three separate collections contains more than 120,000 individual records.
+Based on the size of the UAV payload and available battery capacity, the collection on 11-23-2020 was chosen to cover the broadest possible area resulting in small horizontal gaps between flight tracks.
+The collections on 12-09-2020 and 12-10-2020 were designed to complement this collection by sampling a smaller spatial extent with uniform coverage.
 
@@
 The performance of the model is identified by the $R^2$, RMSE, and MAE out-of-fold estimates (mean $\pm$ standard deviation) of the final hyperparameter optimized model in the training set with the target variables ranked in descending order by the $R^2$ value and separated by sensor type (physical variables, ions, biochemical variables, and chemical variables).
+The final hyperparameter values for each model are listed in Table~\ref{tab:hyperparameters} in Appendix~\ref{Model Hyperparameters}.
 The small variation in values across folds confirms that the reported performance is independent of how the training set was sampled.
@@
 
-\begin{table}[t!]
+\begin{table}[b!]
   \caption{Summary of fitting statistics for each target measurement.
@@
 \centering
+\vspace{-0.3in}
 \includegraphics[width=\columnwidth]{paper/figures/results/maps/physical.pdf}
@@
 \centering
+\vspace{-0.3in}
 \includegraphics[width=\columnwidth]{paper/figures/results/maps/biochemical.pdf}
+\vspace{-0.2in}
 \caption{Maps generated by applying the trained biochemical models to the data cubes collected on 11-23.
@@
 \centering
+\vspace{-0.3in}
 \includegraphics[width=\columnwidth]{paper/figures/results/maps/chemical.pdf}
@@
 }
+
+Much effort has recently been spent on the curation of comprehensive datasets combining water quality records with decades of satellite imagery to enable the development of new methods for monitoring water quality.
+For example, Aurin et al.
+curated over 30 years of oceanographic field campaign data with associated coincident satellite imagery \cite{aurin2018remote}.
+Similarly, Ross et al.
+have combined more than 600,000 records of dissolved organic carbon, chlorophyll-a and other variables of water quality together with Landsat historical reflectance data for the period 1984--2019 \cite{ross2019aquasat}.
 
@@
 \begin{table}[H] 
-\caption{Hyperparameter values for the final models.\label{tab5}}
+\caption{Final hyperparameter values for each target model.
+The number of trees and sampling ratio were optimized using a random search.
+The maximum tree depth was fixed to 20 to limit overfitting and control the size of the final model.
+The number of sub-features was set to the square root of the total number of features and the minimum samples per leaf and minimum samples per split were left to their default values.
+\label{tab:hyperparameters}}
 \newcolumntype{C}{>{\centering\arraybackslash}X}
@@
 \toprule
-\textbf{Target}	& \textbf{Number of Trees}	& \textbf{Sampling Ratio} & \textbf{Maximum tree depth} & \textbf{Number of Subfeatures} & \textbf{Minimum samples per leaf} & \textbf{Minimum samples per split}\\
+\textbf{Target}	& \textbf{Number of Trees}	& \textbf{Sampling Ratio} & \textbf{Maximum Tree Depth} & \textbf{Number of Sub-features} & \textbf{Minimum Samples Per Leaf} & \textbf{Minimum Samples Per Split}\\
 \midrule
@@
 $\mathrm{Na^+}$ & 153 & 0.979 & 20 & 5 & 1 & 2\\
-Blue-Green Algae (Phycoerythrin) & 153 & 0.979 & 20 & 5 & 1 & 2\\
+%Blue-Green Algae (Phycoerythrin) & 153 & 0.979 & 20 & 5 & 1 & 2\\
+Phycoerythrin & 153 & 0.979 & 20 & 5 & 1 & 2\\
 CDOM & 153 & 0.979 & 20 & 5 & 1 & 2\\
 Chlorophyll A & 153 & 0.979 & 20 & 5 & 1 & 2\\
-Blue-Green Algae (Phycocyanin) & 153 & 0.979 & 20 & 5 & 1 & 2\\
+%Blue-Green Algae (Phycocyanin) & 153 & 0.979 & 20 & 5 & 1 & 2\\
+Phycocyanin & 153 & 0.979 & 20 & 5 & 1 & 2\\
 Crude Oil & 153 & 0.979 & 20 & 5 & 1 & 2\\

### 2024-02-25 paper/paper.tex
updated manuscript to address reviewers' comments

@@
 Inland waters pose a unique challenge for water quality monitoring by remote sensing techniques due to their complicated spectral features and small-scale variability.
-At the same time, collecting the high-quality reference data needed to calibrate remote sensing data products is both time consuming and expensive.
+At the same time, collecting reference data needed to calibrate remote sensing data products is both time consuming and expensive.
 In this study, we present the further development of a robotic team composed of an uncrewed surface vessel (USV) providing in situ reference measurements and an unmanned aerial vehicle (UAV) equipped with a hyperspectral imager.
-Together, this team is able to address the limitations of existing approaches by enabling the simultaneous collection of comprehensive in situ data together with high-resolution hyperspectral imagery.
-We showcase the capabilities of this team using data collected in a north Texas pond during three collections in 2020.
+Together this team is able to address the limitations of existing approaches by enabling the simultaneous collection of hyperspectral imagery with precisely collocated in situ data.
+We showcase the capabilities of this team using data collected in a north Texas pond across three days in 2020.
 Machine learning models for 13 variables are trained using the data set of paired in situ measurements and coincident reflectance spectra.
-These models can successfully estimate physical variables, including temperature, conductivity, pH, and turbidity, as well as the concentrations of blue-green algae, colored dissolved organic matter (CDOM), chlorophyll-a, crude oil, optical brighteners and the ions $\mathrm{Ca}^{2+}$, $\mathrm{Cl}^{-}$, and $\mathrm{Na}^{+}$.
+These models successfully estimate physical variables including temperature, conductivity, pH, and turbidity, as well as the concentrations of blue-green algae, colored dissolved organic matter (CDOM), chlorophyll-a, crude oil, optical brighteners and the ions $\mathrm{Ca}^{2+}$, $\mathrm{Cl}^{-}$, and $\mathrm{Na}^{+}$.
 We extend the training procedure to utilize conformal prediction to estimate 90\% confidence intervals for the output of each trained model.
-Maps generated by applying each trained model to the collected images reveal the small-scale spatial variability within the pond.
-Additionally, the permutation importance computed for each feature of the trained models highlights the spectral features relevant to each water quality variable.
+Maps generated by applying the models to the collected images reveal small-scale spatial variability within the pond.
+This study highlights the value of combining real-time, in situ measurements together with hyperspectral imaging for the rapid characterization of water composition.
 }
@@
 As a consequence, curating comprehensive datasets can require decades of observations \cite{aurin2018remote, ross2019aquasat}.
-This poses a significant challenge for assessing natural and anthropogenic changes to water composition in real time.
+This poses a significant challenge for assessing natural and anthropogenic changes to water composition in real time, for example, during oil spills \cite{fingas2017review}.
 
-Where datasets have been compiled, many studies have shown success extracting optically active water quality variables such as colored dissolved organic matter (CDOM), chlorophyll-a, and suspended sediment concentration by using combinations of spectral bands from from remote sensing satellites \cite{remote-sensing-finland,bonansea2015using}.
-These approaches can be further augmented by machine learning methods which consist of nonlinear and non-parametric models designed to learn representations of functions directly from data \cite{sagan2020monitoring}.
-For example Petersen et al.
-utilized a deep neural network to successfully estimate blue-green algae, chlorophyal-a, CDOM, as well as the optically in-active
+Where datasets have been compiled, many studies have shown success extracting optically active water quality variables such as colored dissolved organic matter (CDOM), chlorophyll-a, and suspended sediment concentrations by using combinations of spectral bands from from remote sensing satellites \cite{remote-sensing-finland,bonansea2015using}.
+These approaches can be further augmented by machine learning methods which consist of nonlinear and non-parametric models designed to learn representations of functions directly from data \cite{lary2010artificial}.
+For example, Petersen et al.
+utilized a deep neural network to successfully estimate blue-green algae, chlorophyl-a, CDOM, dissolved oxygen, specific conductance, and turbidity from a fused dataset of Landsat-8 and Sentinel-2 imagery \cite{peterson2020deep}.
+Other methods such as support vector machines and decision trees have also been successfully applied to retrieve water quality parameters from remote sensing imagery \cite{belgiu2016random,sagan2020monitoring}.
+However, the low spatial and spectral resolution of available multiband remote sensing satellites makes it difficult to analyze inland waters with small spatial features and complicated spectral signatures.
 
-which are often related indirectly to optically active variables.
+Advances in multispectral and hyperspectral imaging technology have led to a considerable reduction in size making it possible to incorporate these cameras into the payload of autonomous aerial vehicles (UAVs) such as quadcopters, hexacopters, and other drones \cite{hruska2012radiometric}.
+Flying at low altitudes enables the collection of centimeter scale imagery whilst limiting the need for complicated atmospheric corrections to account for scattering by atmospheric aerosols and gasses \cite{adao2017hyperspectral, banerjee2020uav}.
+Already UAVs equipped with multispectral and hyperspectral imagers are being used in a variety of domains to great effect including biomass estimation, forest management, precision agriculture, and recently, water quality monitoring \cite{adao2017hyperspectral, padua2017uas,arroyo2019implementation,kurihara2020unmanned, ehmann2019monitoring}.
+Despite the superior spectral and spatial resolution enabled by UAV platforms, these improvements alone do not address the limited spatial coverage of in situ reference data used for associated water composition retrieval.
+For instance, Lu et al.
+used a UAV-born hyperspectral imager to develop machine learning models for the inversion of chlorophyl-a and suspended solids using samples from 33 fixed locations \cite{lu2021retrieval}.
+Similarly, Zhang et al utilized a UAV equipped with a hyperspectral imager to estimate water quality parameters by collecting imagery coincident with samples taken from 18 sampling sites \cite{zhang2022selection}.
+In both of these examples, the collection of in situ reference data remains the key challenge for the application of UAV systems to water quality quantification.
 
-which  \cite{sagan2020monitoring, peterson2020deep}
+To address this gap and enable comprehensive, real-time evaluation of water composition, we have developed a robotic team comprised of an autonomous uncrewed surface vessel (USV) equipped with a collection of reference grade instruments together with a UAV carrying a hyperspectral imager.
+By incorporating reference instruments on a maneuverable USV platform, we are able to rapidly collect large volumes of water quality data for a comprehensive suite of physical, biochemical, and chemical variables precisely collocated with spectra captured by the UAV.
+Critically, the USV enables the collection of reference data with significantly improved spatial resolution compared to other approaches.
+In our previous work, we introduced this paradigm and described how in situ measurements collected by the USV can be used to provide the ground-truth data for machine learning models which map reflectance spectra captured by the hyperspectral imager to the desired water quality variables \cite{robotTeam1}.
 
-can augment traditional approaches using reflectance band ratios to enable estimation of water quality variables and perform water quality classification \cite{schiller1999neural, brown2008neural, lary2010artificial, feng2015urban,belgiu2016random}.
-
-However, the low spatial and spectral resolution of available multiband remote sensing satellites makes it difficult to analyze inland waters with small spatial features and complicated spectral signatures.
-Furthermore, the long return times of these satellites limit their use for real-time monitoring, for example, during oil spills \cite{fingas2017review}.
-
-Advances in multispectral and hyperspectral imaging technology have considerably reduced their size, making it possible to incorporate these cameras into the payload of autonomous aerial vehicles (UAVs) such as quadcopters, hexacopters, and other drones \cite{hruska2012radiometric}.
-
-Bringing the imaging technology closer to the ground enables UAVs to address the spectral, spatial, and temporal shortcomings of remote sensing satellites.
-
-Controlling altitude during flight, UAVs can produce imagery with pixels at the centimeter scale and limit the need for complicated atmospheric corrections to account for scattering by atmospheric aerosols and gases \cite{adao2017hyperspectral,banerjee2020uav}.
-Already, UAVs equipped with multispectral and hyperspectral imagers are being used in a variety of domains to great effect, including biomass estimation, forest management, precision agriculture, and now water quality monitoring \cite{adao2017hyperspectral, padua2017uas,arroyo2019implementation,kurihara2020unmanned,ehmann2019monitoring, lu2021retrieval}.
-Despite the increased spectral and spatial resolution afforded by UAV platforms, these improvements alone cannot address the limited spatial resolution of in situ reference data.
-
-To address this gap and enable comprehensive real-time water quality \textcolor{red}{detection}, we have developed a robotic team composed of an autonomous uncrewed surface vessel (USV) equipped with a collection of reference grade instruments together with a UAV carrying a hyperspectral imager \cite{robotTeam1}.
-By incorporating these reference instruments on a maneuverable USV platform, we are able to rapidly collect large volumes of water quality data for a variety of physical, biochemical, and chemical variables.
-Critically, the USV enables the collection of reference data with significantly improved spatial resolution compared to other approaches.
-These in situ measurements then provide the ground-truth data used to train machine learning models which map reflectance spectra captured by the hyperspectral imager to the desired water quality variables.
-
-In this study, we expand on our previous work by demonstrating the capabilities of this coordinated robot team using data collected at a pond in North Texas over three separate days in 2020.
-Specifically, we show the ability to accurately predict physical variables such as temperature, conductivity, pH, and turbidity, as well as biochemical constituents, including blue-green algae pigments, CDOM, and chlorophyll-a, in addition to concentrations of crude oils, optical brighteners, and a variety of ions.
-In addition, the considerable size of the collected data set allows us to quantify the uncertainty in the resulting machine learning models by using conformal prediction techniques.
-This methodology addresses the shortcomings of existing approaches by facilitating rapid, real-time data collection coupled with on-board hyperspectral image processing and machine learning model deployment with uncertainty quantification.
-The resulting models are small enough to be deployed on board the UAV to enable real-time streaming of data products to the ground.
-This approach drastically reduces the time from data collection to insight.
-
-\textcolor{red}{The primary goal of this study is to demonstrate the capabilities of a coordinated robotic team combining in situ sensing together with hyperspectral imaging for the rapid characterization of water composition.
-Specifically, we seek to address the primary challenge of acquiring remote sensing data products coincident with reference measurements that are critical for the retrieval of water composition and water quality parameters.
-By bringing together
-- there are three key goals in this study: The first is to demonstrate the variety of water quality and composition variables that can be predicted from our collected hypserspectral imager.
-The second is to demonstrate that hyperspectral imagery from multiple observations can by combined despite variability in lighting conditions, and the third is to introduce a method for uncertainty quantification which is crucial for the evaluation of model predictions.
-}
+The main objective of this study is to expand on our previous work in three new ways: The first is to explore the breadth of water quality variables that can be inferred from collected hyperspectral imagery.
+With the goal of comprehensive measurement in mind, we demonstrate the ability to accurately predict physical variables such as temperature, conductivity, pH, and turbidity, as well as biochemical constituents including blue-green algae pigments, CDOM, and chlorophyll-a, in addition to concentrations of crude oils, optical brighteners, and a variety of ions.
+The second addition is to demonstrate that observations from separate collections can effectively be combined by carefully accounting for variability in the viewing and illumination geometries of the scene.
+Finally, we expand our machine learning approach to take advantage of the considerable volume of collected data in order to determine reliable confidence intervals for each predicted parameter using conformal prediction.
 
@@
 
-\textcolor{red}{Should we add something here about non-optically active substances?}
-\textcolor{blue}{Good idea if you have something}
+The inclusion of optically inactive variables such as conductivity, pH, and ion concentrations was motivated by a desire to be comprehensive.
+Multiple studies have classified inland water bodies according to their ionic compositions \cite{piper1944graphic, dordoni2023preliminary}.
+Other research indicates that the structure of dissolved organic matter is affected by changes in pH and cation concentration\cite{pace2012ph}.
+Therefore changes in physical parameters and ionic content can be expected to be related to the observed distribution of optically active variables in the water.
+It is therefore reasonable to expect that these parameters may be estimated from hyperspectral images at a given site.
 
@@
 For each of the 13 target variables listed in Table~\ref{tab:sensors}, the data was randomly partitioned into a 90:10 training/testing split.
-To model the data, we chose to use the Random Forest Regressor (RFR) as implemented in the Machine Learning Framework for Julia package,  MLJ \cite{MLJ1}.
+To model the data, we chose to use the Random Forest Regressor (RFR) as implemented in the Machine Learning Framework for Julia package,  MLJ \cite{ben_sadeghi_2022_7359268, MLJ1}.
 Random forests are an ensembling technique based on bagged predictions of individual decision tree regressors trained using the classification and regression trees (CART) algorithm.
@@
 
-\begin{figure}[p]
-\centering
-\includegraphics[width=\columnwidth]{paper/figures/results/fits/physical-fitres.png}
-\caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the physical variables measured by the USV.\label{fig:physical-fit}}
-\end{figure}
-
 The permutation importance of the top 25 features for each of the models of the physical variables is shown in Figure~\ref{fig:physical-fi}.
@@
 
-\begin{figure}[t!]
+By applying the trained models to the full hyperspectral data cubes, we can produce maps of the distribution of the target variables as in Figure~\ref{fig:map-physical}.
+Here we have chosen to show the map produced from the imagery collected during the 11-23 collection period, as they showcase the largest spatial extent.
+The temperature map shows lower values near the shore, which is to be expected as the air temperature was below the water temperature.
+The temperature, conductivity, and pH maps all show a distinction between the main body of water and the alcove to the east, which receives little flow from the main body.
+The turbidity map confirms that the water is largely clear, with elevated levels near the shore.
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{paper/figures/results/fits/physical-fitres.png}
+\caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the physical variables measured by the USV.\label{fig:physical-fit}}
+\end{figure}
+
+\begin{figure}
 \centering
@@
 
-By applying the trained models to the full hyperspectral data cubes, we can produce maps of the distribution of the target variables as in Figure~\ref{fig:map-physical}.
-Here we have chosen to show the map produced from the imagery collected during the 11-23 collection period, as they showcase the largest spatial extent.
-The temperature map shows lower values near the shore, which is to be expected as the air temperature was below the water temperature.
-The temperature, conductivity, and pH maps all show a distinction between the main body of water and the alcove to the east, which receives little flow from the main body.
-The turbidity map confirms that the water is largely clear, with elevated levels near the shore.
-
-\begin{figure}[t!]
+\begin{figure}
 \centering
@@
 
+The permutation importance ranking for the top 25 features of each of the ion models is shown in Figure~\ref{fig:ions-fi}.
+Here, we see that all three models depend on the solar illumination and viewing geometries as well as the total downwelling intensity and the total pixel intensity measured at the hyperspectral imager.
+All three models utilize a combination of spectral indices that combine green, red, and infrared reflectance bins.
+The $\textrm{Ca}^{+}$ and $\textrm{Cl}^{-}$ models depend on specific red wavelengths of 740 to 769 nm.
+$\textrm{Cl}^{-}$ and $\textrm{Na}^{+}$ also depend on green and yellow reflectance bins of 541 to 589 nanometers.
+
+The maps produced by applying the fitted models to the hyperspectral data cubes for 11-23 are shown in Figure~\ref{fig:map-ions}.
+Both positive ions $\mathrm{Ca}^{2+}$ and $\mathrm{Na}^{+}$ show high concentrations in the northwest portion of the pond with lower values in the alcove on the eastern side.
+Positive ion concentrations also appear to decrease near the shore.
+The negative ion $\mathrm{Cl}^{-}$ shows the opposite distribution with larger values in the alcove to the east and lowest values on the western side of the pond.
+The $\mathrm{Cl}^{-}$ ion concentration also appears to increase near the shore.
+
 \begin{figure}
@@
 \end{figure}
-
-The permutation importance ranking for the top 25 features of each of the ion models is shown in Figure~\ref{fig:ions-fi}.
-Here, we see that all three models depend on the solar illumination and viewing geometries as well as the total downwelling intensity and the total pixel intensity measured at the hyperspectral imager.
-All three models utilize a combination of spectral indices that combine green, red, and infrared reflectance bins.
-The $\textrm{Ca}^{+}$ and $\textrm{Cl}^{-}$ models depend on specific red wavelengths of 740 to 769 nm.
-$\textrm{Cl}^{-}$ and $\textrm{Na}^{+}$ also depend on green and yellow reflectance bins of 541 to 589 nanometers.
 
@@
 
-The maps produced by applying the fitted models to the hyperspectral data cubes for 11-23 are shown in Figure~\ref{fig:map-ions}.
-Both positive ions $\mathrm{Ca}^{2+}$ and $\mathrm{Na}^{+}$ show high concentrations in the northwest portion of the pond with lower values in the alcove on the eastern side.
-Positive ion concentrations also appear to decrease near the shore.
-The negative ion $\mathrm{Cl}^{-}$ shows the opposite distribution with larger values in the alcove to the east and lowest values on the western side of the pond.
-The $\mathrm{Cl}^{-}$ ion concentration also appears to increase near the shore.
-
 \begin{figure}
@@
 \end{figure}
+
+\newpage
 
@@
 
+The permutation importance ranking of the top 25 features of each biochemical model is shown in Figure~\ref{fig:biochem-fi}.
+Again, all four models include the solar illumination and viewing geometries amongst their most important features as well as the total downwelling intensity and total pixel intensity at the imager.
+Additionally, all four models include some vegetation indices amongst the top features, which utilize combinations of blue, green, yellow, red, and infrared reflectance bands.
+The phycoerythrin model shows a preference for green reflectance bins from 544 to 556 nm while the phycocyanin model prefers blue and red reflectance bins.
+The CDOM model uses mainly red reflectance values, whereas the chlorophyll-a model includes red, green, and blue reflectance bins.
+
+The maps generated for the 11-23 collection by applying trained biochemical models are shown in Figure~\ref{fig:map-biochem}.
+The three pigments show low concentrations in the body of water with elevated levels near the shore.
+The CDOM distribution shows spatial variability with higher values in the eastern alcove similar to the separation seen in the maps for temperature, conductivity, $\textrm{Ca}^{2+}$, $\textrm{Cl}^{-}$, and $\textrm{Na}^{+}$.
+
 \begin{figure}
@@
 
-The permutation importance ranking of the top 25 features of each biochemical model is shown in Figure~\ref{fig:biochem-fi}.
-Again, all four models include the solar illumination and viewing geometries amongst their most important features as well as the total downwelling intensity and total pixel intensity at the imager.
-Additionally, all four models include some vegetation indices amongst the top features, which utilize combinations of blue, green, yellow, red, and infrared reflectance bands.
-The phycoerythrin model shows a preference for green reflectance bins from 544 to 556 nm while the phycocyanin model prefers blue and red reflectance bins.
-The CDOM model uses mainly red reflectance values, whereas the chlorophyll-a model includes red, green, and blue reflectance bins.
-
 \begin{figure}
@@
 \end{figure}
-
-The maps generated for the 11-23 collection by applying trained biochemical models are shown in Figure~\ref{fig:map-biochem}.
-The three pigments show low concentrations in the body of water with elevated levels near the shore.
-The CDOM distribution shows spatial variability with higher values in the eastern alcove similar to the separation seen in the maps for temperature, conductivity, $\textrm{Ca}^{2+}$, $\textrm{Cl}^{-}$, and $\textrm{Na}^{+}$.
 
@@
 
+The ranked permutation importances of the top 25 features for each model are shown in Figure~\ref{fig:chemicals-fi}.
+Both models rank the solar illumination and viewing geometries together with the total downwelling intensity and total pixel intensities amongst the top features.
+Both models include a combination of spectral indices using blue, green, yellow, red, and infrared reflectance bins.
+Additionally, the CO model includes green-yellow reflectances from 539 to 589 nm as well as red reflectances from 749 to 769 nm.
+The OB model includes a yellow reflectance at 584.6 nm and red reflectance bins.
+
+The maps generated by applying the CO and OB models to the 11-23 data cubes are shown in Figure ~\ref{fig:map-chem}.
+Both models show a distinct spatial distribution with elevated values in the eastern alcove of the pond similar to the CDOM distribution in Figure~\ref{fig:map-biochem}
+
 \begin{figure}
@@
 \end{figure}
-
-The ranked permutation importances of the top 25 features for each model are shown in Figure~\ref{fig:chemicals-fi}.
-Both models rank the solar illumination and viewing geometries together with the total downwelling intensity and total pixel intensities amongst the top features.
-Both models include a combination of spectral indices using blue, green, yellow, red, and infrared reflectance bins.
-Additionally, the CO model includes green-yellow reflectances from 539 to 589 nm as well as red reflectances from 749 to 769 nm.
-The OB model includes a yellow reflectance at 584.6 nm and red reflectance bins.
 
@@
 \end{figure}
-
-The maps generated by applying the CO and OB models to the 11-23 data cubes are shown in Figure ~\ref{fig:map-chem}.
-Both models show a distinct spatial distribution with elevated values in the eastern alcove of the pond similar to the CDOM distribution in Figure~\ref{fig:map-biochem}
 
@@
 
-% \cite{cohen2004landsat, melesse2007remote, allison2016airborne, joyce2009review, robert2017analysis}
-
-\textcolor{red}{test
-- We need to discuss how we are building on the original paper. 
-- The key advancements are a demonstration of more optically active substances that can be successfully modelled from the HSIs 
-- The ability to model physical parameters that are not considered to be optically active in the sense that they have uniquelly identifiable absorption features (ions, etc...) 
-- The ability to successfully combine mutliple observations
-    - This is particularly noteworthy as there was significant variation in total downwelling intensity between the separate collections which could introduce bias between reflectance values measured on separate days
-    - Key result is that by incorporating the relevant information (solar illumination geometry and viewing geometry) we are able to successfully account for these biases and produce models that are consistent between multiple observation periods
-- Estimation of uncertainty using conformal prediction
-- The trained models are small enough so as to be deployable on the UAV for real time processing
-
-- part one: overview of method and description of how we are able to collect comparable data quantities which traditionally require decades i.e.
-Aurin et al.
-We can also mention how existing approaches using HSI on UAV platforms suffer from a lack of comprehensive in-situ data needed to reliably calibrate the (machine learning) data products.
-By creating a coordinated team with both autonomous in situ data collection and rapid HSI acquisition by a UAV we effectively bridge this gap by enabling the precise collection of collocated data points.
-- part two: We extend our previous work in three key ways: first we model significantly more target variables, second we confirm that it is possible to utilize imagery from multiple collections despite the impact of light variability so long as we appropriately augment the data to include illumination and viewing geometry, third we implemented a method for robust uncertainty quantification by using conformal prediction so that we can evaluate the certainty of our trained models.
-- finally we can comment on limitations, extensions, and future work
-    - Limitation: total area surveyed is determined by battery life (suggestion --> multiple drones) 
-    - Limitation: predictions of trained tree-based models are litmied by the range of available data.
-To extend the model to be sensitive across a broader range of values/concentrations, we need to collect more training data.
-However we have demonstrated that data from disparate observations can be combined despite the limitations of lighting variability.
-Indeed it is preciesly the fact that we are interested in the water composition and not the absolute reflectance values themselves that makes this possible because so long as we include enough descriptive variables which capture the lighting dynamics, we can account for differences in ambient lighting conditions between observations.
-}
-
-Much effort has recently been spent on the curation of comprehensive datasets combining water quality records with decades of satellite imagery to enable the development of new methods for monitoring water quality.
+In recent years, much effort has been spent on the curation of comprehensive datasets combining water quality records with decades of satellite imagery to enable the development of new methods for retrieving water quality parameters.
 For example, Aurin et al.
@@
 Similarly, Ross et al.
-have combined more than 600,000 records of dissolved organic carbon, chlorophyll-a and other variables of water quality together with Landsat historical reflectance data for the period 1984--2019 \cite{ross2019aquasat}.
+combined more than 600,000 records of dissolved organic carbon, chlorophyll-a and other water quality variables with historical Landsat reflectance data for the period 1984--2019 \cite{ross2019aquasat}.
+The sensing paradigm we have demonstrated here was able to rapidly collect comparable volumes of data within the span of just three observation periods.
+Therefore, despite the fact that individual UAV tracks cover far less spatial extent than remote sensing imagery, the ability to collect coordinated in situ measurements together with detailed hyperspectral images offers a significant improvement over these traditional approaches.
+With a coordinated robot team, one does not need to rely on infrequent satellite overpasses when planning data collection.
+Further, the time offset between reference measurements and remote sensing is significantly reduced from days to minutes.
 
-In this paper, we have validated the methodology introduced in our previous work\cite{robotTeam1}. Specifically, we demonstrate that by using an autonomous team of sensing sentinels, we can
-\begin{enumerate}
-    \item Rapidly acquire large volumes in in-situ reference data points for a variety of relevant water quality variables including physical measurements such as temperature, pH, and conductivity as well as ion concentrations, chemicals such as crude oil, and relevant biochemical variables such as blue-green algae pigments, chlorophyll-a, and CDOM.
-    \item Simultaneously collect hyperspectral remote sensing imagery using an UAV.
-    \item Rapidly process captured imagery into georectified reflectance data cubes.
-    \item Train machine learning models to map captured reflectance spectra to water quality variables measured by reference sensors.
-    \item Apply trained models to rapidly map large bodies of water and identify areas of interest.
-\end{enumerate}
-Additionally, we have demonstrated that we can extend this methodology in two new ways.
-First, we have shown that it is possible to combine data sets from separate collection periods and successfully train models using \textit{all} of the records despite variability in incident lighting conditions that affects the assumptions made in the reflectance conversion of captured hyperspectral data cubes.
-Second, we have shown that by leveraging the large amount of data collected, we can simultaneously train machine learning models and quantify their prediction uncertainties by utilizing conformal prediction.
+This study is not the first to employ UAVs equipped with multispectral or hyperspectral imagers for the purpose of assessing water composition and quality.
+Indeed there are many such examples focused on assessing optically active and inactive water quality parameters using band ratios and machine learning methods \cite{vogt2016near,lu2021retrieval, zhang2022selection}.
+The key advancement demonstrated by our robot team is the ability to combine UAV-borne hyperspectral imagers together with comprehensive, autonomous in situ sensing for a significant improvement in data volume.
+Removing the need to collect individual samples, often by hand, for the calibration of water quality models dramatically reduces the time required to perform these analyses.
+Furthermore, the USV enables rapid validation of model predictions.
+If a region of water imaged by the UAV predicts elevated levels of a particular water quality parameter, the USV can be provisioned to validate these estimates with its reference sensors.
 
-As Figure~\ref{fig:downwelling-hist} indicates, there is variation in the total downwelling intensity between images collected on the same day \textit{and} between each separate collection period despite acquiring the imagery consistently near solar noon.
+In \cite{robotTeam1}, we introduced this paradigm.
+In this study, we have built on this approach in three new ways.
+First, we have demonstrated the ability to effectively combine observations from disparate collections by augmenting the machine learning models with sufficient features describing the illumination and viewing geometries.
+As Figure~\ref{fig:downwelling-hist} indicates, we observed variation in the total downwelling intensity between images collected on the same day \textit{and} between each separate collection period.
 These within-collection variations are due to a combination of the stability of the UAV (on which the upward facing downwelling irradiance spectrometer is mounted) together with the occasional interference of clouds.
 Moreover, the assumption that the water's surface can be treated as Lambertian is clearly violated when the water is not perfectly still.
-Despite the potential impact of these limitations on the quality of the resulting reflectance data cubes, the smoothness of the maps generated by our models suggests that we have provided sufficient context by including the relevant solar illumination and viewing geometries as additional features in the final data set.
+Despite the potential impact of these limitations on the quality of the resulting reflectance data cubes, the smoothness of the maps generated by our models suggests that we have provided sufficient context by including the relevant solar illumination and viewing angles as additional features in the final data set.
 This fact is reinforced by the position of these variables as the most important features for \textit{each} of the estimated water quality variables.
-As long as we are primarily interested in these values and not the reflectances themselves, we are able to successfully account for these lighting effects.
+As long as we are primarily interested in these values and not the reflectances themselves, we are able to successfully account for these lighting effects when combining data from multiple collections.
+
+The second contribution of this study is to explore the breadth of possible water quality and composition parameters that can be accurately mapped by hyperspectral imagery collected by the UAV.
+The results presented here confirm the ability of the robot team to predict optically active parameters including blue-green algae, chlorophyll-a, CDOM, crude oil, optical brighteners, turbidity, and temperature.
+Additionally, we are also also able to infer the distributions of optically inactive variables including conductivity, pH, and ion concentrations.
+Other studies using multispectral and hyperspectral remote sensing imagery have also estimated optically inactive water quality parameters with the ability to do so stemming from the relationship of these variables to optically active properties of the water \cite{vakili2020determination,guo2021machine,niu2021deep}.
+We note that in our investigation, the models trained for many of these variables often outperformed their optically active counterparts.
+As the abundance of these variables is likely tied to the specific composition and content of the pond, it is unlikely that models trained for these optically inactive variables can generalized to other bodies of water.
+
+The third contribution of this work is the extension of our machine learning approach to include uncertainty quantification via conformal prediction.
+For water quality risk assessment, the trustworthiness of model predictions is of equal or greater importance to the values themselves.
+However, robust uncertainty quantification has historically been challenging for many machine learning models which behave like black boxes.
+By leveraging the large data volume collected by the robot team, we are able to simultaneously train predictive models and evaluate confidence intervals for their predictions.
+As the final column of Table~\ref{tab:fit-results} confirms, the empirical coverage on the holdout testing set provided by the inferred confidence intervals achieves the desired coverage to within 1\%.
+We chose to use a 90\% confidence interval for this study, but this can easily be adapted to suite the needs of a specific application if greater confidence is required.
 
 With respect to the real-time deployment of these models in the field, we note that training a reduced feature model without further hyperparameter optimization takes roughly 1 minute per target variable of interest using the processing computer included on the UAV.
-This means that in principle the necessary training data can be collected by the USV, hyperspectral imagery can be acquired and processed into reflectance data cubes by the UAV, the resulting data sets can be combined to identify coincindent records, and this collection can then be used to train machine learning models and generate maps as in Figure~\ref{fig:map-biochem} all while the investigators are still in the field.
-Analyzing these resulting maps enables areas of interest to be readily pinpointed, as demonstrated by the identification of elevated crude oil, optical brighteners, and CDOM in the eastern alcove of the pond on 11-23.
-Having identified a region of interest, the USV can then be sent to collect additional reference data and confirm the presence of any spill, bloom, or other source.
+This means that, in principle, training data can be collected by the USV, imagery can be acquired and processed by the UAV, the resulting data sets can be combined to identify coincident records, and this collection can then be used to train machine learning models and generate maps all while the investigators are still in the field.
+Analyzing these resulting maps enables areas of interest to be readily pinpointed, as demonstrated by the identification of slightly elevated crude oil, optical brighteners, and CDOM in the eastern alcove of the pond on 11-23.
 
-Beyond the potential applications of this robot team for direct water quality monitoring, the combination of reference instruments together with easily co-located hyperspectral imagery provides fertile ground for the development of new spectral indices targeted towards specific water quality variables.
-In this paper, we have shown how permutation importance ranking for trained machine learning models enables a straightforward interpretation of the relative value of each reflectance bin to the final model predictions.
-In future work, we plan to utilize this information to construct new combinations of spectral bands which can be readily extended for use remote sensing platforms equipped with hyperspectral imagers.
-\textcolor{red}{The recently launched Environmental Mapping and Analysis Program (EnMAP) is one such example which includes over 91 spectral bands in the VNIR that overlap with our hyperspectral imager \cite{Storch2023TheEI}.}
+Finally, we note that the high spectral resolution of the UAV imagery together with the ability to collect precisely co-located reference measurements provides a fertile ground for the development of new spectral indices targeted towards water quality variables.
+In this paper, we have shown that permutation importance ranking for trained machine learning models enables a straightforward interpretation of the relative value of each reflectance bin to the final model predictions.
+In future work, we plan to utilize this information to identify combinations of spectral bands which can be applied to remote sensing imagery captured by satellites equipped with hyperspectral imagers.
+The recently launched Environmental Mapping and Analysis Program (EnMAP) is one such example which includes over 91 spectral bands in the VNIR that overlap with those of our hyperspectral imager \cite{Storch2023TheEI}.
 
@@
 
-In this study, we address the two key limitations of current remote sensing approaches to characterizing water quality, namely the limited spatial, spectral, and temporal resolution provided by existing satellite platforms and the lack of comprehensive, highly resolved in-situ data needed to validate remote sensing data products.
-By equipping an autonomous USV with a suite of reference sensors, we can collect significantly more data than existing approaches that rely on the collection of individual samples for lab analysis or are constrained to continuous sensing at fixed sites.
-Utilizing an autonomous UAV equipped with a hyperspectral imager in tandem with the USV allows us to rapidly generate aligned datasets which can be used to train machine learning models which map measured reflectance spectra to the desired water quality variables of interest.
-Furthermore, by virtue of collecting large training datasets, we are able to simultaneously estimate the uncertainty of our trained models using conformal prediction.
-This addresses the lack of uncertainty quantification in traditional machine learning approaches.
-Finally, the rapid hyperspectral data cube processing pipeline employed on board the UAV makes it possible to deploy these trained models in order to rapidly generate maps of the desired target variables across entire bodies of water.
-The rapid turnaround time from data collection to model deployment is critical for real-time water quality assessment and threat identification.
+In this study, we address two key limitations of current remote sensing approaches to characterizing water quality, namely the limited spatial, spectral, and temporal resolution provided by existing satellite platforms and the lack of comprehensive in-situ measurements needed to validate remote sensing data products.
+By equipping an autonomous USV with a suite of reference sensors, we rapidly collect significantly more data than existing approaches which rely on the collection of individual samples for lab analysis or are constrained to continuous sensing at fixed sites.
+Utilizing an autonomous UAV equipped with a hyperspectral imager in tandem with the USV allows us to quickly generate aligned datasets which are used to train machine learning models mapping measured reflectance spectra to the desired water quality variables.
+By virtue of this increased data volume, we are able to simultaneously estimate the uncertainty of our models by using conformal prediction.
+Finally, the hyperspectral data cube processing pipeline employed on board the UAV makes it possible to deploy these trained models to swiftly generate maps of the target variables across bodies of water.
+The rapid turnaround time from data collection to model deployment is critical for real-time water quality evaluation and risk assessment.
 
@@
 Temperature & 153 & 0.979 & 20 & 5 & 1 & 2 \\
-Conductivity & 153 & 0.979 & 20 & 5 & 1 & 2\\
-pH & 153 & 0.979 & 20 & 5 & 1 & 2\\
-Turbidity & 153 & 0.979 & 20 & 5 & 1 & 2\\
-$\mathrm{Ca}^{2+}$ & 153 & 0.979 & 20 & 5 & 1 & 2\\
-$\mathrm{Cl^-}$ & 153 & 0.979 & 20 & 5 & 1 & 2\\
-$\mathrm{Na^+}$ & 153 & 0.979 & 20 & 5 & 1 & 2\\
+Conductivity & 154 & 0.992 & 20 & 5 & 1 & 2\\
+pH & 103 & 0.972 & 20 & 5 & 1 & 2\\
+Turbidity & 158 & 0.998 & 20 & 5 & 1 & 2\\
+$\mathrm{Ca}^{2+}$ & 172 & 0.984 & 20 & 5 & 1 & 2\\
+$\mathrm{Cl^-}$ & 110 & 0.999 & 20 & 5 & 1 & 2\\
+$\mathrm{Na^+}$ & 103 & 0.972 & 20 & 5 & 1 & 2\\
 %Blue-Green Algae (Phycoerythrin) & 153 & 0.979 & 20 & 5 & 1 & 2\\
-Phycoerythrin & 153 & 0.979 & 20 & 5 & 1 & 2\\
-CDOM & 153 & 0.979 & 20 & 5 & 1 & 2\\
-Chlorophyll A & 153 & 0.979 & 20 & 5 & 1 & 2\\
+Phycoerythrin & 158 & 0.998 & 20 & 5 & 1 & 2\\
+CDOM & 157 & 0.982 & 20 & 5 & 1 & 2\\
+Chlorophyll A & 158 & 0.998 & 20 & 5 & 1 & 2\\
 %Blue-Green Algae (Phycocyanin) & 153 & 0.979 & 20 & 5 & 1 & 2\\
-Phycocyanin & 153 & 0.979 & 20 & 5 & 1 & 2\\
-Crude Oil & 153 & 0.979 & 20 & 5 & 1 & 2\\
-Optical Brighteners & 153 & 0.979 & 20 & 5 & 1 & 2\\
+Phycocyanin & 142 & 0.995 & 20 & 5 & 1 & 2\\
+Crude Oil & 154 & 0.992 & 20 & 5 & 1 & 2\\
+Optical Brighteners & 157 & 0.982 & 20 & 5 & 1 & 2\\
 \bottomrule

### 2024-03-04 paper/paper.tex
updated text with the minor revisions from round 2 of review

@@
 At the same time, collecting reference data needed to calibrate remote sensing data products is both time consuming and expensive.
-In this study, we present the further development of a robotic team composed of an uncrewed surface vessel (USV) providing in situ reference measurements and an unmanned aerial vehicle (UAV) equipped with a hyperspectral imager.
-Together this team is able to address the limitations of existing approaches by enabling the simultaneous collection of hyperspectral imagery with precisely collocated in situ data.
-We showcase the capabilities of this team using data collected in a north Texas pond across three days in 2020.
-Machine learning models for 13 variables are trained using the data set of paired in situ measurements and coincident reflectance spectra.
+In this study, we present the further development of a robotic team composed of an uncrewed surface vessel (USV) providing in-situ reference measurements and an unmanned aerial vehicle (UAV) equipped with a hyperspectral imager.
+Together this team is able to address the limitations of existing approaches by enabling the simultaneous collection of hyperspectral imagery with precisely collocated in-situ data.
+We showcase the capabilities of this team using data collected in a North Texas pond across three days in 2020.
+Machine learning models for 13 variables are trained using the data set of paired in-situ measurements and coincident reflectance spectra.
 These models successfully estimate physical variables including temperature, conductivity, pH, and turbidity, as well as the concentrations of blue-green algae, colored dissolved organic matter (CDOM), chlorophyll-a, crude oil, optical brighteners and the ions $\mathrm{Ca}^{2+}$, $\mathrm{Cl}^{-}$, and $\mathrm{Na}^{+}$.
@@
 Maps generated by applying the models to the collected images reveal small-scale spatial variability within the pond.
-This study highlights the value of combining real-time, in situ measurements together with hyperspectral imaging for the rapid characterization of water composition.
+This study highlights the value of combining real-time, in-situ measurements together with hyperspectral imaging for the rapid characterization of water composition.
 }
@@
 For decades, remote sensing imagery have been used for environmental monitoring with applications ranging from resource mapping, land type classification, and urban growth assessment to wildfire monitoring, natural disaster tracking, and many more \cite{melesse2007remote, joyce2009review}.
-Among these applications, the retrieval of water quality variables from remote sensing imagery remains challenging due to the difficulty of obtaining in situ reference data coincident with available satellite imagery.
+Among these applications, the retrieval of water quality variables from remote sensing imagery remains challenging due to the difficulty of obtaining in-situ reference data coincident with available satellite imagery.
 Traditional approaches to obtain these data have relied on serendipitous satellite passes over fixed sensing sites or sensor-equipped vessels.
@@
 
-Where datasets have been compiled, many studies have shown success extracting optically active water quality variables such as colored dissolved organic matter (CDOM), chlorophyll-a, and suspended sediment concentrations by using combinations of spectral bands from from remote sensing satellites \cite{remote-sensing-finland,bonansea2015using}.
+Where remote sensing imagery and in-situ measurements have been combined, studies have demonstrated successful extraction of optically active water quality variables such as colored dissolved organic matter (CDOM), chlorophyll-a, and suspended sediment concentrations by using combinations of spectral bands \cite{remote-sensing-finland,bonansea2015using, absalon2023detection}.
 These approaches can be further augmented by machine learning methods which consist of nonlinear and non-parametric models designed to learn representations of functions directly from data \cite{lary2010artificial}.
@@
 
-Advances in multispectral and hyperspectral imaging technology have led to a considerable reduction in size making it possible to incorporate these cameras into the payload of autonomous aerial vehicles (UAVs) such as quadcopters, hexacopters, and other drones \cite{hruska2012radiometric}.
+Advances in multispectral and hyperspectral imaging technology have led to a considerable reduction in size making it possible to incorporate these cameras into the payload of autonomous aerial vehicles (UAVs) \cite{hruska2012radiometric}.
 Flying at low altitudes enables the collection of centimeter scale imagery whilst limiting the need for complicated atmospheric corrections to account for scattering by atmospheric aerosols and gasses \cite{adao2017hyperspectral, banerjee2020uav}.
 Already UAVs equipped with multispectral and hyperspectral imagers are being used in a variety of domains to great effect including biomass estimation, forest management, precision agriculture, and recently, water quality monitoring \cite{adao2017hyperspectral, padua2017uas,arroyo2019implementation,kurihara2020unmanned, ehmann2019monitoring}.
-Despite the superior spectral and spatial resolution enabled by UAV platforms, these improvements alone do not address the limited spatial coverage of in situ reference data used for associated water composition retrieval.
+Despite the superior spectral and spatial resolution enabled by UAV platforms, these improvements alone do not address the limited spatial coverage of in-situ reference data used for associated water composition retrieval.
 For instance, Lu et al.
@@
 Similarly, Zhang et al utilized a UAV equipped with a hyperspectral imager to estimate water quality parameters by collecting imagery coincident with samples taken from 18 sampling sites \cite{zhang2022selection}.
-In both of these examples, the collection of in situ reference data remains the key challenge for the application of UAV systems to water quality quantification.
+In both of these examples, the collection of in-situ reference data remains the key challenge for the application of UAV systems to water quality quantification.
 
@@
 Critically, the USV enables the collection of reference data with significantly improved spatial resolution compared to other approaches.
-In our previous work, we introduced this paradigm and described how in situ measurements collected by the USV can be used to provide the ground-truth data for machine learning models which map reflectance spectra captured by the hyperspectral imager to the desired water quality variables \cite{robotTeam1}.
+In our previous work, we introduced this paradigm and described how in-situ measurements collected by the USV can be used to provide the ground-truth data for machine learning models which map reflectance spectra captured by the hyperspectral imager to the desired water quality variables \cite{robotTeam1}.
 
@@
 
- The robotic team presented in this study consists of two key sensing sentinels: An uncrewed surface vessel (USV) used to collect in situ reference measurements, and an unmanned aerial vehicle (UAV) for performing rapid, wide-area surveys to gather remote sensing data products.
+ The robotic team presented in this study consists of two key sensing sentinels: An uncrewed surface vessel (USV) used to collect in-situ reference measurements, and an unmanned aerial vehicle (UAV) for performing rapid, wide-area surveys to gather remote sensing data products.
 Both platforms are coordinated using open source QGroundControl software for flight control and mission planning and are equipped with high-accuracy GPS and INS such that all data points collected are uniquely geolocated and time-stamped \cite{qgroundcontrol}.
@@
 
-The USV employed in the robot team is a Maritime Robotics Otter equipped with an in situ sensing payload consisting of a combination of Eureka Manta+40 multiprobes.
+The USV employed in the robot team is a Maritime Robotics Otter equipped with an in-situ sensing payload consisting of a combination of Eureka Manta+40 multiprobes.
 These sensors include fluorometers, ion selective electrodes, and other physical sensors and are mounted on the underside of boat as illustrated in Figure~\ref{fig:boat-components}.
@@
 For these collections, a resolution of 10 cm was utilized, however, this can be adjusted to optimize the processing time and final resolution for real-time applications.
-Finally, the UTM pixel coordinates obtained are transformed to latitude and longitude for easy comparison with in situ data collected by the USV.
+Finally, the UTM pixel coordinates obtained are transformed to latitude and longitude for easy comparison with in-situ data collected by the USV.
 The final result is a georectified hyperspectral reflectance data cube.
@@
 
-The above processing pipeline was implemented using the Julia programming language, a just-in-time compiled language with native multi-threading support \cite{julia-1}.
+The above processing workflow was implemented using the Julia programming language, a just-in-time compiled language with native multi-threading support \cite{julia-1}.
 By running this pipeline on the on board computer, we are able to process the collected hyperspectral data cubes in near real time.
@@
 
-Data were collected using the robot team at a site in North Texas during three observations on 11-23-2020, 12-09-2020, and 12-10-2020.
-For each collection period, the UAV first completed a broad survey of the pond, capturing multiple hyperspectral data cubes.
-Subsequently, the USV sampled across the pond, collecting in situ reference measurements.
+The robot team was deployed at a private pond ($<0.1$ km$^{2}$) in Montague Texas close to the Oklahoma border for three separate collections on 11-23-2020, 12-09-2020, and 12-10-2020.
+For each acquisition, the UAV first completed a broad survey of the pond, capturing multiple hyperspectral data cubes.
+Subsequently, the USV sampled across the pond, collecting in-situ reference measurements.
 Each of these reference measurements was then collocated with individual pixel spectra, where the USV track overlapped with UAV pixels.
-To account for any time lag in the values measured by the in situ instruments and to account for the USV size in comparison to the data cube's spatial resolution, each in-situ measurement is associated with a 3$\times$3 grid of HSI pixels, that is, a 30 cm $\times$ 30 cm square.
+To account for any time lag in the values measured by the in-situ instruments and to account for the USV size in comparison to the data cube's spatial resolution, each in-situ measurement is associated with a 3$\times$3 grid of HSI pixels, that is, a 30 cm $\times$ 30 cm square.
 These combined data form the tabular data set on which we train regression models; pixel spectra form input features, and each separate USV sensor forms a distinct target variable.
@@
 
-\begin{figure}[t!]
+The variability of incident lighting conditions for each collection is visualized in Figure~\ref{fig:downwelling-hist} where the distribution of the total downwelling intensity measured by the downwelling irradiance spectrometer across all hyperspectral data cubes is visualized.
+Despite performing all UAV flights near solar noon, there was a difference in minimum solar zenith angle between collections due to the time of year.
+Additionally, there was some slight cloudiness during the 12-09 and 12-10 collections.
+
+\begin{figure}[b!]
 \vspace{-0.2in}
@@
 \end{figure}
-
-The variability of incident lighting conditions for each collection is visualized in Figure~\ref{fig:downwelling-hist} where the distribution of the total downwelling intensity measured by the downwelling irradiance spectrometer across all hyperspectral data cubes is visualized.
-Despite performing all UAV flights near solar noon, there was a difference in minimum solar zenith angle between collections due to the time of year.
-Additionally, there was some slight cloudiness during the 12-09 and 12-10 collections.
 
@@
 
-\begin{table}[b!]
+From Table~\ref{tab:fit-results},  we see that the empirical coverage achieved by the inferred confidence interval evaluated in the independent test set is within 1\% of our desired coverage for each target modeled.
+This indicates that the uncertainties obtained by the conformal prediction procedure are reliable, at least within the bounds of the collected data set.
+We also note that in all cases, the inferred model uncertainties are larger than the resolution of the in-situ sensors.
+This lends further credence to the inferred uncertainty estimates as we should not expect to be able to have lower uncertainty than the smallest resolvable difference in reference sensor measurements.
+
+To further examine the differences in model performance between the target variables, we can consider the difference between the RMSE and MAE scores.
+The MAE is less sensitive to outlier impacts than the RMSE, and, as a consequence, any large difference between the two is indicative of impacts due to the distribution of target values.
+Indeed, this is the case for turbidity, for which almost all measurements were below 10 FNU with only a small fraction of observations from a small area near the shore.
+The rest of the models all show a mean perfold RMSE value with size comparable to the mean per-fold MAE.
+
+In the remainder of this section, we compare the models within each target category.
+
+\pagebreak
+
+\begin{table}[hp!]
   \caption{Summary of fitting statistics for each target measurement.
@@
 
-From Table~\ref{tab:fit-results},  we see that the empirical coverage achieved by the inferred confidence interval evaluated in the independent test set is within 1\% of our desired coverage for each target modeled.
-This indicates that the uncertainties obtained by the conformal prediction procedure are reliable, at least within the bounds of the collected data set.
-We also note that in all cases, the inferred model uncertainties are larger than the resolution of the in-situ sensors.
-This lends further credence to the inferred uncertainty estimates as we should not expect to be able to have lower uncertainty than the smallest resolvable difference in reference sensor measurements.
-
-To further examine the differences in model performance between the target variables, we can consider the difference between the RMSE and MAE scores.
-The MAE is less sensitive to outlier impacts than the RMSE, and, as a consequence, any large difference between the two is indicative of impacts due to the distribution of target values.
-Indeed, this is the case for turbidity, for which almost all measurements were below 10 FNU with only a small fraction of observations from a small area near the shore.
-The rest of the models all show a mean perfold RMSE value with size comparable to the mean per-fold MAE.
-
-In the remainder of this section, we compare the models within each target category.
-
 \subsection{Physical Variables}
@@
 
-\begin{figure}
+\begin{figure}[h!]
 \centering
-\includegraphics[width=\columnwidth]{paper/figures/results/fits/physical-fitres.png}
+\includegraphics[width=0.9\columnwidth]{paper/figures/results/fits/physical-fitres.png}
 \caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the physical variables measured by the USV.\label{fig:physical-fit}}
@@
 
-\begin{figure}
+\pagebreak
+
+\begin{figure}[h!]
 \centering
-\vspace{-0.2in}
 \includegraphics[width=\columnwidth]{paper/figures/results/fits/physical-ranking.pdf}
@@
 
-\begin{figure}
+\begin{figure}[h!]
 \centering
-\vspace{-0.3in}
-\includegraphics[width=\columnwidth]{paper/figures/results/maps/physical.pdf}
+\includegraphics[width=0.9\columnwidth]{paper/figures/results/maps/physical.pdf}
 \caption{Maps generated by applying each of the physical variable models to the hyperspectral data cubes collected on 11-23.
@@
 \end{figure}
+
+\pagebreak
 
@@
 The maps generated by applying the CO and OB models to the 11-23 data cubes are shown in Figure ~\ref{fig:map-chem}.
-Both models show a distinct spatial distribution with elevated values in the eastern alcove of the pond similar to the CDOM distribution in Figure~\ref{fig:map-biochem}
+Both models show a distinct spatial distribution with elevated values in the eastern alcove of the pond similar to the CDOM distribution in Figure~\ref{fig:map-biochem}.
 
@@
 The sensing paradigm we have demonstrated here was able to rapidly collect comparable volumes of data within the span of just three observation periods.
-Therefore, despite the fact that individual UAV tracks cover far less spatial extent than remote sensing imagery, the ability to collect coordinated in situ measurements together with detailed hyperspectral images offers a significant improvement over these traditional approaches.
+Therefore, despite the fact that individual UAV tracks cover far less spatial extent than remote sensing imagery, the ability to collect coordinated in-situ measurements together with detailed hyperspectral images offers a significant improvement over these traditional approaches.
 With a coordinated robot team, one does not need to rely on infrequent satellite overpasses when planning data collection.
@@
 This study is not the first to employ UAVs equipped with multispectral or hyperspectral imagers for the purpose of assessing water composition and quality.
-Indeed there are many such examples focused on assessing optically active and inactive water quality parameters using band ratios and machine learning methods \cite{vogt2016near,lu2021retrieval, zhang2022selection}.
-The key advancement demonstrated by our robot team is the ability to combine UAV-borne hyperspectral imagers together with comprehensive, autonomous in situ sensing for a significant improvement in data volume.
-Removing the need to collect individual samples, often by hand, for the calibration of water quality models dramatically reduces the time required to perform these analyses.
-Furthermore, the USV enables rapid validation of model predictions.
-If a region of water imaged by the UAV predicts elevated levels of a particular water quality parameter, the USV can be provisioned to validate these estimates with its reference sensors.
+Indeed there are many such examples focused on inferring optically active and inactive water quality parameters using band ratios and machine learning methods \cite{vogt2016near,lu2021retrieval, zhang2022selection}.
+The key advancement demonstrated by our robot team is the ability to combine UAV-borne hyperspectral imagers together with comprehensive, in-situ sensing for a significant improvement in data volume.
+Purposefully coordinating USV sampling with the flight tracks of the UAV greatly accelerates data collection by removing the need to acquire individual samples for the calibration of water quality models.
+Additionally, the USV facilitates rapid validation of model predictions.
+When a trained model applied to collected hyperspectral imagery suggests elevated levels of a particular water quality parameter, the USV can quickly be provisioned to confirm these estimates with its reference instruments.
 
@@
 
-The third contribution of this work is the extension of our machine learning approach to include uncertainty quantification via conformal prediction.
+The third contribution of this work is the extension of our machine learning approach to enable uncertainty quantification through conformal prediction.
 For water quality risk assessment, the trustworthiness of model predictions is of equal or greater importance to the values themselves.
 However, robust uncertainty quantification has historically been challenging for many machine learning models which behave like black boxes.
+Conformal prediction is an attractive approach to enable model agnostic uncertainty estimation and recently has seen adoption to remote sensing classification tasks such as land-type classification and object identification \cite{valle2023quantifying, zhu2024inductive}.
+In this setting the goal is to produce predictive \textit{sets} guaranteed to contain the correct class label at a predetermined confidence level.
+Nevertheless, conformal prediction works equally well for regression tasks.
 By leveraging the large data volume collected by the robot team, we are able to simultaneously train predictive models and evaluate confidence intervals for their predictions.
@@
 
-With respect to the real-time deployment of these models in the field, we note that training a reduced feature model without further hyperparameter optimization takes roughly 1 minute per target variable of interest using the processing computer included on the UAV.
-This means that, in principle, training data can be collected by the USV, imagery can be acquired and processed by the UAV, the resulting data sets can be combined to identify coincident records, and this collection can then be used to train machine learning models and generate maps all while the investigators are still in the field.
-Analyzing these resulting maps enables areas of interest to be readily pinpointed, as demonstrated by the identification of slightly elevated crude oil, optical brighteners, and CDOM in the eastern alcove of the pond on 11-23.
+Despite the wealth of information provided by the increased resolution of hyperspectral images, their considerable size impedes their \textit{complete} utilization in real-time applications.
+Often much of the available spectral information is discarded in favor of indices like the NDVI which can be quickly computed as images are captured \cite{horstrand2019uav}.
+Utilizing machine learning allows us to take advantage of the full spectrum captured by each pixel while simultaneously reducing the size of the final data product to single band "images" of selected water quality variables.
+We note that training a reduced-feature model without further hyperparameter optimization takes roughly one minute per target variable of interest using the processing computer included on the UAV.
+This means that, in principle, training data can be collected by the USV, imagery can be acquired and processed by the UAV, coincident records can be selected, and the resulting dataset can be used to train machine learning models all while investigators are still in the field.
+Analyzing the maps produced by applying each trained model enables areas of interest to be readily pinpointed, as demonstrated by the identification of slightly elevated crude oil, optical brighteners, and CDOM in the eastern alcove of the pond on 11-23.
 

### 2024-03-05 paper/paper.tex
Updates from Overleaf

@@
 
-The robot team was deployed at a private pond ($<0.1$ km$^{2}$) in Montague Texas close to the Oklahoma border for three separate collections on 11-23-2020, 12-09-2020, and 12-10-2020.
+The robot team was deployed at a private pond in Montague Texas close to the Oklahoma border for three separate collections on 11-23-2020, 12-09-2020, and 12-10-2020.
+The pond spans an area $<0.1$ km$^{2}$ with a maximum depth of 3 meters.
+As shown in Figure~\ref{fig:study-area}, the area includes multiple distinct regions with significant small-scale variability.
 For each acquisition, the UAV first completed a broad survey of the pond, capturing multiple hyperspectral data cubes.
@@
 These combined data form the tabular data set on which we train regression models; pixel spectra form input features, and each separate USV sensor forms a distinct target variable.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\columnwidth]{paper/figures/materials-and-methods/study-area.pdf}
+\caption{The pond in Montague Texas where the robot team was deployed. The pond includes multiple distinct regions separated by small islands and grasses. \label{fig:study-area}}
+\end{figure}
 
@@
 
-\begin{figure}[b!]
-\vspace{-0.2in}
+\begin{figure}[h!]
 \includegraphics[width=0.7\columnwidth]{paper/figures/results/downwelling-hist.pdf}
-\vspace{-0.2in}
 \caption{Distribution of total downwelling intensity during each of the three HSI collection flights.
@@
 
-\pagebreak
+% \pagebreak
 
-\begin{table}[hp!]
+\begin{table}[t!]
   \caption{Summary of fitting statistics for each target measurement.

### 2024-03-05 paper/paper.tex
Updates from Overleaf

@@
 \centering
+\vspace{-0.3in}
 \includegraphics[width=\columnwidth]{paper/figures/materials-and-methods/study-area.pdf}
+\vspace{-0.3in}
 \caption{The pond in Montague Texas where the robot team was deployed. The pond includes multiple distinct regions separated by small islands and grasses. \label{fig:study-area}}
@@
 
-\begin{figure}[h!]
+\begin{figure}[t!]
+\vspace{-0.3in}
 \includegraphics[width=0.7\columnwidth]{paper/figures/results/downwelling-hist.pdf}
+\vspace{-0.15in}
 \caption{Distribution of total downwelling intensity during each of the three HSI collection flights.
@@
 
-\begin{figure}[h!]
+\begin{figure}[t!]
 \centering
+\vspace{-0.3in}
 \includegraphics[width=0.9\columnwidth]{paper/figures/results/fits/physical-fitres.png}
+\vspace{-0.2in}
 \caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the physical variables measured by the USV.\label{fig:physical-fit}}
@@
 
-\begin{figure}[h!]
+\begin{figure}[t!]
 \centering
+\vspace{-0.3in}
 \includegraphics[width=\columnwidth]{paper/figures/results/fits/physical-ranking.pdf}
+\vspace{-0.2in}
 \caption{Ranked permutation importance for each feature in the physical variable models.
@@
 
-\begin{figure}[h!]
+\begin{figure}[t!]
 \centering
+\vspace{-0.3in}
 \includegraphics[width=0.9\columnwidth]{paper/figures/results/maps/physical.pdf}
+\vspace{-0.2in}
 \caption{Maps generated by applying each of the physical variable models to the hyperspectral data cubes collected on 11-23.
@@
 
-\begin{figure}
+\begin{figure}[t!]
 \centering
+\vspace{-0.3in}
 \includegraphics[width=\columnwidth]{paper/figures/results/fits/ions-fitres.png}
+\vspace{-0.2in}
 \caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the ion measurements made by the USV.\label{fig:ions-fit}}
@@
 
-\begin{figure}
+\begin{figure}[t!]
 \begin{adjustwidth}{-\extralength}{0cm}
 \centering
+\vspace{-0.1in}
 \includegraphics[width=18 cm]{paper/figures/results/fits/ions-ranking.pdf}
+\vspace{-0.1in}
 \end{adjustwidth}
@@
 
-\begin{figure}
+\begin{figure}[t!]
 \centering
+\vspace{-0.3in}
 \includegraphics[width=\columnwidth]{paper/figures/results/maps/ions.pdf}
+\vspace{-0.2in}
 \caption{Maps generated by applying the trained ion models to the data cubes collected on 11-23.
@@
 
-\begin{figure}
+\begin{figure}[t!]
 \centering
+\vspace{-0.3in}
 \includegraphics[width=\columnwidth]{paper/figures/results/fits/biochemical-fitres.png}
+\vspace{-0.2in}
 \caption{Scatter plots (left) and quantile-quantile plots (right) for the final hyperparameter optimized models for the biochemical targets blue-green algae (phycoerythrin), CDOM, chlorophyll-a, and blue-green algae (phycocyanin).
@@
 
-\begin{figure}
+\begin{figure}[t!]
 \centering
-\includegraphics[width=\columnwidth]{paper/figures/results/fits/biochemical-ranking.pdf}
+\vspace{-0.3in}
+\includegraphics[width=0.9\columnwidth]{paper/figures/results/fits/biochemical-ranking.pdf}
+\vspace{-0.15in}
 \caption{Ranked permutation importance for each feature in the trained biochemical models.
 The permutation importance measures the decrease in model $R^2$ value after replacing each feature with a random permutation of its values.\label{fig:biochem-fi}}
+\end{figure}
+
+\begin{figure}[b!]
+\centering
+\vspace{-0.35in}
+\includegraphics[width=0.92\columnwidth]{paper/figures/results/maps/biochemical.pdf}
+\vspace{-0.15in}
+\caption{Maps generated by applying the trained biochemical models to the data cubes collected on 11-23.
+Overlaid are the in-situ reference data for the same collection period.
+The size of the squares has been exaggerated for the visualization.
+We note there is good agreement between the predicted map and the reference data.
+\label{fig:map-biochem}}
+\end{figure}
+
+\begin{figure}[t!]
+\centering
+\vspace{-0.3in}
+\includegraphics[width=\columnwidth]{paper/figures/results/fits/chemical-fitres.png}
+\vspace{-0.25in}
+\caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the chemical variables measured by the USV.\label{fig:chemicals-fit}}
+\end{figure}
+
+\begin{figure}[t!]
+\centering
+\vspace{-0.25in}
+\includegraphics[width=\columnwidth]{paper/figures/results/fits/chemical-ranking.pdf}
+\vspace{-0.25in}
+\caption{Ranked permutation importance for for the top 25 features of the chemical models.
+The permutation importance measures the deacrease in model $R^2$ value after replacing each feature in the prediction set with a random permutation of its values.\label{fig:chemicals-fi}}
 \end{figure}
@@
 \vspace{-0.3in}
-\includegraphics[width=\columnwidth]{paper/figures/results/maps/biochemical.pdf}
-\vspace{-0.2in}
-\caption{Maps generated by applying the trained biochemical models to the data cubes collected on 11-23.
-Overlaid are the in-situ reference data for the same collection period.
-The size of the squares has been exaggerated for the visualization.
-We note there is good agreement between the predicted map and the reference data.
-\label{fig:map-biochem}}
+\includegraphics[width=\columnwidth]{paper/figures/results/maps/chemical.pdf}
+\vspace{-0.25in}
+\caption{Maps generated by applying the trained chemical variable models to the hyperspectral data cubes collected on 11-23.
+Overlaid are color-filled squares showing the in-situ reference data for the same collection period.
+The size of the squares is exaggerated for the visualization.
+We note that there is good agreement between the model predictions and reference data.\label{fig:map-chem}}
 \end{figure}
@@
 Both models show a distinct spatial distribution with elevated values in the eastern alcove of the pond similar to the CDOM distribution in Figure~\ref{fig:map-biochem}.
-
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{paper/figures/results/fits/chemical-fitres.png}
-\caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the chemical variables measured by the USV.\label{fig:chemicals-fit}}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{paper/figures/results/fits/chemical-ranking.pdf}
-\caption{Ranked permutation importance for for the top 25 features of the chemical models.
-The permutation importance measures the deacrease in model $R^2$ value after replacing each feature in the prediction set with a random permutation of its values.\label{fig:chemicals-fi}}
-\end{figure}
-
-\begin{figure}
-\centering
-\vspace{-0.3in}
-\includegraphics[width=\columnwidth]{paper/figures/results/maps/chemical.pdf}
-\caption{Maps generated by applying the trained chemical variable models to the hyperspectral data cubes collected on 11-23.
-Overlaid are color-filled squares showing the in-situ reference data for the same collection period.
-The size of the squares is exaggerated for the visualization.
-We note that there is good agreement between the model predictions and reference data.\label{fig:map-chem}}
-\end{figure}
 

### 2024-03-05 paper/paper.tex
Updates from Overleaf
final edits

@@
 \includegraphics[width=0.9\columnwidth]{paper/figures/results/fits/physical-fitres.png}
-\vspace{-0.2in}
+\vspace{-0.1in}
 \caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the physical variables measured by the USV.\label{fig:physical-fit}}
@@
 \includegraphics[width=0.9\columnwidth]{paper/figures/results/maps/physical.pdf}
-\vspace{-0.2in}
+\vspace{-0.1in}
 \caption{Maps generated by applying each of the physical variable models to the hyperspectral data cubes collected on 11-23.
@@
 \centering
-\vspace{-0.3in}
+\vspace{-0.31in}
 \includegraphics[width=\columnwidth]{paper/figures/results/fits/chemical-fitres.png}
-\vspace{-0.25in}
+\vspace{-0.31in}
 \caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the chemical variables measured by the USV.\label{fig:chemicals-fit}}
@@
 
-\begin{figure}[t!]
+\begin{figure}[b!]
 \centering
@@
 With a coordinated robot team, one does not need to rely on infrequent satellite overpasses when planning data collection.
-Further, the time offset between reference measurements and remote sensing is significantly reduced from days to minutes.
+Furthermore, the time offset between reference measurements and remote sensing is significantly reduced from days to minutes.
 
@@
 Other studies using multispectral and hyperspectral remote sensing imagery have also estimated optically inactive water quality parameters with the ability to do so stemming from the relationship of these variables to optically active properties of the water \cite{vakili2020determination,guo2021machine,niu2021deep}.
-We note that in our investigation, the models trained for many of these variables often outperformed their optically active counterparts.
-As the abundance of these variables is likely tied to the specific composition and content of the pond, it is unlikely that models trained for these optically inactive variables can generalized to other bodies of water.
+We note that in our investigation, the models trained for many of these variables outperformed their optically active counterparts.
+As the abundance of these variables is likely tied to the specific composition and content of the pond, it is unlikely that models trained for these optically inactive variables will generalize to other bodies of water.
 
@@
 By virtue of this increased data volume, we are able to simultaneously estimate the uncertainty of our models by using conformal prediction.
-Finally, the hyperspectral data cube processing pipeline employed on board the UAV makes it possible to deploy these trained models to swiftly generate maps of the target variables across bodies of water.
+Finally, the hyperspectral data cube processing workflow employed on board the UAV makes it possible to deploy these trained models to swiftly generate maps of the target variables across bodies of water.
 The rapid turnaround time from data collection to model deployment is critical for real-time water quality evaluation and risk assessment.

### 2024-03-10 paper/remotesensing-2870812-english.tex
updating with version for proofreading

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[remotesensing,article,accept,pdftex,moreauthors]{Definitions/mdpi}

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerobiology, aerospace, agriculture, agriengineering, agrochemicals, agronomy, ai, air, algorithms, allergies, alloys, analytica, analytics, anatomia, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arm, arthropoda, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, cyber, dairy, data, ddc, dentistry, dermato, dermatopathology, designs, devices, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, future, futureinternet, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, grasses, gucdd, hazardousmatters, healthcare, hearts, hemato, hematolrep, heritage, higheredu, highthroughput, histories, horticulturae, hospitals, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijpb, ijtm, ijtpp, ime, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jcto, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jvd, jzbg, kidneydial, kinasesphosphatases, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing,\gdef\@continuouspages{yes}} nanomaterials, ncrna, ndt, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, %%nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, %oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology,\gdef\@ISSN{2813-0618}\gdef\@continuous pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, platforms, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, receptors, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, sclerosis, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, spectroscj, sports, standards, stats, std, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, targets, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, virtualworlds, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal. Changing "submit" to "accept" before posting will remove line numbers.

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. Remove "pdftex" for (1) compiling with LaTeX & dvi2pdf (if eps figures are used) or for (2) compiling with XeLaTeX.

%=================================================================
% MDPI internal commands - do not modify
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2024}
\copyrightyear{2024}
\externaleditor{Academic Editor: }
\datereceived{29 January 2024} 
\daterevised{5 March 2024} % Comment out if no revised date
\dateaccepted{8 March 2024} 
\datepublished{ } 
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org
%\CorrStatement{yes}  % For updates

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
% cleveref: load \crefname definitions after \begin{document}

%=================================================================
% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
 \Title{Characterizing Water Composition with an Autonomous Robotic Team Employing Comprehensive In Situ Sensing, Hyperspectral Imaging, Machine Learning, and Conformal Prediction}%AE title change
%\Title{\textcolor{red}{Towards Real-Time Water Quality Characterization Using an Autonomous Robotic Team Employing Comprehensive In-Situ Sensing, Hyperspectral Imaging, and Conformal Prediction}}

% MDPI internal command: Title for citation in the left column
%\TitleCitation{Robot Team II: Electric Boogaloo}
\TitleCitation{Characterizing Water Composition with an Autonomous Robotic Team Employing Comprehensive In Situ Sensing, Hyperspectral Imaging, Machine Learning, and Conformal Prediction}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-5910-0183} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0003-4265-9543} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{\hl{John} %MDPI: Please carefully check the accuracy of names and affiliations.
 Waczak \orcidA{}, Adam Aker, Lakitha O. H. Wijeratne, Shawhin Talebi, Bharana Fernando, \hl{Prabuddha Hathurusinghe}%MDPI: The name of this author is different from the one submitted online at susy.mdpi.com. Please confirm which one is correct.
, Mazhar Iqbal, Matthew Lary, David Schaefer and David J. Lary *\orcidB{}}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{John Waczak, Adam Aker, Lakitha O. H. Wijeratne, Shawhin Talebi, Bharana Fernando, Prabuddha Hathurusinghe, Mazhar Iqbal, Matthew Lary, David Schaefer and David J. Lary}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Waczak, J.; Aker, A.; Wijeratne, L.O.H.; Talebi, S.; Fernando, B.; Hathurusinghe, P.; Iqbal, M.; Lary, M.; Schaefer, D.; Lary, D.J.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address[1]{%
Hanson Center for Space Sciences, University of Texas at Dallas, Richardson, TX 75080, USA;  \hl{john.waczak@utdallas.edu} %MDPI: We changed all emails into lowercase. Please confirm.
 (J.W.); adam.aker@utdallas.edu (A.A.); lhw150030@utdallas.edu (L.O.H.W.); shawhintalebi@gmail.com (S.T.); ashen.fernando@utdallas.edu  (B.F.); prabuddhamadusanka.hathurusinghedewage@utdallas.edu (P.H.); mazhar.iqbal@utdallas.edu (M.I.); \hl{mdlary@me.com} %MDPI: This email address is different from the one submitted online at susy.mdpi.com. Please confirm which one is correct.
 (M.L.); captdaveschaefer@gmail.com (D.S.)}

\corres{\hangafter=1 \hangindent=1.05em \hspace{-0.82em}Correspondence: {David.Lary@utdallas.edu}}

% Contact information of the corresponding author
\corres{Correspondence: david.lary@utdallas.edu} %; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}

% Current address and/or shared authorship

% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Inland waters pose a unique challenge for water quality monitoring by remote sensing techniques due to their complicated spectral features and small-scale variability. At the same time, collecting the reference data needed to calibrate remote sensing data products is both time consuming and expensive. In this study, we present the further development of a robotic team composed of an uncrewed surface vessel (USV) providing in situ reference measurements and an unmanned aerial vehicle (UAV) equipped with a hyperspectral imager. Together, this team is able to address the limitations of existing approaches by enabling the simultaneous collection of hyperspectral imagery with precisely collocated in situ data. We showcase the capabilities of this team using data collected in a northern Texas pond across three days in 2020. Machine learning models for 13~variables are trained using the dataset of paired in situ measurements and coincident reflectance spectra. These models successfully estimate physical variables including temperature, conductivity, pH, and turbidity as well as the concentrations of blue--green algae, colored dissolved organic matter (CDOM), chlorophyll-a, %AE this paper had several variations of this term (e.g., chlorophyll a, chlorophyll A, chlorophyll-A); I standardized to what seemed to be the authors' most common usage; however, other publications seem to prefer 'chlorophyll a'; authors should confirm
crude oil, optical brighteners, and the ions $\mathrm{Ca}^{2+}$, $\mathrm{Cl}^{-}$, and $\mathrm{Na}^{+}$. We extend the training procedure to utilize conformal prediction to estimate 90\% confidence intervals for the output of each trained model. Maps generated by applying the models to the collected images reveal small-scale spatial variability within the pond. This study highlights the value of combining real-time, in situ measurements together with hyperspectral imaging for the rapid characterization of water composition.}

% A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusions: indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions

% Keywords
\keyword{water quality; robotic teams; hyperspectral imaging; machine learning; conformal prediction}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data
%\dataset{DOI number or link to the deposited data set if the data set is published separately. If the data set shall be published as a supplement to this paper, this field will be filled by the journal editors. In this case, please submit the data set as a supplement.}
%\datasetlicense{License under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{For entry manuscripts only: please provide a brief overview of the entry title instead of an abstract.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Advances in Respiratory Medicine
%\addhighlights{yes}
%\renewcommand{\addhighlights}{%

%\noindent This is an obligatory section in “Advances in Respiratory Medicine”, whose goal is to increase the discoverability and readability of the article via search engines and other scholars. Highlights should not be a copy of the abstract, but a simple text allowing the reader to quickly and simplified find out what the article is about and what can be cited from it. Each of these parts should be devoted up to 2~bullet points.\vspace{3pt}\\
%\textbf{What are the main findings?}
% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
% \item First bullet.
% \item Second bullet.
% \end{itemize}\vspace{3pt}
%\textbf{What is the implication of the main finding?}
% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
% \item First bullet.
% \item Second bullet.
% \end{itemize}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

For decades, remote sensing imagery has been used for environmental monitoring, with applications ranging from resource mapping, land type classification, and urban growth assessment to wildfire monitoring, natural disaster tracking, and many more~\cite{melesse2007remote, joyce2009review}. Among these applications, the retrieval of water quality variables from remote sensing imagery remains challenging due to the difficulty of obtaining in situ reference data coincident with available satellite imagery. Traditional approaches to obtain these data have relied on serendipitous satellite passes over fixed sensing sites or sensor-equipped vessels. As a consequence, curating comprehensive datasets can require decades of observations~\cite{aurin2018remote, ross2019aquasat}. This poses a significant challenge for assessing natural and anthropogenic changes to water composition in real time, for example, during oil spills \cite{fingas2017review}.

Where remote sensing imagery and in situ measurements have been combined, studies have demonstrated successful extraction of optically active water quality variables such as colored dissolved organic matter (CDOM), chlorophyll-a, and suspended sediment concentrations by using combinations of spectral bands \cite{remote-sensing-finland,bonansea2015using, absalon2023detection}. These approaches can be further augmented by machine learning methods, which consist of nonlinear and non-parametric models designed to learn representations of functions directly from data \cite{lary2010artificial}. For example, Petersen et al. utilized a deep neural network to successfully estimate blue--green algae, chlorophyll-a, CDOM, dissolved oxygen, specific conductance, and turbidity from a fused dataset of Landsat-8 and Sentinel-2 imagery \cite{peterson2020deep}. Other methods such as support vector machines and decision trees have also been successfully applied to retrieve water quality parameters from remote sensing imagery \cite{belgiu2016random,sagan2020monitoring}. However, the low spatial and spectral resolution of available multiband remote sensing satellites makes it difficult to analyze inland waters with small spatial features and complicated spectral signatures.

Advances in multispectral and hyperspectral imaging technology have led to considerable reductions in size, making it possible to incorporate these cameras into the payloads of autonomous aerial vehicles (UAVs) \cite{hruska2012radiometric}. Flying at low altitudes enables the collection of centimeter-scale imagery whilst limiting the need for complicated atmospheric corrections to account for scattering by atmospheric aerosols and gasses \cite{adao2017hyperspectral, banerjee2020uav}. Already, UAVs equipped with multispectral and hyperspectral imagers are being used in a variety of domains to great effect, including for biomass estimation, forest management, precision agriculture, and, recently, water quality monitoring \cite{adao2017hyperspectral, padua2017uas,arroyo2019implementation,kurihara2020unmanned, ehmann2019monitoring}. Despite the superior spectral and spatial resolution enabled by UAV platforms, these improvements alone do not address the limited spatial coverage of the in situ reference data used for the associated water composition retrieval. For instance, Lu et al. used a UAV-born hyperspectral imager to develop machine learning models for the inversion of chlorophyll-a and suspended solids using samples from 33 fixed locations \cite{lu2021retrieval}. Similarly, Zhang et al. utilized a UAV equipped with a hyperspectral imager to estimate water quality parameters by collecting imagery coincident with samples taken from 18 sampling sites \cite{zhang2022selection}. In both of these examples, the collection of in situ reference data remains the key challenge for the application of UAV systems to water quality quantification.

To address this gap and enable comprehensive, real-time evaluation of water composition, we have developed a robotic team comprised of an autonomous uncrewed surface vessel (USV) equipped with a collection of reference grade instruments together with a UAV carrying a hyperspectral imager. By incorporating reference instruments on a maneuverable USV platform, we are able to rapidly collect large volumes of water quality data for a comprehensive suite of physical, biochemical, and chemical variables that are precisely collocated with spectra captured by the UAV. Critically, the USV enables the collection of reference data with significantly improved spatial resolution compared to other approaches. In our previous work, we introduced this paradigm and described how in situ measurements collected by the USV can be used to provide the ground-truth data for machine learning models that map the reflectance spectra captured by the hyperspectral imager to the desired water quality variables \cite{robotTeam1}.

The main objective of this study is to expand on our previous work in three new ways: The first is to explore the breadth of water quality variables that can be inferred from collected hyperspectral imagery. With the goal of comprehensive measurement in mind, we demonstrate the ability to accurately predict physical variables such as temperature, conductivity, pH, and turbidity as well as biochemical constituents, including blue--green algae pigments, CDOM, and chlorophyll-a, in addition to concentrations of crude oil, optical brighteners, and a variety of ions. The second addition is to demonstrate that observations from separate collections can effectively be combined by carefully accounting for variability in the viewing and illumination geometries of the scene. Finally, we expand our machine learning approach to take advantage of the considerable volume of collected data in order to determine reliable confidence intervals for each predicted parameter using conformal prediction.

% critical to this approach

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

 The robotic team presented in this study consists of two key sensing sentinels: an uncrewed surface vessel (USV) used to collect in situ reference measurements and an unmanned aerial vehicle (UAV) for performing rapid, wide-area surveys to gather remote sensing data products. Both platforms are coordinated using open source \hl{QGroundControl software} %MDPI: Please state the version number of the software.
 for flight control and mission planning and are equipped with high-accuracy GPS and INS such that all data points collected are uniquely geolocated and time-stamped~\cite{qgroundcontrol}. Both the USV and UAV include long-range Ubiquiti 5 GHz LiteBeam airMAX WiFi to enable streaming of data products to a ground station with network-attached storage to provide redundancy.

\subsection{USV: In Situ Measurements}

The USV employed in the robot team is a Maritime Robotics Otter equipped with an in situ sensing payload consisting of a combination of Eureka Manta+40 multiprobes. These sensors include fluorometers, ion-selective electrodes, and other physical sensors and are mounted on the underside of the boat as illustrated in Figure~\ref{fig:boat-components}. Together, this sensor array enables the collection of comprehensive near-surface measurements including colored dissolved organic matter (CDOM), crude oil, blue--green algae (phycoerythrin and phycocyanin), chlorophyll-a, $\mathrm{Na^+}$, $\mathrm{Ca^{2+}}$, $\mathrm{Cl^-}$, temperature, conductivity, and many others. The full list of measurements utilized in this study is outlined in Table~\ref{tab:sensors} and is categorized into four distinct types: physical measurements, ion measurements, biochemical measurements, and chemical measurements. Additionally, the USV is equipped with an ultrasonic weather monitoring sensor for measuring air speed and direction as well as a BioSonics MX Aquatic Habitat Echosounder sonar, which are not explored in this study.

\begin{figure}[H]
\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/materials-and-methods/annotated-boat.pdf}
\caption{Configuration of the USV: (\textbf{a}) Frontal view of the USV showing the Eureka Manta+40 multiprobes mounted on the underside of the boat. (\textbf{b}) The USV deployed in the water.\label{fig:boat-components}}
\end{figure}

As shown in Table~\ref{tab:sensors}, the physical measurements and ion sensors are largely based on different electrode configurations, while the chemical and biochemical measurements are all optically significant in UV and visible light, enabling their determination by fluorometry~\mbox{\cite{de2007ion,trees2002fluorometric,tillman2017evaluation}}. The pigments phycoerythrin and phycocyanin are used to determine the blue--green algae content, which together with chlorophyll-a enables us to assess the distribution of photosynthetic life in the pond~\cite{Brient2008APP, boyer2009phytoplankton}. In addition, we also measured the concentration of colored dissolved organic matter (CDOM), which impacts light penetration and serves as a primary source of bioavailable carbon. Crude oil (natural petroleum) and optical brightener concentrations are also measured with fluorometers and are relevant for identifying sources of industrial contamination, natural seepage, and sewage \cite{brown2003review,cao2009evaluation}. 
% add table describing sensors here:

\begin{table}[H] 
\caption{In situ reference sensors utilized in this study.\label{tab:sensors}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCCCC}
\toprule
\textbf{Sensor}	& \textbf{Units} & \textbf{Resolution} & \textbf{Sensor Type} & \textbf{Target Category}\\
\midrule
Temperature		                    & $^{\circ}$C        & 0.01  & Thermistor                           & Physical \\
Conductivity                        & $\upmu$S/cm          & 0.01  & Four-Electrode Graphite Sensor       & Physical  \\
pH                                  & logarithmic (0--14) & 0.01  & Flowing-Junction Reference Electrode & Physical \\
Turbidity                           & FNU                & 0.01  & Ion-Selective Electrode              & Physical \\
$\mathrm{Ca^{2+}}$                  & mg/L               & 0.1   & Ion-Selective Electrode              & Ions \\
$\mathrm{Cl^-}$                     & mg/L              & 0.1   & Ion-Selective Electrode              & Ions \\
$\mathrm{Na^+}$                     & mg/L          & 0.1   & Ion-Selective Electrode              & Ions \\
Blue--Green Algae (phycoerythrin)    & ppb                & 0.01  & Fluorometer                          & Biochemical \\
Blue--Green Algae (phycocyanin)      & ppb                & 0.01  & Fluorometer                          & Biochemical \\
CDOM                                & ppb                & 0.01  & Fluorometer                          & Biochemical \\
Chlorophyll-a                       & ppb                & 0.01  & Fluorometer                          & Biochemical \\
Optical Brighteners                 & ppb                & 0.01  & Fluorometer                          & Chemical \\
Crude Oil                           & ppb                & 0.01  & Fluorometer                          & Chemical\\
\bottomrule
\end{tabularx}
% \noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table}

The inclusion of optically inactive variables such as conductivity, pH, and ion concentrations was motivated by a desire to be comprehensive. Multiple studies have classified inland water bodies according to their ionic compositions \cite{piper1944graphic, dordoni2023preliminary}. Other research indicates that the structure of dissolved organic matter is affected by changes in pH and cation concentration~\cite{pace2012ph}. Therefore, changes in physical parameters and ionic content can be expected to be related to the observed distribution of optically active variables in the water. It is therefore reasonable to expect that these parameters may be estimated from hyperspectral images at a given site.

\subsection{UAV: Hyperspectral Data Cubes}

A Freefly Alta-X autonomous quadcopter was used as a UAV platform for the robotic team. The Alta-X is specifically designed to carry cameras and has a payload of up to 35~lbs. We equipped the UAV with a Resonon Pika XC2 visible+near-infrared (VNIR) hyperspectral imager. For each image pixel, this camera samples 462 wavelengths ranging from 391 to 1011 nm.  Additionally, the UAV includes an upward facing Ocean Optics UV-Vis-NIR spectrometer with a cosine corrector to capture the incident downwelling irradiance spectrum. Data collection by the hyperspectral imager is controlled by an attached Intel NUC small-form-factor computer. A second processing NUC is also included for onboard georectification and generation of data products. The collected hyperspectral images (HSIs) are stored locally on a solid state drive that is simultaneously mounted by the processing computer. The configuration of the drone is shown in Figure~\ref{fig:drone-components}.

\begin{figure}[H]
\vspace{-0.3in}
\hspace{-16pt}\includegraphics[width=\columnwidth]{figures/materials-and-methods/annotated-drone.pdf}
\vspace{-0.2in}
\caption{Configuration of the UAV: (\textbf{a}) The hyperspectral imager and acquisition computer. (\textbf{b}) The assembled UAV with secondary processing computer and (upward facing) downwelling irradiance spectrometer. \label{fig:drone-components}}
\end{figure}

To effectively utilize the spectra collected by our UAV, we must account for the variability of the incident light that illuminates the water and transform the raw hyperspectral data cubes from their native \textit{\hl{imaging~reference~frame}} %MDPI: Please confirm if the italics is unnecessary and can be removed. The following highlights are the same.
 to a chosen coordinate system compatible with the data collected by the USV. This procedure is illustrated in Figure~\ref{fig:hsi-pipeline}.

\begin{figure}[H]
%\begin{adjustwidth}{-\extralength}{0cm}
%\centering
\vspace{-0.3in}
\hspace{-6pt}\includegraphics[width=14cm]{figures/materials-and-methods/pipeline-figure-2.pdf}
%\end{adjustwidth}
\vspace{-0.4in}
\caption{\hl{Hyperspectral} %MDPI: Please add the explanation for different color in the figure.
 image processing: Hyperspectral data cubes are collected one scan-line at a time (left). By utilizing downwelling irradiance spectra, we convert each pixel from spectral radiance to reflectance. By using orientation and position data from the on-board GPS and INS, we georeference each pixel to assign it a latitude and longitude on the ground. The final data product is the georectified hyperspectral reflectance data cube visualized on the right. \label{fig:hsi-pipeline}}
\end{figure}

The hyperspectral imager utilized in our robot team is in a so-called \textit{\hl{pushbroom}} configuration: that is, each image captured by the drone is formed one scan line at a time as the UAV flies. Each scan line consists of 1600 pixels, for which incoming light is diffracted into 462 wavelength bins. In the collection software, a regular cutoff of 1000 lines is chosen so that each resulting \hl{\textit{image}} forms an array of size 462 $\times$ 1600 $\times$ 1000 called a \textit{\hl{hyperspectral data cube}}. Initially, the captured spectra are in units of spectral radiance (measured in microflicks); however, this does not account for the variability of incident light illuminating the water. To this end, we convert the hyperspectral data cubes into units of reflectance by utilizing the skyward-facing downwelling irradiance spectrometer. When the camera is normal to the water surface, the reflectance is given by
\begin{equation}
    R(\lambda) = \pi L(\lambda)/E_d(\lambda)
\end{equation}
where $L$ is the spectral radiance, $E_d$ is the downwelling irradiance, and a factor of $\pi$ steradians results from assuming the water surface is Lambertian (diffuse) \cite{reflectance-conversion}.

Having converted the hyperspectral data cube to units of reflectance, we must also georeference each pixel into a geographic coordinate system so that each image pixel can be assigned a latitude and longitude corresponding to the location on the ground from which it was sampled. During our three surveys, the UAV was flown at an altitude of approximately %Please ensure meaning has been retained. 
50 m above the water. At this scale, the surface is essentially flat, so the hyperspectral data cube can be reliably georectified without the need for an on-board digital elevation map (DEM). We adopt the approach outlined in \cite{GeorectificationMuller, GeorectificationBaumker, GeorectificationMostafa} whereby each scan line is georeferenced using the known field of view (30.8$^\circ$) together with the position and orientation of the UAV as provided by the on-board GPS/INS. After a sequence of coordinate transformations, the pixel coordinates are obtained in the relevant UTM zone (in meters). The resulting image is then re-sampled to a final output resolution. For these collections, a resolution of 10 cm was utilized; however, this can be adjusted to optimize the processing time and final resolution for real-time applications. Finally, the UTM pixel coordinates obtained are transformed to latitude and longitude for easy comparison with in situ data collected by the USV. The final result is a georectified hyperspectral reflectance data cube. In Figure~\ref{fig:hsi-infographic}, we visualize one such data cube, highlighting a selection of exemplar pixel spectra as well as the incident downward irradiance spectrum. A pseudo-color image is generated (plotted on the top of the data cube) to illustrate the scene.

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\vspace{-0.1in}
\includegraphics[width=15.5cm]{figures/materials-and-methods/HyperSpectralInfoGraphic.pdf}
\end{adjustwidth}
\caption{A georectified reflectance data cube is visualized (center) with the $\log10$-reflectance along the z-axis and a pseudo-color image on the top. In the top left, we visualize the downwelling irradiance spectrum (the incident light). The surrounding plots showcase exemplar pixel reflectance spectra for open water, dry grass, algae, and a rhodamine dye plume used to test the system.\label{fig:hsi-infographic}}
\end{figure}

The above processing workflow was implemented using the Julia programming language: a just-in-time compiled language with native multi-threading support \cite{julia-1}. By running this pipeline on the onboard computer, we are able to process the collected hyperspectral data cubes in near real time. This feature is critical for time-sensitive applications wherein we need to quickly assess if an area is safe and cannot afford to wait to download and post-process collected imagery after a flight.

\subsection{Data Collection}

The robot team was deployed at a private pond in Montague, Texas, close to the Oklahoma border for three separate collections on \hl{23} %MDPI: We changed all date format in main tex. Please confirm.
 November 2020, 9 December 2020, and 10 December 2020. The pond spans an area $<$0.1 km$^{2}$ and has a maximum depth of 3 m. As shown in Figure~\ref{fig:study-area}, the area includes multiple distinct regions with significant small-scale variability. For each acquisition, the UAV first completed a broad survey of the pond, capturing multiple hyperspectral data cubes. Subsequently, the USV sampled across the pond, collecting in situ reference measurements. Each of these reference measurements was then collocated with individual pixel spectra, whereby the USV track overlapped with the UAV's pixels. To account for any time lag in the values measured by the in situ instruments and to account for the USV's size in comparison to the data cube's spatial resolution, each in situ measurement is associated with a 3 $\times$ 3 grid of HSI pixels: that is, a \mbox{30 cm $\times$ 30 cm} square. These combined data form the tabular dataset on which we train regression models; pixel spectra form input features, and each separate USV sensor forms a distinct target variable.

\begin{figure}[H]
\centering
\vspace{-0.1in}
\hspace{-9pt}\includegraphics[width=\columnwidth]{figures/materials-and-methods/study-area.pdf}
\vspace{-0.1in}
\caption{The pond in Montague, Texas, where the robot team was deployed. The pond includes multiple distinct regions separated by small islands and grasses. \label{fig:study-area}}
\end{figure}

Each collection was performed near solar noon to maximize the amount of incident sunlight illuminating the water. For the site in northern Texas, this corresponded to average solar zenith angles of 54.9$^{\circ}$, 56.7$^{\circ}$, and 56.75$^{\circ}$ for 23 November 2020, 9 December 2020, and 10 December 2020, respectively. Given the hyperspectral imager acquires data cubes at nadir, there was little concern for effects due to sunglint. However, to account for any potential variation in lighting conditions between data cubes, we augment the training set with additional features including the drone's viewing geometry (roll, pitch, and heading) and solar illumination geometry (solar azimuth, solar elevation, and solar zenith) as well as the total at-pixel intensity before reflectance conversion, the total downwelling intensity, and the drone's altitude. Further feature engineering is performed to add additional spectral indices that utilize combinations of specific wavelength bands such as the normalized difference vegetation index (NDVI), normalized difference water index (NDWI), simple ratio (SR), photochemical reflectance index (PRI), and more, as outlined in \cite{envi_vegetation_indices, thenkabail2018hyperspectral,kaufman1992atmospherically, SpectralIndexWheat}. A comprehensive list of these added features is provided in Supplementary Table S1. The final dataset includes a total of 526 features (462 reflectance bands plus 64 additional features) with over 120,000 records.

\subsection{Machine Learning Methods}

For each of the 13 target variables listed in Table~\ref{tab:sensors}, the data were randomly partitioned into a 90:10 training/testing split. To model the data, we chose to use the random forest regressor (RFR) as implemented in the machine learning framework for Julia package  \hl{MLJ} %MDPI: There is no ref {ben_sadeghi_2022_7359268}. Please check and revise.
%AE unsure if MLJ is an acronym and should thus be in parentheses
 \cite{ben_sadeghi_2022_7359268, MLJ1}.  Random forests are an ensembling technique based on bagged predictions of individual decision tree regressors trained using the classification and regression trees (CART) algorithm. Each tree in an RFR is trained on a random subset of features \textit{\hl{and}} a random subset of training records \cite{decision-trees, random-forest}. Random forests are particularly attractive due to their fast training and inference times. Furthermore, studies continue to observe that tree-based models like random forest remain superior for tabular datasets \cite{grinsztajn2022tree, shwartz2022tabular}.

As reflectance values in adjacent wavelength bins tend to correlate with each other and, therefore, may not necessarily contribute additional information content to the final model, it is desirable to evaluate the relative importance of each feature to the trained model predictions. This is useful both for identifying the most relevant features and for performing feature selection to reduce the final model size. By default, tree-based methods such as RFR allow for impurity-based ranking as described in \cite{random-forest, rfr-importance-ranking}. However, these methods have been shown to be biased towards high cardinality and correlated features \cite{strobl2008conditional}. Therefore, we choose to use the model-agnostic permutation importance as described by \cite{parr2018beware}. To do this, we further partition the training dataset, resulting in an 80:10:10 split with 80\% of the points used for model training, 10\% of the points used for validation and determination of feature importance, and the final 10\% held out as an independent testing set. The importance of the $j^{\text{th}}$ feature is then computed as
\begin{equation}
    \text{Imp}_j = R^2(f(X_{\text{val}}), y_{\text{val}}) - R^2(f(X_{\text{val}}^{(j)}), y_{\text{val}})
\end{equation}
where $(X_{\text{val}}, y_{\text{val}})$ is the validation set, $f(\cdot)$ is the trained model, $R^2(\cdot, \cdot)$ is the coefficient of determination, and $X_{\text{val}}^{(j)}$ is the validation feature set with the $j^{th}$ column randomly permuted. The permutation importance is therefore understood to be the decrease in model performance when the $j^{th}$ feature is replaced by random values from the validation set.

To assess the uncertainty of the final model's predictions, we employed inductive conformal prediction as described in \cite{conformal-prediction-1, conformal-prediction-2, conformal-prediction-3, conformal-prediction-4}. To do this, we computed a set of nonconformity scores of the trained model on the validation set using an uncertainty heuristic: in this case, the absolute error:
\begin{equation}
    s_i = s(X_i, y_i) = \lvert f(X_i) - y_i \rvert = \lvert \hat{y}_i - y_i \rvert
\end{equation}
where $f(X_i)=\hat{y}_i$ denotes the trained ML model applied to the $i^{th}$ calibration record. These n-many scores are sorted, and the interval half width, $d$, is calculated as the $\frac{\lceil(1-\alpha)(n+1) \rceil}{n}$ quantile of this set in order to achieve coverage of $1-\alpha$ on the calibration set. Prediction intervals for new data are then formed as $f(X)\pm d$. For this study, we chose $\alpha=0.1$ for coverage corresponding to a 90\% confidence interval.

Using these tools, the training procedure for each model was as follows: First, each model was trained using six-fold cross-validation on the full 526-feature training set with default hyperparameter values. Feature importances for the trained model were then computed, and the top 25 features were identified. A second model was then trained using the same six-fold cross-validation scheme with \textit{\hl{only}} these 25 most important features together with hyperparameter optimization using a random search over the number of trees and sampling fraction. The number of trees was optimized, as it has a significant impact on both model performance and inference time. The sampling ratio determines the fraction of training records that each individual tree is exposed to during training. Tuning this parameter helps limit overfitting by increasing the diversity of trees in the ensemble. Additionally, we chose to fix the maximum tree depth to 20 to control the final model size such that each trained model can fit in-memory on the onboard UAV processing computer. The remaining hyperparameters were left to their default values in order to constrain the total optimization space. The performance of each model was evaluated by computing out-of-fold scores for the coefficient of determination as well as the
\begin{align}
    \text{RMSE} &= \sqrt{\frac{\sum\limits_{i=1}^N (\hat{y}_i-y_i)^2}{N}}, \\
    \text{MAE} &= \frac{\sum\limits_{i=1}^N \lvert \hat{y}_i - y_i \vert}{N},
\end{align}
where RMSE is the root-mean-square error, and MAE is the mean absolute error between the true measurements $y_i$ and the predictions $\hat{y}_i$.

Having identified the model with the best out-of-fold performance, we proceeded to train the final hyperparameter-optimized model on the full training set with the associated uncertainty estimated using conformal prediction.  Then, each final model was evaluated on the previously untouched testing set. We visualize model performance across the distribution of the testing data with a scatter diagram and a quantile--quantile plot, for which successful model predictions should lie close to a 1:1 line.

These trained models can then easily be deployed on the onboard processing computer so that during subsequent surveys, target concentrations can be inferred as imagery are collected and processed. The application of each model to the collected hyperspectral data cubes results in a map of the distribution of the water composition across the pond.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

The final dataset of combined observations from each of the three separate collections contains more than 120,000 individual records. Based on the size of the UAV payload and the available battery capacity, the collection on 23 November 2020 was chosen to cover the broadest possible area, resulting in small horizontal gaps between flight tracks. The collections on 9 December 2020 and 10 December 2020 were designed to complement this collection by sampling a smaller spatial extent with uniform coverage.

The variability of incident lighting conditions for each collection is visualized in Figure~\ref{fig:downwelling-hist}, wherein the distribution of the total downwelling intensity measured by the downwelling irradiance spectrometer across all hyperspectral data cubes is visualized. Despite performing all UAV flights near solar noon, there were differences in the minimum solar zenith angles between collections due to the time of year. Additionally, there was some slight cloudiness during the 9 December and 10 December collections.

\begin{figure}[H]
\vspace{-0.1in}
\hspace{-9pt}\includegraphics[width=0.7\columnwidth]{figures/results/downwelling-hist.pdf}
\vspace{-0.15in}
\caption{\hl{Distribution} %MDPI: Please use commas to separate thousands for numbers with five or more digits (not four digits) in the picture, e.g., "10000" should be "10,000".
 of total downwelling intensity during each of the three HSI collection flights. The multi-modal nature of these distributions reflects the impact of the relative orientation of the drone to the sun as well as potential occlusion due to the presence of clouds.\label{fig:downwelling-hist}}
\end{figure}

The results of the model training procedure are presented in Table~\ref{tab:fit-results}. The performance of the model is identified by the $R^2$, RMSE, and MAE out-of-fold estimates (mean $\pm$ standard deviation) of the final hyperparameter-optimized model in the training set, with the target variables ranked in descending order by the $R^2$ value and separated by sensor type (physical variables, ions, biochemical variables, and chemical variables). The final hyperparameter values for each model are listed in Table~\ref{tab:hyperparameters} in Appendix~\ref{Model Hyperparameters}. The small variation in values across folds confirms that the reported performance is independent of how the training set was sampled. Furthermore, we report the interval width that yields a 90\% confidence interval on the holdout validation set determined by the conformal prediction procedure. We then evaluate how the estimated uncertainty generalizes by computing the \textit{\hl{empirical coverage}} on the holdout testing set: that is, we compute the percentage of predictions in the test set that \textit{\hl{actually}} fall within the estimated 90\% confidence interval.

From Table~\ref{tab:fit-results},  we see that the empirical coverage achieved by the inferred confidence interval evaluated in the independent test set is within 1\% of our desired coverage for each target modeled. This indicates that the uncertainties obtained by the conformal prediction procedure are reliable---at least within the bounds of the collected dataset. We also note that in all cases, the inferred model uncertainties are larger than the resolution of the in situ sensors. This lends further credence to the inferred uncertainty estimates, as we should not expect to be able to have lower uncertainty than the smallest resolvable difference in reference sensor measurements.

To further examine the differences in model performance between the target variables, we can consider the difference between the RMSE and MAE scores. The MAE is less sensitive to the impact of outliers than the RMSE, and as a consequence, any large difference between the two is indicative of impacts due to the distribution of target values. Indeed, this is the case for turbidity, for which almost all measurements were below 10 FNU, with only a small fraction of observations from a small area near the shore being above this value. %Please ensure meaning has been retained. 
The rest of the models all show mean per-fold RMSE values with sizes comparable to the mean per-fold MAEs.

In the remainder of this section, we compare the models within each target category.

% \pagebreak

\begin{table}[H] 
\tablesize{\footnotesize}
  \caption{Summary of fitting statistics for each target measurement. Models were evaluated using 6-fold cross-validation on the training set. The estimated uncertainty is evaluated so that a prediction $\hat{y}\pm \Delta y$ achieves 90\% coverage on the calibration holdout set. The empirical coverage is the percentage of predictions in the testing set that fall within the inferred confidence interval. \label{tab:fit-results}}
  \begin{adjustwidth}{-\extralength}{0cm}
  \newcolumntype{C}{>{\centering\arraybackslash}X}
  \begin{tabularx}{\fulllength}{CCCCCCC}
    \toprule
    \textbf{Target} & \textbf{Units} & \textbf{$\text{R}^2$} & \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty} & \textbf{Empirical Coverage (\%)} \\
    \midrule
    Temperature & $^{\circ}$C & 1.0 ± 6.04 $\times$ 10$^{-6}$ & 0.0289 ± 0.000466 & 0.0162 ± 0.00016 &  ±0.039 & 90.3 \\
    Conductivity & $\upmu$S/cm & 1.0 ± 1.54 $\times$ 10$^{-5}$ & 0.574 ± 0.0128 & 0.322 ± 0.00579 &  ±0.76 & 90.6 \\
    pH & 0--14 & 0.994 ± 0.000288 & 0.0145 ± 0.000304 & 0.00739 ± 9.49 $\times$ 10$^{-5}$ &  ±0.017 & 89.5 \\
    Turbidity & FNU & 0.897 ± 0.00611 & 3.13 ± 0.084 & 0.736 ± 0.0156 &  ±1.1 & 89.8 \\
    \midrule
    $\mathrm{Ca}^{2+}$ & mg/L & 1.0 ± 1.06 $\times$ 10$^{-5}$ & 0.285 ± 0.00357 & 0.137 ± 0.00224 &  ±0.33 & 89.8 \\
    $\mathrm{Cl^-}$ & mg/L & 0.995 ± 0.000196 & 0.895 ± 0.0202 & 0.516 ± 0.00759 &  ±1.2 & 90.1 \\
    $\mathrm{Na^+}$ & mg/L &0.993 ± 0.000229 & 6.16 ± 0.102 & 2.83 ± 0.0303 &  ±7.3 & 90.0 \\
    \midrule
    Blue--Green Algae (Phycoerythrin) & ppb & 0.995 ± 0.000601 & 0.783 ± 0.0489 & 0.287 ± 0.00959 &  ±0.73 & 89.3 \\
    CDOM & ppb &  0.965 ± 0.00352 & 0.248 ± 0.0142 & 0.0921 ± 0.0024 &  ±0.15 & 89.9 \\
    Chlorophyll-a & ppb & 0.908 ± 0.00664 & 0.37 ± 0.00934 & 0.131 ± 0.00228 &  ±0.27 & 89.2 \\
    Blue--Green Algae (Phycocyanin) & ppb & 0.708 ± 0.00689 & 0.749 ± 0.0129 & 0.446 ± 0.00405 &  ±0.93 & 89.8 \\
    \midrule
    Crude Oil & ppb & 0.949 ± 0.00267 & 0.247 ± 0.00597 & 0.0935 ± 0.00114 &  ±0.17 & 89.8 \\
    Optical Brighteners & ppb & 0.943 ± 0.00122 & 0.0806 ± 0.0014 & 0.0481 ± 0.000416 &  ±0.095 & 89.8 \\
    \bottomrule
  \end{tabularx}
  \end{adjustwidth}
\end{table}

\subsection{Physical Variables}

Physical variables included temperature, conductivity, pH, and turbidity. In the combined dataset, the distributions for temperature and conductivity had two distinct, nonoverlapping regions corresponding to the measurements from 23 November and the measurements from 9 December and 10 December, respectively. The pH value of the pond was slightly alkaline, showing a multimodal spatial distribution with values ranging from 8.0 to 8.6. As mentioned above, the pond water was very clear for each observation period, with most turbidity values ranging between 1 and 3 FNU and very few above 10.

The results of the hyperparameter-optimized RFR fits are shown in Figure~\ref{fig:physical-fit}. Temperature and conductivity show the best performance in the independent training set, with $R^2$ values of 1.0 (to three decimal places). Similarly, the pH model achieves an excellent fit, with most predictions falling close to the 1:1 line. Quantile--quantile plots for these three models further confirm that the distributions of the true and predicted values match. The turbidity model also achieves a strong fit, with a $R^2$ value of 0.905. The scatter diagram and quantile--quantile plot for this target show that the model performance degrades with larger values, for which deviation in the predicted distribution is apparent past 25 FNU.

\begin{figure}[H]
\vspace{-0.15in}
\includegraphics[width=0.9\columnwidth]{figures/results/fits/physical-fitres.png}
\vspace{-0.1in}
\caption{\hl{Scatter} %MDPI: 1. Please change hyphen into endash for range. 2. Please use commas to separate thousands for numbers with five or more digits (not four digits) in the picture, e.g., "10000" should be "10,000". 
 diagrams (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the hyperparameter-optimized RFR models for the physical variables measured by the USV.\label{fig:physical-fit}}
\end{figure}

The permutation importance of the top 25 features for each of the models of the physical variables is shown in Figure~\ref{fig:physical-fi}. All four models show strong dependence on the solar illumination geometry (solar azimuth, elevation, and solar zenith) as well as the viewing geometry (pitch, altitude, heading, etc.). All four models also include the total downwelling intensity and the total pixel intensity as highly important features. The temperature, conductivity, and pH models all include red-to-infrared reflectance bins and a combination of spectral indices within their most important features. Finally, the turbidity model relies mainly on blue wavelengths from 462 to 496 nm and did not include any spectral indices amongst the 25 most important features.

By applying the trained models to the full hyperspectral data cubes, we can produce maps of the distributions of the target variables as in Figure~\ref{fig:map-physical}. Here, we have chosen to show the map produced from the imagery collected during the 23 November collection period, as it showcases the largest spatial extent. The temperature map shows lower values near the shore, which is to be expected as the air temperature was below the water temperature. The temperature, conductivity, and pH maps all show a distinction between the main body of water and the alcove to the east, which receives little flow from the main body. The turbidity map confirms that the water is largely clear but has elevated levels near the shore.

\begin{figure}[H]

\vspace{-0.15in}
\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/fits/physical-ranking.pdf}
\vspace{-0.1in}
\caption{Ranked
 \hl{permutation} %MDPI: Please change the hyphen (-) into a minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
 importance for each feature in the physical variable models. Permutation importance measured the decrease in the model's $R^2$ value after replacing each feature in the prediction set with a random permutation of its values.\label{fig:physical-fi}}
\end{figure}

\begin{figure}[H]

\vspace{-0.15in}
\hspace{-6pt}\includegraphics[width=0.9\columnwidth]{figures/results/maps/physical.pdf}
\vspace{-0.05in}
\caption{\hl{Maps} %MDPI: Please change the hyphen (-) into a minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
 generated by applying each of the physical variable models to the hyperspectral data cubes collected on 23 November. Overlaid over the predictions are color-filled squares showing the associated in situ reference data for the same collection period. The size of the squares has been exaggerated for visualization. We note that there is good agreement between the model predictions and the reference data. \label{fig:map-physical}}
\end{figure}

\subsection{Ions}

The measured ions include $\mathrm{Ca}^{2+}$, $\mathrm{Cl}^{-}$, and $\mathrm{Na}^{+}$. All three measurements showed multimodal spatial distributions throughout the pond on each of the three collections. The scatter diagrams and quantile--quantile graphs for the resulting fits are shown in Figure~\ref{fig:ions-fit}. All three models achieved excellent fits, with $R^2$ values of 1.0, 0.996, and 0.993 on the independent testing set, respectively. Furthermore, there is no clear decrease in model performance for low or high concentrations; rather, for $\textrm{Cl}^{-}$ and $\textrm{Na}^{+}$, the models have the most difficulty in the middle of the target distributions.

The permutation importance rankings for the top 25 features of each of the ion models is shown in Figure~\ref{fig:ions-fi}. Here, we see that all three models depend on the solar illumination and viewing geometries as well as the total downwelling intensity and the total pixel intensity measured by the hyperspectral imager. All three models utilize a combination of spectral indices that combine green, red, and infrared reflectance bins. The $\textrm{Ca}^{+}$ and $\textrm{Cl}^{-}$ models depend on specific red wavelengths of 740 to 769 nm. $\textrm{Cl}^{-}$ and $\textrm{Na}^{+}$ also depend on green and yellow reflectance bins of 541 to 589 nanometers.

The maps produced by applying the fitted models to the hyperspectral data cubes for 23 November are shown in Figure~\ref{fig:map-ions}. Both positive ions $\mathrm{Ca}^{2+}$ and $\mathrm{Na}^{+}$ show high concentrations in the northwest portion of the pond, with lower values being measured in the alcove on the eastern side. Positive ion concentrations also appear to decrease near the shore. The negative ion $\mathrm{Cl}^{-}$ shows the opposite distribution, with larger values in the alcove to the east and the lowest values on the western side of the pond. The $\mathrm{Cl}^{-}$ ion concentration also appears to increase near the shore.

\begin{figure}[H]

\vspace{-0.15in}
\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/fits/ions-fitres.png}
\vspace{-0.1in}
\caption{\hl{Scatter} %MDPI: Please use commas to separate thousands for numbers with five or more digits (not four digits) in the picture, e.g., "10000" should be "10,000".
 diagrams (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the hyperparameter-optimized RFR models for the ion measurements made by the USV.\label{fig:ions-fit}}
\end{figure}

\vspace{-9pt}
\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\vspace{-0.1in}
\includegraphics[width=18 cm]{figures/results/fits/ions-ranking.pdf}
\vspace{-0.1in}
\end{adjustwidth}
\caption{\hl{Ranked} %MDPI: Please change the hyphen (-) into a minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
 permutation importance for the top 25 features of the ion models. The permutation importance measures the decrease in the model's $R^2$ value when each feature is replaced by a random permutation of its values.\label{fig:ions-fi}}
\end{figure}

\begin{figure}[H]

\vspace{-0.15in}
\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/maps/ions.pdf}
\vspace{-0.1in}
\caption{\hl{Maps} %MDPI: Please change the hyphen (-) into a minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
 generated by applying the trained ion models to the data cubes collected on 23 November. Overlaid on the maps are the in situ reference measurements for the same collection period. The size of the squares has been exaggerated for the visualization. We note that there is good agreement between the generated map and the reference data. \label{fig:map-ions}}
\end{figure}

\subsection{Biochemical Variables}

The measured biochemical variables include the pigments phycoerythrin, phycocyanin, and chlorophyll-a, as well as CDOM. Phycoerythrin and phycocyanin are both present in blue--green algae, and chlorophyll-a is found in all photosynthetic organisms except bacteria. In the combined dataset, the three pigments showed multimodal distributions separated by the collection day and with little spatial variation within each individual collection. CDOM showed a variable spatial distribution throughout the pond between the main water body and the eastern alcove on 23 November.

The results of the RFR fits for the biochemical variables are shown in Figure~\ref{fig:biochem-fit}. Phycoerythrin showed the best model performance, with an $R^2$ value of 0.995 in the training set. Both CDOM and chlorophyll-a achieved good performance, with $R^2$ values of 0.967 and 0.917 in the training set. Quantile--quantile plots indicate that the CDOM model degrades for values below 16 ppb, where data are sparse. The chlorophyll-a model shows the opposite trend, with poorer performance for concentrations above 5 ppb, for which there are very few records. The phycocyanin model had the lowest performance of the biochemical sensors, with an $R^2$ value of 0.727 and with model predictions rapidly decreasing in quality for concentrations greater than 3 ppb.

The permutation importance ranking of the top 25 features of each biochemical model is shown in Figure~\ref{fig:biochem-fi}. Again, all four models include the solar illumination and viewing geometries amongst their most important features as well as the total downwelling intensity and total pixel intensity at the imager. Additionally, all four models include some vegetation indices amongst the top features, which utilize combinations of blue, green, yellow, red, and infrared reflectance bands. The phycoerythrin model shows a preference for green reflectance bins from 544 to 556 nm, while the phycocyanin model prefers blue and red reflectance bins. The CDOM model uses mainly red reflectance values, whereas the chlorophyll-a model includes red, green, and blue reflectance bins.

The maps generated for the 23 November collection by applying trained biochemical models are shown in Figure~\ref{fig:map-biochem}. The three pigments show low concentrations in the body of water but elevated levels near the shore. The CDOM distribution shows spatial variability, with higher values in the eastern alcove---similar to the separation seen in the maps for temperature, conductivity, $\textrm{Ca}^{2+}$, $\textrm{Cl}^{-}$, and $\textrm{Na}^{+}$.

\begin{figure}[H]

\vspace{-0.15in}
\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/fits/biochemical-fitres.png}
\vspace{-0.1in}
\caption{\hl{Scatter} %MDPI: Please use commas to separate thousands for numbers with five or more digits (not four digits) in the picture, e.g., "10000" should be "10,000".
 plots (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the final hyperparameter-optimized models for the biochemical targets blue--green algae (phycoerythrin), CDOM, chlorophyll-a, and blue--green algae (phycocyanin). \label{fig:biochem-fit}}
\end{figure}

\begin{figure}[H]

\vspace{-0.15in}
\hspace{-6pt}\includegraphics[width=0.9\columnwidth]{figures/results/fits/biochemical-ranking.pdf}
\vspace{-0.1in}
\caption{\hl{Ranked} %MDPI: Please change the hyphen (-) into a minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
 permutation importance for each feature in the trained biochemical models. The permutation importance measures the decrease in the model's $R^2$ value after replacing each feature with a random permutation of its values.\label{fig:biochem-fi}}
\end{figure}

\vspace{-9pt}
\begin{figure}[H]

\vspace{-0.15in}
\hspace{-6pt}\includegraphics[width=0.92\columnwidth]{figures/results/maps/biochemical.pdf}
\vspace{-0.1in}
\caption{\hl{Maps} %MDPI: Please change the hyphen (-) into a minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
 \hl{generated} %MDPI: There are overlapped content (``longitude} in top and left subfigure). please revise.
 by applying the trained biochemical models to the data cubes collected on 23 November. Overlaid are the in situ reference data for the same collection period. The size of the squares has been exaggerated for the visualization. We note there is good agreement between the predicted map and the reference data. \label{fig:map-biochem}}
\end{figure}

\subsection{Chemical Variables}

The final two models to consider are for the measured chemical concentrations of crude oil (CO) and optical brighteners (OB). The crude oil measurement includes natural unprocessed petroleum, whereas optical brighteners consist of whitening agents that are often added to products such as soaps, detergents, and cleaning agents. Both the crude oil and optical brightener measurements show multi-modal spatial distributions across each collection period. Scatter diagrams and quantile--quantile plots for the fitted models are shown in Figure~\ref{fig:chemicals-fit}. Both models achieve good performance, with $R^2$ values of 0.957 and 0.941 for CO and OB, respectively, %Please ensure meaning has been retained. 
on the holdout test set. The performance of the CO model degrades for concentrations below 24 ppb, for which there are few records. Similarly, the OB model shows worse performance for concentrations below roughly 3.5 ppb.

The ranked permutation importances of the top 25 features for each model are shown in Figure~\ref{fig:chemicals-fi}. Both models rank the solar illumination and viewing geometries together with the total downwelling intensity and total pixel intensities amongst the top features. Both models include a combination of spectral indices using blue, green, yellow, red, and infrared reflectance bins. Additionally, the CO model includes green--yellow reflectances from 539 to 589 nm as well as red reflectances from 749 to 769 nm. The OB model includes yellow reflectance at 584.6 nm and red reflectance bins.

The maps generated by applying the CO and OB models to the 23 November data cubes are shown in Figure~\ref{fig:map-chem}. Both models show a distinct spatial distribution, with elevated values in the eastern alcove of the pond---similar to the CDOM distribution in Figure~\ref{fig:map-biochem}.

% Example of a figure that spans the whole page width. The same concept works for tables, too.
%\begin{figure}[H]
%\begin{adjustwidth}{-\extralength}{0cm}
%\centering
%\includegraphics[width=18.0cm]{figures/results/map-combined.pdf}
%\end{adjustwidth}
%\caption{Maps generated by applying the ML model to hyperspectral data cubes. (\textbf{a}) The CDOM model applied to the 11-23 collection. (\textbf{b}) The CDOM model applied the the 12-09 collection. (\textbf{c}) the Crude Oil model applied to the 11-23 collection. (\textbf{d}) The Crude Oil model applied to the 12-09 collection. In each panel, boat data are overlaid as color-filled squares. We note that there is good agreement between estimated values at boat locations and the in situ reference measurements. \label{fig:maps}}
%\end{figure}  
\begin{figure}[H]

\vspace{-0.21in}
\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/fits/chemical-fitres.png}
\vspace{-0.11in}
\caption{\hl{Scatter} %MDPI: Please use commas to separate thousands for numbers with five or more digits (not four digits) in the picture, e.g., "10000" should be "10,000".
 diagrams (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the hyperparameter-optimized RFR models for the chemical variables measured by the USV.\label{fig:chemicals-fit}}
\end{figure}

\vspace{-9pt}
\begin{figure}[H]
\vspace{-0.15in}
\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/fits/chemical-ranking.pdf}
\vspace{-0.15in}
\caption{\hl{Ranked} %MDPI: Please change the hyphen (-) into a minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
 permutation importance for the top 25 features of the chemical models. The permutation importance measures the decrease in the model's $R^2$ value after replacing each feature in the prediction set with a random permutation of its values.\label{fig:chemicals-fi}}
\end{figure}

\begin{figure}[H]

\vspace{-0.2in}
\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/maps/chemical.pdf}
\vspace{-0.1in}
\caption{\hl{Maps} %MDPI: Please change the hyphen (-) into a minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
 generated by applying the trained chemical variable models to the hyperspectral data cubes collected on 23 November. Overlaid are color-filled squares showing the in situ reference data for the same collection period. The size of the squares is exaggerated for the visualization. We note that there is good agreement between the model predictions and reference data.\label{fig:map-chem}}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion} \label{sec:discussion}

In recent years, much effort has been spent on the curation of comprehensive datasets combining water quality records with decades of satellite imagery to enable the development of new methods for retrieving water quality parameters. For example, Aurin et al. curated over 30 years of oceanographic field campaign data with associated coincident satellite imagery \cite{aurin2018remote}. Similarly, Ross et al. combined more than 600,000 records of dissolved organic carbon, chlorophyll-a and other water quality variables with historical Landsat reflectance data for the period 1984--2019 \cite{ross2019aquasat}. The sensing paradigm we have demonstrated here was able to rapidly collect comparable volumes of data within the span of just three observation periods. Therefore, despite the fact that individual UAV tracks cover far less spatial extent than remote sensing imagery, the ability to collect coordinated in situ measurements together with detailed hyperspectral images offers a significant improvement over these traditional approaches. With a coordinated robot team, one does not need to rely on infrequent satellite overpasses when planning data collection. Furthermore, the time offset between reference measurements and remote sensing is significantly reduced from days to minutes.

This study is not the first to employ UAVs equipped with multispectral or hyperspectral imagers for the purpose of assessing water composition and quality. Indeed there are many such examples focused on inferring optically active and inactive water quality parameters using band ratios and machine learning methods \cite{vogt2016near,lu2021retrieval, zhang2022selection}. The key advancement demonstrated by our robot team is the ability to combine UAV-borne hyperspectral imagers together with comprehensive, in situ sensing for a significant improvement in data volume. Purposefully coordinating USV sampling with the flight tracks of the UAV greatly accelerates data collection by removing the need to acquire individual samples for the calibration of water quality models. Additionally, the USV facilitates rapid validation of model predictions. When a trained model applied to collected hyperspectral imagery suggests elevated levels of a particular water quality parameter, the USV can quickly be provisioned to confirm these estimates with its reference instruments.

In \cite{robotTeam1}, we introduced this paradigm. In this study, we have built on this approach in three new ways. First, we have demonstrated the ability to effectively combine observations from disparate collections by augmenting the machine learning models with sufficient features describing the illumination and viewing geometries. As Figure~\ref{fig:downwelling-hist} indicates, we observed variation in the total downwelling intensity between the images collected on the same day \textit{\hl{and}} between each separate collection period. These within-collection variations are due to a combination of the stability of the UAV (on which the upward facing downwelling irradiance spectrometer is mounted) together with the occasional interference of clouds. Moreover, the assumption that the water's surface can be treated as Lambertian is clearly violated when the water is not perfectly still. Despite the potential impact of these limitations on the quality of the resulting reflectance data cubes, the smoothness of the maps generated by our models suggests that we have provided sufficient context by including the relevant solar illumination and viewing angles as additional features in the final dataset.  This fact is reinforced by the position of these variables as the most important features for \textit{each} of the estimated water quality variables. As long as we are primarily interested in these values and not the reflectances themselves, we are able to successfully account for these lighting effects when combining data from multiple collections.

The second contribution of this study is to explore the breadth of possible water quality and composition parameters that can be accurately mapped by hyperspectral imagery collected by the UAV. The results presented here confirm the ability of the robot team to predict optically active parameters including blue--green algae, chlorophyll-a, CDOM, crude oil, optical brighteners, turbidity, and temperature. Additionally, we are also able to infer the distributions of optically inactive variables including conductivity, pH, and ion concentrations. Other studies using multispectral and hyperspectral remote sensing imagery have also estimated optically inactive water quality parameters, with the ability to do so stemming from the relationship of these variables to optically active properties of the water \cite{vakili2020determination,guo2021machine,niu2021deep}. We note that in our investigation, the models trained for many of these variables outperformed their optically active counterparts. As the abundance of these variables is likely tied to the specific composition and content of the pond, it is unlikely that models trained for these optically inactive variables will generalize to other bodies of water.

The third contribution of this work is the extension of our machine learning approach to enable uncertainty quantification through conformal prediction. For water quality risk assessment, the trustworthiness of model predictions is of equal or greater importance to the values themselves. However, robust uncertainty quantification has historically been challenging for many machine learning models, which behave like black boxes.
Conformal prediction is an attractive approach to enable model-agnostic uncertainty estimation and has recently seen adoption to remote sensing classification tasks such as land-type classification and object identification \cite{valle2023quantifying, zhu2024inductive}. In this setting, the goal is to produce predictive \textit{\hl{sets}} guaranteed to contain the correct class labels at a predetermined confidence level. Nevertheless, conformal prediction works equally well for regression tasks. By leveraging the large data volume collected by the robot team, we are able to simultaneously train predictive models and evaluate confidence intervals for their predictions. As the final column of Table~\ref{tab:fit-results} confirms, the empirical coverage on the holdout testing set provided by the inferred confidence intervals achieves the desired coverage to within 1\%. We chose to use a 90\% confidence interval for this study, but this can easily be adapted to suite the needs of a specific application if greater confidence is required.

Despite the wealth of information provided by the increased resolution of hyperspectral images, their considerable size impedes their \textit{\hl{complete}} utilization in real-time applications. Often, much of the available spectral information is discarded in favor of indices like the NDVI, which can be quickly computed as images are captured \cite{horstrand2019uav}. Utilizing machine learning allows us to take advantage of the full spectrum captured by each pixel while simultaneously reducing the size of the final data product to single-band ``images'' of selected water quality variables. We note that training a reduced-feature model without further hyperparameter optimization takes roughly one minute per target variable of interest using the processing computer included on the UAV. This means that, in principle, training data can be collected by the USV, imagery can be acquired and processed by the UAV, coincident records can be selected, and the resulting dataset can be used to train machine learning models all while investigators are still in the field. Analyzing the maps produced by applying each trained model enables areas of interest to be readily pinpointed, as demonstrated by the identification of slightly elevated levels of %Please ensure meaning has been retained. 
crude oil, optical brighteners, and CDOM in the eastern alcove of the pond on 23 November.

Finally, we note that the high spectral resolution of the UAV imagery together with the ability to collect precisely co-located reference measurements provides fertile ground for the development of new spectral indices targeted towards water quality variables. In this paper, we have shown that permutation importance ranking for trained machine learning models enables a straightforward interpretation of the relative values of each reflectance bin to the final model predictions. In future work, we plan to utilize this information to identify combinations of spectral bands that can be applied to remote sensing imagery captured by satellites equipped with hyperspectral imagers. The recently launched Environmental Mapping and Analysis Program (EnMAP) is one such example and includes over 91 spectral bands in the VNIR that overlap with those of our hyperspectral imager \cite{Storch2023TheEI}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

In this study, we address two key limitations of current remote sensing approaches to characterize water quality: namely, the limited spatial, spectral, and temporal resolution provided by existing satellite platforms and the lack of comprehensive in situ measurements needed to validate remote sensing data products. By equipping an autonomous USV with a suite of reference sensors, we rapidly collect significantly more data than existing approaches that rely on the collection of individual samples for lab analysis or are constrained to continuous sensing at fixed sites. Utilizing an autonomous UAV equipped with a hyperspectral imager in tandem with the USV allows us to quickly generate aligned datasets that are used to train machine learning models mapping measured reflectance spectra to the desired water quality variables. By virtue of this increased data volume, we are able to simultaneously estimate the uncertainty of our models by using conformal prediction. Finally, the hyperspectral data cube processing workflow employed onboard the UAV makes it possible to deploy these trained models to swiftly generate maps of the target variables across bodies of water. The rapid turnaround time from data collection to model deployment is critical for real-time water quality evaluation and risk assessment.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, \hl{Table S1:} %MDPI: please provide an independent file to indicate supplementary materials.
 Hyperspectral reflectance indices.}

% Only for journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title. A supporting video article is available at doi: link.}

% Only for journal Hardware:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.\vspace{6pt}\\
%\begin{tabularx}{\textwidth}{lll}
%\toprule
%\textbf{Name} & \textbf{Type} & \textbf{Description} \\
%\midrule
%S1 & Python script (.py) & Script of python source code used in XX \\
%S2 & Text (.txt) & Script of modelling code used to make Figure X \\
%S3 & Text (.txt) & Raw data from experiment X \\
%S4 & Video (.mp4) & Video demonstrating the hardware in use \\
%... & ... & ... \\
%\bottomrule
%\end{tabularx}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Conceptualization, D.J.L.; methodology, \hl{J.W.} %MDPI: We changed all J.L.W. into J.W. Please confirm.
 and D.J.L; software, J.W.; field deployment and preparation, J.W., A.A., L.O.H.W., S.T., B.F., P.H., M.I., M.L., D.S., and D.J.L.; validation, J.W.; formal analysis, J.W.; investigation J.W.; resources, D.J.L.; data curation, J.W., A.A., L.O.H.W., and D.J.L; writing---original draft preparation, J.W.; writing---review and editing, J.W. and D.J.L.; visualization, J.W.; supervision, D.J.L.; project administration, D.J.L.; funding acquisition, D.J.L. All authors have read and agreed to the published version of the manuscript.
}

\newpage
\funding{This research was funded by the following grants: the Texas National Security Network Excellence Fund award for Environmental Sensing Security Sentinels; the SOFWERX award for Machine Learning for Robotic Teams %Please ensure meaning has been retained. 
	and NSF Award OAC-2115094; support from the University of Texas at Dallas Office of Sponsored Programs, Dean of Natural Sciences and Mathematics, and Chair of the Physics Department is gratefully acknowledged; TRECIS CC* Cyberteam (NSF \#2019135); NSF OAC-2115094 Award; and EPA P3 grant number 84057001-0.
}

\institutionalreview{Not applicable.}

\informedconsent{Not applicable.}

\dataavailability{The raw data supporting the conclusions of this article will be made available by the authors on request.}

% Only for journal Nursing Reports
%\publicinvolvement{Please describe how the public (patients, consumers, carers) were involved in the research. Consider reporting against the GRIPP2 (Guidance for Reporting Involvement of Patients and the Public) checklist. If the public were not involved in any aspect of the research add: ``No public involvement in any aspect of this research''.}

% Only for journal Nursing Reports
%\guidelinesstandards{Please add a statement indicating which reporting guideline was used when drafting the report. For example, ``This manuscript was drafted against the XXX (the full name of reporting guidelines and citation) for XXX (type of research) research''. A complete list of reporting guidelines can be accessed via the equator network: \url{https://www.equator-network.org/}.}

\acknowledgments{Don MacLaughlin, Scotty MacLaughlin, and the city of Plano, TX, are gratefully acknowledged for allowing us to deploy the autonomous robot team on their property.  Christopher Simmons is gratefully acknowledged for his computational support. We thank  Antonio Mannino for his advice with regard to selecting the robotic boat's sensing suite. Annette Rogers is gratefully acknowledged for supporting the arrangement of insurance coverage. Steven Lyles is gratefully acknowledged for supporting the arrangement of a secure place for the robot team. The authors acknowledge the OIT-Cyberinfrastructure Research Computing group at the University of Texas at Dallas and the TRECIS CC* Cyberteam (NSF \#2019135) for providing HPC resources that contributed to this research; the authors also acknowledge their receipt of the %Please ensure meaning has been retained. 
	NSF OAC-2115094 Award and EPA P3 grant number 84057001-0.}

\conflictsofinterest{The authors declare no conflicts of interest.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional

%% Only for journal Encyclopedia
%\entrylink{The Link to this entry published on the encyclopedia platform.}

\abbreviations{Abbreviations}{
The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
GPS & Global Positioning System \\ 
INS & Inertial Navigation System \\
UTM & Universal Transverse Mercator \\
UV & Ultraviolet \\
ML & Machine Learning \\
USV & Uncrewed Surface Vessel \\
UAV & Unmanned Aerial Vehicle \\
CDOM & Colored Dissolved Organic Matter \\
CO & Crude Oil \\ 
OB & Optical Brighteners \\
FNU & Formazin Nephelometric Unit \\
RFR & Random Forest Regressor \\
RMSE & Root Mean Square Error \\ 
MAE & Mean Absolute Error \\
RENDVI & Red-Edge Normalized Difference Vegetation Index
\end{tabular}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixstart
\appendix
\section[\appendixname~\thesection]{}\label{Model Hyperparameters}
%% \subsection[\appendixname~\thesubsection]{}

\vspace{-6pt}
\begin{table}[H] 
\caption{Final hyperparameter values for each target model. The number of trees and the sampling ratio were optimized using a random search. The maximum tree depth was fixed to 20 to limit overfitting and to control the size of the final model. The number of sub-features was set to the square root of the total number of features, and the minimum samples per leaf and minimum samples per split were left to their default values. \label{tab:hyperparameters}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCCCCCC}
\toprule
\textbf{Target}	& \textbf{Number of Trees}	& \textbf{Sampling Ratio} & \textbf{Maximum Tree Depth} & \textbf{Number of Sub-Features} & \textbf{Minimum Samples per Leaf} & \textbf{Minimum Samples per Split}\\
\midrule
Temperature & 153 & 0.979 & 20 & 5 & 1 & 2 \\
Conductivity & 154 & 0.992 & 20 & 5 & 1 & 2\\
pH & 103 & 0.972 & 20 & 5 & 1 & 2\\
Turbidity & 158 & 0.998 & 20 & 5 & 1 & 2\\

\bottomrule
\end{tabularx}
%\end{adjustwidth}
\end{table}

\begin{table}[H]\ContinuedFloat
\small
\caption{\textit{Cont.}}

\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCCCCCC}
\toprule
\textbf{Target}	& \textbf{Number of Trees}	& \textbf{Sampling Ratio} & \textbf{Maximum Tree Depth} & \textbf{Number of Sub-Features} & \textbf{Minimum Samples per Leaf} & \textbf{Minimum Samples per Split}\\
\midrule
$\mathrm{Ca}^{2+}$ & 172 & 0.984 & 20 & 5 & 1 & 2\\
$\mathrm{Cl^-}$ & 110 & 0.999 & 20 & 5 & 1 & 2\\
$\mathrm{Na^+}$ & 103 & 0.972 & 20 & 5 & 1 & 2\\
%\begin{adjustwidth}{-\extralength}{0cm}%\centering
%Blue-Green Algae (Phycoerythrin) & 153 & 0.979 & 20 & 5 & 1 & 2\\
Phycoerythrin & 158 & 0.998 & 20 & 5 & 1 & 2\\
CDOM & 157 & 0.982 & 20 & 5 & 1 & 2\\
Chlorophyll-a & 158 & 0.998 & 20 & 5 & 1 & 2\\
%Blue-Green Algae (Phycocyanin) & 153 & 0.979 & 20 & 5 & 1 & 2\\
Phycocyanin & 142 & 0.995 & 20 & 5 & 1 & 2\\
Crude Oil & 154 & 0.992 & 20 & 5 & 1 & 2\\
Optical Brighteners & 157 & 0.982 & 20 & 5 & 1 & 2\\
\bottomrule
\end{tabularx}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{adjustwidth}{-\extralength}{0cm}
%\printendnotes[custom] % Un-comment to print a list of endnotes

\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================

\begin{thebibliography}{999}

\bibitem[Melesse et~al.(2007)Melesse, Weng, Thenkabail, and
  Senay]{melesse2007remote}
Melesse, A.M.; Weng, Q.; Thenkabail, P.S.; Senay, G.B.
\newblock Remote sensing sensors and applications in environmental resources
  mapping and modelling.
\newblock {\em Sensors} {\bf 2007}, {\em 7},~3209--3241.

\bibitem[Joyce et~al.(2009)Joyce, Belliss, Samsonov, McNeill, and
  Glassey]{joyce2009review}
Joyce, K.E.; Belliss, S.E.; Samsonov, S.V.; McNeill, S.J.; Glassey, P.J.
\newblock A review of the status of satellite remote sensing and image
  processing techniques for mapping natural hazards and disasters.
\newblock {\em Prog. Phys. Geogr.} {\bf 2009}, {\em 33},~183--207.

\bibitem[Aurin et~al.(2018)Aurin, Mannino, and Lary]{aurin2018remote}
Aurin, D.; Mannino, A.; Lary, D.J.
\newblock Remote sensing of CDOM, CDOM spectral slope, and dissolved organic
  carbon in the global ocean.
\newblock {\em Appl. Sci.} {\bf 2018}, {\em 8},~2687.

\bibitem[Ross et~al.(2019)Ross, Topp, Appling, Yang, Kuhn, Butman, Simard, and
  Pavelsky]{ross2019aquasat}
Ross, M.R.; Topp, S.N.; Appling, A.P.; Yang, X.; Kuhn, C.; Butman, D.; Simard,
  M.; Pavelsky, T.M.
\newblock AquaSat: A data set to enable remote sensing of water quality for
  inland waters.
\newblock {\em Water Resour. Res.} {\bf 2019}, {\em 55},~10012--10025.

\bibitem[Fingas and Brown(2017)]{fingas2017review}
Fingas, M.; Brown, C.E.
\newblock A review of oil spill remote sensing.
\newblock {\em Sensors} {\bf 2017}, {\em 18},~91.

\bibitem[Koponen et~al.(2007)Koponen, Attila, Pulliainen, Kallio,
  Pyh{\"a}lahti, Lindfors, Rasmus, and Hallikainen]{remote-sensing-finland}
Koponen, S.; Attila, J.; Pulliainen, J.; Kallio, K.; Pyh{\"a}lahti, T.;
  Lindfors, A.; Rasmus, K.; Hallikainen, M.
\newblock A case study of airborne and satellite remote sensing of a spring
  bloom event in the Gulf of Finland.
\newblock {\em Cont. Shelf Res.} {\bf 2007}, {\em 27},~228--244.

\bibitem[Bonansea et~al.(2015)Bonansea, Rodriguez, Pinotti, and
  Ferrero]{bonansea2015using}
Bonansea, M.; Rodriguez, M.C.; Pinotti, L.; Ferrero, S.
\newblock Using multi-temporal Landsat imagery and linear mixed models for
  assessing water quality parameters in R{\'\i}o Tercero reservoir (Argentina).
\newblock {\em Remote Sens. Environ.} {\bf 2015}, {\em 158},~28--41.

\bibitem[Absalon et~al.(2023)Absalon, Matysik, Wo{\'z}nica, and
  Janczewska]{absalon2023detection}
Absalon, D.; Matysik, M.; Wo{\'z}nica, A.; Janczewska, N.
\newblock Detection of changes in the hydrobiological parameters of the Oder
  River during the ecological disaster in July 2022 based on multi-parameter
  probe tests and remote sensing methods.
\newblock {\em Ecol. Indic.} {\bf 2023}, {\em 148},~110103.

\bibitem[Lary(2010)]{lary2010artificial}
Lary, D.J.
\newblock Artificial intelligence in geoscience and remote sensing. In {\em
  Geoscience and Remote Sensing New Achievements}; \hl{IntechOpen:} %MDPI: Please add the location of the publisher (City and Country).
  2010.

\bibitem[Peterson et~al.(2020)Peterson, Sagan, and Sloan]{peterson2020deep}
Peterson, K.T.; Sagan, V.; Sloan, J.J.
\newblock Deep learning-based water quality estimation and anomaly detection
  using Landsat-8/Sentinel-2 virtual constellation and cloud computing.
\newblock {\em GIScience  Remote Sens.} {\bf 2020}, {\em 57},~510--525.

\bibitem[Belgiu and Dr{\u{a}}gu{\c{t}}(2016)]{belgiu2016random}
Belgiu, M.; Dr{\u{a}}gu{\c{t}}, L.
\newblock Random forest in remote sensing: A review of applications and future
  directions.
\newblock {\em ISPRS J. Photogramm. Remote Sens.} {\bf 2016},
  {\em 114},~24--31.

\bibitem[Sagan et~al.(2020)Sagan, Peterson, Maimaitijiang, Sidike, Sloan,
  Greeling, Maalouf, and Adams]{sagan2020monitoring}
Sagan, V.; Peterson, K.T.; Maimaitijiang, M.; Sidike, P.; Sloan, J.; Greeling,
  B.A.; Maalouf, S.; Adams, C.
\newblock Monitoring inland water quality using remote sensing: Potential and
  limitations of spectral indices, bio-optical simulations, machine learning,
  and cloud computing.
\newblock {\em Earth-Sci. Rev.} {\bf 2020}, {\em 205},~103187.

\bibitem[Hruska et~al.(2012)Hruska, Mitchell, Anderson, and
  Glenn]{hruska2012radiometric}
Hruska, R.; Mitchell, J.; Anderson, M.; Glenn, N.F.
\newblock Radiometric and geometric analysis of hyperspectral imagery acquired
  from an unmanned aerial vehicle.
\newblock {\em Remote Sens.} {\bf 2012}, {\em 4},~2736--2752.

\bibitem[Ad{\~a}o et~al.(2017)Ad{\~a}o, Hru{\v{s}}ka, P{\'a}dua, Bessa, Peres,
  Morais, and Sousa]{adao2017hyperspectral}
Ad{\~a}o, T.; Hru{\v{s}}ka, J.; P{\'a}dua, L.; Bessa, J.; Peres, E.; Morais,
  R.; Sousa, J.J.
\newblock Hyperspectral imaging: A review on UAV-based sensors, data processing
  and applications for agriculture and forestry.
\newblock {\em Remote Sens.} {\bf 2017}, {\em 9},~1110.

\bibitem[Banerjee et~al.(2020)Banerjee, Raval, and Cullen]{banerjee2020uav}
Banerjee, B.P.; Raval, S.; Cullen, P.
\newblock UAV-hyperspectral imaging of spectrally complex environments.
\newblock {\em Int. J. Remote Sens.} {\bf 2020}, {\em
  41},~4136--4159.

\bibitem[P{\'a}dua et~al.(2017)P{\'a}dua, Vanko, Hru{\v{s}}ka, Ad{\~a}o, Sousa,
  Peres, and Morais]{padua2017uas}
P{\'a}dua, L.; Vanko, J.; Hru{\v{s}}ka, J.; Ad{\~a}o, T.; Sousa, J.J.; Peres,
  E.; Morais, R.
\newblock UAS, sensors, and data processing in agroforestry: A review towards
  practical applications.
\newblock {\em Int. J.  Remote Sens.} {\bf 2017}, {\em
  38},~2349--2391.

\bibitem[Arroyo-Mora et~al.(2019)Arroyo-Mora, Kalacska, Inamdar, Soffer,
  Lucanus, Gorman, Naprstek, Schaaf, Ifimov, Elmer,
  et~al.]{arroyo2019implementation}
Arroyo-Mora, J.P.; Kalacska, M.; Inamdar, D.; Soffer, R.; Lucanus, O.; Gorman,
  J.; Naprstek, T.; Schaaf, E.S.; Ifimov, G.; Elmer, K.;  et~al.
\newblock Implementation of a UAV--hyperspectral pushbroom imager for
  ecological monitoring.
\newblock {\em Drones} {\bf 2019}, {\em 3},~12.

\bibitem[Kurihara et~al.(2020)Kurihara, Ishida, and
  Takahashi]{kurihara2020unmanned}
Kurihara, J.; Ishida, T.; Takahashi, Y.
\newblock Unmanned Aerial Vehicle (UAV)-based hyperspectral imaging system for
  precision agriculture and forest management.
\newblock In {\em Unmanned Aerial Vehicle: Applications in Agriculture and
  Environment}; \hl{2020} %MDPI: Please add the name of the publisher and their location.
; pp. 25--38.

\bibitem[Ehmann et~al.(2019)Ehmann, Kelleher, and Condon]{ehmann2019monitoring}
Ehmann, K.; Kelleher, C.; Condon, L.E.
\newblock Monitoring turbidity from above: Deploying small unoccupied aerial
  vehicles to image in-stream turbidity.
\newblock {\em Hydrol. Process.} {\bf 2019}, {\em 33},~1013--1021.

\bibitem[Lu et~al.(2021)Lu, Si, Wei, Li, Xia, Ye, and Xia]{lu2021retrieval}
Lu, Q.; Si, W.; Wei, L.; Li, Z.; Xia, Z.; Ye, S.; Xia, Y.
\newblock Retrieval of water quality from UAV-borne hyperspectral imagery: A
  comparative study of machine learning algorithms.
\newblock {\em Remote Sens.} {\bf 2021}, {\em 13},~3928.

\bibitem[Zhang et~al.(2022)Zhang, Zeng, and He]{zhang2022selection}
Zhang, D.; Zeng, S.; He, W.
\newblock Selection and Quantification of Best Water Quality Indicators Using
  UAV-Mounted Hyperspectral Data: A Case Focusing on a Local River Network in
  Suzhou City, China.
\newblock {\em Sustainability} {\bf 2022}, {\em 14},~16226.

\bibitem[Lary et~al.(2021)Lary, Schaefer, Waczak, Aker, Barbosa, Wijeratne,
  Talebi, Fernando, Sadler, Lary, and Lary]{robotTeam1}
Lary, D.J.; Schaefer, D.; Waczak, J.; Aker, A.; Barbosa, A.; Wijeratne, L.O.H.;
  Talebi, S.; Fernando, B.; Sadler, J.Z.; Lary, T.;  et~al.
\newblock Autonomous Learning of New Environments with a Robotic Team Employing
  Hyper-Spectral Remote Sensing, Comprehensive In-Situ Sensing and Machine
  Learning.
\newblock {\em Sensors} {\bf 2021}, {\em 21}, 2240.

\bibitem[Meier(2010)]{qgroundcontrol}
Meier, L.
\newblock QGroundControl.
\newblock  MAVLink Micro Air Vehicle Communication Protocol. 2010. Available
  online: \url{http://qgroundcontrol. org/mavlink/start} (accessed on 30 January
  2019).

\bibitem[De~Marco et~al.(2007)De~Marco, Clarke, and Pejcic]{de2007ion}
De~Marco, R.; Clarke, G.; Pejcic, B.
\newblock Ion-selective electrode potentiometry in environmental analysis.
\newblock {\em Electroanal. An Int. J. Devoted Fundam. Pract. Asp. Electroanal.} {\bf 2007}, {\em 19},~1987--2001.

\bibitem[Trees et~al.(2002)Trees, Bidigare, Karl, Van~Heukelem, and
  Dore]{trees2002fluorometric}
Trees, C.C.; Bidigare, R.R.; Karl, D.M.; Van~Heukelem, L.; Dore, J.
\newblock Fluorometric chlorophyll a: Sampling, laboratory methods, and data
  analysis protocols.
\newblock In \emph{Ocean Optics Protocols for Satellite Ocean Color Sensor
  Validation, NASA/TM-2002-210004/Rev3-Vol2};  Mueller, J.L., Fargion, G.S., Eds.; NASA Goddard Space Flight Center: Greenbelt, MD, USA, {2002}; pp. 269--283.

\bibitem[Tillman(2017)]{tillman2017evaluation}
Tillman, E.F.
\newblock \emph{Evaluation of the Eureka Manta2 Water-Quality Multiprobe Sonde};
\newblock Technical report; \hl{US Geological Survey:} %MDPI: Please add the location of the publisher (City and Country).
  2017.

\bibitem[Brient et~al.(2008)Brient, Lengronne, Bertrand, Rolland, Sipel,
  Steinmann, Baudin, Legeas, Rouzic, and Bormans]{Brient2008APP}
Brient, L.; Lengronne, M.; Bertrand, E.; Rolland, D.C.; Sipel, A.; Steinmann,
  D.; Baudin, I.; Legeas, M.; Rouzic, B.L.; Bormans, M.
\newblock A phycocyanin probe as a tool for monitoring cyanobacteria in
  freshwater bodies.
\newblock {\em J. Environ. Monit. JEM} {\bf 2008}, {\em 10},~248--255.

\bibitem[Boyer et~al.(2009)Boyer, Kelble, Ortner, and
  Rudnick]{boyer2009phytoplankton}
Boyer, J.N.; Kelble, C.R.; Ortner, P.B.; Rudnick, D.T.
\newblock Phytoplankton bloom status: Chlorophyll a biomass as an indicator of
  water quality condition in the southern estuaries of Florida, USA.
\newblock {\em Ecol. Indic.} {\bf 2009}, {\em 9},~S56--S67.

\bibitem[Brown and Fingas(2003)]{brown2003review}
Brown, C.E.; Fingas, M.F.
\newblock Review of the development of laser fluorosensors for oil spill
  application.
\newblock {\em Mar. Pollut. Bull.} {\bf 2003}, {\em 47},~477--484.

\bibitem[Cao et~al.(2009)Cao, Griffith, and Weisberg]{cao2009evaluation}
Cao, Y.; Griffith, J.F.; Weisberg, S.B.
\newblock Evaluation of optical brightener photodecay characteristics for
  detection of human fecal contamination.
\newblock {\em Water Res.} {\bf 2009}, {\em 43},~2273--2279.

\bibitem[Piper(1944)]{piper1944graphic}
Piper, A.M.
\newblock A graphic procedure in the geochemical interpretation of
  water-analyses.
\newblock {\em Eos Trans. Am. Geophys. Union} {\bf 1944}, {\em
  25},~914--928.

\bibitem[Dordoni et~al.(2023)Dordoni, Zappal{\`a}, and
  Barth]{dordoni2023preliminary}
Dordoni, M.; Zappal{\`a}, P.; Barth, J.A.
\newblock A preliminary global hydrochemical comparison of lakes and
  reservoirs.
\newblock {\em Front. Water} {\bf 2023}, {\em 5},~1084050.

\bibitem[Pace et~al.(2012)Pace, Reche, Cole, Fern{\'a}ndez-Barbero, Mazuecos,
  and Prairie]{pace2012ph}
Pace, M.L.; Reche, I.; Cole, J.J.; Fern{\'a}ndez-Barbero, A.; Mazuecos, I.P.;
  Prairie, Y.T.
\newblock pH change induces shifts in the size and light absorption of
  dissolved organic matter.
\newblock {\em Biogeochemistry} {\bf 2012}, {\em 108},~109--118.

\bibitem[Ruddick et~al.(2019)Ruddick, Voss, Banks, Boss, Castagna, Frouin,
  Hieronymi, Jamet, Johnson, Kuusk, et~al.]{reflectance-conversion}
Ruddick, K.G.; Voss, K.; Banks, A.C.; Boss, E.; Castagna, A.; Frouin, R.;
  Hieronymi, M.; Jamet, C.; Johnson, B.C.; Kuusk, J.;  et~al.
\newblock A review of protocols for fiducial reference measurements of
  downwelling irradiance for the validation of satellite remote sensing data
  over water.
\newblock {\em Remote Sens.} {\bf 2019}, {\em 11},~1742.

\bibitem[M{\"u}ller et~al.(2002)M{\"u}ller, Lehner, Muller, Reinartz,
  Schroeder, and Vollmer]{GeorectificationMuller}
M{\"u}ller, R.; Lehner, M.; Muller, R.; Reinartz, P.; Schroeder, M.; Vollmer,
  B.
\newblock \emph{A Program for Direct Georeferencing of Airborne and Spaceborne Line
  Scanner Images};
\newblock  \hl{2002.} %MDPI: Please add the name of the publisher and their location.

\bibitem[B{\"a}umker and Heimes(2001)]{GeorectificationBaumker}
B{\"a}umker, M.; Heimes, F.
\newblock New calibration and computing method for direct georeferencing of
  image and scanner data using the position and angular data of an hybrid
  inertial navigation system.
\newblock In Proceedings of the OEEPE Workshop, Integrated Sensor Orientation, Hannover, Germany,
 17--18 September  2001; pp. 1--17.

\bibitem[Mostafa and Schwarz(2000)]{GeorectificationMostafa}
Mostafa, M.M.R.; Schwarz, K.P.
\newblock A Multi-Sensor System for Airborne Image Capture and Georeferencing.
\newblock {\em Photogramm. Eng.  Remote Sens.} {\bf 2000}, {\em
  66},~1417--1424.

\bibitem[Bezanson et~al.(2012)Bezanson, Karpinski, Shah, and Edelman]{julia-1}
Bezanson, J.; Karpinski, S.; Shah, V.B.; Edelman, A.
\newblock Julia: A fast dynamic language for technical computing.
\newblock {\em arXiv} {\bf 2012}, arXiv:1209.5145.

\bibitem[env(2023)]{envi_vegetation_indices}
\textls[-25]{Vegetation Indices Background,  2023.
  Available online:  \url{https://www.nv5geospatialsoftware.com/docs/backgroundvegetationindices.html}} (accessed on 3 January 2024).

\bibitem[Thenkabail et~al.(2018)Thenkabail, Lyon, and
  Huete]{thenkabail2018hyperspectral}
Thenkabail, P.S.; Lyon, J.G.; Huete, A.
\newblock {\em Hyperspectral Indices and Image Classifications for Agriculture
  and Vegetation}; CRC Press:  \hl{Boca Raton, FL, USA,} %We added the location of publisher. Please confirm
 2018.

\bibitem[Kaufman and Tanre(1992)]{kaufman1992atmospherically}
Kaufman, Y.J.; Tanre, D.
\newblock Atmospherically resistant vegetation index (ARVI) for EOS-MODIS.
\newblock {\em IEEE Trans. Geosci.  Remote Sens.} {\bf 1992},
  {\em 30},~261--270.

\bibitem[Zheng et~al.(2018)Zheng, Huang, Cui, Shi, and Liu]{SpectralIndexWheat}
Zheng, Q.; Huang, W.; Cui, X.; Shi, Y.; Liu, L.
\newblock New Spectral Index for Detecting Wheat Yellow Rust Using Sentinel-2
  Multispectral Imagery.
\newblock {\em Sensors} {\bf 2018}, {\em 18}, 868.

\bibitem[Blaom et~al.(2020)Blaom, Kiraly, Lienart, Simillides, Arenas, and
  Vollmer]{MLJ1}
Blaom, A.D.; Kiraly, F.; Lienart, T.; Simillides, Y.; Arenas, D.; Vollmer, S.J.
\newblock {MLJ}: A Julia package for composable machine learning.
\newblock {\em J. Open Source Softw.} {\bf 2020}, {\em 5},~2704.
\newblock {\url{https://doi.org/10.21105/joss.02704}}.

\bibitem[Breiman(2017)]{decision-trees}
Breiman, L.
\newblock {\em Classification and Regression Trees}; \hl{Routledge:} %MDPI: Please add the location of the publisher (City and Country).
  2017.

\bibitem[Breiman(2001)]{random-forest}
Breiman, L.
\newblock Random forests.
\newblock {\em Machine Learn.} {\bf 2001}, {\em 45},~5--32.

\bibitem[Grinsztajn et~al.(2022)Grinsztajn, Oyallon, and
  Varoquaux]{grinsztajn2022tree}
Grinsztajn, L.; Oyallon, E.; Varoquaux, G.
\newblock Why do tree-based models still outperform deep learning on typical
  tabular data?
\newblock {\em Adv. Neural Inf. Process. Syst.} {\bf 2022},
  {\em 35},~507--520.

\bibitem[Shwartz-Ziv and Armon(2022)]{shwartz2022tabular}
Shwartz-Ziv, R.; Armon, A.
\newblock Tabular data: Deep learning is not all you need.
\newblock {\em Inf. Fusion} {\bf 2022}, {\em 81},~84--90.

\bibitem[Louppe et~al.(2013)Louppe, Wehenkel, Sutera, and
  Geurts]{rfr-importance-ranking}
Louppe, G.; Wehenkel, L.; Sutera, A.; Geurts, P.
\newblock Understanding variable importances in forests of randomized trees.
\newblock {\em Adv. Neural Inf. Process. Syst.} {\bf 2013},
  {\em \hl{26}}.
%MDPI: Please add page.

\bibitem[Strobl et~al.(2008)Strobl, Boulesteix, Kneib, Augustin, and
  Zeileis]{strobl2008conditional}
Strobl, C.; Boulesteix, A.L.; Kneib, T.; Augustin, T.; Zeileis, A.
\newblock Conditional variable importance for random forests.
\newblock {\em BMC Bioinform.} {\bf 2008}, {\em 9},~307.

\bibitem[Parr et~al.(2018)Parr, Turgutlu, Csiszar, and Howard]{parr2018beware}
Parr, T.; Turgutlu, K.; Csiszar, C.; Howard, J.
\newblock Beware default random forest importances.
\newblock {\em March} {\bf 2018}, {\em 26},~2018.

\bibitem[Shafer and Vovk(2008)]{conformal-prediction-1}
Shafer, G.; Vovk, V.
\newblock A Tutorial on Conformal Prediction.
\newblock {\em J. Mach. Learn. Res.} {\bf 2008}, {\em 9}, 371--421.

\bibitem[Angelopoulos and Bates(2021)]{conformal-prediction-2}
Angelopoulos, A.N.; Bates, S.
\newblock A gentle introduction to conformal prediction and distribution-free
  uncertainty quantification.
\newblock {\em arXiv} {\bf 2021},  arXiv:2107.07511.

\bibitem[Fontana et~al.(2023)Fontana, Zeni, and
  Vantini]{conformal-prediction-3}
Fontana, M.; Zeni, G.; Vantini, S.
\newblock Conformal prediction: A unified review of theory and new challenges.
\newblock {\em Bernoulli} {\bf 2023}, {\em 29},~1--23.

\bibitem[Papadopoulos(2008)]{conformal-prediction-4}
Papadopoulos, H.
\newblock Inductive conformal prediction: Theory and application to neural
  networks. In {\em Tools in Artificial Intelligence}; \hl{Citeseer:} %MDPI: Please add the location of the publisher (City and Country).
 2008.

\bibitem[Vogt and Vogt(2016)]{vogt2016near}
Vogt, M.C.; Vogt, M.E.
\newblock Near-remote sensing of water turbidity using small unmanned aircraft
  systems.
\newblock {\em Environ. Pract.} {\bf 2016}, {\em 18},~18--31.

\bibitem[Vakili and Amanollahi(2020)]{vakili2020determination}
Vakili, T.; Amanollahi, J.
\newblock Determination of optically inactive water quality variables using
  Landsat 8 data: A case study in Geshlagh reservoir affected by agricultural
  land use.
\newblock {\em J. Clean. Prod.} {\bf 2020}, {\em 247},~119134.

\bibitem[Guo et~al.(2021)Guo, Huang, Chen, Guo, and Singh]{guo2021machine}
Guo, H.; Huang, J.J.; Chen, B.; Guo, X.; Singh, V.P.
\newblock A machine learning-based strategy for estimating non-optically active
  water quality parameters using Sentinel-2 imagery.
\newblock {\em Int. J.  Remote Sens.} {\bf 2021}, {\em
  42},~1841--1866.

\bibitem[Niu et~al.(2021)Niu, Tan, Jia, and Wang]{niu2021deep}
Niu, C.; Tan, K.; Jia, X.; Wang, X.
\newblock Deep learning based regression for optically inactive inland water
  quality parameter estimation using airborne hyperspectral imagery.
\newblock {\em Environ. Pollut.} {\bf 2021}, {\em 286},~117534.

\bibitem[Valle et~al.(2023)Valle, Izbicki, and Leite]{valle2023quantifying}
Valle, D.; Izbicki, R.; Leite, R.V.
\newblock Quantifying uncertainty in land-use land-cover classification using
  conformal statistics.
\newblock {\em Remote Sens. Environ.} {\bf 2023}, {\em 295},~113682.

\bibitem[Zhu et~al.(2024)Zhu, Xi, Wu, Zhong, Qi, Chen, Xu, and
  Ji]{zhu2024inductive}
Zhu, N.; Xi, Z.; Wu, C.; Zhong, F.; Qi, R.; Chen, H.; Xu, S.; Ji, W.
\newblock Inductive Conformal Prediction Enhanced LSTM-SNN Network:
  Applications to Birds and UAVs Recognition.
\newblock {\em IEEE Geosci. Remote. Sens. Lett.} {\bf 2024}, \emph{21}, 3502705. \url{https://doi.org/10.1109/LGRS.2024.3361481}.

\bibitem[Horstrand et~al.(2019)Horstrand, Guerra, Rodr{\'\i}guez, D{\'\i}az,
  L{\'o}pez, and L{\'o}pez]{horstrand2019uav}
Horstrand, P.; Guerra, R.; Rodr{\'\i}guez, A.; D{\'\i}az, M.; L{\'o}pez, S.;
  L{\'o}pez, J.F.
\newblock A UAV platform based on a hyperspectral sensor for image capturing
  and on-board processing.
\newblock {\em IEEE Access} {\bf 2019}, {\em 7},~66919--66938.

\bibitem[Storch et~al.(2023)Storch, Honold, Chabrillat, Habermeyer, Tucker,
  Brell, Ohndorf, Wirth, Betz, Kuchler, M{\"u}hle, Carmona, Baur, M{\"u}cke,
  L{\"o}w, Schulze, Zimmermann, Lenzen, Wiesner, Aida, Kahle, Willburger,
  Hartung, Dietrich, Plesia, Tegler, Schork, Alonso, Marshall, Gerasch,
  Schwind, Pato, Schneider, de~los Reyes, Langheinrich, Wenzel, Bachmann,
  Holzwarth, Pinnel, Guanter, Segl, Scheffler, Foerster, Bohn, Bracher, Soppa,
  Gascon, Green, Kokaly, Moreno, Ong, Sornig, Wernitz, Bagschik, Reintsema,
  Porta, Schickling, and Fischer]{Storch2023TheEI}
Storch, T.; Honold, H.P.; Chabrillat, S.; Habermeyer, M.; Tucker, P.; Brell,
  M.; Ohndorf, A.; Wirth, K.; Betz, M.; Kuchler, M.;  et~al.
\newblock The EnMAP imaging spectroscopy mission towards operations.
\newblock {\em Remote Sens. Environ.} {\bf 2023}, \emph{294}, 113632.

\end{thebibliography}

% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\PublishersNote{}
\end{adjustwidth}
\end{document}

### 2024-03-10 paper/remotesensing-2870812-english.tex
working on proof comments

@@
 % Author Orchid ID: enter ID or remove command
-\newcommand{\orcidauthorA}{0000-0002-5910-0183} % Add \orcidA{} behind the author's name
-\newcommand{\orcidauthorB}{0000-0003-4265-9543} % Add \orcidA{} behind the author's name
-%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
+\newcommand{\orcidauthorA}{0000-0002-5910-0183} % John
+\newcommand{\orcidauthorB}{0000-0003-2688-648X} % Lakitha
+\newcommand{\orcidauthorC}{0000-0002-9841-6703} % Shawhin
+\newcommand{\orcidauthorD}{0000-0003-2657-3416} % Prabuddha
+\newcommand{\orcidauthorE}{0000-0003-4265-9543} % David
+\newcommand{\orcidauthorF}{0000-0003-0667-2345} % Ash
+\newcommand{\orcidauthorG}{0000-0002-0126-218X} % Adam
 
 % Authors, for the paper (add full first names)
-\Author{\hl{John} %MDPI: Please carefully check the accuracy of names and affiliations.
- Waczak \orcidA{}, Adam Aker, Lakitha O.
+\Author{John Waczak \orcidA{}, Adam Aker \orcidG{}, Lakitha O.
 H.
-Wijeratne, Shawhin Talebi, Bharana Fernando, \hl{Prabuddha Hathurusinghe}%MDPI: The name of this author is different from the one submitted online at susy.mdpi.com.
-Please confirm which one is correct.
-, Mazhar Iqbal, Matthew Lary, David Schaefer and David J. Lary *\orcidB{}}
+Wijeratne \orcidB{}, Shawhin Talebi \orcidC{}, Ashen Fernando \orcidF{}, Prabuddha M.
+H.
+Dewage \orcidD{}, Mazhar Iqbal, Matthew Lary, David Schaefer and David J.
+Lary *\orcidE{}}
 
@@
 \address[1]{%
-Hanson Center for Space Sciences, University of Texas at Dallas, Richardson, TX 75080, USA;  \hl{john.waczak@utdallas.edu} %MDPI: We changed all emails into lowercase. Please confirm.
- (J.W.); adam.aker@utdallas.edu (A.A.); lhw150030@utdallas.edu (L.O.H.W.); shawhintalebi@gmail.com (S.T.); ashen.fernando@utdallas.edu  (B.F.); prabuddhamadusanka.hathurusinghedewage@utdallas.edu (P.H.); mazhar.iqbal@utdallas.edu (M.I.); \hl{mdlary@me.com} %MDPI: This email address is different from the one submitted online at susy.mdpi.com.
-Please confirm which one is correct.
- (M.L.); captdaveschaefer@gmail.com (D.S.)}
+Hanson Center for Space Sciences, University of Texas at Dallas, Richardson, TX 75080, USA;  john.waczak@utdallas.edu (J.W.); adam.aker@utdallas.edu (A.A.); lhw150030@utdallas.edu (L.O.H.W.); shawhintalebi@gmail.com (S.T.); ashen.fernando@utdallas.edu  (B.F.); pxh180012@utdallas.edu (P.M.H.D.); mazhar.iqbal@utdallas.edu (M.I.); matthew.lary@utdallas.edu (M.L.); captdaveschaefer@gmail.com (D.S.)}
 
@@
 
-To effectively utilize the spectra collected by our UAV, we must account for the variability of the incident light that illuminates the water and transform the raw hyperspectral data cubes from their native \textit{\hl{imaging~reference~frame}} %MDPI: Please confirm if the italics is unnecessary and can be removed.
-The following highlights are the same.
- to a chosen coordinate system compatible with the data collected by the USV. This procedure is illustrated in Figure~\ref{fig:hsi-pipeline}.
+To effectively utilize the spectra collected by our UAV, we must account for the variability of the incident light that illuminates the water and transform the raw hyperspectral data cubes from their native imaging reference frame to a chosen coordinate system compatible with the data collected by the USV.
+This procedure is illustrated in Figure~\ref{fig:hsi-pipeline}.
 
@@
 \vspace{-0.4in}
-\caption{\hl{Hyperspectral} %MDPI: Please add the explanation for different color in the figure.
- image processing: Hyperspectral data cubes are collected one scan-line at a time (left).
+\caption{Hyperspectral image processing: Hyperspectral data cubes are collected one scan-line at a time (left).
 By utilizing downwelling irradiance spectra, we convert each pixel from spectral radiance to reflectance.
 By using orientation and position data from the on-board GPS and INS, we georeference each pixel to assign it a latitude and longitude on the ground.
-The final data product is the georectified hyperspectral reflectance data cube visualized on the right.
-\label{fig:hsi-pipeline}}
-\end{figure}
-
-The hyperspectral imager utilized in our robot team is in a so-called \textit{\hl{pushbroom}} configuration: that is, each image captured by the drone is formed one scan line at a time as the UAV flies.
+The final data product is the georectified hyperspectral reflectance data cube (right) visualized as a pseudo-color image with reflectance  as a function of wavelength along the z-axis.\label{fig:hsi-pipeline}}
+\end{figure}
+
+The hyperspectral imager utilized in our robot team is in a so-called pushbroom configuration: that is, each image captured by the drone is formed one scan line at a time as the UAV flies.
 Each scan line consists of 1600 pixels, for which incoming light is diffracted into 462 wavelength bins.
-In the collection software, a regular cutoff of 1000 lines is chosen so that each resulting \hl{\textit{image}} forms an array of size 462 $\times$ 1600 $\times$ 1000 called a \textit{\hl{hyperspectral data cube}}.
+In the collection software, a regular cutoff of 1000 lines is chosen so that each resulting image forms an array of size 462 $\times$ 1600 $\times$ 1000 called a hyperspectral data cube.
 Initially, the captured spectra are in units of spectral radiance (measured in microflicks); however, this does not account for the variability of incident light illuminating the water.
@@
 
-The robot team was deployed at a private pond in Montague, Texas, close to the Oklahoma border for three separate collections on \hl{23} %MDPI: We changed all date format in main tex. Please confirm.
- November 2020, 9 December 2020, and 10 December 2020.
+The robot team was deployed at a private pond in Montague, Texas, close to the Oklahoma border for three separate collections on 23 November 2020, 9 December 2020, and 10 December 2020.
 The pond spans an area $<$0.1 km$^{2}$ and has a maximum depth of 3 m.
@@
 %AE unsure if MLJ is an acronym and should thus be in parentheses
- \cite{ben_sadeghi_2022_7359268, MLJ1}.
+ \cite{decision-tree-julia, MLJ1}.
 Random forests are an ensembling technique based on bagged predictions of individual decision tree regressors trained using the classification and regression trees (CART) algorithm.
@@
 \authorcontributions{Conceptualization, D.J.L.; methodology, \hl{J.W.} %MDPI: We changed all J.L.W. into J.W. Please confirm.
- and D.J.L; software, J.W.; field deployment and preparation, J.W., A.A., L.O.H.W., S.T., B.F., P.H., M.I., M.L., D.S., and D.J.L.; validation, J.W.; formal analysis, J.W.; investigation J.W.; resources, D.J.L.; data curation, J.W., A.A., L.O.H.W., and D.J.L; writing---original draft preparation, J.W.; writing---review and editing, J.W.
+ and D.J.L; software, J.W.; field deployment and preparation, J.W., A.A., L.O.H.W., S.T., B.F., P.M.H.D., M.I., M.L., D.S., and D.J.L.; validation, J.W.; formal analysis, J.W.; investigation J.W.; resources, D.J.L.; data curation, J.W., A.A., L.O.H.W., and D.J.L; writing---original draft preparation, J.W.; writing---review and editing, J.W.
 and D.J.L.; visualization, J.W.; supervision, D.J.L.; project administration, D.J.L.; funding acquisition, D.J.L.

### 2024-03-10 paper/remotesensing-2870812-english.tex
more paper updates

@@
  The robotic team presented in this study consists of two key sensing sentinels: an uncrewed surface vessel (USV) used to collect in situ reference measurements and an unmanned aerial vehicle (UAV) for performing rapid, wide-area surveys to gather remote sensing data products.
-Both platforms are coordinated using open source \hl{QGroundControl software} %MDPI: Please state the version number of the software.
- for flight control and mission planning and are equipped with high-accuracy GPS and INS such that all data points collected are uniquely geolocated and time-stamped~\cite{qgroundcontrol}.
+Both platforms are coordinated using open-source QGroundControl version 4.0.11 software for flight control and mission planning and are equipped with high-accuracy GPS and INS such that all data points collected are uniquely geolocated and time-stamped~\cite{qgroundcontrol}.
 Both the USV and UAV include long-range Ubiquiti 5 GHz LiteBeam airMAX WiFi to enable streaming of data products to a ground station with network-attached storage to provide redundancy.
@@
 \end{adjustwidth}
-\caption{A georectified reflectance data cube is visualized (center) with the $\log10$-reflectance along the z-axis and a pseudo-color image on the top.
+\caption{A georectified reflectance data cube is visualized (center) with the $\log_{10}$ reflectance along the z-axis and a pseudo-color image on the top.
 In the top left, we visualize the downwelling irradiance spectrum (the incident light).
@@
 For each of the 13 target variables listed in Table~\ref{tab:sensors}, the data were randomly partitioned into a 90:10 training/testing split.
-To model the data, we chose to use the random forest regressor (RFR) as implemented in the machine learning framework for Julia package  \hl{MLJ} %MDPI: There is no ref {ben_sadeghi_2022_7359268}.
-Please check and revise.
-%AE unsure if MLJ is an acronym and should thus be in parentheses
- \cite{decision-tree-julia, MLJ1}.
+To model the data, we chose to use the random forest regressor (RFR) as implemented in the Machine Learning framework for Julia (MLJ) \cite{random-forest-regression, MLJ1}.
 Random forests are an ensembling technique based on bagged predictions of individual decision tree regressors trained using the classification and regression trees (CART) algorithm.
-Each tree in an RFR is trained on a random subset of features \textit{\hl{and}} a random subset of training records \cite{decision-trees, random-forest}.
+Each tree in an RFR is trained on a random subset of features and a random subset of training records \cite{decision-tree, random-forest}.
 Random forests are particularly attractive due to their fast training and inference times.
@@
 Feature importances for the trained model were then computed, and the top 25 features were identified.
-A second model was then trained using the same six-fold cross-validation scheme with \textit{\hl{only}} these 25 most important features together with hyperparameter optimization using a random search over the number of trees and sampling fraction.
+A second model was then trained using the same six-fold cross-validation scheme with only these 25 most important features together with hyperparameter optimization using a random search over the number of trees and sampling fraction.
 The number of trees was optimized, as it has a significant impact on both model performance and inference time.
@@
 RFR & Random Forest Regressor \\
+MLJ & Machine Learning framework for Julia \\
 RMSE & Root Mean Square Error \\ 
@@
 
+\bibitem[Sadeghi et~al.(2022)Sadeghi, Chiarawongse, Squire, Jones, Noack, St-Jean, Huijzer, Schätzle, Butterworth, Peng, and Blaom]{random-forest-regression}
+Sadeghi, B.; Chiarowongse, P.; Squire, K.; Jones, D.C.; Noack, A.; St-Jean, C.; Huijzer, R.; Schätzle, R.; Butterworth, I.; Peng, Y.; Blaom, A.
+\newblock DecisionTree.jl - A Julia implementation of the CART Decision Tree and Random Forest algorithms.
+\newblock {\em Zenodo} {\bf 2022}.
+\newblock {\url{https://doi.org/10.5281/zenodo.7359268}}.
+
 \bibitem[Breiman(2017)]{decision-trees}

### 2024-03-10 paper/remotesensing-2870812-english.tex

@@
 Furthermore, we report the interval width that yields a 90\% confidence interval on the holdout validation set determined by the conformal prediction procedure.
-We then evaluate how the estimated uncertainty generalizes by computing the \textit{\hl{empirical coverage}} on the holdout testing set: that is, we compute the percentage of predictions in the test set that \textit{\hl{actually}} fall within the estimated 90\% confidence interval.
+We then evaluate how the estimated uncertainty generalizes by computing the empirical coverage on the holdout testing set: that is, we compute the percentage of predictions in the test set that actually fall within the estimated 90\% confidence interval.
 
@@
 First, we have demonstrated the ability to effectively combine observations from disparate collections by augmenting the machine learning models with sufficient features describing the illumination and viewing geometries.
-As Figure~\ref{fig:downwelling-hist} indicates, we observed variation in the total downwelling intensity between the images collected on the same day \textit{\hl{and}} between each separate collection period.
+As Figure~\ref{fig:downwelling-hist} indicates, we observed variation in the total downwelling intensity between the images collected on the same day and between each separate collection period.
 These within-collection variations are due to a combination of the stability of the UAV (on which the upward facing downwelling irradiance spectrometer is mounted) together with the occasional interference of clouds.
@@
 Despite the potential impact of these limitations on the quality of the resulting reflectance data cubes, the smoothness of the maps generated by our models suggests that we have provided sufficient context by including the relevant solar illumination and viewing angles as additional features in the final dataset.
-This fact is reinforced by the position of these variables as the most important features for \textit{each} of the estimated water quality variables.
+This fact is reinforced by the position of these variables as the most important features for each of the estimated water quality variables.
 As long as we are primarily interested in these values and not the reflectances themselves, we are able to successfully account for these lighting effects when combining data from multiple collections.
@@
 Conformal prediction is an attractive approach to enable model-agnostic uncertainty estimation and has recently seen adoption to remote sensing classification tasks such as land-type classification and object identification \cite{valle2023quantifying, zhu2024inductive}.
-In this setting, the goal is to produce predictive \textit{\hl{sets}} guaranteed to contain the correct class labels at a predetermined confidence level.
+In this setting, the goal is to produce predictive sets guaranteed to contain the correct class labels at a predetermined confidence level.
 Nevertheless, conformal prediction works equally well for regression tasks.
@@
 
-Despite the wealth of information provided by the increased resolution of hyperspectral images, their considerable size impedes their \textit{\hl{complete}} utilization in real-time applications.
+Despite the wealth of information provided by the increased resolution of hyperspectral images, their considerable size impedes their complete utilization in real-time applications.
 Often, much of the available spectral information is discarded in favor of indices like the NDVI, which can be quickly computed as images are captured \cite{horstrand2019uav}.

### 2024-03-11 3_feature-exploration.jl
updated figures

@@ -5,8 +5,11 @@ using Random
 
 using Dates
 using CairoMakie
-using MintsMakieRecipes
 
+include("./makie-defaults.jl")
+
+
+# a few changes to our defaults
 set_theme!(mints_theme)
 update_theme!(
     figure_padding=30,
@@ -16,16 +19,20 @@ update_theme!(
         xlabelsize=22,
         ylabelsize=22,
         titlesize=25,
+        labelsize=10,
     ),
     Colorbar=(
         ticklabelsize=20,
-        labelsize=22
     )
 )
 
 
+
+
+
+
 #using MLJ, Flux, ConformalPrediction
-using MLJ, Flux
+using MLJ
 using MLJBase: train_test_pairs
 
 # add in ConformalPrediction via GitHub until my fix ships
@@ -62,10 +69,10 @@ datapath = "/Users/johnwaczak/data/robot-team/supervised"
 
 ETR = @load EvoTreeRegressor pkg=EvoTrees
 RFR = @load RandomForestRegressor pkg=DecisionTree
-DTR = @load DecisionTreeRegressor pkg=DecisionTree
-XGBR = @load XGBoostRegressor pkg=XGBoost
-NNR = @load NeuralNetworkRegressor pkg=MLJFlux
-Standardizer = @load Standardizer pkg=MLJModels
+# DTR = @load DecisionTreeRegressor pkg=DecisionTree
+# XGBR = @load XGBoostRegressor pkg=XGBoost
+# NNR = @load NeuralNetworkRegressor pkg=MLJFlux
+# Standardizer = @load Standardizer pkg=MLJModels
 
 
 # 1. Construct dictionary of models
@@ -130,13 +137,13 @@ use_metrics = false
 #                  )
 
 
-MODELS[:etr] = (;
-                :longname=>"Evo Tree Regressor",
-                :savename=>"EvoTreeRegressor",
-                :packagename => "EvoTrees",
-                :suffix => "vanilla",
-                :mdl => ETR(nrounds=100, nbins=255, eta=0.3, max_depth=6, lambda=1.0, alpha=0.0),
-                )
+# MODELS[:etr] = (;
+#                 :longname=>"Evo Tree Regressor",
+#                 :savename=>"EvoTreeRegressor",
+#                 :packagename => "EvoTrees",
+#                 :suffix => "vanilla",
[…]

### 2024-03-11 3b_make-maps.jl

@@ -4,7 +4,54 @@ using Random, Statistics
 using ProgressMeter
 
 import CairoMakie as cmk
-using MintsMakieRecipes
+
+
+montserrat_path = "./font-files/montserrat"
+@assert ispath(montserrat_path)
+
+mints_colors = [
+    cmk.colorant"#3cd184", # mint green
+    cmk.colorant"#f97171", # dark coral
+    cmk.colorant"#1e81b0", # dark blue
+    cmk.colorant"#66beb2", # dark blue-green
+    cmk.colorant"#f99192", # light coral
+    cmk.colorant"#8ad6cc", # middle blue-green
+    cmk.colorant"#3d6647", # dark green
+]
+
+
+mints_font = (;
+              regular = joinpath(montserrat_path, "static", "Montserrat-Regular.ttf"),
+              italic = joinpath(montserrat_path, "static", "Montserrat-Italic.ttf"),
+              bold = joinpath(montserrat_path, "static", "Montserrat-Bold.ttf"),
+              bold_italic = joinpath(montserrat_path, "static", "Montserrat-BoldItalic.ttf"),
+              )
+
+
+mints_theme = cmk.Theme(
+    fontsize=17,
+    fonts = mints_font,
+    #colormap = :haline,
+    colormap = :viridis,
+    palette = (
+        color = mints_colors,
+        patchcolor = mints_colors,
+    ),
+    cycle = [[:linecolor, :markercolor,] => :color,],
+    Axis=(
+        xlabelsize=15,                   ylabelsize=15,
+        xticklabelsize=13,               yticklabelsize=13,
+        xticksize=3,                     yticksize=3,
+        xminorgridvisible=true,          yminorgridvisible=true,
+        xgridwidth=2,                    ygridwidth=2,
+        xminorgridwidth=1,               yminorgridwidth=1,
+        xminorticks=cmk.IntervalsBetween(5), yminorticks=cmk.IntervalsBetween(5)
+    ),
+    Colorbar=(
+        fontsize=13,
+    )
+)
+
 
 cmk.set_theme!(mints_theme)
 cmk.update_theme!(
@@ -55,6 +102,76 @@ e= -97.712413
 
 
 satmap = get_background_satmap(w,e,s,n)
+
+# create map of area
+
[…]

### 2024-03-11 3c_extra-plots.jl

@@ -27,9 +27,6 @@ include("./viz.jl")
 datapath = "/Users/johnwaczak/data/robot-team/supervised"
 
 
-
-
-
 df_1123 = CSV.read(joinpath(datapath, "11-23", "CDOM", "data", "X.csv"), DataFrame)
 df_1209 = CSV.read(joinpath(datapath, "12-09", "CDOM", "data", "X.csv"), DataFrame)
 df_1210 = CSV.read(joinpath(datapath, "12-10", "CDOM", "data", "X.csv"), DataFrame)

### 2024-03-11 config.jl

@@ -33,7 +33,7 @@ targets_dict = Dict(
     :Turb3490 => ["FNU", "Turbidity"],
     :bg => ["ppb", "Blue-Green Algae\n (Phycocyanin)", 0.0],
     :bgm => ["ppb", "Blue-Green Algae\n (Phycoerythrin)", 0.0],
-    :pH => ["0-14", "pH", 0.0],
+    :pH => ["0–14", "pH", 0.0],
     :pH_mV => ["mV", "pH"],
 )
 

### 2024-03-11 sat-viz.jl

@@ -44,4 +44,3 @@ function get_background_satmap(w::Float64, e::Float64, s::Float64, n::Float64; o
     )
 end
 
-

### 2024-03-11 training-functions.jl

@@ -13,8 +13,8 @@ hpo_ranges = Dict("DecisionTree" => Dict("DecisionTreeRegressor" => [(hpname=:mi
                                                                       #(hpname=:min_samples_leaf, lower=1, upper=100),
                                                                       #(hpname=:max_depth, values=[-1, 3, 5, 7]),
                                                                       #(hpname=:n_subfeatures, lower=10, upper=100,),
-                                                                      (hpname=:n_trees, lower=50, upper=200),
-                                                                      (hpname=:sampling_fraction, lower=0.8, upper=1.0)
+                                                                      (hpname=:n_trees, lower=75, upper=175),
+                                                                      (hpname=:sampling_fraction, lower=0.85, upper=1.0)
                                                                       ],
                                           ),
                  "XGBoost" => Dict("XGBoostRegressor" => [(hpname=:num_round, lower=50, upper=100),
@@ -951,7 +951,7 @@ function train_hpo(
     rng=Xoshiro(42),
     )
 
-    suffix = "hpo"
+    suffix = "hpo_2"
 
     @info "\tSetting up save paths"
 
@@ -1028,7 +1028,7 @@ function train_hpo(
 
         @info "\t...\tFinished training"
 
-        open(joinpath(path_to_use, "$(savename)__hpo.txt"), "w") do f
+        open(joinpath(path_to_use, "$(savename)__$(suffix).txt"), "w") do f
             show(f,"text/plain", fitted_params(mach).best_model)
             println(f, "\n")
             println(f,"---------------------")

### 2024-03-11 viz.jl

@@ -1,6 +1,6 @@
 using MLJ: rsq
 using StatsBase: iqr
-
+using Format
 
 
 function scatter_folds(
@@ -115,7 +115,7 @@ function scatter_results(
     varname
     )
 
-    fig = Figure();
+    fig = Figure(size=(800,600));
     ga = fig[1, 1] = GridLayout()
     axtop = Axis(ga[1, 1];
                 leftspinevisible = false,
@@ -142,13 +142,14 @@ function scatter_results(
     s2 = scatter!(axmain, ytest, ŷtest, marker=:rect, alpha=0.75)
 
     labels=[
-        "Training R²=$(round(rsq(ŷ, y), digits=3)) (n=$(length(y)))",
-        "Testing   R²=$(round(rsq(ŷtest, ytest), digits=3)) (n=$(length(ytest)))",
+        "Training R²=$(round(rsq(ŷ, y), digits=3)) (n=$(format(length(y), commas=true)))",
+        "Testing   R²=$(round(rsq(ŷtest, ytest), digits=3)) (n=$(format(length(ytest), commas=true)))",
         "1:1"
     ]
 
     # leg = Legend(ga[1, 2], [s1, s2, l1], labels)
     leg = axislegend(axmain, [s1, s2, l1], labels; position=:lt)
+    #leg = axislegend(axmain, [s1, s2, l1], labels; position=:lt)
 
     density!(axtop, y, color=(mints_colors[1], 0.5), strokecolor=mints_colors[1], strokewidth=2)
     density!(axtop, ytest, color=(mints_colors[2], 0.5), strokecolor=mints_colors[2], strokewidth=2)
@@ -257,15 +258,15 @@ function quantile_results(
     varname
     )
 
-    fig = Figure();
+    fig = Figure(size=(800,600));
     ax = Axis(fig[1,1], xlabel="True $(varname)", ylabel="Predicted $(varname)")
 
     minval, maxval = extrema([extrema(y)..., extrema(ytest)..., extrema(ŷ)..., extrema(ŷtest)...])
     δ_edge = 0.1*(maxval-minval)
 
     l1 = lines!(ax, [minval-δ_edge, maxval+δ_edge], [minval-δ_edge, maxval+δ_edge], color=:gray, linewidth=3)
-    qtrain = qqplot!(ax, y, ŷ, alpha=0.5)
[…]

### 2024-03-11 paper/remotesensing-2870812-english.tex

@@
 \vspace{-0.15in}
-\caption{\hl{Distribution} %MDPI: Please use commas to separate thousands for numbers with five or more digits (not four digits) in the picture, e.g., "10000" should be "10,000".
- of total downwelling intensity during each of the three HSI collection flights.
+\caption{Distribution of total downwelling intensity during each of the three HSI collection flights.
 The multi-modal nature of these distributions reflects the impact of the relative orientation of the drone to the sun as well as potential occlusion due to the presence of clouds.\label{fig:downwelling-hist}}
@@
 Despite the potential impact of these limitations on the quality of the resulting reflectance data cubes, the smoothness of the maps generated by our models suggests that we have provided sufficient context by including the relevant solar illumination and viewing angles as additional features in the final dataset.
-This fact is reinforced by the position of these variables as the most important features for each of the estimated water quality variables.
+This fact is reinforced by the position of these variables as the most important features for \textit{each} of the estimated water quality variables.
 As long as we are primarily interested in these values and not the reflectances themselves, we are able to successfully account for these lighting effects when combining data from multiple collections.
@@
 %% optional
-\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, \hl{Table S1:} %MDPI: please provide an independent file to indicate supplementary materials.
+\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Table S1: %MDPI: please provide an independent file to indicate supplementary materials.
  Hyperspectral reflectance indices.}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{Conceptualization, D.J.L.; methodology, \hl{J.W.} %MDPI: We changed all J.L.W. into J.W. Please confirm.
+\authorcontributions{Conceptualization, D.J.L.; methodology, J.W.
 and D.J.L; software, J.W.; field deployment and preparation, J.W., A.A., L.O.H.W., S.T., B.F., P.M.H.D., M.I., M.L., D.S., and D.J.L.; validation, J.W.; formal analysis, J.W.; investigation J.W.; resources, D.J.L.; data curation, J.W., A.A., L.O.H.W., and D.J.L; writing---original draft preparation, J.W.; writing---review and editing, J.W.
@@
 \newblock Artificial intelligence in geoscience and remote sensing. In {\em
-  Geoscience and Remote Sensing New Achievements}; \hl{IntechOpen:} %MDPI: Please add the location of the publisher (City and Country).
+  Geoscience and Remote Sensing New Achievements}; IntechOpen: London, United Kingdom,
   2010.
@@
 \newblock In {\em Unmanned Aerial Vehicle: Applications in Agriculture and
-  Environment}; \hl{2020} %MDPI: Please add the name of the publisher and their location.
+  Environment}; Springer International Publishing: Cham, Switzerland, 2020 %MDPI: Please add the name of the publisher and their location.
 ; pp. 25--38.
@@
 \newblock \emph{Evaluation of the Eureka Manta2 Water-Quality Multiprobe Sonde};
-\newblock Technical report; \hl{US Geological Survey:} %MDPI: Please add the location of the publisher (City and Country).
+\newblock Technical report; US Geological Survey: Reston, VA, United States, %MDPI: Please add the location of the publisher (City and Country).
   2017.
@@
   B.
-\newblock \emph{A Program for Direct Georeferencing of Airborne and Spaceborne Line
-  Scanner Images};
-\newblock  \hl{2002.} %MDPI: Please add the name of the publisher and their location.
+\newblock A Program for Direct Georeferencing of Airborne and Spaceborne Line
+  Scanner Images;
+\newblock In {\em International Archives of Photogrammetry Remote Sensing and 
+  Spatial Information Sciences}; {2002}; pp. 148--153. %MDPI: Please add the name of the publisher and their location.
 
@@
 \newblock {\em Hyperspectral Indices and Image Classifications for Agriculture
-  and Vegetation}; CRC Press:  \hl{Boca Raton, FL, USA,} %We added the location of publisher. Please confirm
+  and Vegetation}; CRC Press:  Boca Raton, FL, USA,
  2018.
@@
 Breiman, L.
-\newblock {\em Classification and Regression Trees}; \hl{Routledge:} %MDPI: Please add the location of the publisher (City and Country).
+\newblock {\em Classification and Regression Trees}; CRC Press: Boca Raton, FL, USA,  %MDPI: Please add the location of the publisher (City and Country).
   2017.
@@
 \newblock {\em Adv. Neural Inf. Process. Syst.} {\bf 2013},
-  {\em \hl{26}}.
-%MDPI: Please add page.
+  {\em 26}, ~431--439.
 
@@
 \newblock Inductive conformal prediction: Theory and application to neural
-  networks. In {\em Tools in Artificial Intelligence}; \hl{Citeseer:} %MDPI: Please add the location of the publisher (City and Country).
+  networks. In {\em Tools in Artificial Intelligence}; IntechOpen: London, United Kingdom %MDPI: Please add the location of the publisher (City and Country).
  2008.

### 2024-03-11 paper/figures/results/maps/supplementary-material/spectral-indices.qmd
final updates

--- 2024-01-03 paper/supplementary-material/spectral-indices.qmd
@@
 \end{align}
-We also define $R_{swir} = R(1009 \text{ nm})$ as the *almost*-SWIR band representing the infrared edge of the hyperspectral imager.
+We also define $R_{far} = R(1009 \text{ nm})$ as the band representing the farthest infrared bin for our hyperspectral imager which we use instead of the usual SWIR band.
 
@@
 | Normalized Difference Water Index 1 | NDWI1 | $\dfrac{R_g - R_{nir}}{R_g + R_{nir}}$ |
-| Normalized Difference Water Index 2 | NDWI2 | $\dfrac{R_{nir} - R_{swir}}{R_{nir} + R_{swir}}$ |
-| Modified Normalized Difference Water Index | MNDWI | $\dfrac{R_g - R_{swir}}{R_g + R_{swir}}$ |
+| Normalized Difference Water Index 2 | NDWI2 | $\dfrac{R_{nir} - R_{far}}{R_{nir} + R_{far}}$ |
+| Modified Normalized Difference Water Index | MNDWI | $\dfrac{R_g - R_{far}}{R_g + R_{far}}$ |
 | Water Band Index | WBI | $\dfrac{970}{900}$ |
@@
 | Modified Anthocyanin Reflectance Index | MARI | $\left(\dfrac{1}{R_{550}} - \dfrac{1}{R_{700}} \right)R_{nir}$ |
-| Moisture Stress Index | MSI | $\dfrac{R_{swir}}{R_{nir}}$ |
+| Moisture Stress Index | MSI | $\dfrac{R_{far}}{R_{nir}}$ |
 | MERIS Terrestrial Chlorophyll Index | MTCI | $\dfrac{R_{753.75} - R_{708.75}}{R_{708.75} - R_{681.25}}$ |
-| Normalzied Difference Infrared Index | NDII | $\dfrac{R_{nir} - R_{swir}}{R_{nir} + R_{swir}}$ |
+| Normalzied Difference Infrared Index | NDII | $\dfrac{R_{nir} - R_{far}}{R_{nir} + R_{far}}$ |
 | Normalized Difference Red Edge | NDRE | $\dfrac{R_{790} - R_{720}}{R_{790} + R_{720}}$ |

### 2024-03-11 paper/remotesensing-2870812-english.tex
final updates

@@
  \Title{Characterizing Water Composition with an Autonomous Robotic Team Employing Comprehensive In Situ Sensing, Hyperspectral Imaging, Machine Learning, and Conformal Prediction}%AE title change
-%\Title{\textcolor{red}{Towards Real-Time Water Quality Characterization Using an Autonomous Robotic Team Employing Comprehensive In-Situ Sensing, Hyperspectral Imaging, and Conformal Prediction}}
 
@@
 \address[1]{%
-Hanson Center for Space Sciences, University of Texas at Dallas, Richardson, TX 75080, USA;  john.waczak@utdallas.edu (J.W.); adam.aker@utdallas.edu (A.A.); lhw150030@utdallas.edu (L.O.H.W.); shawhintalebi@gmail.com (S.T.); ashen.fernando@utdallas.edu  (B.F.); pxh180012@utdallas.edu (P.M.H.D.); mazhar.iqbal@utdallas.edu (M.I.); matthew.lary@utdallas.edu (M.L.); captdaveschaefer@gmail.com (D.S.)}
+Hanson Center for Space Sciences, University of Texas at Dallas, Richardson, TX 75080, USA;  john.waczak@utdallas.edu (J.W.); adam.aker@utdallas.edu (A.A.); lhw150030@utdallas.edu (L.O.H.W.); shawhintalebi@gmail.com (S.T.); ashen.fernando@utdallas.edu  (B.F.); pxh180012@utdallas.edu (P.M.H.D.); mazhar.iqbal@utdallas.edu (M.I.); MDL210001@utdallas.edu (M.L.); captdaveschaefer@gmail.com (D.S.)}
 
@@
 \vspace{-0.1in}
-\caption{\hl{Scatter} %MDPI: 1.
-Please change hyphen into endash for range.
-2.
-Please use commas to separate thousands for numbers with five or more digits (not four digits) in the picture, e.g., "10000" should be "10,000".
- diagrams (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the hyperparameter-optimized RFR models for the physical variables measured by the USV.\label{fig:physical-fit}}
+\caption{Scatter diagrams (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the hyperparameter-optimized RFR models for the physical variables measured by the USV.\label{fig:physical-fit}}
 \end{figure}
@@
 \vspace{-0.1in}
-\caption{Ranked
- \hl{permutation} %MDPI: Please change the hyphen (-) into a minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
- importance for each feature in the physical variable models.
+\caption{Ranked permutation importance for each feature in the physical variable models.
 Permutation importance measured the decrease in the model's $R^2$ value after replacing each feature in the prediction set with a random permutation of its values.\label{fig:physical-fi}}
@@
 \vspace{-0.05in}
-\caption{\hl{Maps} %MDPI: Please change the hyphen (-) into a minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
- generated by applying each of the physical variable models to the hyperspectral data cubes collected on 23 November.
+\caption{Maps generated by applying each of the physical variable models to the hyperspectral data cubes collected on 23 November.
 Overlaid over the predictions are color-filled squares showing the associated in situ reference data for the same collection period.
@@
 \vspace{-0.1in}
-\caption{\hl{Scatter} %MDPI: Please use commas to separate thousands for numbers with five or more digits (not four digits) in the picture, e.g., "10000" should be "10,000".
- diagrams (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the hyperparameter-optimized RFR models for the ion measurements made by the USV.\label{fig:ions-fit}}
+\caption{Scatter diagrams (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the hyperparameter-optimized RFR models for the ion measurements made by the USV.\label{fig:ions-fit}}
 \end{figure}
@@
 \end{adjustwidth}
-\caption{\hl{Ranked} %MDPI: Please change the hyphen (-) into a minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
- permutation importance for the top 25 features of the ion models.
+\caption{Ranked permutation importance for the top 25 features of the ion models.
 The permutation importance measures the decrease in the model's $R^2$ value when each feature is replaced by a random permutation of its values.\label{fig:ions-fi}}
@@
 \vspace{-0.1in}
-\caption{\hl{Maps} %MDPI: Please change the hyphen (-) into a minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
- generated by applying the trained ion models to the data cubes collected on 23 November.
+\caption{Maps generated by applying the trained ion models to the data cubes collected on 23 November.
 Overlaid on the maps are the in situ reference measurements for the same collection period.
@@
 \vspace{-0.1in}
-\caption{\hl{Scatter} %MDPI: Please use commas to separate thousands for numbers with five or more digits (not four digits) in the picture, e.g., "10000" should be "10,000".
- plots (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the final hyperparameter-optimized models for the biochemical targets blue--green algae (phycoerythrin), CDOM, chlorophyll-a, and blue--green algae (phycocyanin).
+\caption{Scatter plots (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the final hyperparameter-optimized models for the biochemical targets blue--green algae (phycoerythrin), CDOM, chlorophyll-a, and blue--green algae (phycocyanin).
 \label{fig:biochem-fit}}
@@
 \vspace{-0.1in}
-\caption{\hl{Ranked} %MDPI: Please change the hyphen (-) into a minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
- permutation importance for each feature in the trained biochemical models.
+\caption{Ranked permutation importance for each feature in the trained biochemical models.
 The permutation importance measures the decrease in the model's $R^2$ value after replacing each feature with a random permutation of its values.\label{fig:biochem-fi}}
@@
 \vspace{-0.1in}
-\caption{\hl{Maps} %MDPI: Please change the hyphen (-) into a minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
- \hl{generated} %MDPI: There are overlapped content (``longitude} in top and left subfigure). please revise.
+\caption{Maps generated 
  by applying the trained biochemical models to the data cubes collected on 23 November.
@@
 Scatter diagrams and quantile--quantile plots for the fitted models are shown in Figure~\ref{fig:chemicals-fit}.
-Both models achieve good performance, with $R^2$ values of 0.957 and 0.941 for CO and OB, respectively, %Please ensure meaning has been retained.
-on the holdout test set.
+Both models achieve good performance, with $R^2$ values of 0.957 and 0.941 for CO and OB on the holdout test set.
 The performance of the CO model degrades for concentrations below 24 ppb, for which there are few records.
@@
 \vspace{-0.11in}
-\caption{\hl{Scatter} %MDPI: Please use commas to separate thousands for numbers with five or more digits (not four digits) in the picture, e.g., "10000" should be "10,000".
- diagrams (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the hyperparameter-optimized RFR models for the chemical variables measured by the USV.\label{fig:chemicals-fit}}
+\caption{Scatter diagrams (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the hyperparameter-optimized RFR models for the chemical variables measured by the USV.\label{fig:chemicals-fit}}
 \end{figure}
@@
 \vspace{-0.15in}
-\caption{\hl{Ranked} %MDPI: Please change the hyphen (-) into a minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
- permutation importance for the top 25 features of the chemical models.
+\caption{Ranked permutation importance for the top 25 features of the chemical models.
 The permutation importance measures the decrease in the model's $R^2$ value after replacing each feature in the prediction set with a random permutation of its values.\label{fig:chemicals-fi}}
@@
 \vspace{-0.1in}
-\caption{\hl{Maps} %MDPI: Please change the hyphen (-) into a minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
- generated by applying the trained chemical variable models to the hyperspectral data cubes collected on 23 November.
+\caption{Maps generated by applying the trained chemical variable models to the hyperspectral data cubes collected on 23 November.
 Overlaid are color-filled squares showing the in situ reference data for the same collection period.

### 2024-03-11 old/1__make_datasets.jl

@@ -1,124 +1,0 @@
-using mintsML
-using MLJ
-using DataFrames, CSV
-using ProgressMeter
-using SolarGeometry
-
-include("./config.jl")
-include("./utils.jl")
-
-outpath = "/media/john/HSDATA/datasets"
-ispath(outpath)
-
-function make_datasets(datapath, outpath)
-    @showprogress for (target, info) ∈ targetsDict
-        # make output
-        target_name = String(target)
-        date = split(datapath, "/")[end]
-        outpath_base = joinpath(outpath, date, target_name)
-
-        # make sure outpath exists
-        if !isdir(outpath_base)
-            println("making folder $(outpath_base)")
-            mkpath(outpath_base)
-        end
-
-        (y, X), (ytest, Xtest) = makeDatasets(datapath, target)
-
-        # compute solar azimuth and elevation
-        solar_geo = solar_azimuth_altitude.(X.utc_dt, X.ilat, X.ilon, X.altitude)
-        az_el = hcat(collect.(solar_geo)...)'
-        X.solar_az .= az_el[:, 1]
-        X.solar_el .= az_el[:, 2]
-
-        solar_geo = solar_azimuth_altitude.(Xtest.utc_dt, Xtest.ilat, Xtest.ilon, Xtest.altitude)
-        az_el = hcat(collect.(solar_geo)...)'
-        Xtest.solar_az .= az_el[:, 1]
-        Xtest.solar_el .= az_el[:, 2]
-
-        # drop off time, ilat, and ilon from X variables
-        X = X[:, Not([:ilat, :ilon, :utc_dt])]
-        Xtest = Xtest[:, Not([:ilat, :ilon, :utc_dt])]
-
-
-
-        # now we want to save the data.
-        CSV.write(joinpath(outpath_base, "X.csv"), X)
-        CSV.write(joinpath(outpath_base, "y.csv"), DataFrame(Dict(target => y)))
-
-        # CSV.write(joinpath(outpath_base, "Xval.csv"), Xval)
-        # CSV.write(joinpath(outpath_base, "yval.csv"), DataFrame(Dict(target => yval)))
-
-        CSV.write(joinpath(outpath_base, "Xtest.csv"), Xtest)
-        CSV.write(joinpath(outpath_base, "ytest.csv"), DataFrame(Dict(target => ytest)))
-
-
-    end
-end
-
[…]

### 2024-03-11 old/3__feature_exploration.jl

@@ -1,537 +1,0 @@
-using mintsML
-using MLJ
-using Plots, StatsPlots
-using DataFrames, CSV
-using ShapML
-using ProgressMeter
-using Interpolations
-using Flux, MLJFlux
-
-# using DecisionTree: impurity_importance
-
-# set the plotting theme
-add_mints_theme()
-theme(:mints)
-
-include("./config.jl")
-include("./utils.jl")
-include("./training_functions.jl")
-
-# MLJ.default_resource(CPUProcesses())
-MLJ.default_resource(CPUThreads())
-
-datapath = "/media/john/HSDATA/datasets/Full"
-outpath = "/media/john/HSDATA/analysis_full"
-
-isdir(datapath)
-isdir(outpath)
-
-RFR = @load RandomForestRegressor pkg=DecisionTree
-XGBR = @load XGBoostRegressor pkg=XGBoost
-NNR = @load NeuralNetworkRegressor pkg=MLJFlux
-Standardizer = @load Standardizer pkg=MLJModels
-
-# need to add evotree regressor here and some other models.
-
-# 1. Construct dictionary of models
-MODELS = Dict()
-
-# 2. Add Neural Network with defaults to mirror sk-learn
-#    https://scikit-learn.org/stable/modules/generated/sklearn.neural_network.MLPRegressor.html
-nnr = NNR(builder=MLJFlux.MLP(hidden=(250,100,50), σ=NNlib.relu),
-          batch_size = 200,
-          optimiser=Flux.Optimise.ADAM(0.001),
-          lambda = 0.0001,  # default regularization strength (I'm a bit confused by this as sk-learn only has alpha but that seems different here)
-          rng=42,
-          epochs=200,
-          )
-
-MODELS[:nnr] = (;
-                :longname=>"Neural Network Regressor",
-                :savename => "NeuralNetworkRegressor",
-                :mdl => Standardizer() |> nnr
-                )
-
-# 3. Add XGBoostRegressor. Defaults seem fine...
-MODELS[:xgbr] = (;
-                 :longname=>"XGBoost Regressor",
-                 :savename=>"XGBoostRegressor",
-                 :mdl => XGBR()
-                 )
-
-# 4. Add Random Forest using sk-learn defaults
-rfr = RFR(;
-          n_trees = 100,
-          max_depth = -1,
-          min_samples_split=2,
-          min_samples_leaf=1,
-          min_purity_increase=0,
-          n_subfeatures=0,
[…]

### 2024-03-11 old/4__vanilla_models_1123.jl

@@ -1,298 +1,0 @@
-using mintsML
-using MLJ
-using Plots, StatsPlots
-using DataFrames, CSV
-using ProgressMeter
-using LaTeXStrings
-
-
-using StableRNGs
-# seed rng for reproducibility
-rng = StableRNG(42)
-
-
-# set the plotting theme
-add_mints_theme()
-theme(:mints)
-
-# Plots.showtheme(:mints)
-
-
-include("./config.jl")
-include("./utils.jl")
-include("./training_functions.jl")
-
-# set default resource for parallelization
-MLJ.default_resource(CPUThreads(4))
-
-datapath = "/media/john/HSDATA/datasets/Full"
-outpath = "/media/john/HSDATA/analysis_full"
-
-isdir(datapath)
-isdir(outpath)
-
-summary_file = joinpath(outpath, "vanilla_comparison_full.csv")
-isfile(summary_file)
-
-# ignore_models = ["ConstantRegressor",
-#                  "EvoTreeGaussian",
-#                  "TheilSenRegressor",
-#                  "LinearRegressor"]
-ignore_models = []
-
-if !isfile(summary_file)
-    # we will train the vanilla version of all compatible models
-    target = :CDOM
-    target_name = String(target)
-    target_long = targetsDict[target][2]
-    units = targetsDict[target][1]
-
-
-    # load datasets
-    data_path = joinpath(datapath, target_name)
-
-    X = CSV.File(joinpath(data_path, "X.csv")) |> DataFrame
-    y = vec(Array(CSV.File(joinpath(data_path, "y.csv")) |> DataFrame))
-
-    Xtest = CSV.File(joinpath(data_path, "Xtest.csv")) |> DataFrame
-    ytest = vec(Array(CSV.File(joinpath(data_path, "ytest.csv")) |> DataFrame))
-
-    # make sure to include the orientation stuff...
-    # use only reflectances as they seem to do fine
-    others = [:altitude, :pitch, :roll, :heading, :solar_az, :solar_el]
-    refs = [Symbol("λ_$(i)") for i ∈ 1:462]
-    X̃ = X[:, vcat(refs, others)]
-    X̃test = Xtest[:, vcat(refs, others)]
-
-    filter(model) = model.is_supervised && scitype(y) <: model.target_scitype && scitype(X̃) <: model.input_scitype
-
-    mdls = models(filter)
-
[…]

### 2024-03-11 old/5a__hpo_DecisionTreeRegressor.jl

@@ -1,119 +1,0 @@
-# https://discourse.julialang.org/t/generation-of-documentation-fails-qt-qpa-xcb-could-not-connect-to-display/60988
-ENV["GKSwstype"] = "100"
-
-
-using Pkg
-Pkg.instantiate()
-
-using mintsML
-using MLJ
-using Plots, StatsPlots
-using DataFrames, CSV
-using ProgressMeter
-using StableRNGs
-using ArgParse
-
-include("./config.jl")
-include("./utils.jl")
-include("./training_functions.jl")
-
-function parse_commandline()
-    s = ArgParseSettings()
-
-    @add_arg_table! s begin
-        "--target","-T"
-            help = "Target variable for training. See targetsDict in config.jl for full list."
-            arg_type = Symbol
-            default = :CDOM
-        "--datapath", "-d"
-            help = "Path to directory with data to be used in training"
-            arg_type = String
-            default = "/media/john/HSDATA/datasets/Full"
-        "--outpath", "-o"
-            help = "Path to directory for storing output"
-            arg_type = String
-            default ="/media/john/HSDATA/analysis_full"
-    end
-
-
-    parsed_args = parse_args(ARGS, s; as_symbols=true)
-
-    @assert (parsed_args[:target] ∈ keys(targetsDict)) "Supplied target does not exist"
-
-    # make sure that the datapath and outpath exist
-    if !isdir(parsed_args[:datapath])
-        println("$(parsed_args[:datapath]) does not exist. Creating now...")
-        mkpath(parsed_args[:datapath])
-    end
-
-    if !isdir(parsed_args[:outpath])
-        println("$(parsed_args[:outpath]) does not exist. Creating now...")
-        mkpath(parsed_args[:outpath])
-    end
-
-    return parsed_args
-end
-
-
-function main(mdl)
-    # parse args making sure that supplied target does exist
-    parsed_args = parse_commandline()
-    target = parsed_args[:target]
-    datapath = parsed_args[:datapath]
-    outpath = parsed_args[:outpath]
-
-    target_name = String(target)
-    target_long = targetsDict[target][2]
-    units = targetsDict[target][1]
-
-    # now that we've verified the cl args, move on with the script
-    println("Loading packages...")
-
-    println("Setting random seed for reproducability...")
-    rng = StableRNG(42)
-
[…]

### 2024-03-11 old/5b__hpo_RandomForestRegressor.jl

@@ -1,116 +1,0 @@
-# https://discourse.julialang.org/t/generation-of-documentation-fails-qt-qpa-xcb-could-not-connect-to-display/60988
-ENV["GKSwstype"] = "100"
-
-
-using Pkg
-Pkg.instantiate()
-
-using mintsML
-using MLJ
-using Plots, StatsPlots
-using DataFrames, CSV
-using ProgressMeter
-using StableRNGs
-using ArgParse
-
-include("./config.jl")
-include("./utils.jl")
-include("./training_functions.jl")
-
-function parse_commandline()
-    s = ArgParseSettings()
-
-    @add_arg_table! s begin
-        "--target","-T"
-            help = "Target variable for training. See targetsDict in config.jl for full list."
-            arg_type = Symbol
-            default = :CDOM
-        "--datapath", "-d"
-            help = "Path to directory with data to be used in training"
-            arg_type = String
-            default = "/media/john/HSDATA/datasets/Full"
-        "--outpath", "-o"
-            help = "Path to directory for storing output"
-            arg_type = String
-            default ="/media/john/HSDATA/analysis_full"
-    end
-
-
-    parsed_args = parse_args(ARGS, s; as_symbols=true)
-
-    @assert (parsed_args[:target] ∈ keys(targetsDict)) "Supplied target does not exist"
-
-    # make sure that the datapath and outpath exist
-    if !isdir(parsed_args[:datapath])
-        println("$(parsed_args[:datapath]) does not exist. Creating now...")
-        mkpath(parsed_args[:datapath])
-    end
-
-    if !isdir(parsed_args[:outpath])
-        println("$(parsed_args[:outpath]) does not exist. Creating now...")
-        mkpath(parsed_args[:outpath])
-    end
-
-    return parsed_args
-end
-
-
-function main(mdl)
-    # parse args making sure that supplied target does exist
-    parsed_args = parse_commandline()
-    target = parsed_args[:target]
-    datapath = parsed_args[:datapath]
-    outpath = parsed_args[:outpath]
-
-    target_name = String(target)
-    target_long = targetsDict[target][2]
-    units = targetsDict[target][1]
-
-    # now that we've verified the cl args, move on with the script
-    println("Loading packages...")
-
-    println("Setting random seed for reproducability...")
-    rng = StableRNG(42)
-
[…]

### 2024-03-11 old/5c__hpo_XGBoostRegressor.jl

@@ -1,114 +1,0 @@
-# https://discourse.julialang.org/t/generation-of-documentation-fails-qt-qpa-xcb-could-not-connect-to-display/60988
-ENV["GKSwstype"] = "100"
-
-using Pkg
-Pkg.instantiate()
-
-using mintsML
-using MLJ
-using Plots, StatsPlots
-using DataFrames, CSV
-using ProgressMeter
-using StableRNGs
-using ArgParse
-
-include("./config.jl")
-include("./utils.jl")
-include("./training_functions.jl")
-
-function parse_commandline()
-    s = ArgParseSettings()
-
-    @add_arg_table! s begin
-        "--target","-T"
-            help = "Target variable for training. See targetsDict in config.jl for full list."
-            arg_type = Symbol
-            default = :CDOM
-        "--datapath", "-d"
-            help = "Path to directory with data to be used in training"
-            arg_type = String
-            default = "/media/john/HSDATA/datasets/Full"
-        "--outpath", "-o"
-            help = "Path to directory for storing output"
-            arg_type = String
-            default ="/media/john/HSDATA/analysis_full"
-    end
-
-
-    parsed_args = parse_args(ARGS, s; as_symbols=true)
-
-    @assert (parsed_args[:target] ∈ keys(targetsDict)) "Supplied target does not exist"
-
-    # make sure that the datapath and outpath exist
-    if !isdir(parsed_args[:datapath])
-        println("$(parsed_args[:datapath]) does not exist. Creating now...")
-        mkpath(parsed_args[:datapath])
-    end
-
-    if !isdir(parsed_args[:outpath])
-        println("$(parsed_args[:outpath]) does not exist. Creating now...")
-        mkpath(parsed_args[:outpath])
-    end
-
-    return parsed_args
-end
-
-
-function main(mdl)
-    # parse args making sure that supplied target does exist
-    parsed_args = parse_commandline()
-    target = parsed_args[:target]
-    datapath = parsed_args[:datapath]
-    outpath = parsed_args[:outpath]
-
-    target_name = String(target)
-    target_long = targetsDict[target][2]
-    units = targetsDict[target][1]
-
-    # now that we've verified the cl args, move on with the script
-    println("Loading packages...")
-
-    println("Setting random seed for reproducability...")
-    rng = StableRNG(42)
-
[…]

### 2024-03-11 old/5d__hpo_KNNRegressor.jl

@@ -1,117 +1,0 @@
-# https://discourse.julialang.org/t/generation-of-documentation-fails-qt-qpa-xcb-could-not-connect-to-display/60988
-ENV["GKSwstype"] = "100"
-
-
-using Pkg
-Pkg.instantiate()
-
-using mintsML
-using MLJ
-using Plots, StatsPlots
-using DataFrames, CSV
-using ProgressMeter
-using StableRNGs
-using ArgParse
-
-include("./config.jl")
-include("./utils.jl")
-include("./training_functions.jl")
-
-function parse_commandline()
-    s = ArgParseSettings()
-
-    @add_arg_table! s begin
-        "--target","-T"
-            help = "Target variable for training. See targetsDict in config.jl for full list."
-            arg_type = Symbol
-            default = :CDOM
-        "--datapath", "-d"
-            help = "Path to directory with data to be used in training"
-            arg_type = String
-            default = "/media/john/HSDATA/datasets/Full"
-        "--outpath", "-o"
-            help = "Path to directory for storing output"
-            arg_type = String
-            default ="/media/john/HSDATA/analysis_full"
-    end
-
-
-    parsed_args = parse_args(ARGS, s; as_symbols=true)
-
-    @assert (parsed_args[:target] ∈ keys(targetsDict)) "Supplied target does not exist"
-
-    # make sure that the datapath and outpath exist
-    if !isdir(parsed_args[:datapath])
-        println("$(parsed_args[:datapath]) does not exist. Creating now...")
-        mkpath(parsed_args[:datapath])
-    end
-
-    if !isdir(parsed_args[:outpath])
-        println("$(parsed_args[:outpath]) does not exist. Creating now...")
-        mkpath(parsed_args[:outpath])
-    end
-
-    return parsed_args
-end
-
-
-
-# parse args making sure that supplied target does exist
-function main(mdl)
-    parsed_args = parse_commandline()
-    target = parsed_args[:target]
-    datapath = parsed_args[:datapath]
-    outpath = parsed_args[:outpath]
-
-    target_name = String(target)
-    target_long = targetsDict[target][2]
-    units = targetsDict[target][1]
-
-    # now that we've verified the cl args, move on with the script
-    println("Loading packages...")
-
-    println("Setting random seed for reproducability...")
-    rng = StableRNG(42)
-
[…]

### 2024-03-11 old/5e__hpo_EvoTreeRegressor.jl

@@ -1,115 +1,0 @@
-# https://discourse.julialang.org/t/generation-of-documentation-fails-qt-qpa-xcb-could-not-connect-to-display/60988
-ENV["GKSwstype"] = "100"
-
-
-using Pkg
-Pkg.instantiate()
-
-using mintsML
-using MLJ
-using Plots, StatsPlots
-using DataFrames, CSV
-using ProgressMeter
-using StableRNGs
-using ArgParse
-
-include("./config.jl")
-include("./utils.jl")
-include("./training_functions.jl")
-
-function parse_commandline()
-    s = ArgParseSettings()
-
-    @add_arg_table! s begin
-        "--target","-T"
-            help = "Target variable for training. See targetsDict in config.jl for full list."
-            arg_type = Symbol
-            default = :CDOM
-        "--datapath", "-d"
-            help = "Path to directory with data to be used in training"
-            arg_type = String
-            default = "/media/john/HSDATA/datasets/Full"
-        "--outpath", "-o"
-            help = "Path to directory for storing output"
-            arg_type = String
-            default ="/media/john/HSDATA/analysis_full"
-    end
-
-
-    parsed_args = parse_args(ARGS, s; as_symbols=true)
-
-    @assert (parsed_args[:target] ∈ keys(targetsDict)) "Supplied target does not exist"
-
-    # make sure that the datapath and outpath exist
-    if !isdir(parsed_args[:datapath])
-        println("$(parsed_args[:datapath]) does not exist. Creating now...")
-        mkpath(parsed_args[:datapath])
-    end
-
-    if !isdir(parsed_args[:outpath])
-        println("$(parsed_args[:outpath]) does not exist. Creating now...")
-        mkpath(parsed_args[:outpath])
-    end
-
-    return parsed_args
-end
-
-
-function main(mdl)
-    # parse args making sure that supplied target does exist
-    parsed_args = parse_commandline()
-    target = parsed_args[:target]
-    datapath = parsed_args[:datapath]
-    outpath = parsed_args[:outpath]
-
-    target_name = String(target)
-    target_long = targetsDict[target][2]
-    units = targetsDict[target][1]
-
-    # now that we've verified the cl args, move on with the script
-    println("Loading packages...")
-
-    println("Setting random seed for reproducability...")
-    rng = StableRNG(42)
-
[…]

### 2024-03-11 old/5f__hpo_LGBMRegressor.jl

@@ -1,116 +1,0 @@
-# https://discourse.julialang.org/t/generation-of-documentation-fails-qt-qpa-xcb-could-not-connect-to-display/60988
-ENV["GKSwstype"] = "100"
-
-
-using Pkg
-Pkg.instantiate()
-
-using mintsML
-using MLJ
-using Plots, StatsPlots
-using DataFrames, CSV
-using ProgressMeter
-using StableRNGs
-using ArgParse
-
-include("./config.jl")
-include("./utils.jl")
-include("./training_functions.jl")
-
-function parse_commandline()
-    s = ArgParseSettings()
-
-    @add_arg_table! s begin
-        "--target","-T"
-            help = "Target variable for training. See targetsDict in config.jl for full list."
-            arg_type = Symbol
-            default = :CDOM
-        "--datapath", "-d"
-            help = "Path to directory with data to be used in training"
-            arg_type = String
-            default = "/media/john/HSDATA/datasets/Full"
-        "--outpath", "-o"
-            help = "Path to directory for storing output"
-            arg_type = String
-            default ="/media/john/HSDATA/analysis_full"
-    end
-
-
-    parsed_args = parse_args(ARGS, s; as_symbols=true)
-
-    @assert (parsed_args[:target] ∈ keys(targetsDict)) "Supplied target does not exist"
-
-    # make sure that the datapath and outpath exist
-    if !isdir(parsed_args[:datapath])
-        println("$(parsed_args[:datapath]) does not exist. Creating now...")
-        mkpath(parsed_args[:datapath])
-    end
-
-    if !isdir(parsed_args[:outpath])
-        println("$(parsed_args[:outpath]) does not exist. Creating now...")
-        mkpath(parsed_args[:outpath])
-    end
-
-    return parsed_args
-end
-
-
-function main(mdl)
-    # parse args making sure that supplied target does exist
-    parsed_args = parse_commandline()
-    target = parsed_args[:target]
-    datapath = parsed_args[:datapath]
-    outpath = parsed_args[:outpath]
-
-    target_name = String(target)
-    target_long = targetsDict[target][2]
-    units = targetsDict[target][1]
-
-    # now that we've verified the cl args, move on with the script
-    println("Loading packages...")
-
-    println("Setting random seed for reproducability...")
-    rng = StableRNG(42)
-
[…]

### 2024-03-11 old/6__explore_hpo_results.jl

@@ -1,126 +1,0 @@
-# we can use this file to look through the HPO results for each model
-# and generate a set of reasonable defaults to use
-
-using Pkg
-Pkg.instantiate()
-
-using mintsML
-using MLJ
-using Plots, StatsPlots
-using DataFrames, CSV
-using JSON
-
-include("./config.jl")
-include("./utils.jl")
-include("./training_functions.jl")
-
-# set up the paths
-path_to_data = "/scratch/jwaczak/data/analysis_full"
-# path_to_data = "/media/john/HSDATA/analysis_full"
-ispath(path_to_data)
-
-# # testpath = joinpath(path_to_data, "CDOM", "DecisionTreeRegressor", "hyperparameter_optimized")
-# testpath = joinpath(path_to_data, "CDOM", "KNNRegressor", "hyperparameter_optimized")
-# readdir(testpath)
-
-# testmach = joinpath(testpath, "KNNRegressor__hpo.jls")
-# isfile(testmach)
-
-# model = @load KNNRegressor pkg=NearestNeighborModels
-
-# mach = machine(testmach)
-
-
-
-
-# mdl = model()
-# ps = params(fitted_params(mach).best_model)
-# for (p, val) ∈ zip(keys(ps), ps)
-#     println(p, "\t", val)
-#     setproperty!(mdl, Symbol(p), val)
-# end
-
-
-models_to_ignore = ["MLJFlux"]
-
-summary_dict = Dict()
-for model_package ∈ keys(hpo_ranges)
-    if !(model_package ∈ models_to_ignore)
-        models = keys(hpo_ranges[model_package])
-        for model_name ∈ models
-            df = DataFrame()
-            for (target, info) ∈ targetsDict
-                try
-                    load_string = "model = @load $(model_name) pkg=$(model_package) verbosity=0 add=true"
-                    eval(Meta.parse(load_string))
-
-                    path = joinpath(path_to_data, String(target), model_name, "hyperparameter_optimized")
-                    fpath = joinpath(path, model_name*"__hpo.jls")
-
-                    mach = machine(fpath)
-                    fitted_ps = fitted_params(mach).best_model
-
-                    params_dict = Dict{Any,Any}(:target => target)
-
-                    for hp ∈ hpo_ranges[model_package][model_name]
-                        #params_dict[String(hp.hpname)] = getproperty(fitted_ps, hp.hpname)
-                        val = getproperty(fitted_ps, hp.hpname)
-                        name = hp.hpname
[…]

### 2024-03-11 old/7__superlearner.jl

@@ -1,124 +1,0 @@
-# https://discourse.julialang.org/t/generation-of-documentation-fails-qt-qpa-xcb-could-not-connect-to-display/60988
-ENV["GKSwstype"] = "100"
-
-
-using Pkg
-Pkg.instantiate()
-
-using mintsML
-using MLJ
-using Flux, MLJFlux
-using Plots, StatsPlots
-using DataFrames, CSV
-using ProgressMeter
-using StableRNGs
-using ArgParse
-
-include("./config.jl")
-include("./utils.jl")
-include("./training_functions.jl")
-
-function parse_commandline()
-    s = ArgParseSettings()
-
-    @add_arg_table! s begin
-        "--target","-T"
-            help = "Target variable for training. See targetsDict in config.jl for full list."
-            arg_type = Symbol
-            default = :CDOM
-        "--datapath", "-d"
-            help = "Path to directory with data to be used in training"
-            arg_type = String
-            default = "/media/john/HSDATA/datasets/Full"
-        "--outpath", "-o"
-            help = "Path to directory for storing output"
-            arg_type = String
-            default ="/media/john/HSDATA/analysis_full"
-    end
-
-
-    parsed_args = parse_args(ARGS, s; as_symbols=true)
-
-    @assert (parsed_args[:target] ∈ keys(targetsDict)) "Supplied target does not exist"
-
-    # make sure that the datapath and outpath exist
-    if !isdir(parsed_args[:datapath])
-        println("$(parsed_args[:datapath]) does not exist. Creating now...")
-        mkpath(parsed_args[:datapath])
-    end
-
-    if !isdir(parsed_args[:outpath])
-        println("$(parsed_args[:outpath]) does not exist. Creating now...")
-        mkpath(parsed_args[:outpath])
-    end
-
-    return parsed_args
-end
-
-
-function main()
-    # parse args making sure that supplied target does exist
-    parsed_args = parse_commandline()
-    target = parsed_args[:target]
-    datapath = parsed_args[:datapath]
-    outpath = parsed_args[:outpath]
-
-    target_name = String(target)
-    target_long = targetsDict[target][2]
-    units = targetsDict[target][1]
-
-    # now that we've verified the cl args, move on with the script
-    println("Loading packages...")
-
[…]

### 2024-03-11 old/8__evaluate_superlearners.jl

@@ -1,165 +1,0 @@
-# https://discourse.julialang.org/t/generation-of-documentation-fails-qt-qpa-xcb-could-not-connect-to-display/60988
-ENV["GKSwstype"] = "100"
-
-
-using Pkg
-Pkg.instantiate()
-
-using mintsML
-using MLJ
-using Flux, MLJFlux
-using Plots, StatsPlots
-using DataFrames, CSV
-using ProgressMeter
-using StableRNGs
-using ArgParse
-
-include("./config.jl")
-include("./utils.jl")
-include("./training_functions.jl")
-
-function parse_commandline()
-    s = ArgParseSettings()
-
-    @add_arg_table! s begin
-        "--target","-T"
-            help = "Target variable for training. See targetsDict in config.jl for full list."
-            arg_type = Symbol
-            default = :CDOM
-        "--datapath", "-d"
-            help = "Path to directory with data to be used in training"
-            arg_type = String
-            default = "/media/john/HSDATA/datasets/11-23"
-        "--outpath", "-o"
-            help = "Path to directory for storing output"
-            arg_type = String
-            default ="/media/john/HSDATA/analysis_full"
-    end
-
-
-    parsed_args = parse_args(ARGS, s; as_symbols=true)
-
-    @assert (parsed_args[:target] ∈ keys(targetsDict)) "Supplied target does not exist"
-
-    # make sure that the datapath and outpath exist
-    if !isdir(parsed_args[:datapath])
-        println("$(parsed_args[:datapath]) does not exist. Creating now...")
-        mkpath(parsed_args[:datapath])
-    end
-
-    if !isdir(parsed_args[:outpath])
-        println("$(parsed_args[:outpath]) does not exist. Creating now...")
-        mkpath(parsed_args[:outpath])
-    end
-
-    return parsed_args
-end
-
-
-function main()
-    # parse args making sure that supplied target does exist
-    parsed_args = parse_commandline()
-    target = parsed_args[:target]
-    datapath = parsed_args[:datapath]
-    outpath = parsed_args[:outpath]
-
-    date = split(datapath, "/")[end]
-
-    target_name = String(target)
-    target_long = targetsDict[target][2]
-    units = targetsDict[target][1]
-
[…]

### 2024-03-11 old/9__apply_models.jl

@@ -1,143 +1,0 @@
-# # https://discourse.julialang.org/t/generation-of-documentation-fails-qt-qpa-xcb-could-not-connect-to-display/60988
-# ENV["GKSwstype"] = "100"
-
-using Pkg
-Pkg.instantiate()
-
-using mintsML
-using MLJ
-using Flux, MLJFlux
-using Plots, StatsPlots
-using DataFrames, CSV
-using ProgressMeter
-using StableRNGs
-using ArgParse
-using Dates
-
-include("./config.jl")
-include("./utils.jl")
-include("./training_functions.jl")
-
-
-
-# now that we've verified the cl args, move on with the script
-println("Setting random seed for reproducability...")
-rng = StableRNG(42)
-
-println("Loading plotting theme...")
-add_mints_theme()
-theme(:mints)
-
-println("Setting compute resources...")
-# we should grab this from the envrionment variable for number of julia threads
-MLJ.default_resource(CPUThreads())
-
-
-# load in base models
-DTR = @load DecisionTreeRegressor pkg=DecisionTree
-RFR = @load RandomForestRegressor pkg=DecisionTree
-XGBR = @load XGBoostRegressor pkg=XGBoost
-KNNR = @load KNNRegressor pkg=NearestNeighborModels
-ETR = @load EvoTreeRegressor pkg=EvoTrees
-LGBR = @load LGBMRegressor pkg=LightGBM
-NNR = @load NeuralNetworkRegressor pkg=MLJFlux
-LR = @load LassoRegressor pkg=MLJLinearModels
-LinearR = @load LinearRegressor pkg=MLJLinearModels
-RR = @load RidgeRegressor pkg=MLJLinearModels
-
-
-
-# set up paths
-modelbasepath = "/media/john/HSDATA/analysis_full"
-basepath = "/media/john/HSDATA/processed"
-dates = ["11-23", "12-09", "12-10"]
-collections_11_23 = ["Scotty_1",
-                     "Scotty_2",
-                     "Scotty_3",
-                     "Scotty_4",
-                     "Scotty_5",
-                     ]
-collections_12_09 = ["NoDye_1",
-                     "NoDye_2",
-                     "Dye_1",
-                     "Dye_2",
-                     ]
-collections_12_10 = ["NoDye_1",
-                     "NoDye_2",
-                     "Dye_1",
-                     "Dye_2",
-                     ]
-
-
-paths_dict = Dict("11_23" => [joinpath(basepath, dates[1], c) for c ∈ collections_11_23],
[…]

### 2024-03-11 old/config.jl

@@ -1,173 +1,0 @@
-ignorecols = [:latitude,
-              :longitude,
-#              :ilat,
-#              :ilon,
-              :unix_dt,
-#              :utc_dt,
-              :category,
-              :predye_postdye,
-              :times,
-              :row_index,
-              ]
-
-targets_vars = [:Br,
-                :CDOM,
-                :CO,
-                :Ca,
-                :Chl,
-                :ChlRed,
-                :Cl,
-                :HDO,
-                :HDO_percent,
-                :NH4,
-                :NO3,
-                :Na,
-                :OB,
-                :RefFuel,
-                :SSC,
-                :Salinity3488,
-                :Salinity3490,
-                :SpCond,
-                :TDS,
-                :TRYP,
-                :Temp3488,
-                :Temp3489,
-                :Temp3490,
-                :Turb3488,
-                :Turb3489,
-                :Turb3490,
-                :bg,
-                :bgm,
-                :pH,
-                :pH_mV,
-                ]
-
-
-targetsDict = Dict(
-    :Temp3488 => ["°C", "Temperature (3488)"],
-    :pH => ["dimensionless", "pH", 0.0],
-    :SpCond => ["μS/cm", "Conductivity"],
-    :Turb3488 => ["FNU", "Turbidity (3488)"],
-    :Br => ["mg/l", "Br⁻", 0.0],
-    :Ca => ["mg/l", "Ca⁺⁺", 0.0],
-    :Cl => ["mg/l", "Cl⁻", 0.0],
-    :Na => ["mg/l", "Na⁺", 0.0],
-    :NO3 => ["mg/l-N", "NO₃⁻", 0.0],
-    :NH4 => ["mg/l-N", "NH₄⁺", 0.0],
-    :HDO => ["mg/l", "Dissolved Oxygen", 0.0],
-    :HDO_percent => ["% Sat", "Dissolved Oxygen", 0.0],
-    :pH_mV => ["mV", "pH"],
-#    :Salinity3488 => ["PSS", "Salinity (3488)"],
-#    :TDS => ["mg/l", "Total Dissolved Solids", 0.0],
-    :Temp3489 => ["°C", "Temperature (3489)"],
[…]

### 2024-03-11 old/make_slurm_scripts.jl

@@ -1,123 +1,0 @@
-include("./config.jl")
-
-targets = keys(targetsDict)
-
-
-function make_slurm_jobs(;script_to_run="5a__hpo_DecisionTreeRegressor.jl", basename="5a_hpo_", n_tasks=8, datapath="/media/john/HSDATA/datasets/Full", outpath="/media/john/HSDATA/analysis_full")
-    for target ∈ targets
-        job_name = basename*"$(target)"
-
-        file_text = """
-        #!/bin/bash
-
-        #SBATCH     --job-name=$(job_name)
-        #SBATCH     --output=$(job_name).out
-        #SBATCH     --error=$(job_name).err
-        #SBATCH     --nodes=1
-        #SBATCH     --ntasks=1
-        #SBATCH     --cpus-per-task=$(n_tasks)   # number of threads for multi-threading
-        #SBATCH     --time=2-00:00:00
-        #SBATCH     --mem=30G
-        #SBATCH     --mail-type=ALL
-        #SBATCH     --mail-user=jxw190004@utdallas.edu
-        #SBATCH     --partition=normal
-
-        julia --threads \$SLURM_CPUS_PER_TASK --project=../../ $(script_to_run) -T $(target) -d $(datapath) -o $(outpath)
-        """
-
-
-
-        open(basename*String(target)*".slurm", "w") do f
-            println(f, file_text)
-        end
-    end
-end
-
-
-# make_slurm_jobs(;
-#                 script_to_run="5a__hpo_DecisionTreeRegressor.jl",
-#                 basename="5a__hpo_",
-#                 n_tasks=4,
-# 		datapath="/scratch/jwaczak/data/datasets/Full",
-# 		outpath="/scratch/jwaczak/data/analysis_full",
-#                 )
-
-
-# make_slurm_jobs(;
-#                 script_to_run="5b__hpo_RandomForestRegressor.jl",
-#                 basename="5b_hpo_",
-#                 n_tasks=4,
-# 		            datapath="/scratch/jwaczak/data/datasets/Full",
-# 		            outpath="/scratch/jwaczak/data/analysis_full",
-#                 )
-
-
-# make_slurm_jobs(;
-#                 script_to_run="5d__hpo_KNNRegressor.jl",
-#                 basename="5d__hpo_",
-#                 n_tasks=4,
-# 		            datapath="/scratch/jwaczak/data/datasets/Full",
-# 		            outpath="/scratch/jwaczak/data/analysis_full",
-#                 )
-
-
-# make_slurm_jobs(;
[…]

### 2024-03-11 old/old/applyModels.jl

@@ -1,114 +1,0 @@
-using CSV, DataFrames
-using MLJ
-using Plots
-using HDF5
-using MLJFlux
-using Flux
-using HDF5
-using ProgressMeter
-include("mlp.jl")
-include("utils.jl")
-
-
-
-basepath = "/media/snuc/HSDATA/georectified/11/23/Scotty/"
-modelpath ="/media/snuc/HSDATA/georectified/11/23/models/"
-
-# basepath = "/media/john/HSDATA/georectified/11/23/Scotty/"
-# modelpath ="/media/john/HSDATA/georectified/11/23/models/"
-
-
-
-# Load in model ---------------------------------------------------
-
-CR = @load ConstantRegressor pkg=MLJModels
-DTR = @load DecisionTreeRegressor pkg=DecisionTree
-DCR = @load DeterministicConstantRegressor pkg=MLJModels
-ENR = @load ElasticNetRegressor pkg=MLJLinearModels
-ETG = @load EvoTreeGaussian pkg=EvoTrees
-ETR = @load EvoTreeRegressor pkg=EvoTrees
-HR = @load HuberRegressor pkg=MLJLinearModels
-KNNR = @load KNNRegressor pkg=NearestNeighborModels
-LADR = @load LADRegressor pkg=MLJLinearModels
-LGBMR = @load LGBMRegressor pkg=LightGBM
-LR = @load LassoRegressor pkg=MLJLinearModels
-LinearR = @load LinearRegressor pkg=MLJLinearModels
-NNR = @load NeuralNetworkRegressor pkg=MLJFlux
-QR = @load QuantileRegressor pkg=MLJLinearModels
-RFR = @load RandomForestRegressor pkg=DecisionTree
-RR = @load RidgeRegressor pkg=MLJLinearModels
-RobustR = @load RobustRegressor pkg=MLJLinearModels
-XGBR = @load XGBoostRegressor pkg=XGBoost
-PCA = @load PCA pkg = MultivariateStats
-
-
-
-mystack = Stack(;metalearner=LinearR(),
-                resampling=CV(),
-                cr = CR(),
-                dtr = DTR(),
-                dcr = DCR(),
-                enr = ENR(),
-                etg = ETG(),
-                etr = ETR(nrounds=100),
-                hr = HR(),
-                #knnr = KNNR(),  # too memory intensive
-                ladr = LADR(),
-                lgbmr = LGBMR(), # too slow to train
-                lr = LR(),
-                nnr = NNR(builder=MLP((100, 50, 30), relu),
[…]

### 2024-03-11 old/old/makeMaps.jl

@@ -1,75 +1,0 @@
-using CSV, DataFrames
-using Plots
-using HDF5
-using ProgressMeter
-
-
-basepath = "/media/snuc/HSDATA/georectified/11/23/Scotty"
-# basepath = "/media/john/HSDATA/georectified/11/23/Scotty"
-
-f = h5open("scotty.h5", "r")
-g = f["Satellite"]
-tile = read(g["img"])
-tile_lat = read(g["lat"])
-tile_lon = read(g["lon"])
-tile = RGB.(tile[1,:,:], tile[2,:,:], tile[3,:,:])
-close(f)
-
-
-p = plot(tile_lon,
-         tile_lat,
-         tile,
-         yflip=false,
-         xlabel="Longitude",
-         ylabel="Latitude",
-         title="CO",
-         size=(1600, 900),
-         xtickfontsize=18,
-         ytickfontsize=18,
-         xguidefontsize=20,
-         yguidefontsize=20,
-         titlefontsize=22,
-         margin=10Plots.mm
-         )
-
-
-for (root, dirs, files) ∈ walkdir(basepath)
-    for f ∈ files
-        #if occursin("1-", root) && !occursin("No", root)
-        if occursin("1-", root)
-            if occursin("df.csv", f)
-                println("Loading ", joinpath(root, f))
-                df = DataFrame(CSV.File(joinpath(root, f)))
-                println("Filter water out...")
-                try
-                    X = df[df.mNDWI .> 0.25, :]
-                    println("plotting...")
-                    plot!(p, X.ilon, X.ilat, seriestype=:scatter, zcolor = X.CO_rfr, c=:vik, clims=(25, 28), alpha=0.7, ms = 1, markerstrokewidth=0, label="" )
-                    display(p)
-                catch e
-                    println(e)
-                end
-            end
-        end
-    end
-end
-
-
-title!(p, "Crude Oil 11-23-2020 Flight 1 -- Random Forest")
-
-basepath = "/media/snuc/HSDATA/georectified/11/23"
-#basepath = "/media/john/HSDATA/georectified/11/23"
-data = DataFrame(CSV.File(joinpath(basepath, "TargetsAndFeatures.csv")))
-gdf = groupby(data, :predye_postdye)
-gdf[2].predye_postdye[1]
-data = gdf[2]
[…]

### 2024-03-11 old/old/mltrain_1123.jl

@@ -1,177 +1,0 @@
-using CSV, DataFrames
-using Plots, StatsPlots
-using Random
-using HDF5
-using MLJ
-using MLDataUtils
-using ProgressMeter
-using Statistics
-include("mlp.jl")
-include("utils.jl")
-include("config.jl")
-Random.seed!(42)
-
-
-# load in training data
-basepath = "/media/snuc/HSDATA/georectified/11/23/"
-# basepath = "/media/john/HSDATA/georectified/11/23/"
-
-ispath(basepath)
-
-# for parallelism
-MLJ.default_resource(CPUThreads())
-
-
-# load in models
-bf = 0.7
-PCA = @load PCA pkg = MultivariateStats
-
-CR = @load ConstantRegressor pkg=MLJModels
-
-DTR = @load DecisionTreeRegressor pkg=DecisionTree
-# ensemble_dtr = EnsembleModel(atom=DTR(post_prune=true, rng=42), n=100, bagging_fraction=bf)
-
-RFR = @load RandomForestRegressor pkg=DecisionTree
-
-DCR = @load DeterministicConstantRegressor pkg=MLJModels
-
-ENR = @load ElasticNetRegressor pkg=MLJLinearModels
-
-ETG = @load EvoTreeGaussian pkg=EvoTrees
-
-ETR = @load EvoTreeRegressor pkg=EvoTrees
-
-HR = @load HuberRegressor pkg=MLJLinearModels
-
-KNNR = @load KNNRegressor pkg=NearestNeighborModels
-knnr = KNNR(K=10)
-
-LADR = @load LADRegressor pkg=MLJLinearModels
-
-LGBMR = @load LGBMRegressor pkg=LightGBM
-
-LR = @load LassoRegressor pkg=MLJLinearModels
-
-LinearR = @load LinearRegressor pkg=MLJLinearModels
-
-NNR = @load NeuralNetworkRegressor pkg=MLJFlux
-# nn = NNR(builder=MLJFlux.Short(n_hidden=50, σ=relu), epochs=25)
-# ensemble_nn = EnsembleModel(atom=nn, n=20, bagging_fraction=bf)
-nnr = NNR(builder=MLP((30, 30, 30, 30, 30), relu),
-          batch_size = 32,
-          optimiser=ADAM(0.01),
-          rng=42,
-          epochs=250,
-          )
-
-
-QR = @load QuantileRegressor pkg=MLJLinearModels
-
[…]

### 2024-03-11 old/old/mltrain_1123_baggedNN.jl

@@ -1,94 +1,0 @@
-using CSV, DataFrames
-using Plots, StatsPlots
-using Random
-using HDF5
-using MLJ
-using MLDataUtils
-using MLJFlux
-using ProgressMeter
-using Statistics
-include("mlp.jl")
-include("utils.jl")
-include("config.jl")
-Random.seed!(42)
-
-
-# load in training data
-basepath = "/media/snuc/HSDATA/georectified/11/23/"
-# basepath = "/media/john/HSDATA/georectified/11/23/"
-ispath(basepath)
-
-# for parallelism
-MLJ.default_resource(CPUThreads())
-
-PCA = @load PCA pkg = MultivariateStats
-NN = @load NeuralNetworkRegressor pkg=MLJFlux
-# 1 hidden layer with 50 hidden nodes
-nn = NN(builder=MLJFlux.Short(n_hidden=100, σ=relu), epochs=25)
-
-# build a Homogenous Ensemble of short NN
-ensemble_model = EnsembleModel(atom=nn, n=20)
-
-
-pipe = @pipeline(Standardizer(),
-                 PCA(pratio= 0.9999),
-                 ensemble_model,
-                 target=Standardizer(),
-                 name="Ensemble of NN",
-                 )
-
-
-
-for (key, val) ∈ targetsDict
-    GC.gc()
-    println("Working on $(key)...")
-
-    target = key
-    targetUnits = val[1]
-    targetName = val[2]
-
-    outpath = joinpath(basepath, "models", "$(Symbol(target))")
-    if !ispath(outpath)
-        mkdir(outpath)
-    end
-    println("Outpath: ", outpath)
-
-
-    targetsandfeatures = joinpath(basepath, "TargetsAndFeatures.csv")
-
-
-    println("Grabbing training data...")
-    Xtrain, ytrain, Xtest, ytest = getTrainingData(targetsandfeatures, target, 0.85, outpath)
-
-
-    println("Fitting...")
-    mach = machine(pipe, Xtrain, ytrain) |> fit!
-
-    report(mach)
-
-
-    println("Saving model...")
-    MLJ.save(joinpath(outpath, "baggedNN_$(Symbol(target)).jlso"), mach)
-
-    println("Plotting results...")
-    p1_1, qqp = plotTrainingResults(mach,
-                                    Xtrain, Xtest,
-                                    ytrain, ytest,
-                                    "$(targetName)",
-                                    "Bag of Neural Networks")
-
-    p1_1, qqp = plotTrainingResults(mach,
[…]

### 2024-03-11 old/old/mltrain_1123_hporfr.jl

@@ -1,88 +1,0 @@
-using CSV, DataFrames
-using Plots, StatsPlots
-using Random
-using HDF5
-using MLJ
-using MLDataUtils
-using ProgressMeter
-using Statistics
-using ShapML
-include("config.jl")
-include("mlp.jl")
-include("utils.jl")
-Random.seed!(42)
-
-# for parallelism
-MLJ.default_resource(CPUThreads())
-
-
-DTR = @load DecisionTreeRegressor pkg=DecisionTree
-PCA = @load PCA pkg = MultivariateStats
-RFR = @load RandomForestRegressor pkg=DecisionTree
-
-
-
-# load in training data
-# basepath = "/media/snuc/HSDATA/georectified/11/23/"
-basepath = "/media/john/HSDATA/georectified/11/23/"
-ispath(basepath)
-
-# first let's hyperparameter optimize a single decision tree.
-targetsDict
-target = :CDOM
-targetUnits, targetName, targetMin = targetsDict[target]
-
-
-
-# collect the data
-outpath = joinpath(basepath, "models", "$(Symbol(target))")
-if !ispath(outpath)
-    mkdir(outpath)
-end
-
-targetsandfeatures = joinpath(basepath, "TargetsAndFeatures.csv")
-Xtrain, ytrain, Xtest, ytest = getTrainingData(targetsandfeatures, target, 0.85, outpath)
-
-# try training on only reflectance values
-λs = [Symbol("λ_$(i)") for i ∈ 1:462]
-λs_rad = [Symbol("λ_$(i)_rad") for i ∈ 1:462]
-Xtrain = Xtrain[!, Not(λs)]
-Xtest = Xtest[!, Not(λs)]
-
-
-rfr = RFR()
-pipe = @pipeline(#Standardizer(),
-                 #pca,
-                 rfr,
-                 target=Standardizer(),
-                 name="Tuned RFR Pipe",
-                 )
-
-r0 = range(pipe, :(random_forest_regressor.n_trees), lower=10, upper=250)
-r1 = range(pipe, :(random_forest_regressor.max_depth), lower=2, upper=100);
-r2 = range(pipe, :(random_forest_regressor.min_samples_leaf), lower=1, upper=20);
-r3 = range(pipe, :(random_forest_regressor.min_samples_split), lower=2, upper=100);
-
-
-tuned_dtr = TunedModel(model=pipe,
-                       tuning=RandomSearch(rng=42),
[…]

### 2024-03-11 old/old/mltrain_1123_rfr.jl

@@ -1,167 +1,0 @@
-using CSV, DataFrames
-using Plots, StatsPlots
-using Random
-using HDF5
-using MLJ
-using MLDataUtils
-using ProgressMeter
-using Statistics
-using ShapML
-include("config.jl")
-include("mlp.jl")
-include("utils.jl")
-Random.seed!(42)
-
-# for parallelism
-MLJ.default_resource(CPUThreads())
-
-
-# load in training data
-basepath = "/media/snuc/HSDATA/georectified/11/23/"
-# basepath = "/media/john/HSDATA/georectified/11/23/"
-ispath(basepath)
-
-
-DTR = @load DecisionTreeRegressor pkg=DecisionTree
-PCA = @load PCA pkg = MultivariateStats
-
-RFR = @load RandomForestRegressor pkg=DecisionTree
-# dtr = DTR(post_prune=true, rng=42)
-# bagOfTrees = EnsembleModel(atom=dtr, n=100,  bagging_fraction=0.7)
-
-pca = PCA(pratio= 0.999)
-
-# don't standardize inputs but do standardize outputs
-# pipe = @pipeline(#Standardizer(),
-#                  #pca,
-#                  RFR(n_trees=200, rng=42),
-#                  target=Standardizer(),
-#                  name="RFR Pipe",
-#                  )
-
-rfr = RFR()
-pipe = @pipeline(#Standardizer(),
-                 #pca,
-                 rfr,
-                 target=Standardizer(),
-                 name="Tuned RFR Pipe",
-                 )
-
-r0 = range(pipe, :(random_forest_regressor.n_trees), lower=10, upper=250)
-#r1 = range(pipe, :(random_forest_regressor.max_depth), lower=2, upper=100);
-r2 = range(pipe, :(random_forest_regressor.min_samples_leaf), lower=1, upper=20);
-r3 = range(pipe, :(random_forest_regressor.min_samples_split), lower=2, upper=100);
-
-
-tuned_rfr = TunedModel(model=pipe,
-                       tuning=RandomSearch(rng=42),
-                       resampling=CV(),
-                       # range=[r0, r1, r2, r3],
-                       range=[r0, r2, r3],
-                       n = 500,
-                       measure=rms);
-
-
-
-
-
-
-for (key, val) ∈ targetsDict
-    GC.gc()
-    println("Working on $(key)...")
-
-    target = key
-    targetUnits = val[1]
-    targetName = val[2]
-
[…]

### 2024-03-11 old/old/plotCorrMatrices.jl

@@ -1,153 +1,0 @@
-using CSV, DataFrames
-using Plots, StatsPlots
-using Statistics
-using Random
-Random.seed!(42)
-
-dataPath = "/media/john/HSDATA/georectified/11/23/TargetsAndFeatures.csv"
-outpath = "/media/john/HSDATA/georectified/11/23/figures"
-isfile(dataPath)
-ispath(outpath)
-
-df = DataFrame(CSV.File(dataPath))
-size(df)
-
-ignorecols = [:latitude,
-              :longitude,
-              :ilat,
-              :ilon,
-              :unix_dt,
-              :utc_dt,
-              :category,
-              :predye_postdye,
-              ]
-
-targets_vars = [:Br,
-                :CDOM,
-                :CO,
-                :Ca,
-                :Chl,
-                :ChlRed,
-                :Cl,
-                :HDO,
-                :HDO_percent,
-                :NH4,
-                :NO3,
-                :Na,
-                :OB,
-                :RefFuel,
-                :SSC,
-                :Salinity3488,
-                :Salinity3490,
-                :SpCond,
-                :TDS,
-                :TRYP,
-                :Temp3488,
-                :Temp3489,
-                :Temp3490,
-                :Turb3488,
-                :Turb3489,
-                :Turb3490,
-                :bg,
-                :bgm,
-                :pH,
-                :pH_mV,
-                ]
-
-
-data = DataFrames.select(df, Not(ignorecols))
-Targets = DataFrames.select(df, targets_vars)
-X = DataFrames.select(df, Not(vcat(targets_vars, ignorecols)))
-
-targets_cor = cor(Matrix(Targets))
-p1= heatmap(targets_cor,
-            cb_title = "Pearson Correlation Coefficient",
-            xticks=(1:size(Targets)[2], String.(targets_vars)),
-            yticks=(1:size(Targets)[2], String.(targets_vars)),
-            xrotation=90,
-            size=(1200,900),
-            margin=5*Plots.mm,
-            )
-title!("Correlation Matrix for Target Variables")
-
-savefig(p1, joinpath(outpath, "target_cor.png"))
-savefig(p1, joinpath(outpath, "target_cor.svg"))
-
-
-X_cor = cor(Matrix(dropmissing(X)))
-p2 = heatmap(names(X),
-             names(X),
-             X_cor,
[…]

### 2024-03-11 old/old/unsupervised.jl

@@ -1,116 +1,0 @@
-using CSV, DataFrames
-using Plots, StatsPlots
-using Random
-using HDF5
-using MLJ
-using MLDataUtils
-using ProgressMeter
-using Statistics
-include("mlp.jl")
-include("utils.jl")
-include("config.jl")
-Random.seed!(42)
-
-
-# load in training data
-# basepath = "/media/snuc/HSDATA/georectified/11/23/"
-basepath = "/media/john/HSDATA/georectified/11/23/"
-outpath = joinpath(basepath, "figures")
-ispath(outpath)
-
-ispath(basepath)
-
-# for parallelism
-MLJ.default_resource(CPUThreads())
-
-
-
-df = DataFrame(CSV.File(joinpath(basepath, "TargetsAndFeatures.csv")))
-ignorecols = [:latitude,
-              :longitude,
-              :ilat,
-              :ilon,
-              :unix_dt,
-              :utc_dt,
-              :category,
-              :predye_postdye,
-              :roll,
-              :pitch,
-              :heading
-              ]
-
-targets_vars = [:Br,
-                :CDOM,
-                :CO,
-                :Ca,
-                :Chl,
-                :ChlRed,
-                :Cl,
-                :HDO,
-                :HDO_percent,
-                :NH4,
-                :NO3,
-                :Na,
-                :OB,
-                :RefFuel,
-                :SSC,
-                :Salinity3488,
-                :Salinity3490,
-                :SpCond,
-                :TDS,
-                :TRYP,
-                :Temp3488,
-                :Temp3489,
-                :Temp3490,
-                :Turb3488,
-                :Turb3489,
-                :Turb3490,
-                :bg,
-                :bgm,
-                :pH,
-                :pH_mV,
-                ]
-
-
-dropmissing!(df)
-Targets = DataFrames.select(df, targets_vars)
-X = DataFrames.select(df, Not(vcat(targets_vars, ignorecols)))
-Xfinal = X[!, Not([:MSR_705, :rad_MSR_705])]
-
-
-KMEANS = @load KMeans pkg=Clustering
-k = 10
-km = KMEANS(k=k)
-mach = machine(km, Xfinal) |> fit!
-
-y = MLJ.predict(mach, Xfinal)
-#yfinal = convert.(Float64, y)
[…]

### 2024-03-11 old/old/utils.jl

@@ -1,358 +1,0 @@
-using HDF5
-using Plots
-using ProgressMeter
-include("config.jl")
-
-
-default(titlefontsize=20, guidefontsize=16, legendfontsize=16, tickfontsize=16, linewidth=3, margin=3Plots.mm, size=(1200,800))
-
-"""
-Generate a plot of Scotty's Ranch from the saved HDF5 file and return the resulting plot object.
-"""
-function Scotty(pathToScotty::String)
-    f = h5open(pathToScotty, "r")
-    g = f["Satellite"]
-    tile = read(g["img"])
-    tile_lat = read(g["lat"])
-    tile_lon = read(g["lon"])
-    tile = RGB.(tile[1,:,:], tile[2,:,:], tile[3,:,:])
-    close(f)
-
-    p = plot(tile_lon,
-             tile_lat,
-             tile,
-             yflip=false,
-             xlabel="Longitude",
-             ylabel="Latitude",
-#             size=(1600, 900),
-#             xtickfontsize=18,
-#             ytickfontsize=18,
-#             xguidefontsize=20,
-#             yguidefontsize=20,
-#             titlefontsize=22,
-             margin=10Plots.mm
-             )
-
-    return p
-end
-
-
-
-"""
-Generate a plot of Scotty's Ranch from the saved HDF5 file and return the resulting plot object.
-"""
-function OakPoint(pathToOakpoint::String)
-    f = h5open(pathToOakpoint, "r")
-    g = f["Satellite"]
-    tile = read(g["img"])
-    tile_lat = read(g["lat"])
-    tile_lon = read(g["lon"])
-    tile = RGB.(tile[1,:,:], tile[2,:,:], tile[3,:,:])
-    close(f)
-
-    p = plot(tile_lon,
-             tile_lat,
-             tile,
-             yflip=false,
-             xlabel="Longitude",
-             ylabel="Latitude",
-             #             size=(1600, 900),
-             #             xtickfontsize=18,
-             #             ytickfontsize=18,
-             #             xguidefontsize=20,
-             #             yguidefontsize=20,
-             #             titlefontsize=22,
-             margin=10Plots.mm
-             )
-
-    return p
-end
-
-
-
-
-
-
-
-"""
-Compute the r² value between two vectors.
-"""
-function r²(y_pred, y_true)
-    ȳ = mean(y_true)
[…]

### 2024-03-11 old/submit-all.sh

@@ -1,6 +1,0 @@
-#!/bin/bash
-
-for script in $(ls *.slurm)
-do
-	sbatch $script
-done

### 2024-03-11 old/training_functions.jl

@@ -1,562 +1,0 @@
-using StableRNGs
-using JSON
-
-# seed rng for reproducibility
-rng = StableRNG(42)
-
-
-
-function train_basic(y, X̃,
-                     ytest, X̃test,
-                     longname, savename, mdl,
-                     target_name, units, target_long,
-                     outpath;
-                     suffix="",
-                     predict_function = MLJ.predict,
-                      )
-
-    #######################################################################################
-    #                        0. Set up outgoing paths                                     #
-    #######################################################################################
-    outpathtarget = joinpath(outpath, target_name)
-    outpathmodel = joinpath(outpathtarget, savename)
-    outpathdefault = joinpath(outpathmodel, "default")
-    outpath_featuresreduced = joinpath(outpathmodel, "important_only")
-#    outpath_hpo = joinpath(outpathmodel, "hyperparameter_optimized")
-
-    path_to_use = outpathdefault
-
-    for path ∈ [outpathtarget, outpathmodel, outpathdefault, outpath_featuresreduced] # , outpath_hpo]
-        if !isdir(path)
-            mkpath(path) end
-    end
-
-    scitype(y) <: target_scitype(mdl)
-    scitype(X̃) <: input_scitype(mdl)
-
-    #######################################################################################
-    #   1. Train model
-    #######################################################################################
-    try
-        mdl.rng = rng
-    catch
-        println("\t$(longname) does not have parameter :rng")
-    end
-
-    mach = machine(mdl, X̃, y)
-    fit!(mach)
-
-
-    ŷ = predict_function(mach, X̃)  # generate predictions on training set
-    ŷtest = predict_function(mach, X̃test)  # generate predictions on testing set
-
-
-    p1 = scatterresult(y, ŷ,
-                      ytest, ŷtest;
-                      xlabel="True $(target_long) [$(units)]",
-                      ylabel="Predicted $(target_long) [$(units)]",
-                      plot_title="Fit for $(longname)",)
-
-    savefig(p1, joinpath(path_to_use, "scatterplt__$(suffix).png"))
-    savefig(p1, joinpath(path_to_use, "scatterplt__$(suffix).svg"))
-    savefig(p1, joinpath(path_to_use, "scatterplt__$(suffix).pdf"))
-
-    p2 = quantilequantile(y, ŷ,
-                          ytest, ŷtest;
-                          xlabel="True $(target_long) [$(units)]",
-                          ylabel="Predicted $(target_long) [$(units)]",
-                          title="Fit for $(longname)",)
-
[…]

### 2024-03-11 old/utils.jl

@@ -1,96 +1,0 @@
-using SolarGeometry
-
-"""
-    makeDatasets(datapath::String, target::Symbol)
-
-Given a path to the TargetsAndFeatures.csv and a desired target variable. Return dataframes with a stratified split with percentage `p` as the training set.
-"""
-function makeDatasets(datapath::String, target::Symbol) #, p::Float64)
-    # load data
-    df = CSV.File(joinpath(datapath, "TargetsAndFeatures.csv")) |> DataFrame
-    # get rid of any missing
-    dropmissing!(df)
-
-    # group by predye_postdye and only train on pre-dye
-    gdf = groupby(df, :predye_postdye)
-    data = gdf[(predye_postdye="Pre-Dye",)]
-
-
-    refs = [Symbol("λ_$(i)") for i ∈ 1:462]  # ignore reflectance values since they haven't been helpful
-    # ignored_for_input = [refs..., targets_vars..., ignorecols..., :MSR_705, :rad_MSR_705]
-    ignored_for_input = [targets_vars..., ignorecols..., :MSR_705, :rad_MSR_705]
-
-    # split into dev set and holdout
-    df, df_test = partition(data,
-                            .85;
-#                            stratify = data[!,target], # make sure we maintain target distribution
-                            rng=42  # set the seed for reproducability
-                            )
-
-    # now we further split into targets and features
-    y, X = unpack(df, ==(target), col -> !(col ∈ ignored_for_input))
-#    yval, Xval= unpack(df_val, ==(target), col -> !(col ∈ ignored_for_input))
-    ytest, Xtest = unpack(df_test, ==(target), col -> !(col ∈ ignored_for_input))
-
-    # if there's a third column in the targetsDict, set everything below it to 0.0, i.e. the threshold
-    if length(targetsDict[target]) == 3
-        ymin = targetsDict[target][3]
-        y[y .< ymin] .= 0.0
-        ytest[ytest .< ymin] .= 0.0
-    end
-
-    return (y, X), (ytest, Xtest) #(yval, Xval), (ytest, Xtest)
-end
-
-
-
-
-
-
-
-
-function makeFullDatasets(datapaths::Array{String}, target::Symbol) #, p::Float64)
-    dfs = []
-    for datapath ∈ datapaths
-        # load data
-        df = CSV.File(joinpath(datapath, "TargetsAndFeatures.csv")) |> DataFrame
-        # get rid of any missing
-        dropmissing!(df)
-
[…]

### 2024-03-11 paper/remotesensing-2870812-english.tex
switching png for pdf

@@
 \vspace{-0.15in}
-\includegraphics[width=0.9\columnwidth]{figures/results/fits/physical-fitres.png}
+\includegraphics[width=0.9\columnwidth]{figures/results/fits/physical-fitres.pdf}
 \vspace{-0.1in}
@@
 \vspace{-0.15in}
-\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/fits/ions-fitres.png}
+\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/fits/ions-fitres.pdf}
 \vspace{-0.1in}
@@
 \vspace{-0.15in}
-\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/fits/biochemical-fitres.png}
+\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/fits/biochemical-fitres.pdf}
 \vspace{-0.1in}
@@
 \vspace{-0.21in}
-\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/fits/chemical-fitres.png}
+\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/fits/chemical-fitres.pdf}
 \vspace{-0.11in}
